### 2020-04-28 doc/FAS-GLoBES.tex
docs upload

\documentclass[a4paper,11pt]{article}
\pdfoutput=1 % if your are submitting a pdflatex (i.e. if you have
             % images in pdf, png or jpg format)

\usepackage{jheppub} % for details on the use of the package, please
                     % see the JHEP-author-manual

\usepackage[T1]{fontenc} % if needed
\usepackage{amsmath}
\usepackage{leftidx}
\usepackage{multirow}
\title{\boldmath  Flavour Symmetry Embedded - GLoBES}

% more complex case: 4 authors, 3 institutions, 2 footnotes
\author[a]{Jian Tang,}
\author[a]{Tse-Chun Wang}

% The "\note" macro will give a warning: "Ignoring empty anchor..."
% you can safely ignore it.

\affiliation[a]{School of Physics, Sun Yat-Sen University, Guangzhou 510275, China}
%\affiliation[c]{A School for Advanced Studies,\\some-location, Country}

% e-mail addresses: one for each author, in the same order as the authors
\emailAdd{tangjian5@mail.sysu.edu.cn}
\emailAdd{wangzejun@mail.sysu.edu.cn}

\abstract{Abstract...}

\begin{document} 
\maketitle
\flushbottom

\section{Introduction}\label{sec:intro}
{\color{red}intro flavour symmetry, and summarise some phenon works}

The discovery of neutrino oscillations points out the fact that neutrinos have mass, and provides evidence beyond the Standard Model (BSM). This phenomenon is successfully described by a theoretical framework with the help of three neutrino mixing angles ($\theta_{12}$, $\theta_{13}$, $\theta_{23}$), two mass-square splittings ($\Delta m_{21}^2$, $\Delta m_{31}^2$), and one Dirac CP phase ($\delta$) \cite{Pontecorvo:1967fh,Maki:1962mu,Pontecorvo:1957qd,Esteban:2018azc}. Thanks to the great efforts in the past two decades, we almost have a complete understanding of such a neutrino oscillation framework. More data in the neutrino oscillation experiments is needed to determine the sign of $\Delta m_{31}^2$, to measure the value of $\sin\theta_{23}$, to discover the potential CP violation in the leptonic sector and even to constrain the size of $\delta$ \cite{Esteban:2018azc}. For these purposes, the on-going long baseline experiments (LBLs), such as the NuMI Off-axis $\nu_e$ Appearance experiment (NO$\nu$A)~\cite{Ayres:2007tu} and the Tokai-to-Kamioka experiment (T2K)~\cite{Abe:2011ks}, can answer these questions with the statistical significance $\gtrsim 3\sigma$ in most of the parameter space. Based on the analysis with their data, the normal mass ordering ($\Delta m_{31}^2>0$), the higher $\theta_{23}$ octant ($\theta_{23}>45^\circ$), and $\delta\sim270^\circ$ are preferred so far~\cite{Esteban:2018azc}. The future LBLs, Deep Underground Neutrino Experiment (DUNE)~\cite{Acciarri:2015uup}, Tokai to Hyper-Kamiokande (T2HK)~\cite{Abe:2014oxa}, and the medium baseline reactor experiment, the Jiangmen Underground Neutrino Observatory (JUNO)~\cite{Djurcic:2015vqa,An:2015jdp} will further complete our knowledge of neutrino oscillations.

Flavour symmetry models are used to explain the origin of the neutrino mixing, and to predict the value of oscillation parameters (some of useful review articles are~\cite{Altarelli:2010gt,Ishimori:2010au,King:2013eh,King:2014nza,King:2015aea,King:2015ata,King:2017guk}). These models are motivated by some interesting features, \textit{such as} $\theta_{12}\sim 33^\circ$, and $\theta_{23}\sim 45^\circ$. Before the discovery of non-zero $\theta_{13}$ measurement by Daya Bay experiment~\cite{An:2013zwz}, the `tri-bi-maximal' neutrino mixing (TBM) ansatz, which was proposed in 2002 by Horrison, Perkins, and Scott~\cite{Harrison:2002er}, fitted with the experimental data in a good agreement:
\begin{equation*}
U_{\text{TBM}}=\left(
\begin{array}{ccc}
2/\sqrt{6} & 1/\sqrt{3} & 0\\
-1/\sqrt{6} & 1/\sqrt{3} & 1/\sqrt{2}\\
1/\sqrt{6}  & -1/\sqrt{3} & 1/\sqrt{2}
\end{array}\right).
\end{equation*} 
With the fact that $\theta_{13}\approx 8^\circ$, several ways to obtain such non-zero value of $\theta_{13}$ are proposed. One of popular proposals is to correct the tri-bi-maximal neutrino mixing such that 
\begin{equation*}
\sin\theta_{12}=(1+s)/\sqrt{3},~\sin\theta_{13}=r/\sqrt{2},~\text{and}~\sin\theta_{23}=(1+a)/\sqrt{2}.
\end{equation*}
Th neutrino mixing ansatz can be realised by high-energy symmetries $G_f$.
The symmetry of discrete groups $G_f$, preserved at the high energy but slightly broken at the lower energy, predicts the neutrino mixing, mass-square splittings, and the CP violation phase (Dirac and Majorana phases), with reduced degrees of freedom. 
The symmetries need to be broken at the low energy. Otherwise, the flavour of leptons cannot be distinguished. There are several approaches for the symmetry breaking, including the direct, indirect, and semi approaches. Direct approach preserves the residual symmetries of $G_f$ in the charged-lepton or neutrino sector. On the other hand, there is no residual symmetry preserved in neither charged-lepton nor neutrino sector in the indirect approach. In the semi approach, the charged-lepton and neutrino sectors preserve different residual symmetries, respectively. This symmetry is broken by extending the Higgs sector or introducing the flavons.
%As a result, these models do not only simplify the theoretical framework for neutrino oscillations, but also provide a theoretical reason for this phenomenon. Many of these models can well describe the current neutrino-oscillation data. 
%
To achieve the $\delta$ prediction, many models are based on a discrete family symmetry $G_f$ together with a non-commuting CP symmetry $H_\mathrm{CP}$. Broken in different approaches, the symmetry $G_f\otimes H_\mathrm{CP}$ can predict different patterns for the neutrino mixing. For example, in the semi-direct approach, $S_4$ is preserved in the leading order, and leads the bimaximal (MB) or tri-bimaximal (TB) neutrino mixing, while the higher order terms bring the correction to the neutrino mixing.

Currently, some works discuss on how the future experiments can be used for testing these flavour symmetry models in the phenomenological point of view, \textit{e.g.}~\cite{Ballett:2016yod,Chatterjee:2017xkb,Ding:2019zhn,Tang:2019edw}. A large number of these works are based on the \texttt{c}-library -- \textbf{G}eneral \textbf{Lo}ng \textbf{B}aseline \textbf{E}xperiment \textbf{S}imulator (\textbf{GLoBES}) \cite{Huber:2004ka,Huber:2007ji}, which is a convenient simulation tool to simulate neutrino oscillation experiments via the Abstract Experiment Definition Language (AEDL). Some AEDL files for experiments are also available on \textbf{GLoBES} website. In addition, the working group of DUNE experiment also releases their AEDL files~\cite{Alion:2016uaj}.  \textbf{GLoBES} can be taken as one of popular and useful tools in the community of neutrino oscillation physics. However, it has not yet to be extended for the purpose of analysing flavour symmetry models.

In this work, we will present our simulation tool \textbf{F}l\textbf{a}vour \textbf{S}ymmetry \textbf{E}mbedded - \textbf{GLoBES} (\textbf{FaSE-GloBES}) that is a simulation code based on GLoBES library and specific for studying the flavour symmetry.

%One of the most predictive flavour-symmetry models is the littlest seesaw model (LSS), which includes two massive right-handed neutrinos: one corresponds to the atmospheric-mass term, while the other is included for the solar-mass term~\cite{King:2013iva,King:2015dvf,King:2016yvg}.  The littlest seesaw model in the tri-direct approach (TDLS) has been proposed and succeeds in describing the current global-fit results~\cite{Ding:2018fyz,Ding:2018tuj}. The tri-direct approach is that after the breaking of the family symmetry $G_f\otimes H_\mathrm{CP}$, three residual symmetries are preserved in different sectors: one in the charged-lepton sector, two in the sectors of right-handed neutrinos for atmospheric and solar mass terms, respectively. In this model, four parameters $x$, $\eta$, $r$, $m_a$ are used to describe neutrino oscillations. This model has been studied with simulated data at NO$\nu$A, T2K, DUNE, T2HK and JUNO~\cite{Ding:2019zhn}. In this work, we study how the next-generation neutrino project using muon-decay beams such as MOMENT can further extend our knowledge on the TDLS model. We have two reasons to motivate this study. Firstly, TDLS describes the current data successfully and tends to be a nice way to offer neutrino mass terms from theoretical point of view. Secondly, it must be straightforward to test the underlying model predictions and compare the performance of MOMENT to the other experiments, \textit{such as} NO$\nu$A, T2K, DUNE, and T2HK.

\section{Overview FASE-GloBES}

\begin{figure}[!h]%
\centering
\includegraphics[width=5in]{Figs/FASE-chart-1_v1.pdf}
\caption{A scheme to correlate the model parameters with standard neutrino oscillation parameters. The error propagation is implemented in the simulation code up to the spectra analysis.}%
\label{fig:FASE}
\end{figure}

The FASE-GLoBES is based on GLoBES as shown in Fig.~\ref{fig:FASE}, in which three parts are shown: 1. \textbf{the parameter translation} (the blue box), 2. \textbf{giving oscillation-parameter values} (the green box), and 3. \textbf{the $\chi^2$-value calculation} (the orange box). 
The idea behind this flow chart Fig.~\ref{fig:FASE} is that given a set of value for model parameter, the corresponding values for oscillation parameters are obtained by a translation, which is assigned by the user in \textbf{model-input\_diag.c} or \textbf{model-input.c}. And then, through \textbf{FASE\_GLoBES.c}, these oscillation-parameter values are passed in to \textbf{GLoBES} library to simulate the event spectrum for evaluating the $\chi^2$ value. Using prior needs

In the following, we give more details about using FASE-GLoBES. In Sec.~\ref{sec:download}, we will give the instruction to download and install GLoBES and FASE-GLoBES. Then, in Sec.~\ref{sec:compile}, we will introduce how to compile and run the code. More complicated is setting the model, and the way to do this will be described in Sec.~\ref{sec:model_set}. Finally, we will discuss how to set up the prior in Sec.~\ref{sec:prior}.

\subsection{Download and Installation}\label{sec:download}
\textbf{download and install GLoBES and FASE-GLoBES}\\
{\color{red}[will fill in after the code ready on Github]}

\subsection{Compile and Run}\label{sec:compile}
{\color{red}[will fill in after the code ready on Github]}

To initial \textbf{FASE-GLoBES}, we need to include the following code\\
\texttt{    MODEL\_init($N_{para}$); }\\
where $N_{para}$ is the number of model parameters.

\subsection{Model setting}\label{sec:model_set}

FASE includes three \texttt{c++} files: \textbf{model-input\_diag.c}, \textbf{model-input.c}, and \textbf{FASE\_GLoBES.c}. As shown in the previous paragraph, these files are for different service. In \textbf{model-input\_diag.c} and \textbf{model-input.c}, the user can assign the relation between the oscillation and model parameter sets. The difference between these two code is that in \textbf{model-input.c}, the user give the relation between these two parameter sets directly (\textit{e.g.}~Table~\ref{tab:TD_parameters} for tri-direct littlest seesaw), while in \textbf{model-input.c}, the mass matrix (\textit{e.g.}~Eq.~\ref{eq:mnu} for tir-direct littlest seesaw), which is provided by the user, can be diagonalised to obtain the corresponding oscillation-parameter values.

We now take the littlest seesaw model in the tri-direct approach as an example. In this model, the atmospheric and solar flavon vacuum alignments are $\langle\phi_{\text{atm}}\rangle\propto\left(1, \omega^2, \omega\right)^T$ and $\langle\phi_{\text{sol}}\rangle\propto\left(1, x, x\right)^T$,
where  stands for a cube root of unity and the parameter $x$ is real because of the imposed CP symmetry. Under this model, the light left-handed Majorana neutrino mass matrix is given by
\begin{equation}
\label{eq:mnu}  m_{\nu}=m_{a}\begin{pmatrix}
 1 &~ \omega  &~ \omega ^2 \\
 \omega  &~ \omega ^2 &~ 1 \\
 \omega ^2 &~ 1 &~ \omega  \\
\end{pmatrix}+e^{i\eta}m_{s}
\begin{pmatrix}
 1 &~  x &~  x \\
 x &~ x^2 &~ x^2 \\
 x &~ x^2 &~ x^2 \\
\end{pmatrix}\,,
\end{equation}
where $x$, $\eta$, $m_a$, and the ratio $r\equiv m_s/m_a$ are four parameters and will be constrained by experimental data. We note that from Eq.~(\ref{eq:mnu}), $m_1=0$ and the normal mass ordering are imposed, and will need to be imposed in \textbf{FASE-GLoBES}. We will introduce the way to do it in Sec.~\ref{sec:prior}.

\begin{table}[h!]
\caption{\label{tab:TD_parameters}A summary of the relation between oscillation parameters and TDLS model parameters~\cite{Ding:2018fyz}. Two requirements are imposed by TDLS: the smallest mass state $m_1=0$ and the normal mass ordering. The sign of $\sin\delta$ depends on the sign of $x\cos\psi$: ``$+$'' (``$-$'') is for $x\cos\psi>0$ ($<0$).}
\begin{tabular}{l|l}
\hline\hline
model parameters                                 & $x$, $\eta$, $r$, $m_a$                                                                                                                                                                         \\\hline
\multirow{6}{*}{combinations of model parameters} & $y=\frac{5x^2+2x+2}{2\left(x^2+x+1\right)}(m_{a}+e^{i \eta } m_{s})$,                                                                                                                            \\
                                                 & $z=-\frac{\sqrt{5x^2+2x+2}}{2\left(x^2+x+1\right)}\left[ (x+2)m_{a}-x(2x+1)e^{i \eta }m_{s}\right]$,                                                                                             \\
                                                 & $w=\frac{1}{2(x^2+x+1)}\left[(x+2)^2m_{a}+x^2\left(2x+1\right)^2e^{i \eta } m_{s}\right]$,                                                                                                       \\
                                                 & $\sin\psi=\frac{\Im\left(y^{*}z+wz^{*}\right)}{|y^{*}z+wz^{*}|},\quad \cos\psi=\frac{\Re\left(y^{*}z+wz^{*}\right)}{|y^{*}z+wz^{*}|}$.                                                           \\
                                                 & \begin{tabular}[c]{@{}l@{}}$\sin2\theta=\frac{2|y^{*}z+wz^{*}|} {\sqrt{(|w|^2-|y|^2)^2+4|y^{*}z+wz^{*}|^2}},$\end{tabular}                                                                     \\
                                                 & $\cos2\theta=\frac{|w|^2-|y|^2}{\sqrt{(|w|^2-|y|^2)^2+4|y^{*}z+wz^{*}|^2}}$.                                                                                                                     \\\hline
\multirow{7}{*}{oscillation parameters}          & $\Delta m_{21}^2=m^2_2=\frac{1}{2}\left[\left|y\right|^2+\left|w\right|^2+2\left|z\right|^2-\frac{\left|w\right|^2-\left|y\right|^2}{\cos\theta}\right]$,                                        \\
                                                 & $\Delta m_{31}^2=m^2_3=\frac{1}{2}\left[\left|y\right|^2+\left|w\right|^2+2\left|z\right|^2+\frac{\left|w\right|^2-\left|y\right|^2}{\cos\theta}\right]$,                                        \\
                                                 & $\sin^2\theta_{12}=1-\frac{3x^2 }{3x^2+2\left(x^2+x+1\right) \cos^2\theta }$,                                                                                                                  \\
                                                                                                  & $\sin^2\theta_{13}=\frac{2\left(x^2+x+1\right)\sin^2\theta}{5x^2+2x+2}$,                                                                                                                       \\
                                                 & $\sin^2\theta_{23}=\frac{1}{2}+\frac{x\sqrt{3\left(5x^2+2x+2\right)}\sin2\theta\sin\psi }{2\left[3x^2+2\left(x^2+x+1\right) \cos^ 2 \theta\right]}$,                                          \\
                                                 & $\cos\delta=\frac{ \cot 2 \theta_{23} \left[3x^2-\left(4x^2+ x+1\right)\cos^2\theta_{13}\right]}{\sqrt{3} \left|x\right| \sin \theta_{13} \sqrt{\left(5x^2+2x+2\right)\cos^2\theta_{13}-3x^2}}$, \\
                                                 & $\sin\delta= \pm\csc 2 \theta_{23} \sqrt{1+\frac{\left(x^2+x+1\right)^2 \cot ^2\theta_{13} \cos ^22 \theta_{23}}{3x^2 \left[3x^2 \tan ^2\theta_{13}-2 \left(x^2+x+1\right)\right]}}$.   \\\hline \hline       
\end{tabular}
\end{table}

For different methods to include the model, we use different \texttt{c++} file. Adopting the mass matrix Eq.~\ref{eq:mnu}, we assign this model in \textbf{model-input\_diag.c}. In function \texttt{MtoS}, we give
the mass matrix Eq.~\ref{eq:mnu} in the $3\times3$ complex matrix \texttt{Mass\_Matrix[]}.\vspace{0.5cm}

\texttt{int MtoS(double OSC\_PARAMS[6],~double M\_para[])}\\
\texttt{\{}
\\        
   \texttt{double x=M\_para[0];}\\
    \texttt{double eta=M\_para[1];}\\
    \texttt{double r=M\_para[2];}\\
    \texttt{double ma=M\_para[3];}\\
    \texttt{double ms=ma*r;}\\

    \texttt{double complex Mass\_Matrix[] = \{ma+ms*(cos(eta) + I*sin(eta)), ma*(cos(6.6666e-1*M\_PI) + I*sin(6.6666e-1*M\_PI))+x*ms*(cos(eta) + I*sin(eta)), ma*(cos(6.6666e-1*M\_PI) + I*sin(6.6666e-1*M\_PI))*(cos(6.6666e-1*M\_PI) + I*sin(6.6666e-1*M\_PI))+x*ms*(cos(eta) + I*sin(eta)), ma*(cos(6.6666e-1*M\_PI) + I*sin(6.6666e-1*M\_PI))+x*ms*(cos(eta) + I*sin(eta)), ma*(cos(6.6666e-1*M\_PI) + I*sin(6.6666e-1*M\_PI))*(cos(6.6666e-1*M\_PI) + I*sin(6.6666e-1*M\_PI))+x*x*ms*(cos(eta) + I*sin(eta)), ma+x*x*ms*(cos(eta) + I*sin(eta)), ma*(cos(6.6666e-1*M\_PI) + I*sin(6.6666e-1*M\_PI))*(cos(6.6666e-1*M\_PI) + I*sin(6.6666e-1*M\_PI))+x*ms*(cos(eta) + I*sin(eta)), ma+x*x*ms*(cos(eta) + I*sin(eta)), ma*(cos(6.6666e-1*M\_PI) + I*sin(6.6666e-1*M\_PI))+x*x*ms*(cos(eta) + I*sin(eta))\};}\\

    \texttt{STAN\_OSC(Mass\_Matrix,OSC\_PARAMS);}\\

    \texttt{return 0;}\\
\texttt{\} }

Passing the complex matrix \texttt{Mass\_Matrix[]} into the function \texttt{STAN\_OSC}, we will get the corresponding oscillation parameters in an array \texttt{OSC\_PARAMS}, components of which are the value for $\theta_{12}$, $\theta_{13}$, $\theta_{23}$, $\delta$, $\Delta m_{21}^2$, and $\Delta m_{31}^2$. The expression of \texttt{Mass\_Matrix[]} is given by the user. For the first four components, values are given in the unit of \textbf{rad}, while the other two are in eV$^2$.

We can also assign the relation between oscillation and model parameters Table~\ref{tab:TD_parameters} in \textbf{model-input.c}. The relations are given in \texttt{MtoS} as well.\vspace{0.5cm}

\texttt{double MtoS(double osc\_para[6], double M\_para[])}\\
\texttt{\{}\\
    \texttt{/*example: tri-direct*/}\\
\\    
    \texttt{double x\_in   = M\_para[0];}\\
    \texttt{double eta\_in = M\_para[1];}\\
    \texttt{double r\_in   = M\_para[2];}\\
    \texttt{double ma\_in  = M\_para[3];}\\
\\  
    \texttt{osc\_para[0]=TDth12(x\_in,eta\_in,r\_in, ma\_in);}\\
    \texttt{osc\_para[1]=TDth13(x\_in,eta\_in,r\_in, ma\_in);}\\
    \texttt{osc\_para[2]=TDth23(x\_in,eta\_in,r\_in, ma\_in);}\\
    \texttt{osc\_para[3]=TDdCP(x\_in,eta\_in,r\_in, ma\_in);}\\
    \texttt{osc\_para[4]=TDdm21(x\_in,eta\_in,r\_in, ma\_in);}\\
    \texttt{osc\_para[5]=TDdm31(x\_in,eta\_in,r\_in, ma\_in);}\\
\\    
    \texttt{return 0;}\\
\texttt{\}}\\

The functions \texttt{TDth12}, \texttt{TDth13}, \texttt{TDth23}, \texttt{TDdCP}, \texttt{TDdm21}, and \texttt{TDdm31} are included for obtaining the value of $\theta_{12}$, $\theta_{13}$, $\theta_{23}$, $\delta$, $\Delta m_{21}^2$, and $\Delta m_{31}^2$ according to Table~\ref{tab:TD_parameters}, respectively.

\subsection{Prior setting}\label{sec:prior}
The \texttt{c++} file \textbf{FASE\_GLoBES.c} then will call these oscillation-parameter values and pass these to simulate the event spectrum. The $\chi^2$ value from priors is also given in \textbf{FASE\_GLoBES.c}. And these functions are given by the user.

\subsection{Summary of API}

\section{Examples}
\subsection{Constraint of model parameters}
%\subsection{Projection on the PMNS parameters}
\begin{figure}[!h]%
\centering
\includegraphics[width=2in]{figs/x.pdf}
\includegraphics[width=2in]{figs/eta.pdf}\\
\includegraphics[width=2in]{figs/r.pdf}
\includegraphics[width=2in]{figs/ma.pdf}
\caption{The $\Delta\chi^2$ value against each model parameters for MOMENT. True values for the model parameters are used $(x,~\eta,~r,~M_a)=(-3.65,~1.13\pi,~0.511,~3.71~\text{meV})$. The range shown here is according to the $3\sigma$ uncertainty with NuFit4.0 results:  $-5.475<x<-3.37$ (red band),~$0.455<\eta/\pi<1.545$ (dark grey band), ~$0.204<r<0.606$ (blue band),~$3.343<m_a/\text{meV}<4.597$ (yellow band).}%
\label{fig:model_1D}
\end{figure}

\begin{figure}[!h]
 \flushleft
\hspace{15mm}\includegraphics[width=0.32\textwidth]{figs/x_eta.pdf}$~~~~~~$\\
\hspace{15mm} \includegraphics[width=0.32\textwidth]{figs/x_r.pdf}\hspace{-11mm}
 \includegraphics[width=0.32\textwidth]{figs/eta_r.pdf}$~~~~~~$\\
\hspace{15mm} \includegraphics[width=0.32\textwidth]{figs/x_ma.pdf}\hspace{-11mm}
 \includegraphics[width=0.32\textwidth]{figs/eta_ma.pdf}\hspace{-11mm}
 \includegraphics[width=0.32\textwidth]{figs/r_ma.pdf}
 \caption{\label{fig:model_2D}Precision measurements of any two model parameters at 3$\sigma$ confidence level in the framework of three neutrino oscillations taking uncertainties of the current global fit results, for MOMENT, at $1\sigma$ (gray), $2\sigma$ (orange), $3\sigma$ (black). True values for the model parameters are used $(x,~\eta,~r,~M_a)=(-3.65,~1.13\pi,~0.511,~3.71~\text{meV})$.}
\end{figure}

\subsection{Model testing}
\begin{figure}[!h]%
\centering
\includegraphics[width=2in]{figs/SR_th13.pdf}
\includegraphics[width=2in]{figs/SR_th23.pdf}\\
\includegraphics[width=2in]{figs/SR_dCP.pdf}
\includegraphics[width=2in]{figs/SR_ldm.pdf}
\caption{The $\chi^2_{ex.}$ value for tri-direct littlest seesaw model for $\theta_{13}$, $\theta_{23}$, $\delta$ and $\Delta m_{31}^2$. The range for each parameter is taken according to the $3\sigma$ uncertainty in NuFit4.0 results.}%
\label{fig:SR_1D}
\end{figure}

\begin{figure}[!h]
 \flushleft
%
\includegraphics[width=0.32\textwidth]{figs/SR_th13_th23.pdf}$~~~~~~$\\
\includegraphics[width=0.32\textwidth]{figs/SR_th13_dCP.pdf}
\includegraphics[width=0.32\textwidth]{figs/SR_th23_dCP.pdf}$~~~~~~$\\
\includegraphics[width=0.32\textwidth]{figs/SR_th13_ldm.pdf}
\includegraphics[width=0.32\textwidth]{figs/SR_th23_ldm.pdf}
\includegraphics[width=0.32\textwidth]{figs/SR_dCP_ldm.pdf}
 \caption{\label{fig:SR_2D}The 2-D exclusion contour for tri-direct littlest seesaw model on the plane of any two true standard parameters, from $1\sigma$ to $5\sigma$. The range for each parameter is taken according to the $3\sigma$ uncertainty in NuFit4.0 results. The black dot denotes the best fit of NuFit4.0 results ($(\theta_{12},~\theta_{13},~\theta_{23},~\delta,~\Delta m_{21}^2,~\Delta m_{31}^2)=(33.82^\circ,~8.61^\circ,~49.6^\circ,~215^\circ,~7.39\times10^{-5}~\text{eV}^2,~2.525\times10^{-3}~\text{eV}^2)$), while the star is the prediction by the tri-direct littlest seesaw model with NuFit4.0 results ($(\theta_{12},~\theta_{13},~\theta_{23},~\delta,~\Delta m_{21}^2,~\Delta m_{31}^2)\sim(36.25^\circ,~8.63^\circ,~47^\circ,~279^\circ,~7.39\times10^{-5}~\text{eV}^2,~2.525\times10^{-3}~\text{eV}^2)$).}
\end{figure}

\section{Conclusion}

% BIBLIOGRAPHY
% use BIBTEX if you want
\bibliographystyle{JHEP}
\bibliography{FAS-GLoBES.bib}
\end{document}

### 2020-04-28 doc/FAS-GLoBES.tex
Update FAS-GLoBES.tex

@@
 
+For different methods to include the model, we use different \texttt{c++} file.
+Adopting the mass matrix expressed by model parameters, we assign this model in \textbf{model-input\_diag.c}.
+In function \texttt{MtoS}, we give
+the mass matrix in the $3\times3$ complex matrix \texttt{Mass\_Matrix[]}.
+%
+Passing the complex matrix \texttt{Mass\_Matrix[]} into the function \texttt{STAN\_OSC}, we will get the corresponding oscillation parameters in an array \texttt{OSC\_PARAMS}, components of which are the value for $\theta_{12}$, $\theta_{13}$, $\theta_{23}$, $\delta$, $\Delta m_{21}^2$, and $\Delta m_{31}^2$.
+The expression of \texttt{Mass\_Matrix[]} is given by the user.
+For the first four components, values are given in the unit of \textbf{rad}, while the other two are in eV$^2$.
+We can also assign the relation between oscillation and model parameters in \textbf{model-input.c}.
+The relations are given in \texttt{MtoS} as well.
+
+\subsection{Prior setting}\label{sec:prior}
+The \texttt{c++} file \textbf{FASE\_GLoBES.c} then will call these oscillation-parameter values and pass these to simulate the event spectrum.
+The $\chi^2$ value from priors is also given in \textbf{FASE\_GLoBES.c}.
+And these functions are given by the user.
+
+\subsection{Summary of API}
+
+\section{Examples}
+\subsection{Setup for a model}
 We now take the littlest seesaw model in the tri-direct approach as an example.
@@
 
-For different methods to include the model, we use different \texttt{c++} file.
-Adopting the mass matrix Eq.~\ref{eq:mnu}, we assign this model in \textbf{model-input\_diag.c}.
-In function \texttt{MtoS}, we give
-the mass matrix Eq.~\ref{eq:mnu} in the $3\times3$ complex matrix \texttt{Mass\_Matrix[]}.\vspace{0.5cm}
-
 \texttt{int MtoS(double OSC\_PARAMS[6],~double M\_para[])}\\
@@
 \texttt{\} }
-
-Passing the complex matrix \texttt{Mass\_Matrix[]} into the function \texttt{STAN\_OSC}, we will get the corresponding oscillation parameters in an array \texttt{OSC\_PARAMS}, components of which are the value for $\theta_{12}$, $\theta_{13}$, $\theta_{23}$, $\delta$, $\Delta m_{21}^2$, and $\Delta m_{31}^2$.
-The expression of \texttt{Mass\_Matrix[]} is given by the user.
-For the first four components, values are given in the unit of \textbf{rad}, while the other two are in eV$^2$.
-
-We can also assign the relation between oscillation and model parameters Table~\ref{tab:TD_parameters} in \textbf{model-input.c}. The relations are given in \texttt{MtoS} as well.\vspace{0.5cm}
 
@@
 
-\subsection{Prior setting}\label{sec:prior}
-The \texttt{c++} file \textbf{FASE\_GLoBES.c} then will call these oscillation-parameter values and pass these to simulate the event spectrum.
-The $\chi^2$ value from priors is also given in \textbf{FASE\_GLoBES.c}.
-And these functions are given by the user.
-
-\subsection{Summary of API}
-
-\section{Examples}
 \subsection{Constraint of model parameters}

### 2020-04-29 doc/FAS-GLoBES.tex
update tex

@@
 \usepackage{multirow}
+\usepackage{enumerate}
 \title{\boldmath  Flavour Symmetry Embedded - GLoBES}
@@
 
+The FlAvor Symmetry Embedded (FASE) is a supplemental tool for General Long Baseline Experiment Simulator (GLoBES) in order to analysis how a leptonic flavour symmetry model can be tested in neutrino oscillation experiments.
+FASE is written in the \texttt{c/c++} language, and consist with three codes \textbf{FASE\_GLoBES.c}, \textbf{model-input\_diag.c} and \textbf{model-input.c}.
+The user defines the model in to \textbf{model-input\_diag.c} or \textbf{model-input.c}, while \textbf{FASE\_GLoBES.c} does not need to be touched.
+
 \begin{figure}[!h]%
 \centering
-\includegraphics[width=5in]{Figs/FASE-chart-1_v1.pdf}
+\includegraphics[width=4.5in]{Figs/FASE-chart_1_v1.pdf}
 \caption{A scheme to correlate the model parameters with standard neutrino oscillation parameters. The error propagation is implemented in the simulation code up to the spectra analysis.}%
@@
 
-The FASE-GLoBES is based on GLoBES as shown in Fig.~\ref{fig:FASE}, in which three parts are shown: 1.
-\textbf{the parameter translation} (the blue box), 2.
-\textbf{giving oscillation-parameter values} (the green box), and 3.
-\textbf{the $\chi^2$-value calculation} (the orange box).
+The FASE-GLoBES is FASE working with GLoBES as shown in Fig.~\ref{fig:FASE}, in which three parts are shown: 1.~\textbf{the parameter translation} (the blue box), 2.~\textbf{giving oscillation-parameter values} (the green box), and 3.~\textbf{the $\chi^2$-value calculation} (the orange box).
 The idea behind this flow chart Fig.~\ref{fig:FASE} is that given a set of value for model parameter, the corresponding values for oscillation parameters are obtained by a translation, which is assigned by the user in \textbf{model-input\_diag.c} or \textbf{model-input.c}.
 And then, through \textbf{FASE\_GLoBES.c}, these oscillation-parameter values are passed in to \textbf{GLoBES} library to simulate the event spectrum for evaluating the $\chi^2$ value.
-Using prior needs
+
+API functions to use FASE are listed:
+\begin{enumerate}
+\item \texttt{MODEL\_init($N_{para}$)},
+\item  \texttt{FASE\_glb\_probability\_matrix},
+\item  \texttt{FASE\_glb\_set\_oscillation\_parameters},
+\item  \texttt{FASE\_glb\_get\_oscillation\_parameters},
+\item \texttt{FASE\_prior\_OSC},
+\item \texttt{FASE\_prior\_model}.
+\end{enumerate}
+The first one is to initialise FASE with the parameter $N_{para}$ the number of input parameters.
+The next three functions need to be included to replace the default GLoBES probability engine by the one that can read the output from  \textbf{model-input\_diag.c} or \textbf{model-input.c}, as follows\vspace{0.2cm}\\
+\texttt{    glbRegisterProbabilityEngine(6,\\
+                                 \&FASE\_glb\_probability\_matrix,\\
+                                 \&FASE\_glb\_set\_oscillation\_parameters,\\
+                                 \&FASE\_glb\_get\_oscillation\_parameters,\\
+                                 NULL); }\vspace{0.2cm}\\ 
+The final two functions are prior functions.
+Once the user gives the prior in oscillation (model) parameters, the user needs to call \texttt{FASE\_prior\_OSC} (\texttt{FASE\_prior\_model}) as follows.\vspace{0.2cm}\\
+\texttt{glbRegisterPriorFunction(FASE\_prior\_OSC,NULL,NULL,NULL); }  \\
+or\\
+\texttt{glbRegisterPriorFunction(FASE\_prior\_model,NULL,NULL,NULL); } \vspace{0.2cm}\\
 
@@
 In \textbf{model-input\_diag.c} and \textbf{model-input.c}, the user can assign the relation between the oscillation and model parameter sets.
-The difference between these two code is that in \textbf{model-input.c}, the user give the relation between these two parameter sets directly (\textit{e.g.}~Table~\ref{tab:TD_parameters} for tri-direct littlest seesaw), while in \textbf{model-input.c}, the mass matrix (\textit{e.g.}~Eq.~\ref{eq:mnu} for tir-direct littlest seesaw), which is provided by the user, can be diagonalised to obtain the corresponding oscillation-parameter values.
+The difference between these two code is that in \textbf{model-input.c}, the user give the relation between these two parameter sets directly, while in \textbf{model-input.c}, the mass matrix, which is provided by the user, can be diagonalised to obtain the corresponding oscillation-parameter values.
 
@@
 The expression of \texttt{Mass\_Matrix[]} is given by the user.
-For the first four components, values are given in the unit of \textbf{rad}, while the other two are in eV$^2$.
+For the first four components, values are given in the unit of \textbf{rad}, while the other two are in \textbf{eV$^2$}.
 We can also assign the relation between oscillation and model parameters in \textbf{model-input.c}.
@@
 And these functions are given by the user.
-
-\subsection{Summary of API}
 

### 2020-04-29 doc/FAS-GLoBES.tex
update manual

@@
 
-The FlAvor Symmetry Embedded (FASE) is a supplemental tool for General Long Baseline Experiment Simulator (GLoBES) in order to analysis how a leptonic flavour symmetry model can be tested in neutrino oscillation experiments.
-FASE is written in the \texttt{c/c++} language, and consist with three codes \textbf{FASE\_GLoBES.c}, \textbf{model-input\_diag.c} and \textbf{model-input.c}.
+\textbf{F}l\textbf{A}vor \textbf{S}ymmetry \textbf{E}mbedded (\textbf{FASE}) is a supplemental tool for General Long Baseline Experiment Simulator (\textbf{GLoBES}) in order to analysis how a leptonic flavour symmetry model can be tested in neutrino oscillation experiments.
+\textbf{FASE} is written in the \texttt{c/c++} language, and consist with three codes \textbf{FASE\_GLoBES.c}, \textbf{model-input\_diag.c} and \textbf{model-input.c}.
 The user defines the model in to \textbf{model-input\_diag.c} or \textbf{model-input.c}, while \textbf{FASE\_GLoBES.c} does not need to be touched.
@@
 
-The FASE-GLoBES is FASE working with GLoBES as shown in Fig.~\ref{fig:FASE}, in which three parts are shown: 1.~\textbf{the parameter translation} (the blue box), 2.~\textbf{giving oscillation-parameter values} (the green box), and 3.~\textbf{the $\chi^2$-value calculation} (the orange box).
+The \textbf{FASE-GLoBES} is \textbf{FASE} working with \textbf{GLoBES} as shown in Fig.~\ref{fig:FASE}, in which three parts are shown: 1.~\textbf{the parameter translation} (the blue box), 2.~\textbf{giving oscillation-parameter values} (the green box), and 3.~\textbf{the $\chi^2$-value calculation} (the orange box).
 The idea behind this flow chart Fig.~\ref{fig:FASE} is that given a set of value for model parameter, the corresponding values for oscillation parameters are obtained by a translation, which is assigned by the user in \textbf{model-input\_diag.c} or \textbf{model-input.c}.
@@
 
-API functions to use FASE are listed:
+API functions to use \textbf{FASE} are listed:
 \begin{enumerate}
@@
                                  NULL); }\vspace{0.2cm}\\ 
+This probability engine can work with the oscillation or model parameter.
+It can be set by the user with the parameter \texttt{PARA}.
+If \texttt{PARA=STAN} (\texttt{PARA=MODEL}) the probability engine works with oscillation (model) parameters.
 The final two functions are prior functions.
@@
 
-In the following, we give more details about using FASE-GLoBES.
-In Sec.~\ref{sec:download}, we will give the instruction to download and install GLoBES and FASE-GLoBES.
+In the following, we give more details about using \textbf{FASE-GLoBES}.
+In Sec.~\ref{sec:download}, we will give the instruction to download and install \textbf{GLoBES} and \textbf{FASE}.
 Then, in Sec.~\ref{sec:compile}, we will introduce how to compile and run the code.
@@
 \subsection{Prior setting}\label{sec:prior}
-The \texttt{c++} file \textbf{FASE\_GLoBES.c} then will call these oscillation-parameter values and pass these to simulate the event spectrum.
-The $\chi^2$ value from priors is also given in \textbf{FASE\_GLoBES.c}.
-And these functions are given by the user.
+Given a set of values for model parameters, \textbf{FASE\_GLoBES.c} will obtain the corresponding oscillation-parameter values from \textbf{model-input\_diga.c} or \textbf{model-input.c}, and will pass these values to simulate the event spectrum and to give the prior value.
+Two gaussian prior functions are provided in \textbf{FASE} -- \texttt{FASE\_prior\_OSC} and \texttt{FASE\_prior\_model}.
+These two functions are for different purposes.
+If the user give the prior in oscillation (model) parameters, the user should register \texttt{FASE\_prior\_OSC} (\texttt{FASE\_prior\_model}) for the prior with the \textbf{GLoBES} function \texttt{glbRegisterPriorFunction}, as we introduced in the beginning of this section.
+The Gaussian prior is
+\begin{equation}
+\chi^2_{prior}=\sum_{i} \frac{(\theta_i-\theta^c_i)^2}{\sigma_i^2},
+\end{equation}
+ where $\theta_i$ is one of parameters constrained by prior, $\theta^c_i$ ($\sigma_c$) is the central value (Gaussian width) of the prior for $\theta_i$.
+We note that $\theta_i$ can be either model or oscillation parameter.
+ But, oscillation and model parameters can be mixed up together in the using of prior.
+
+The values of $\theta^c_i$ and $\sigma_i$ need to be given by the user through three arrays: \texttt{Central\_prior}, \texttt{UPPER\_prior}, and \texttt{LOWER\_prior}, in which there are six components.
+To treat asymmetry of width for the upper and lower Gaussian widths, we give values in two arrays \texttt{UPPER\_prior}, and \texttt{LOWER\_prior}, respectively.
+If the user gives the prior in model parameters, the order of each component follow with the setup of input of the probability engine.
+While the user gives the prior in oscillation parameters, the six components in order are $\theta_{12}$, $\theta_{13}$, $\theta_{23}$, $\delta$, $\Delta m_{21}^2$, and  $\Delta m_{31}^2$.
+The first four parameter are in \textbf{rad}, and the final two are in \textbf{eV$^2$}.
+
+Finally, some restrictions are imposed by the studied flavour symmetry model.
+We set up these restrictions in the function \texttt{model\_restriction}, which is in \texttt{model-input\_diga.c} and \texttt{model-input.c}.
+In the function \texttt{model\_restriction}, the user needs to \textit{return $0$} once the restriction is broken.
+For example, if the normal ordering is imposed, we give ``\texttt{ if (DMS31<0) \{ return 1;\} } '' in \texttt{model\_restriction}, where \texttt{DMS31} is for $\Delta m_{31}^2$.
+Then, when the restriction is broken, \texttt{model\_restriction} returns the value $1$ to the prior function \texttt{FASE\_prior\_OSC} or \texttt{FASE\_prior\_model}.
+In the following, the prior function will give $10^6$ for the $\chi^2$ value, and it will be selected out when we study the statistically reasonable region in the parameter space.
 
@@
 We note that from Eq.~(\ref{eq:mnu}), $m_1=0$ and the normal mass ordering are imposed, and will need to be imposed in \textbf{FASE-GLoBES}.
-We will introduce the way to do it in Sec.~\ref{sec:prior}.
+Therefore, the restrictions in this model are $m_a>0$ and $r>0$.
 
@@
 
+The restrictions $m_a>0$ and $r>0$ need to be setup in \texttt{model\_restriction} as follows.\vspace{0.2cm}\\
+\texttt{double model\_restriction(double model [])}\\
+\texttt{\{}\\
+\texttt{    double x=model[0];}\\
+\texttt{    double eta=model[1];}\\
+\texttt{    double r=model[2];}\\
+\texttt{    double ma=model[3];}\\
+    \\
+\texttt{    if(ma<0) \{return 1;\}}\\
+\texttt{    if(r<0) \{return 1;\}}\\
+\\ 
+\texttt{    return 0;}\\
+\}\vspace{0.2cm}\\
+If there is no any restrictions, we simply \textit{return $0$} in \texttt{model\_restriction} as follows.\vspace{0.2cm}\\
+\texttt{double model\_restriction(double model [])\{ return 0;\} }\vspace{0.2cm}\\
+
+\subsection{Initialise the code}
+In the beginning of main code, we need to initialise GLoBES and FASE, and include the considered experiment (here we consider MOMENT experiment) as follows.\vspace{0.2cm}\\ 
+\texttt{glbInit(argv[0]);}\\
+\texttt{glbInitExperiment("expMOMENT\_FIX\_FLUX\_150KM\_addATM\_NC.glb",\&glb\_experiment\_list[0],}\\
+\texttt{\&glb\_num\_of\_exps);}\\
+\texttt{MODEL\_init(4);}\vspace{0.2cm}\\
+Then we register the probability engine.\vspace{0.2cm}\\
+\texttt{glb\_init\_probability\_engine();}\\
+\texttt{glbRegisterProbabilityEngine(6,\\
+                                 \&FASE\_glb\_probability\_matrix,\\
+                                 \&FASE\_glb\_set\_oscillation\_parameters,\\
+                                 \&FASE\_glb\_get\_oscillation\_parameters,\\
+                                 NULL); }\vspace{0.2cm}\\                                 
+In the following we define the model-parameter values, and set the true value in model parameters.\vspace{0.2cm}\\
+\texttt{     float degree   = M\_PI/180;}\\
+\texttt{     float x\_true,eta\_true,r\_true,ma\_true;}\\
+\texttt{    x\_true=-3.65029; eta\_true=1.13067*M\_PI; r\_true=0.511325; ma\_true=3.71199e-3;}\\
+%
+\texttt{glb\_params true\_values = glbAllocParams();}\\
+\texttt{glb\_params test\_values = glbAllocParams();}\\
+\texttt{glb\_params input\_errors  = glbAllocParams();}\\
+\texttt{glb\_params centers         = glbAllocParams();}\\
+\texttt{glbDefineParams(true\_values,x\_true,eta\_true,r\_true,ma\_true,0,0);}\\
+\texttt{    glbSetDensityParams(true\_values,1.0,GLB\_ALL);}\\
+\texttt{glbCopyParams(true\_values,test\_values);}\\
+\texttt{PARA=MODEL;\\
+    glbSetOscillationParameters(true\_values);\\
+    glbSetRates();}\vspace{0.2cm}\\
+We then finally set up the projection.
+The projection \texttt{free} is to set all four parameters free to find the minimal value of $\chi^2$, which \texttt{project} is used for studying the constraint on $x$ and $\eta$.\vspace{0.2cm}\\
+\texttt{glb\_projection projection = glbAllocProjection();\\
+    glb\_projection free = glbAllocProjection();  \\
+     glbDefineProjection(free,GLB\_FREE,GLB\_FREE,GLB\_FREE,GLB\_FREE,GLB\_FIXED,GLB\_FIXED);\\
+    glbSetDensityProjectionFlag(free, GLB\_FREE, GLB\_ALL);\\
+glbDefineProjection(projection,GLB\_FIXED,GLB\_FIXED,GLB\_FREE,GLB\_FREE,GLB\_FIXED,GLB\_FIXED);\\    
+glbSetDensityProjectionFlag(projection, GLB\_FREE, GLB\_ALL);\\
+    }
+
+\subsection{Prior setup}
+
+To set up the prior, we need to register the prior function.
+As mentioned, when we use the prior in oscillation and model parameters, we register \texttt{FASE\_prior\_OSC} and \texttt{FASE\_prior\_model}, respectively.
+Here we present an example setting up priors in oscillation parameters according to NUFIT4.0 Table~\ref{tab:nufit4.0}.
+
+\begin{table}[!h]
+\caption{The best fit and $3\sigma$ uncertainty, in the results of NuFit4.0 \cite{Esteban:2018azc}.}
+\begin{tabular}{|c|c|c|c|c|c|c|}
+\hline
+Parameter & $\theta_{12}/^\circ$ & $\theta_{13}/^\circ$ & $\theta_{23}/^\circ$ & $\delta/^\circ$  & $\Delta m_{21}^2/10^{-5}\text{eV}^2$ & $\Delta m_{31}^2/10^{-3}\text{eV}^2$\\ \hline\hline
+best fit & $33.82$ & $8.61$ & $49.6$ & $215$ & $7.39$ & $2.525$ \\\hline
+$3\sigma$ Range & $31.61-36.27$ & $8.22-8.99$ & $40.3-52.4$ & $125-392$ & $6.79-8.01$ & $2.47-2.625$ \\\hline
+\end{tabular}
+\label{tab:nufit4.0}
+\end{table}
+
+We therefore register \texttt{FASE\_prior\_OSC} for the prior function as follows.\vspace{0.2cm}\\
+\texttt{glbRegisterPriorFunction(FASE\_prior\_OSC,NULL,NULL,NULL); }  \vspace{0.2cm}\\
+And, then we give the value for the central values, and upper and lower Gaussian widths as follows.\vspace{0.2cm}\\
+\texttt{    UPPER\_prior[0]=36.27*degree;  LOWER\_prior[0]=31.61*degree;   Central\_prior[0]=33.82*degree;}\\
+\texttt{    UPPER\_prior[1]=8.99*degree; LOWER\_prior[1]=8.22*degree;  Central\_prior[1]=8.61*degree;}\\
+\texttt{    UPPER\_prior[2]=52.4*degree;  LOWER\_prior[2]=40.3*degree;   Central\_prior[2]=49.6*degree;}\\
+\texttt{    UPPER\_prior[3]=392*degree;  LOWER\_prior[3]=125*degree;   Central\_prior[3]=215*degree;}\\
+\texttt{    UPPER\_prior[4]=8.01e-5;     LOWER\_prior[4]=6.79e-5;      Central\_prior[4]=7.39e-5; }\\
+\texttt{    UPPER\_prior[5]=2.625e-3;     LOWER\_prior[5]=2.427e-3;      Central\_prior[5]=2.525e-3;}\\
+   \\ 
+\texttt{int i;}\\
+\texttt{    for (i=0;i<6;i++) \{UPPER\_prior[i]=fabs(UPPER\_prior[i]-Central\_prior[i])/3; }\\
+\texttt{                       LOWER\_prior[i]=fabs(LOWER\_prior[i]-Central\_prior[i])/3;\} }\\
+\texttt{for (i=0; i<6; i++) glbSetOscParams(centers,0,i);}\\
+\texttt{glbSetDensityParams(centers,1.0,GLB\_ALL);}
+\texttt{glbCopyParams(centers,input\_errors);}\\
+\texttt{    glbSetCentralValues(centers);   glbSetInputErrors(input\_errors);}\vspace{0.2cm}\\
+The parameter \texttt{degree} is defined as $\pi/180$.
+
 \subsection{Constraint of model parameters}
-%\subsection{Projection on the PMNS parameters}
-\begin{figure}[!h]%
-\centering
-\includegraphics[width=2in]{figs/x.pdf}
-\includegraphics[width=2in]{figs/eta.pdf}\\
-\includegraphics[width=2in]{figs/r.pdf}
-\includegraphics[width=2in]{figs/ma.pdf}
-\caption{The $\Delta\chi^2$ value against each model parameters for MOMENT.
-True values for the model parameters are used $(x,~\eta,~r,~M_a)=(-3.65,~1.13\pi,~0.511,~3.71~\text{meV})$.
-The range shown here is according to the $3\sigma$ uncertainty with NuFit4.0 results:  $-5.475<x<-3.37$ (red band),~$0.455<\eta/\pi<1.545$ (dark grey band), ~$0.204<r<0.606$ (blue band),~$3.343<m_a/\text{meV}<4.597$ (yellow band).}%
-\label{fig:model_1D}
-\end{figure}
+
+To get the constraint of $x$ and $\eta$, we obtain the minimum of $\chi^2$ value,\vspace{0.2cm}\\
+\texttt{
+    glbSetProjection(free);\\
+    float res0=glbChiNP(true\_values,NULL,GLB\_ALL);\\ } \vspace{0.2cm}\\
+%
+Then, we set two loops to get the $\Delta \chi^2$ value for different $x$ and $\eta$\vspace{0.2cm}\\
+%
+\texttt{     float x,eta,r,ma,dx,deta;\\
+     float lower\_x,upper\_x,lower\_eta,upper\_eta;\\
+     FILE* File=fopen("data/constraint\_x\_eta.dat", "w");\\
+    lower\_x=-5; upper\_x=-3; lower\_eta=0.8*M\_PI; upper\_eta=1.5*M\_PI;\\
+    dx=(upper\_x-lower\_x)/100; deta=(upper\_eta-lower\_eta)/100;\\
+        glbSetProjection(projection);\\
+   for (x=lower\_x;x<=upper\_x;x=x+dx)\{ \\
+    for (eta=lower\_eta;eta<=upper\_eta;eta=eta+deta)\{\\
+     glbSetOscParams(test\_values,x,0); glbSetOscParams(test\_values,eta,1);\\
+        float res=glbChiNP(test\_values,NULL,GLB\_ALL);\\
+            fprintf(File,"\%f \%f  \%f $\backslash$n",x,eta/M\_PI,res-res0);\\
+                     \} fprintf(File,"$\backslash$n");\}\\
+}
+
+%\texttt{
+%glbFreeParams(true\_values);\\
+%glbFreeParams(test\_values); \\
+%glbFreeParams(input\_errors); \\
+%glbFreeParams(centers);\\
+%glbFreeProjection(free);\\
+%glbFreeProjection(projection);\\
+%}
 
@@
 \subsection{Model testing}
-\begin{figure}[!h]%
-\centering
-\includegraphics[width=2in]{figs/SR_th13.pdf}
-\includegraphics[width=2in]{figs/SR_th23.pdf}\\
-\includegraphics[width=2in]{figs/SR_dCP.pdf}
-\includegraphics[width=2in]{figs/SR_ldm.pdf}
-\caption{The $\chi^2_{ex.}$ value for tri-direct littlest seesaw model for $\theta_{13}$, $\theta_{23}$, $\delta$ and $\Delta m_{31}^2$.
-The range for each parameter is taken according to the $3\sigma$ uncertainty in NuFit4.0 results.}%
-\label{fig:SR_1D}
-\end{figure}
 

### 2020-04-29 FASE_GLoBES.c
update code

@@ -1,35 +1,3 @@
-/* GLoBES -- General LOng Baseline Experiment Simulator
- * (C) 2002 - 2007,  The GLoBES Team
- *
- * GLoBES is mainly intended for academic purposes. Proper
- * credit must be given if you use GLoBES or parts of it. Please
- * read the section 'Credit' in the README file.
- *
- * This program is free software; you can redistribute it and/or modify
- * it under the terms of the GNU General Public License as published by
- * the Free Software Foundation; either version 2 of the License, or
- * (at your option) any later version.
- *
- * This program is distributed in the hope that it will be useful,
- * but WITHOUT ANY WARRANTY; without even the implied warranty of
- * MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
- * GNU General Public License for more details.
- *
- * You should have received a copy of the GNU General Public License
- * along with this program; if not, write to the Free Software
- * Foundation, Inc., 59 Temple Place, Suite 330, Boston, MA  02111-1307  USA
- */
-
-/*
- * Example: Non-Standard-Interactions and user-defined priors
- * Compile with ``make example6''
- *
- * This example is similar to Chapter 4 of hep-ph/0502147
- */
-//#if HAVE_CONFIG_H   /* config.h should come before any other includes */
-//#  include "config.h"
-//#endif
-
 #include <stdio.h>
 #include <stdlib.h>
 #include <math.h>
@@ -908,9 +876,9 @@ double FASE_prior_model(const glb_params in, void* user_data)
     
     for(i=0;i<N_M;i++){
         fitvalue=in->osc->osc_params[i]; centralvalue=Central_prior[i];
-        if(inputerror>1e-12) { if(fitvalue>centralvalue) {inputerror=UPPER_prior[i];}
+        if(fitvalue>centralvalue) {inputerror=UPPER_prior[i];}
         else {inputerror=LOWER_prior[i];}
-            pv+=square((centralvalue-fitvalue)/inputerror);} }
+         if(inputerror>1e-12) { pv+=square((centralvalue-fitvalue)/inputerror);} }
     
     /* Add matter parameter priors */
     for(i=0;i<glb_num_of_exps;i++){

### 2020-04-29 model-input.c

@@ -187,8 +187,10 @@ double TDdm31(double x, double eta, double r, double Ma){
 } //checked!
 
 
+
 double MODEL_init(int N) /*initialise the model-input*/
 {
+    if (N>6){printf("the number of parameters cannot be larger than 6.\n");}
     N_M=N;
     return 0;
 }
@@ -223,8 +225,8 @@ double model_restriction(double model [])
     double r=model[2];
     double ma=model[3];
     
-    if(ma<0) {return 1e8;}
-    if(r<0) {return 1e8;}
+    if(ma<0) {return 1;}
+    if(r<0) {return 1;}
     
     return 0;
 }

### 2020-04-29 model-input_diag.c

@@ -26,172 +26,9 @@ typedef struct OSC_PARAMS { double theta12; double theta13; double theta23; doub
 
 double MODEL_init(int N) /*initialise the model-input*/
 {
+    if (N>6){printf("the number of parameters cannot be larger than 6.\n");}
     N_M=N;
-    return 0;
-}
 
-
-
-
-int sinsq(double complex U[], double * a) /*Mark1*/
-{
-    double sinsqth13 = pow(cabs(U[2]),2.0);
-    if(sinsqth13==1.0)
-    {// THIS EXCEPTION NEEDS TO BE DEALT WITH.
-        
-        //printf("BAD ANGLE!\n");
-        //return 1;
-        //My logic is, although finding the angles is hard in this case. They are all ruled out as theta13=90.
-        
-        a[1] = 100.0;
-        a[0] = 100.0;//pow(cabs(U[3]),2.0)+pow(cabs(U[6]),2.0);
-        a[2] = 100.0;
-        a[3] = 100.0;
-        a[4] = 100.0;
-        a[5] = 100.0;
-    }
-    else
-    {
-        a[1] = sinsqth13;
-        a[0] = pow(cabs(U[1]),2.0)/(1.0-sinsqth13);
-        a[2] = pow(cabs(U[5]),2.0)/(1.0-sinsqth13);
-        a[3] = carg(  -U[0]*conj(U[2]*U[3])*U[5] - (1-a[0])*(1-a[1])*a[1]*a[2]  );
-        a[4] = (carg(U[1]*U[1]*conj(U[0]*U[0]))); // \alpha_{21}
-        
-        a[5] = carg(U[2]*U[2]*conj(U[0]*U[0])) + 2.0*a[3];
-        
-        if(a[5]>M_PI+1e-3){ a[5]-=2.0*M_PI;}
-        else if(a[5]<-M_PI-1e-3){ a[5]+=2.0*M_PI;}
-        
-        if(fabs(a[5]-M_PI)<1e-3){a[5]=-M_PI;}
-        
-        //        printf("### a[5] = %.5lf\n", a[5]);
-        
-    }
-    
-    return 0;
-}
-
-double find_PMNS(double complex M[], OSC_PARAMS * output) /*Mark1*/
[…]

### 2020-04-30 doc/FAS-GLoBES.tex
update code and tex

@@
 \usepackage{enumerate}
+%\usepackage{textcomp}
+%\usepackage{underscore}
 \title{\boldmath  Flavour Symmetry Embedded - GLoBES}
@@
 \section{Introduction}\label{sec:intro}
-{\color{red}intro flavour symmetry, and summarise some phenon works}
 
@@
 \texttt{glbRegisterPriorFunction(FASE\_prior\_model,NULL,NULL,NULL); } \vspace{0.2cm}\\
+We note that except for setting the probability engine and the prior function, the other parts in the main code should follow with the GLoBES manual.
 
@@
 \subsection{Compile and Run}\label{sec:compile}
-{\color{red}[will fill in after the code ready on Github]}
+As FASE works based on GLoBES, the user should use the \textbf{GLoBES} \texttt{Makefile}, but include the binary file for FASE.
+To do so, we include the script in the \texttt{Makefile},\vspace{0.2cm}\\
+\texttt{\{makefile\_execution\}: my\_program.o  FASE\_GLoBES.o model-input\_diag.o\\
+	gcc my\_program.o  FASE\_GLoBES.o model-input\_diag.o -o my\_executable  \$(LDFLAGS) \$(local\_LDFLAGS)}\\
+or\\
+\texttt{\{makefile\_execution\}: my\_program.o  FASE\_GLoBES.o model-input.o\\
+	gcc my\_program.o  FASE\_GLoBES.o model-input.o -o my\_executable  \$(LDFLAGS) \$(local\_LDFLAGS)}\vspace{0.2cm}\\	
+where \texttt{\{compile\_execusion\}} is the makefile commend for the program \texttt{my\_program.o} and the execution \texttt{my\_executable} is the output.
+After giving this script in the \textbf{GLoBES} \texttt{Makefile}, the user needs to makefile the program \texttt{my\_program} on the terminal.\vspace{0.2cm}\\
+\texttt{makefile \{makefile\_execution\}}\vspace{0.2cm}\\
+And, the user can execute the program by typing the following commend on the terminal.\vspace{0.2cm}\\ 
+\texttt{./my\_executable}\vspace{0.2cm}\\
 
-To initial \textbf{FASE-GLoBES}, we need to include the following code\\
-\texttt{    MODEL\_init($N_{para}$); }\\
-where $N_{para}$ is the number of model parameters.
+The user can also compile the program without the \textbf{GLoBES} \texttt{Makefile} with the following script.\vspace{0.2cm}\\
+\texttt{gcc my\_program.o FASE\_GLoBES.o model-input\_diag.o -lglobes -LGLB\_DIR/lib/ -o my\_executable}\\
+or\\
+\texttt{gcc my\_program.o FASE\_GLoBES.o model-input.o -lglobes -LGLB\_DIR/lib/ -o my\_executable}\vspace{0.2cm}\\
+And, the execution is also in the same way: \texttt{./my\_executable}.\\
+
+Finally we need to initialize \textbf{FASE} by giving $N_{para}$ which is the number of model parameters. To do so, we need to include the following script in the main code.\\
+\texttt{    MODEL\_init($N_{para}$); }\vspace{0.2cm}\\
 
@@
 
+We use the same code to obtain the constraint of any other combination of two parameters. Then, we can have the result as in Fig.~\ref{fig:model_2D}.
+
 %\texttt{

### 2020-04-30 x_eta.c

@@ -1,0 +1,126 @@
+#if HAVE_CONFIG_H   /* config.h should come before any other includes */
+#  include "config.h"
+#endif
+
+
+#include <stdio.h>
+#include <stdlib.h>
+#include <math.h>
+#include <string.h>
+#include <complex.h>
+#include <float.h>
+
+#include <gsl/gsl_complex.h>
+#include <gsl/gsl_complex_math.h>
+#include <gsl/gsl_matrix.h>
+#include <gsl/gsl_blas.h>
+#include <gsl/gsl_statistics.h>
+#include <gsl/gsl_rng.h>
+#include <gsl/gsl_randist.h>
+#include <gsl/gsl_cblas.h>
+#include <gsl/gsl_eigen.h>
+#include <gsl/gsl_vector.h>
+
+
+#include <globes/globes.h>   /* GLoBES library */
+#include "FASE_GLoBES.h"
+//#include "model-input_diag.h"
+#include "model-input.h"
+
+/***************************************************************************
+ *                            M A I N   P R O G R A M                      *
+ ***************************************************************************/
+
+int main(int argc, char *argv[])
+{
+    /* Initialize libglobes */
+    glbInit(argv[0]);
+    glbInitExperiment("exp/MOMENT_FIX_FLUX_150KM_addATM_NC.glb",&glb_experiment_list[0],&glb_num_of_exps);
+    /*Initialize FASE*/
+    MODEL_init(4);
+    
+    /* Register non-standard probability engine. This has to be done
+     * before any calls to glbAllocParams() or glbAllocProjections() */
+    glb_init_probability_engine();
+    glbRegisterProbabilityEngine(6,
+                                 &FASE_glb_probability_matrix,
+                                 &FASE_glb_set_oscillation_parameters,
+                                 &FASE_glb_get_oscillation_parameters,
+                                 NULL);
+    /*define the true value*/
+    float degree   = M_PI/180;
+    float x_true,eta_true,r_true,ma_true;
+    x_true=-3.65029; eta_true=1.13067*M_PI; r_true=0.511325; ma_true=3.71199e-3;
+    
+    /* Initialize parameter and projection vector(s) */
[…]

### 2020-04-30 th23_dCP.c
update code

@@ -51,7 +51,9 @@ int main(int argc, char *argv[])
     float degree   = M_PI/180;
     float x_true,eta_true,r_true,ma_true;
     x_true=-3.65029; eta_true=1.13067*M_PI; r_true=0.511325; ma_true=3.71199e-3;
-    
+    double M_para[4],OSC_para[6];
+    M_para[0]=x_true; M_para[1]=eta_true; M_para[2]=r_true; M_para[3]=ma_true;
+    MtoS(OSC_para, M_para);
     /* Initialize parameter and projection vector(s) */
     glb_params true_values = glbAllocParams();
     glb_params test_values = glbAllocParams();
@@ -59,24 +61,23 @@ int main(int argc, char *argv[])
     glb_params centers = glbAllocParams();
     
     /*define model parameter: true_values( x, eta, r, ma)*/
-    glbDefineParams(true_values,x_true,eta_true,r_true,ma_true,0,0);
+    glbDefineParams(test_values,x_true,eta_true,r_true,ma_true,0,0);
+    glbSetDensityParams(test_values,1.0,GLB_ALL);
+    int i;
+    for(i=0;i<6;i++){glbSetOscParams(centers,OSC_para[i],i);}
     glbSetDensityParams(true_values,1.0,GLB_ALL);
-    glbCopyParams(true_values,test_values);
     
     /*assign the parameter set*/
-    PARA=STAN; /* if the user is interested in the sensitivity on Standard Oscillation parameters*/ /*Mark4*/
     PARA=MODEL; /* if the user is interested in the sensitivity on model parameters*/
+    PARA=STAN; /* if the user is interested in the sensitivity on Standard Oscillation parameters*/
     /*true value setup for GLoBES*/
     glbSetOscillationParameters(true_values);
     glbSetRates();
     
     /*projection setup*/
-    glb_projection projection = glbAllocProjection();
     glb_projection free = glbAllocProjection();
     glbDefineProjection(free,GLB_FREE,GLB_FREE,GLB_FREE,GLB_FREE,GLB_FIXED,GLB_FIXED);
-    glbSetDensityProjectionFlag(free, GLB_FIXED, GLB_ALL);
[…]

### 2020-04-30 th23_dCP.c
Update th23_dCP.c

@@ -54,6 +54,12 @@ int main(int argc, char *argv[])
     double M_para[4],OSC_para[6];
     M_para[0]=x_true; M_para[1]=eta_true; M_para[2]=r_true; M_para[3]=ma_true;
     MtoS(OSC_para, M_para);
+    double th12_true=OSC_para[0];
+    double th13_true=OSC_para[1];
+    double th23_true=OSC_para[2];
+    double dCP_true=OSC_para[3];
+    double DM21_true=OSC_para[4];
+    double DM31_true=OSC_para[5];
     /* Initialize parameter and projection vector(s) */
     glb_params true_values = glbAllocParams();
     glb_params test_values = glbAllocParams();
@@ -64,8 +70,10 @@ int main(int argc, char *argv[])
     glbDefineParams(test_values,x_true,eta_true,r_true,ma_true,0,0);
     glbSetDensityParams(test_values,1.0,GLB_ALL);
     int i;
-    for(i=0;i<6;i++){glbSetOscParams(centers,OSC_para[i],i);}
+    
+    glbDefineParams(true_values,th12_true,th13_true,th23_true,dCP_true,DM21_true,DM31_true);
     glbSetDensityParams(true_values,1.0,GLB_ALL);
+
     
     /*assign the parameter set*/
     PARA=MODEL; /* if the user is interested in the sensitivity on model parameters*/
@@ -101,19 +109,20 @@ int main(int argc, char *argv[])
     /*two loops for chi^2(x,eta)*/
     float th23,dCP,dth23,ddCP,lower_th23,upper_th23,lower_dCP,upper_dCP;
     FILE* File=fopen("data/ModelTest_th23_dCP_test.dat", "w");
-    lower_th23=40*degree; upper_th23=50*degree; lower_dCP=1.*M_PI; upper_dCP=2*M_PI;
-    dth23=(upper_th23-lower_th23)/100; ddCP=(upper_dCP-lower_dCP)/100;
+    lower_th23=45*degree; upper_th23=50*degree; lower_dCP=1.3*M_PI; upper_dCP=1.8*M_PI;
+    dth23=(upper_th23-lower_th23)/50; ddCP=(upper_dCP-lower_dCP)/50;
     glbSetProjection(free);
     for (th23=lower_th23;th23<=upper_th23;th23=th23+dth23){
     for (dCP=lower_dCP;dCP<=upper_dCP;dCP=dCP+ddCP){
     glbSetOscParams(true_values,th23,GLB_THETA_23);
[…]

### 2020-04-30 doc/FAS-GLoBES.tex
update doc

@@
 The Gaussian prior is
-\begin{equation}
+\begin{equation}\label{eq:prior}
 \chi^2_{prior}=\sum_{i} \frac{(\theta_i-\theta^c_i)^2}{\sigma_i^2},
@@
 
+The user can use \textbf{FASE-GLoBES} to study the constraint of model parameters.
+Here we take tri-direct littlest seesaw as an example to present how we can adopt \textbf{FASE-GLoBES} to constrain two model parameters -- $x$ and $\eta$.
+The $\chi^2$ function is construct based on a log -likelihood ratio,
+\begin{equation}\label{eq:chi-squared}
+\chi^2(\vec{\theta},\xi_s,\xi_b)=2\sum_i\left(\eta_i(\vec{\theta},\xi_s,\xi_b)-n_i+n_i\ln\frac{n_i}{\eta_i(\vec{\theta},\xi_s,\xi_b)} \right)+p(\xi_s,\sigma_s)+p(\xi_b,\sigma_b)+\chi^2_{prior},
+\end{equation}
+where $i$ runs over the number of bins, $\eta_i{\vec{\theta},\xi_s,\xi_b}$ is the hypothesis event rate for bin i and $E_i$ is the central bin energy.
+The vector $\vec{\theta}$ consist test model or oscillation parameters.
+Here, $\vec{\theta}=(x,\eta,r,m_a)$.
+The parameters $\xi_s$ and $\xi_b$ are introduced to account for the systematic uncertainty of normalisation for the signal (subscript $_s$) and background (subscript $_b$) components for the event rate, and are allowed to bary in the fit as nuisance parameters.
+For a given hypothesized set of parmaeters $\vec{\theta}$, the event rate for bin $i$ is calculated as\\
+\begin{equation}
+\eta_i(\vec{\theta},\xi_s,\xi_b)=(1+\xi_s)\times n_i+(1+\xi_b)\times b_i,
+\end{equation}
+where $n_i$ and $b_i$ are the expected number of signal and background events in bin $i$, respectively.
+The nuisance parameters are constrained by the Gaussian prior $p(\xi,\sigma)=\xi^2/\sigma^2$ with corresponding uncertainties $\sigma_s$ and $\sigma_b$ for the signal and background, respectively.
+Finally, $\chi^2_{prior}$ is a set of Gaussian priors for hypothesis, and is expressed as Eq.~\ref{eq:prior}.
 To get the constraint of $x$ and $\eta$, we obtain the minimum of $\chi^2$ value,\vspace{0.2cm}\\
@@
      FILE* File=fopen("data/constraint\_x\_eta.dat", "w");\\
-    lower\_x=-5; upper\_x=-3; lower\_eta=0.8*M\_PI; upper\_eta=1.5*M\_PI;\\
+    lower\_x=-9; upper\_x=-3; lower\_eta=0.8*M\_PI; upper\_eta=2*M\_PI;\\
     dx=(upper\_x-lower\_x)/100; deta=(upper\_eta-lower\_eta)/100;\\
@@
 }
-
-We use the same code to obtain the constraint of any other combination of two parameters. Then, we can have the result as in Fig.~\ref{fig:model_2D}.
-
-%\texttt{
-%glbFreeParams(true\_values);\\
-%glbFreeParams(test\_values); \\
-%glbFreeParams(input\_errors); \\
-%glbFreeParams(centers);\\
-%glbFreeProjection(free);\\
-%glbFreeProjection(projection);\\
-%}
 
@@
 
+We use the same code to obtain the constraint of any other combination of two parameters. Then, we can have the result as in Fig.~\ref{fig:model_2D}.
+
+%\texttt{
+%glbFreeParams(true\_values);\\
+%glbFreeParams(test\_values); \\
+%glbFreeParams(input\_errors); \\
+%glbFreeParams(centers);\\
+%glbFreeProjection(free);\\
+%glbFreeProjection(projection);\\
+%}
+
 \subsection{Model testing}
+
+We can also study on excluding the model, assuming different true values for oscillation parameters.
+In this example, we present testing the tri-driect littlest seesaw model in various $\theta_{23}$ and $\delta$.
+To do so, we set the true value in oscillation parameters.
+We change values of $\theta_{23}$ and $\delta$ of the true theory, and compute the minimal $\chi^2$ value for the tested model with all four model parameters, free to be varied.
+And, the studied statistics function is exactly Eq.~\ref{eq:chi-squared}, but the true event rate $n_i$ is predicted by a set of oscillation parameters, which will be varied in the code.
+And all four model parameter can be varied with the prior given by Eq.~\ref{eq:prior}.
+
+The example code is given below.
+
+\texttt{ \{ ...  initalize the code ...\}\\
+\{ ...  register the probability engine ...\}    }
+
+\texttt{    
+    float degree   = M\_PI/180;\\
+    float x\_true,eta\_true,r\_true,ma\_true;\\
+    x\_true=-3.65029; eta\_true=1.13067*M\_PI; r\_true=0.511325; ma\_true=3.71199e-3;\\
+    double M\_para[4],OSC\_para[6];\\
+    M\_para[0]=x\_true; M\_para[1]=eta\_true; M\_para[2]=r\_true; M\_para[3]=ma\_true;\\
+    MtoS(OSC\_para, M\_para);\\
+    double th12\_true=OSC\_para[0];\\
+    double th13\_true=OSC\_para[1];\\
+    double th23\_true=OSC\_para[2];\\
+    double dCP\_true=OSC\_para[3];\\
+    double DM21\_true=OSC\_para[4];\\
+    double DM31\_true=OSC\_para[5];\\
+    glb\_params true\_values = glbAllocParams();\\
+    glb\_params test\_values = glbAllocParams();\\
+    glb\_params input\_errors = glbAllocParams();\\
+    glb\_params centers = glbAllocParams();\\
+    \\
+    glbDefineParams(test\_values,x\_true,eta\_true,r\_true,ma\_true,0,0);\\
+    glbSetDensityParams(test\_values,1.0,GLB\_ALL);\\
+    glbDefineParams(true\_values,th12\_true,th13\_true,th23\_true,dCP\_true,DM21\_true,DM31\_true);\\
+    glbSetDensityParams(true\_values,1.0,GLB\_ALL); }
 

### 2020-04-30 doc/FAS-GLoBES.tex
update code and docs

@@
 Here we take tri-direct littlest seesaw as an example to present how we can adopt \textbf{FASE-GLoBES} to constrain two model parameters -- $x$ and $\eta$.
-The $\chi^2$ function is construct based on a log -likelihood ratio,
+The $\chi^2$ function is constructed based on a log-likelihood ratio,
 \begin{equation}\label{eq:chi-squared}
@@
 
-The example code is given below.
-
+The example code is given below.\vspace{0.2cm}\\
 \texttt{ \{ ...  initalize the code ...\}\\
-\{ ...  register the probability engine ...\}    }
-
+\{ ...  register the probability engine ...\}    }\vspace{0.2cm}\\
 \texttt{    
@@
     glbDefineParams(true\_values,th12\_true,th13\_true,th23\_true,dCP\_true,DM21\_true,DM31\_true);\\
-    glbSetDensityParams(true\_values,1.0,GLB\_ALL); }
+    glbSetDensityParams(true\_values,1.0,GLB\_ALL); }\vspace{0.2cm}\\
+\texttt{ \{ ...  set up for prior ...\}}\vspace{0.2cm}\\
+\texttt{
+    float th23,dCP,dth23,ddCP,lower\_th23,upper\_th23,lower\_dCP,upper\_dCP;\\
+    FILE* File=fopen("data/ModelTest\_th23\_dCP\_test.dat", "w");\\
+    lower\_th23=40; upper\_th23=50; lower\_dCP=125; upper\_dCP=392;\\
+    dth23=(upper\_th23-lower\_th23)/100; ddCP=(upper\_dCP-lower\_dCP)/100;\\
+    glbSetProjection(free);\\
+    for (th23=lower\_th23;th23<=upper\_th23;th23=th23+dth23)\{\\
+    for (dCP=lower\_dCP;dCP<=upper\_dCP;dCP=dCP+ddCP)\{\\
+    glbSetOscParams(true\_values,th23*degree,GLB\_THETA\_23);\\
+    glbSetOscParams(true\_values,dCP*degree,GLB\_DELTA\_CP);\\
+    PARA=STAN; \\
+    glbSetOscillationParameters(true\_values);\\
+    glbSetRates();\\
+    PARA=MODEL;\\ 
+        float res=glbChiNP(test\_values,NULL,GLB\_ALL);\\
+            fprintf(File,"\%f \%f \%f $\backslash$n",th23,dCP,gsl\_cdf\_chisq\_Qinv(gsl\_cdf\_chisq\_Q(fabs(res),dof),1));\\
+         \} fprintf(File,"$\backslash$n");\\
+    \}
+}\vspace{0.2cm}\\
+\texttt{ \{ ...  destroy the pointer ...\}}\vspace{0.2cm}\\
+Finally, in the code we adopt Wilk's theorem \cite{Wilks:1938dza}.
+When comparing nested models, the $\Delta \chi^2$ test statistics is a random variable asymptotically distributed according to the $\chi^2$-distribution with the number of degrees of freedom, which is equal to the difference in the number of free model parameters \texttt{dof}.
+Here the number \texttt{dof} is $2$.
+And that is our output: \texttt{gsl\_cdf\_chisq\_Qinv(gsl\_cdf\_chisq\_Q(fabs(res),dof),1)}.
 
@@
 
+We use the same code to analysis the exclusion ability for other oscillation-parameter combinations. Then, we have the results shown in Fig.~\ref{fig:SR_2D}.
+
 \section{Conclusion}

### 2020-04-30 th23_dCP.c

@@ -10,6 +10,7 @@
 #include <complex.h>
 #include <float.h>
 
+/*
 #include <gsl/gsl_complex.h>
 #include <gsl/gsl_complex_math.h>
 #include <gsl/gsl_matrix.h>
@@ -20,8 +21,8 @@
 #include <gsl/gsl_cblas.h>
 #include <gsl/gsl_eigen.h>
 #include <gsl/gsl_vector.h>
-
-
+*/
+#include <gsl/gsl_cdf.h>
 #include <globes/globes.h>   /* GLoBES library */
 #include "FASE_GLoBES.h"
 //#include "model-input_diag.h"
@@ -109,19 +110,20 @@ int main(int argc, char *argv[])
     /*two loops for chi^2(x,eta)*/
     float th23,dCP,dth23,ddCP,lower_th23,upper_th23,lower_dCP,upper_dCP;
     FILE* File=fopen("data/ModelTest_th23_dCP_test.dat", "w");
-    lower_th23=45*degree; upper_th23=50*degree; lower_dCP=1.3*M_PI; upper_dCP=1.8*M_PI;
-    dth23=(upper_th23-lower_th23)/50; ddCP=(upper_dCP-lower_dCP)/50;
+    lower_th23=40; upper_th23=52.5; lower_dCP=125; upper_dCP=395;
+    dth23=(upper_th23-lower_th23)/100; ddCP=(upper_dCP-lower_dCP)/100;
+    int dof=2;
     glbSetProjection(free);
     for (th23=lower_th23;th23<=upper_th23;th23=th23+dth23){
     for (dCP=lower_dCP;dCP<=upper_dCP;dCP=dCP+ddCP){
-    glbSetOscParams(true_values,th23,GLB_THETA_23);
-    glbSetOscParams(true_values,dCP,GLB_DELTA_CP);
+    glbSetOscParams(true_values,th23*degree,GLB_THETA_23);
+    glbSetOscParams(true_values,dCP*degree,GLB_DELTA_CP);
     PARA=STAN; /* if the user is interested in the sensitivity on Standard Oscillation parameters*/
     glbSetOscillationParameters(true_values);
     glbSetRates();
     PARA=MODEL; /* if the user is interested in the sensitivity on Standard Oscillation parameters*/
         float res=glbChiNP(test_values,NULL,GLB_ALL);
-            fprintf(File,"%f %f %f\n",th23,dCP,res);
[…]

### 2020-05-04 doc/FAS-GLoBES.tex
update manual

@@
-\documentclass[a4paper,11pt]{article}
-\pdfoutput=1 % if your are submitting a pdflatex (i.e. if you have
-             % images in pdf, png or jpg format)
+%\documentclass[a4paper,11pt]{article}%JHEP%
+%\pdfoutput=1 % if your are submitting a pdflatex (i.e. if you have
+             % images in pdf, png or jpg format)%JHEP%
 
-\usepackage{jheppub} % for details on the use of the package, please
-                     % see the JHEP-author-manual
+%\usepackage{jheppub} % for details on the use of the package, please
+                     % see the JHEP-author-manual%JHEP%
+
+\documentclass[aps,prd,nofootinbib,preprint]{revtex4}
 
@@
 %\usepackage{textcomp}
+
 %\usepackage{underscore}
-\title{\boldmath  Flavour Symmetry Embedded - GLoBES}
+\usepackage[utf8]{inputenc}
+\usepackage[english]{babel}
 
-% more complex case: 4 authors, 3 institutions, 2 footnotes
-\author[a]{Jian Tang,}
-\author[a]{Tse-Chun Wang}
+\usepackage[nottoc]{tocbibind}
 
-% The "\note" macro will give a warning: "Ignoring empty anchor..."
-% you can safely ignore it.
+\usepackage{hyperref}
+%\usepackage{ulem}
+\usepackage{color}
+\usepackage{graphicx}
+\usepackage{multirow}
+\usepackage{amsmath,amssymb,amsthm,amsxtra,overpic,bbm,bm,float
+,epsfig}
 
-\affiliation[a]{School of Physics, Sun Yat-Sen University, Guangzhou 510275, China}
-%\affiliation[c]{A School for Advanced Studies,\\some-location, Country}
+%JHEP%
+%\title{\boldmath  Flavour Symmetry Embedded - GLoBES (FaSE-GLoBES)}
 
-% e-mail addresses: one for each author, in the same order as the authors
-\emailAdd{tangjian5@mail.sysu.edu.cn}
-\emailAdd{wangzejun@mail.sysu.edu.cn}
+%JHEP%
+%\author[a]{Jian Tang,}
+%\author[a]{Tse-Chun Wang}
+%\affiliation[a]{School of Physics, Sun Yat-Sen University, Guangzhou 510275, China}
+%\emailAdd{tangjian5@mail.sysu.edu.cn}
+%\emailAdd{wangzejun@mail.sysu.edu.cn}
+%\abstract{Abstract...}
 
-\abstract{Abstract...}
+%\fontsize{3}{5}\selectfont
+\begin{document} 
+%\title{The user manual: FlAvour Symmetry with the GLoBES library}
+%\title{FlAvour Symmetry with the GLoBES library}
+\title{The user manual: Flavour Symmetry Embedded - GLoBES (FaSE-GLoBES)} %JHEP%
+%\maketitle %JHEP%
+%\flushbottom %JHEP%
+\author{Jian Tang$^1$\footnote{tangjian5@mail.sysu.edu.cn}}
+\author{Tse-Chun Wang$^1$\footnote{wangzejun@mail.sysu.edu.cn}}
+\affiliation{$^1$School of Physics, Sun Yat-Sen University, Guangzhou 510275, China}
 
-\begin{document} 
+\begin{abstract}
+\textbf{Keywords: Neutrino Oscillations, Leptonic Flavour Symmetry}  
+\end{abstract}
+
 \maketitle
-\flushbottom
 
@@
 
-Currently, some works discuss on how the future experiments can be used for testing these flavour symmetry models in the phenomenological point of view, \textit{e.g.}~\cite{Ballett:2016yod,Chatterjee:2017xkb,Ding:2019zhn,Tang:2019edw}.
+Currently, some works discuss on how the future experiments can be used for testing these flavour symmetry models in the phenomenological point of view, \textit{e.g.}~Ref.~\cite{Ballett:2016yod,Chatterjee:2017xkb,Ding:2019zhn,Tang:2019edw}.
 A large number of these works are based on the \texttt{c}-library -- \textbf{G}eneral \textbf{Lo}ng \textbf{B}aseline \textbf{E}xperiment \textbf{S}imulator (\textbf{GLoBES}) \cite{Huber:2004ka,Huber:2007ji}, which is a convenient simulation tool to simulate neutrino oscillation experiments via the Abstract Experiment Definition Language (AEDL).
-Some AEDL files for experiments are also available on \textbf{GLoBES} website.
-In addition, the working group of DUNE experiment also releases their AEDL files~\cite{Alion:2016uaj}.
+Some AEDL files for experiments are also available on \textbf{GLoBES} website, while the working group of DUNE experiment also releases their AEDL files~\cite{Alion:2016uaj}.
 \textbf{GLoBES} can be taken as one of popular and useful tools in the community of neutrino oscillation physics.
 However, it has not yet to be extended for the purpose of analysing flavour symmetry models.
-
-In this work, we will present our simulation tool \textbf{F}l\textbf{a}vour \textbf{S}ymmetry \textbf{E}mbedded - \textbf{GLoBES} (\textbf{FaSE-GloBES}) that is a simulation code based on GLoBES library and specific for studying the flavour symmetry.
+In this work, we will present our simulation tool \textbf{F}l\textbf{a}vour \textbf{S}ymmetry \textbf{E}mbedded - \textbf{GLoBES} (\textbf{FaSE-GloBES}) that is a simulation code based on GLoBES library for studying the flavour symmetry.
+\textbf{FaSE} is a supplemental tool for GLoBES, written in \texttt{c/c++} language, and FASE-GLoBES allows the user to assign the flavour symmetry model and analysis how a flavour symmetry model can be excluded by the simulated neutrino oscillation experiment.
 
@@
 
-\textbf{F}l\textbf{A}vor \textbf{S}ymmetry \textbf{E}mbedded (\textbf{FASE}) is a supplemental tool for General Long Baseline Experiment Simulator (\textbf{GLoBES}) in order to analysis how a leptonic flavour symmetry model can be tested in neutrino oscillation experiments.
-\textbf{FASE} is written in the \texttt{c/c++} language, and consist with three codes \textbf{FASE\_GLoBES.c}, \textbf{model-input\_diag.c} and \textbf{model-input.c}.
+\textbf{F}l\textbf{a}vor \textbf{S}ymmetry \textbf{E}mbedded (\textbf{FaSE}) is a supplemental tool for General Long Baseline Experiment Simulator (\textbf{GLoBES}) in order to analysis how a leptonic flavour symmetry model can be tested in neutrino oscillation experiments.
+\textbf{FaSE} is written in the \texttt{c/c++} language, and consist with three codes \textbf{FASE\_GLoBES.c}, \textbf{model-input\_diag.c} and \textbf{model-input.c}.
 The user defines the model in to \textbf{model-input\_diag.c} or \textbf{model-input.c}, while \textbf{FASE\_GLoBES.c} does not need to be touched.
@@
 
-The \textbf{FASE-GLoBES} is \textbf{FASE} working with \textbf{GLoBES} as shown in Fig.~\ref{fig:FASE}, in which three parts are shown: 1.~\textbf{the parameter translation} (the blue box), 2.~\textbf{giving oscillation-parameter values} (the green box), and 3.~\textbf{the $\chi^2$-value calculation} (the orange box).
+The concept of \textbf{FaSE-GLoBES} is shown in Fig.~\ref{fig:FASE}, in which three parts are shown: 1.~\textbf{the parameter translation} (the blue box), 2.~\textbf{giving oscillation-parameter values} (the green box), and 3.~\textbf{the $\chi^2$-value calculation} (the orange box).
 The idea behind this flow chart Fig.~\ref{fig:FASE} is that given a set of value for model parameter, the corresponding values for oscillation parameters are obtained by a translation, which is assigned by the user in \textbf{model-input\_diag.c} or \textbf{model-input.c}.
@@
 
-API functions to use \textbf{FASE} are listed:
+API functions to use \textbf{FaSE} are listed:
 \begin{enumerate}
@@
 \end{enumerate}
-The first one is to initialise FASE with the parameter $N_{para}$ the number of input parameters.
+The first one is to initialise \textbf{FaSE} with the parameter $N_{para}$ the number of input parameters.
 The next three functions need to be included to replace the default GLoBES probability engine by the one that can read the output from  \textbf{model-input\_diag.c} or \textbf{model-input.c}, as follows\vspace{0.2cm}\\
@@
 \subsection{Compile and Run}\label{sec:compile}
-As FASE works based on GLoBES, the user should use the \textbf{GLoBES} \texttt{Makefile}, but include the binary file for FASE.
+As \textbf{FaSE} works based on \textbf{GLoBES}, the user should use the \textbf{GLoBES} \texttt{Makefile}, but include the binary file of \textbf{FaSE}.
 To do so, we include the script in the \texttt{Makefile},\vspace{0.2cm}\\
@@
 
-Finally we need to initialize \textbf{FASE} by giving $N_{para}$ which is the number of model parameters. To do so, we need to include the following script in the main code.\\
+Finally we need to initialize \textbf{FaSE} by giving $N_{para}$ which is the number of model parameters. To do so, we need to include the following script in the main code.\\
 \texttt{    MODEL\_init($N_{para}$); }\vspace{0.2cm}\\
@@
 where $x$, $\eta$, $m_a$, and the ratio $r\equiv m_s/m_a$ are four parameters and will be constrained by experimental data.
-We note that from Eq.~(\ref{eq:mnu}), $m_1=0$ and the normal mass ordering are imposed, and will need to be imposed in \textbf{FASE-GLoBES}.
+We note that from Eq.~(\ref{eq:mnu}), $m_1=0$ and the normal mass ordering are imposed, and will need to be imposed in \textbf{FaSE-GLoBES}.
 Therefore, the restrictions in this model are $m_a>0$ and $r>0$.
@@
 
-The user can use \textbf{FASE-GLoBES} to study the constraint of model parameters.
-Here we take tri-direct littlest seesaw as an example to present how we can adopt \textbf{FASE-GLoBES} to constrain two model parameters -- $x$ and $\eta$.
+The user can use \textbf{FaSE-GLoBES} to study the constraint of model parameters.
+Here we take tri-direct littlest seesaw as an example to present how we can adopt \textbf{FaSE-GLoBES} to constrain two model parameters -- $x$ and $\eta$.
 The $\chi^2$ function is constructed based on a log-likelihood ratio,
@@
 
-\section{Conclusion}
+\section{Summary and conclusions}
+
+We have presented \textbf{FaSE}, which is a supplemental simulation tool for \textbf{GLoBES} to study the flavour symmetry with neutrino oscillation experiments.
+\textbf{FaSE} provides \texttt{c}-codes: \textbf{model-input.c} and \textbf{FASE\_GLoBES.c}.
+Shown in Fig.~\ref{fig:FASE}, \textbf{FASE\_GLoBES}, which calls functions in \textbf{model-input.c}, plays a role as a bridge between \textbf{FaSE} and \textbf{GLoBES} to simulate the expected spectra and compute the prior value.
+It can be left to be untouched by users.
+However, all inputs of the user needs to be given in the code \textbf{model-input.c}.
+Given a set of model parameters $\vec{M}$, with \textbf{GLoBES}, the output can be the $\chi^2$ value for the hypothesis $\vec{M}$.
+{\color{red}\texttt{Makefile} is easy to include these two binary files (\textbf{model-input} and \textbf{FASE\_GLoBES}) in the \texttt{makefile} script for \textbf{GLoBES}.
+}
+
+We also present two examples for \textbf{FaSE-GLoBES} with the flavour symmetry model -- tri-direct littlest seesaw (TDLS) -- and the future neutrino oscillaiton experiment -- MOMENT.
+We show the model can be assign in two ways: the relation between model and oscillation parameters or the form of mass matrix in model parameters.
+The input of the oscillation probability and prior value can be in model or oscillation parameters.
+We further demonstrate how to use \textbf{FaSE-GLoBES} to obtain the constraint of any two of model parameters, and to study the ability to TDLS by MOMENT experiment.
+
+Finally, \textbf{GLoBES} is a popular and powerful simulation tool to analysis the neutrino oscillation experiments in a simple language (AEDL), without losing too much detail.
+Considering the success of the flavour symmetry theory to explain the neutrino oscillations, \textbf{FaSE-GLoBES} should benefit model builders of leptonic flavour symmetry and phenomenologists for neutrino oscillation physics.
+We leave the flexibility for the user, and some other improvements and extensions might be done in the future.
 
@@
 \bibliographystyle{JHEP}
+%\bibliographystyle{plain}
 \bibliography{FAS-GLoBES.bib}

### 2020-05-04 doc/paper.tex
upload paper manuscript

--- 2020-05-04 doc/FAS-GLoBES.tex
@@
 %\title{FlAvour Symmetry with the GLoBES library}
-\title{The user manual: Flavour Symmetry Embedded - GLoBES (FaSE-GLoBES)} %JHEP%
+\title{Flavour Symmetry Embedded - GLoBES (FaSE-GLoBES)} %JHEP%
 %\maketitle %JHEP%
@@
 \end{equation*}
-Th neutrino mixing ansatz can be realised by high-energy symmetries $G_f$.
-The symmetry of discrete groups $G_f$, preserved at the high energy but slightly broken at the lower energy, predicts the neutrino mixing, mass-square splittings, and the CP violation phase (Dirac and Majorana phases), with reduced degrees of freedom.
-The symmetries need to be broken at the low energy.
-Otherwise, the flavour of leptons cannot be distinguished.
-There are several approaches for the symmetry breaking, including the direct, indirect, and semi approaches.
-Direct approach preserves the residual symmetries of $G_f$ in the charged-lepton or neutrino sector.
-On the other hand, there is no residual symmetry preserved in neither charged-lepton nor neutrino sector in the indirect approach.
-In the semi approach, the charged-lepton and neutrino sectors preserve different residual symmetries, respectively.
-This symmetry is broken by extending the Higgs sector or introducing the flavons.
-%As a result, these models do not only simplify the theoretical framework for neutrino oscillations, but also provide a theoretical reason for this phenomenon.
-Many of these models can well describe the current neutrino-oscillation data.
-%
-To achieve the $\delta$ prediction, many models are based on a discrete family symmetry $G_f$ together with a non-commuting CP symmetry $H_\mathrm{CP}$.
-Broken in different approaches, the symmetry $G_f\otimes H_\mathrm{CP}$ can predict different patterns for the neutrino mixing.
-For example, in the semi-direct approach, $S_4$ is preserved in the leading order, and leads the bimaximal (MB) or tri-bimaximal (TB) neutrino mixing, while the higher order terms bring the correction to the neutrino mixing.
 
@@
 
-%One of the most predictive flavour-symmetry models is the littlest seesaw model (LSS), which includes two massive right-handed neutrinos: one corresponds to the atmospheric-mass term, while the other is included for the solar-mass term~\cite{King:2013iva,King:2015dvf,King:2016yvg}.
-The littlest seesaw model in the tri-direct approach (TDLS) has been proposed and succeeds in describing the current global-fit results~\cite{Ding:2018fyz,Ding:2018tuj}.
-The tri-direct approach is that after the breaking of the family symmetry $G_f\otimes H_\mathrm{CP}$, three residual symmetries are preserved in different sectors: one in the charged-lepton sector, two in the sectors of right-handed neutrinos for atmospheric and solar mass terms, respectively.
-In this model, four parameters $x$, $\eta$, $r$, $m_a$ are used to describe neutrino oscillations.
-This model has been studied with simulated data at NO$\nu$A, T2K, DUNE, T2HK and JUNO~\cite{Ding:2019zhn}.
-In this work, we study how the next-generation neutrino project using muon-decay beams such as MOMENT can further extend our knowledge on the TDLS model.
-We have two reasons to motivate this study.
-Firstly, TDLS describes the current data successfully and tends to be a nice way to offer neutrino mass terms from theoretical point of view.
-Secondly, it must be straightforward to test the underlying model predictions and compare the performance of MOMENT to the other experiments, \textit{such as} NO$\nu$A, T2K, DUNE, and T2HK.
-
 \section{Overview FASE-GloBES}
@@
 \textbf{F}l\textbf{a}vor \textbf{S}ymmetry \textbf{E}mbedded (\textbf{FaSE}) is a supplemental tool for General Long Baseline Experiment Simulator (\textbf{GLoBES}) in order to analysis how a leptonic flavour symmetry model can be tested in neutrino oscillation experiments.
-\textbf{FaSE} is written in the \texttt{c/c++} language, and consist with three codes \textbf{FASE\_GLoBES.c}, \textbf{model-input\_diag.c} and \textbf{model-input.c}.
-The user defines the model in to \textbf{model-input\_diag.c} or \textbf{model-input.c}, while \textbf{FASE\_GLoBES.c} does not need to be touched.
+\textbf{FaSE} is written in the \texttt{c/c++} language, and consist with three codes \textbf{FASE\_GLoBES.c} and \textbf{model-input.c}.
+The user defines the model in to \textbf{model-input.c}, while \textbf{FASE\_GLoBES.c} does not need to be touched.
 
@@
 The concept of \textbf{FaSE-GLoBES} is shown in Fig.~\ref{fig:FASE}, in which three parts are shown: 1.~\textbf{the parameter translation} (the blue box), 2.~\textbf{giving oscillation-parameter values} (the green box), and 3.~\textbf{the $\chi^2$-value calculation} (the orange box).
-The idea behind this flow chart Fig.~\ref{fig:FASE} is that given a set of value for model parameter, the corresponding values for oscillation parameters are obtained by a translation, which is assigned by the user in \textbf{model-input\_diag.c} or \textbf{model-input.c}.
+The idea behind this flow chart Fig.~\ref{fig:FASE} is that given a set of value for model parameter, the corresponding values for oscillation parameters are obtained by a translation, which is assigned by the user in \textbf{model-input.c}.
 And then, through \textbf{FASE\_GLoBES.c}, these oscillation-parameter values are passed in to \textbf{GLoBES} library to simulate the event spectrum for evaluating the $\chi^2$ value.
@@
 The first one is to initialise \textbf{FaSE} with the parameter $N_{para}$ the number of input parameters.
-The next three functions need to be included to replace the default GLoBES probability engine by the one that can read the output from  \textbf{model-input\_diag.c} or \textbf{model-input.c}, as follows\vspace{0.2cm}\\
+The next three functions need to be included to replace the default GLoBES probability engine by the one that can read the output from \textbf{model-input.c}, as follows\vspace{0.2cm}\\
 \texttt{    glbRegisterProbabilityEngine(6,\\
@@
 
-In the following, we give more details about using \textbf{FASE-GLoBES}.
-In Sec.~\ref{sec:download}, we will give the instruction to download and install \textbf{GLoBES} and \textbf{FASE}.
-Then, in Sec.~\ref{sec:compile}, we will introduce how to compile and run the code.
-More complicated is setting the model, and the way to do this will be described in Sec.~\ref{sec:model_set}.
-Finally, we will discuss how to set up the prior in Sec.~\ref{sec:prior}.
+\section{Model setting}\label{sec:model_set}
 
-\subsection{Download and Installation}\label{sec:download}
-\textbf{download and install GLoBES and FASE-GLoBES}\\
-{\color{red}[will fill in after the code ready on Github]}
+In the function \texttt{MtoS} in \textbf{model-input.c}, the user can assign the relation between the oscillation and model parameter sets, or define the mass matrix in model parameters, which will be diagonalised by the function \texttt{ModelTO} to obtain the corresponding oscillation-parameter values.
+The user needs give the input of \texttt{MtoS} -- a set of model parameters ($\vec{\theta}_{Model}$), and the output is the corresponding oscillation parameter $\vec{\theta}_{OSC.}$, of which components are $\theta_{12}$, $\theta_{13}$, $\theta_{23}$, $\delta$, $\Delta m_{21}^2$, and $\Delta m_{31}^2$.
+These values will be passed in to \textbf{FaSE\_GLoBES} to simulate
+the experimental spectra and compute the prior value.
 
-\subsection{Compile and Run}\label{sec:compile}
-As \textbf{FaSE} works based on \textbf{GLoBES}, the user should use the \textbf{GLoBES} \texttt{Makefile}, but include the binary file of \textbf{FaSE}.
-To do so, we include the script in the \texttt{Makefile},\vspace{0.2cm}\\
-\texttt{\{makefile\_execution\}: my\_program.o  FASE\_GLoBES.o model-input\_diag.o\\
-	gcc my\_program.o  FASE\_GLoBES.o model-input\_diag.o -o my\_executable  \$(LDFLAGS) \$(local\_LDFLAGS)}\\
-or\\
-\texttt{\{makefile\_execution\}: my\_program.o  FASE\_GLoBES.o model-input.o\\
-	gcc my\_program.o  FASE\_GLoBES.o model-input.o -o my\_executable  \$(LDFLAGS) \$(local\_LDFLAGS)}\vspace{0.2cm}\\	
-where \texttt{\{compile\_execusion\}} is the makefile commend for the program \texttt{my\_program.o} and the execution \texttt{my\_executable} is the output.
-After giving this script in the \textbf{GLoBES} \texttt{Makefile}, the user needs to makefile the program \texttt{my\_program} on the terminal.\vspace{0.2cm}\\
-\texttt{makefile \{makefile\_execution\}}\vspace{0.2cm}\\
-And, the user can execute the program by typing the following commend on the terminal.\vspace{0.2cm}\\ 
-\texttt{./my\_executable}\vspace{0.2cm}\\
+The relation between the oscillation and model parameter sets can be derived out by the user, 
+\begin{equation}
+\vec{\theta}_{Model}=\vec{f}(\vec{\theta}_{OSC.})
+\end{equation}
+and give in the function \texttt{MtoS}.
+%
+The oscillation parameters are based on
+\begin{equation}\label{eq:MM}
+U^\dagger\mathcal{M}\mathcal{M}^\dagger U = \mathbf{M}^2,~\text{where}~\mathbf{M}^2_{\alpha\beta}=m_\alpha^2\delta_{\alpha\beta},
+\end{equation}
+where $\mathcal{M}$ ($\mathbf{M}$) is the mass matrix in the flavour (mass) state.
+The matrix $\mathcal{M}$ is given by user with model parameters ($\vec{\theta}_{Model}$).
+The matrix $U$ is the mixing matrix, and can be used for getting mixing angles, and the diagonal elements of $\textbf{M}$ are for the corresponding mass-squared differences.
+The diagnolisation will be done in the function \texttt{ModelTO}, which needs to be called in \texttt{MtoS}.
+The output is the vector of oscillation parameters, of which components are  $\theta_{12}$, $\theta_{13}$, $\theta_{23}$, $\delta$, $\Delta m_{21}^2$, and $\Delta m_{31}^2$.
+For the first four components, values are given in the unit of \textbf{rad}, while the other two are in \textbf{eV$^2$}.
 
-The user can also compile the program without the \textbf{GLoBES} \texttt{Makefile} with the following script.\vspace{0.2cm}\\
-\texttt{gcc my\_program.o FASE\_GLoBES.o model-input\_diag.o -lglobes -LGLB\_DIR/lib/ -o my\_executable}\\
-or\\
-\texttt{gcc my\_program.o FASE\_GLoBES.o model-input.o -lglobes -LGLB\_DIR/lib/ -o my\_executable}\vspace{0.2cm}\\
-And, the execution is also in the same way: \texttt{./my\_executable}.\\
-
-Finally we need to initialize \textbf{FaSE} by giving $N_{para}$ which is the number of model parameters. To do so, we need to include the following script in the main code.\\
-\texttt{    MODEL\_init($N_{para}$); }\vspace{0.2cm}\\
-
-\subsection{Model setting}\label{sec:model_set}
-
-FASE includes three \texttt{c++} files: \textbf{model-input\_diag.c}, \textbf{model-input.c}, and \textbf{FASE\_GLoBES.c}.
-As shown in the previous paragraph, these files are for different service.
-In \textbf{model-input\_diag.c} and \textbf{model-input.c}, the user can assign the relation between the oscillation and model parameter sets.
-The difference between these two code is that in \textbf{model-input.c}, the user give the relation between these two parameter sets directly, while in \textbf{model-input.c}, the mass matrix, which is provided by the user, can be diagonalised to obtain the corresponding oscillation-parameter values.
-
-For different methods to include the model, we use different \texttt{c++} file.
-Adopting the mass matrix expressed by model parameters, we assign this model in \textbf{model-input\_diag.c}.
-In function \texttt{MtoS}, we give
-the mass matrix in the $3\times3$ complex matrix \texttt{Mass\_Matrix[]}.
-%
-Passing the complex matrix \texttt{Mass\_Matrix[]} into the function \texttt{STAN\_OSC}, we will get the corresponding oscillation parameters in an array \texttt{OSC\_PARAMS}, components of which are the value for $\theta_{12}$, $\theta_{13}$, $\theta_{23}$, $\delta$, $\Delta m_{21}^2$, and $\Delta m_{31}^2$.
-The expression of \texttt{Mass\_Matrix[]} is given by the user.
-For the first four components, values are given in the unit of \textbf{rad}, while the other two are in \textbf{eV$^2$}.
-We can also assign the relation between oscillation and model parameters in \textbf{model-input.c}.
-The relations are given in \texttt{MtoS} as well.
-
-\subsection{Prior setting}\label{sec:prior}
-Given a set of values for model parameters, \textbf{FASE\_GLoBES.c} will obtain the corresponding oscillation-parameter values from \textbf{model-input\_diga.c} or \textbf{model-input.c}, and will pass these values to simulate the event spectrum and to give the prior value.
+\section{Prior setting}\label{sec:prior}
+Given a set of values for model parameters, \textbf{FASE\_GLoBES.c} will obtain the corresponding oscillation-parameter values from \textbf{model-input.c}, and will pass these values to simulate the event spectrum and to give the prior value.
 Two gaussian prior functions are provided in \textbf{FASE} -- \texttt{FASE\_prior\_OSC} and \texttt{FASE\_prior\_model}.
@@
  where $\theta_i$ is one of parameters constrained by prior, $\theta^c_i$ ($\sigma_c$) is the central value (Gaussian width) of the prior for $\theta_i$.
-We note that $\theta_i$ can be either model or oscillation parameter.
+We note that $\theta_i$ can be either model ($\vec{\theta}_{Model}$) or oscillation parameters ($\vec{\theta}_{OSC.}$).
  But, oscillation and model parameters can be mixed up together in the using of prior.
@@
 In the function \texttt{model\_restriction}, the user needs to \textit{return $0$} once the restriction is broken.
-For example, if the normal ordering is imposed, we give ``\texttt{ if (DMS31<0) \{ return 1;\} } '' in \texttt{model\_restriction}, where \texttt{DMS31} is for $\Delta m_{31}^2$.
+For example, if the normal ordering is imposed, we give ``\texttt{ if (DMS31<0) \{ return 1;\} } '' in \texttt{model\_restriction}, where \texttt{DMS31} is the variable for $\Delta m_{31}^2$.
 Then, when the restriction is broken, \texttt{model\_restriction} returns the value $1$ to the prior function \texttt{FASE\_prior\_OSC} or \texttt{FASE\_prior\_model}.
-In the following, the prior function will give $10^6$ for the $\chi^2$ value, and it will be selected out when we study the statistically reasonable region in the parameter space.
+In the following, the prior function will give $10^6$ for the $\chi^2$ value, and it will be selected out when the user studies the statistically reasonable region in the parameter space.
 
-\section{Examples}
-\subsection{Setup for a model}
-We now take the littlest seesaw model in the tri-direct approach as an example.
-In this model, the atmospheric and solar flavon vacuum alignments are $\langle\phi_{\text{atm}}\rangle\propto\left(1, \omega^2, \omega\right)^T$ and $\langle\phi_{\text{sol}}\rangle\propto\left(1, x, x\right)^T$,
-where  stands for a cube root of unity and the parameter $x$ is real because of the imposed CP symmetry. Under this model, the light left-handed Majorana neutrino mass matrix is given by
-\begin{equation}
-\label{eq:mnu}  m_{\nu}=m_{a}\begin{pmatrix}
- 1 &~ \omega  &~ \omega ^2 \\
- \omega  &~ \omega ^2 &~ 1 \\
- \omega ^2 &~ 1 &~ \omega  \\
-\end{pmatrix}+e^{i\eta}m_{s}
-\begin{pmatrix}
- 1 &~  x &~  x \\
- x &~ x^2 &~ x^2 \\
- x &~ x^2 &~ x^2 \\
-\end{pmatrix}\,,
-\end{equation}
-where $x$, $\eta$, $m_a$, and the ratio $r\equiv m_s/m_a$ are four parameters and will be constrained by experimental data.
-We note that from Eq.~(\ref{eq:mnu}), $m_1=0$ and the normal mass ordering are imposed, and will need to be imposed in \textbf{FaSE-GLoBES}.
-Therefore, the restrictions in this model are $m_a>0$ and $r>0$.
-
-\begin{table}[h!]
-\caption{\label{tab:TD_parameters}A summary of the relation between oscillation parameters and TDLS model parameters~\cite{Ding:2018fyz}.
-Two requirements are imposed by TDLS: the smallest mass state $m_1=0$ and the normal mass ordering.
-The sign of $\sin\delta$ depends on the sign of $x\cos\psi$: ``$+$'' (``$-$'') is for $x\cos\psi>0$ ($<0$).}
-\begin{tabular}{l|l}
-\hline\hline
-model parameters                                 & $x$, $\eta$, $r$, $m_a$                                                                                                                                                                         \\\hline
-\multirow{6}{*}{combinations of model parameters} & $y=\frac{5x^2+2x+2}{2\left(x^2+x+1\right)}(m_{a}+e^{i \eta } m_{s})$,                                                                                                                            \\
-                                                 & $z=-\frac{\sqrt{5x^2+2x+2}}{2\left(x^2+x+1\right)}\left[ (x+2)m_{a}-x(2x+1)e^{i \eta }m_{s}\right]$,                                                                                             \\
-                                                 & $w=\frac{1}{2(x^2+x+1)}\left[(x+2)^2m_{a}+x^2\left(2x+1\right)^2e^{i \eta } m_{s}\right]$,                                                                                                       \\
-                                                 & $\sin\psi=\frac{\Im\left(y^{*}z+wz^{*}\right)}{|y^{*}z+wz^{*}|},\quad \cos\psi=\frac{\Re\left(y^{*}z+wz^{*}\right)}{|y^{*}z+wz^{*}|}$.
-\\
-                                                 & \begin{tabular}[c]{@{}l@{}}$\sin2\theta=\frac{2|y^{*}z+wz^{*}|} {\sqrt{(|w|^2-|y|^2)^2+4|y^{*}z+wz^{*}|^2}},$\end{tabular}                                                                     \\
-                                                 & $\cos2\theta=\frac{|w|^2-|y|^2}{\sqrt{(|w|^2-|y|^2)^2+4|y^{*}z+wz^{*}|^2}}$.
-\\\hline
-\multirow{7}{*}{oscillation parameters}          & $\Delta m_{21}^2=m^2_2=\frac{1}{2}\left[\left|y\right|^2+\left|w\right|^2+2\left|z\right|^2-\frac{\left|w\right|^2-\left|y\right|^2}{\cos\theta}\right]$,                                        \\
-                                                 & $\Delta m_{31}^2=m^2_3=\frac{1}{2}\left[\left|y\right|^2+\left|w\right|^2+2\left|z\right|^2+\frac{\left|w\right|^2-\left|y\right|^2}{\cos\theta}\right]$,                                        \\
-                                                 & $\sin^2\theta_{12}=1-\frac{3x^2 }{3x^2+2\left(x^2+x+1\right) \cos^2\theta }$,                                                                                                                  \\
-                                                                                                  & $\sin^2\theta_{13}=\frac{2\left(x^2+x+1\right)\sin^2\theta}{5x^2+2x+2}$,                                                                                                                       \\
-                                                 & $\sin^2\theta_{23}=\frac{1}{2}+\frac{x\sqrt{3\left(5x^2+2x+2\right)}\sin2\theta\sin\psi }{2\left[3x^2+2\left(x^2+x+1\right) \cos^ 2 \theta\right]}$,                                          \\
-                                                 & $\cos\delta=\frac{ \cot 2 \theta_{23} \left[3x^2-\left(4x^2+ x+1\right)\cos^2\theta_{13}\right]}{\sqrt{3} \left|x\right| \sin \theta_{13} \sqrt{\left(5x^2+2x+2\right)\cos^2\theta_{13}-3x^2}}$, \\
-                                                 & $\sin\delta= \pm\csc 2 \theta_{23} \sqrt{1+\frac{\left(x^2+x+1\right)^2 \cot ^2\theta_{13} \cos ^22 \theta_{23}}{3x^2 \left[3x^2 \tan ^2\theta_{13}-2 \left(x^2+x+1\right)\right]}}$.
-\\\hline \hline
-\end{tabular}
-\end{table}
-
-\texttt{int MtoS(double OSC\_PARAMS[6],~double M\_para[])}\\
-\texttt{\{}
-\\        
-   \texttt{double x=M\_para[0];}\\
-    \texttt{double eta=M\_para[1];}\\
-    \texttt{double r=M\_para[2];}\\
-    \texttt{double ma=M\_para[3];}\\
-    \texttt{double ms=ma*r;}\\
-
-    \texttt{double complex Mass\_Matrix[] = \{ma+ms*(cos(eta) + I*sin(eta)), ma*(cos(6.6666e-1*M\_PI) + I*sin(6.6666e-1*M\_PI))+x*ms*(cos(eta) + I*sin(eta)), ma*(cos(6.6666e-1*M\_PI) + I*sin(6.6666e-1*M\_PI))*(cos(6.6666e-1*M\_PI) + I*sin(6.6666e-1*M\_PI))+x*ms*(cos(eta) + I*sin(eta)), ma*(cos(6.6666e-1*M\_PI) + I*sin(6.6666e-1*M\_PI))+x*ms*(cos(eta) + I*sin(eta)), ma*(cos(6.6666e-1*M\_PI) + I*sin(6.6666e-1*M\_PI))*(cos(6.6666e-1*M\_PI) + I*sin(6.6666e-1*M\_PI))+x*x*ms*(cos(eta) + I*sin(eta)), ma+x*x*ms*(cos(eta) + I*sin(eta)), ma*(cos(6.6666e-1*M\_PI) + I*sin(6.6666e-1*M\_PI))*(cos(6.6666e-1*M\_PI) + I*sin(6.6666e-1*M\_PI))+x*ms*(cos(eta) + I*sin(eta)), ma+x*x*ms*(cos(eta) + I*sin(eta)), ma*(cos(6.6666e-1*M\_PI) + I*sin(6.6666e-1*M\_PI))+x*x*ms*(cos(eta) + I*sin(eta))\};}\\
-
-    \texttt{STAN\_OSC(Mass\_Matrix,OSC\_PARAMS);}\\
-
-    \texttt{return 0;}\\
-\texttt{\} }
-
-\texttt{double MtoS(double osc\_para[6], double M\_para[])}\\
-\texttt{\{}\\
-    \texttt{/*example: tri-direct*/}\\
-\\    
-    \texttt{double x\_in   = M\_para[0];}\\
-    \texttt{double eta\_in = M\_para[1];}\\
-    \texttt{double r\_in   = M\_para[2];}\\
-    \texttt{double ma\_in  = M\_para[3];}\\
-\\  
-    \texttt{osc\_para[0]=TDth12(x\_in,eta\_in,r\_in, ma\_in);}\\
-    \texttt{osc\_para[1]=TDth13(x\_in,eta\_in,r\_in, ma\_in);}\\
-    \texttt{osc\_para[2]=TDth23(x\_in,eta\_in,r\_in, ma\_in);}\\
-    \texttt{osc\_para[3]=TDdCP(x\_in,eta\_in,r\_in, ma\_in);}\\
-    \texttt{osc\_para[4]=TDdm21(x\_in,eta\_in,r\_in, ma\_in);}\\
-    \texttt{osc\_para[5]=TDdm31(x\_in,eta\_in,r\_in, ma\_in);}\\
-\\    
-    \texttt{return 0;}\\
-\texttt{\}}\\
-
-The functions \texttt{TDth12}, \texttt{TDth13}, \texttt{TDth23}, \texttt{TDdCP}, \texttt{TDdm21}, and \texttt{TDdm31} are included for obtaining the value of $\theta_{12}$, $\theta_{13}$, $\theta_{23}$, $\delta$, $\Delta m_{21}^2$, and $\Delta m_{31}^2$ according to Table~\ref{tab:TD_parameters}, respectively.
-
-The restrictions $m_a>0$ and $r>0$ need to be setup in \texttt{model\_restriction} as follows.\vspace{0.2cm}\\
-\texttt{double model\_restriction(double model [])}\\
-\texttt{\{}\\
-\texttt{    double x=model[0];}\\
-\texttt{    double eta=model[1];}\\
-\texttt{    double r=model[2];}\\
-\texttt{    double ma=model[3];}\\
-    \\
-\texttt{    if(ma<0) \{return 1;\}}\\
-\texttt{    if(r<0) \{return 1;\}}\\
-\\ 
-\texttt{    return 0;}\\
-\}\vspace{0.2cm}\\
-If there is no any restrictions, we simply \textit{return $0$} in \texttt{model\_restriction} as follows.\vspace{0.2cm}\\
-\texttt{double model\_restriction(double model [])\{ return 0;\} }\vspace{0.2cm}\\
-
-\subsection{Initialise the code}
-In the beginning of main code, we need to initialise GLoBES and FASE, and include the considered experiment (here we consider MOMENT experiment) as follows.\vspace{0.2cm}\\ 
-\texttt{glbInit(argv[0]);}\\
-\texttt{glbInitExperiment("expMOMENT\_FIX\_FLUX\_150KM\_addATM\_NC.glb",\&glb\_experiment\_list[0],}\\
-\texttt{\&glb\_num\_of\_exps);}\\
-\texttt{MODEL\_init(4);}\vspace{0.2cm}\\
-Then we register the probability engine.\vspace{0.2cm}\\
-\texttt{glb\_init\_probability\_engine();}\\
-\texttt{glbRegisterProbabilityEngine(6,\\
-                                 \&FASE\_glb\_probability\_matrix,\\
-                                 \&FASE\_glb\_set\_oscillation\_parameters,\\
-                                 \&FASE\_glb\_get\_oscillation\_parameters,\\
-                                 NULL); }\vspace{0.2cm}\\                                 
-In the following we define the model-parameter values, and set the true value in model parameters.\vspace{0.2cm}\\
-\texttt{     float degree   = M\_PI/180;}\\
-\texttt{     float x\_true,eta\_true,r\_true,ma\_true;}\\
-\texttt{    x\_true=-3.65029; eta\_true=1.13067*M\_PI; r\_true=0.511325; ma\_true=3.71199e-3;}\\
-%
-\texttt{glb\_params true\_values = glbAllocParams();}\\
-\texttt{glb\_params test\_values = glbAllocParams();}\\
-\texttt{glb\_params input\_errors  = glbAllocParams();}\\
-\texttt{glb\_params centers         = glbAllocParams();}\\
-\texttt{glbDefineParams(true\_values,x\_true,eta\_true,r\_true,ma\_true,0,0);}\\
-\texttt{    glbSetDensityParams(true\_values,1.0,GLB\_ALL);}\\
-\texttt{glbCopyParams(true\_values,test\_values);}\\
-\texttt{PARA=MODEL;\\
-    glbSetOscillationParameters(true\_values);\\
-    glbSetRates();}\vspace{0.2cm}\\
-We then finally set up the projection.
-The projection \texttt{free} is to set all four parameters free to find the minimal value of $\chi^2$, which \texttt{project} is used for studying the constraint on $x$ and $\eta$.\vspace{0.2cm}\\
-\texttt{glb\_projection projection = glbAllocProjection();\\
-    glb\_projection free = glbAllocProjection();  \\
-     glbDefineProjection(free,GLB\_FREE,GLB\_FREE,GLB\_FREE,GLB\_FREE,GLB\_FIXED,GLB\_FIXED);\\
-    glbSetDensityProjectionFlag(free, GLB\_FREE, GLB\_ALL);\\
-glbDefineProjection(projection,GLB\_FIXED,GLB\_FIXED,GLB\_FREE,GLB\_FREE,GLB\_FIXED,GLB\_FIXED);\\    
-glbSetDensityProjectionFlag(projection, GLB\_FREE, GLB\_ALL);\\
-    }
-
-\subsection{Prior setup}
-
-To set up the prior, we need to register the prior function.
-As mentioned, when we use the prior in oscillation and model parameters, we register \texttt{FASE\_prior\_OSC} and \texttt{FASE\_prior\_model}, respectively.
-Here we present an example setting up priors in oscillation parameters according to NUFIT4.0 Table~\ref{tab:nufit4.0}.
-
-\begin{table}[!h]
-\caption{The best fit and $3\sigma$ uncertainty, in the results of NuFit4.0 \cite{Esteban:2018azc}.}
-\begin{tabular}{|c|c|c|c|c|c|c|}
-\hline
-Parameter & $\theta_{12}/^\circ$ & $\theta_{13}/^\circ$ & $\theta_{23}/^\circ$ & $\delta/^\circ$  & $\Delta m_{21}^2/10^{-5}\text{eV}^2$ & $\Delta m_{31}^2/10^{-3}\text{eV}^2$\\ \hline\hline
-best fit & $33.82$ & $8.61$ & $49.6$ & $215$ & $7.39$ & $2.525$ \\\hline
-$3\sigma$ Range & $31.61-36.27$ & $8.22-8.99$ & $40.3-52.4$ & $125-392$ & $6.79-8.01$ & $2.47-2.625$ \\\hline
-\end{tabular}
-\label{tab:nufit4.0}
-\end{table}
-
-We therefore register \texttt{FASE\_prior\_OSC} for the prior function as follows.\vspace{0.2cm}\\
-\texttt{glbRegisterPriorFunction(FASE\_prior\_OSC,NULL,NULL,NULL); }  \vspace{0.2cm}\\
-And, then we give the value for the central values, and upper and lower Gaussian widths as follows.\vspace{0.2cm}\\
-\texttt{    UPPER\_prior[0]=36.27*degree;  LOWER\_prior[0]=31.61*degree;   Central\_prior[0]=33.82*degree;}\\
-\texttt{    UPPER\_prior[1]=8.99*degree; LOWER\_prior[1]=8.22*degree;  Central\_prior[1]=8.61*degree;}\\
-\texttt{    UPPER\_prior[2]=52.4*degree;  LOWER\_prior[2]=40.3*degree;   Central\_prior[2]=49.6*degree;}\\
-\texttt{    UPPER\_prior[3]=392*degree;  LOWER\_prior[3]=125*degree;   Central\_prior[3]=215*degree;}\\
-\texttt{    UPPER\_prior[4]=8.01e-5;     LOWER\_prior[4]=6.79e-5;      Central\_prior[4]=7.39e-5; }\\
-\texttt{    UPPER\_prior[5]=2.625e-3;     LOWER\_prior[5]=2.427e-3;      Central\_prior[5]=2.525e-3;}\\
-   \\ 
-\texttt{int i;}\\
-\texttt{    for (i=0;i<6;i++) \{UPPER\_prior[i]=fabs(UPPER\_prior[i]-Central\_prior[i])/3; }\\
-\texttt{                       LOWER\_prior[i]=fabs(LOWER\_prior[i]-Central\_prior[i])/3;\} }\\
-\texttt{for (i=0; i<6; i++) glbSetOscParams(centers,0,i);}\\
-\texttt{glbSetDensityParams(centers,1.0,GLB\_ALL);}
-\texttt{glbCopyParams(centers,input\_errors);}\\
-\texttt{    glbSetCentralValues(centers);   glbSetInputErrors(input\_errors);}\vspace{0.2cm}\\
-The parameter \texttt{degree} is defined as $\pi/180$.
-
-\subsection{Constraint of model parameters}
+\section{Constraint of model parameters}
 
@@
 
-\subsection{Model testing}
+\section{Model testing}
 

### 2020-05-04 doc/paper.tex
update paper manuscript

@@
 The user needs give the input of \texttt{MtoS} -- a set of model parameters ($\vec{\theta}_{Model}$), and the output is the corresponding oscillation parameter $\vec{\theta}_{OSC.}$, of which components are $\theta_{12}$, $\theta_{13}$, $\theta_{23}$, $\delta$, $\Delta m_{21}^2$, and $\Delta m_{31}^2$.
+For the first four components, values are given in the unit of \textbf{rad}, while the other two are in \textbf{eV$^2$}.
 These values will be passed in to \textbf{FaSE\_GLoBES} to simulate
@@
 The matrix $\mathcal{M}$ is given by user with model parameters ($\vec{\theta}_{Model}$).
-The matrix $U$ is the mixing matrix, and can be used for getting mixing angles, and the diagonal elements of $\textbf{M}$ are for the corresponding mass-squared differences.
-The diagnolisation will be done in the function \texttt{ModelTO}, which needs to be called in \texttt{MtoS}.
-The output is the vector of oscillation parameters, of which components are  $\theta_{12}$, $\theta_{13}$, $\theta_{23}$, $\delta$, $\Delta m_{21}^2$, and $\Delta m_{31}^2$.
-For the first four components, values are given in the unit of \textbf{rad}, while the other two are in \textbf{eV$^2$}.
+The matrix $U$ is the mixing matrix, and can be used for getting mixing angles, and differences between any two diagonal elements of $\textbf{M}$ are the corresponding mass-squared differences.
+The diagnolisation will be done in the function \texttt{ModelTO}, which needs to be called in \texttt{MtoS} and outputs directly the vector $\vec{\theta}_{OSC.}$.
 
@@
 
-\section{Constraint of model parameters}
+\section{The $\chi^2$ value}
 
@@
 Finally, $\chi^2_{prior}$ is a set of Gaussian priors for hypothesis, and is expressed as Eq.~\ref{eq:prior}.
-To get the constraint of $x$ and $\eta$, we obtain the minimum of $\chi^2$ value,\vspace{0.2cm}\\
-\texttt{
-    glbSetProjection(free);\\
-    float res0=glbChiNP(true\_values,NULL,GLB\_ALL);\\ } \vspace{0.2cm}\\
-%
-Then, we set two loops to get the $\Delta \chi^2$ value for different $x$ and $\eta$\vspace{0.2cm}\\
-%
-\texttt{     float x,eta,r,ma,dx,deta;\\
-     float lower\_x,upper\_x,lower\_eta,upper\_eta;\\
-     FILE* File=fopen("data/constraint\_x\_eta.dat", "w");\\
-    lower\_x=-9; upper\_x=-3; lower\_eta=0.8*M\_PI; upper\_eta=2*M\_PI;\\
-    dx=(upper\_x-lower\_x)/100; deta=(upper\_eta-lower\_eta)/100;\\
-        glbSetProjection(projection);\\
-   for (x=lower\_x;x<=upper\_x;x=x+dx)\{ \\
-    for (eta=lower\_eta;eta<=upper\_eta;eta=eta+deta)\{\\
-     glbSetOscParams(test\_values,x,0); glbSetOscParams(test\_values,eta,1);\\
-        float res=glbChiNP(test\_values,NULL,GLB\_ALL);\\
-            fprintf(File,"\%f \%f  \%f $\backslash$n",x,eta/M\_PI,res-res0);\\
-                     \} fprintf(File,"$\backslash$n");\}\\
-}
+
+\section{Constraint of model parameters}
+
+To get the constraint of $x$ and $\eta$, we obtain the minimum of $\chi^2$ value.\\
 
@@
 
-The example code is given below.\vspace{0.2cm}\\
-\texttt{ \{ ...  initalize the code ...\}\\
-\{ ...  register the probability engine ...\}    }\vspace{0.2cm}\\
-\texttt{    
-    float degree   = M\_PI/180;\\
-    float x\_true,eta\_true,r\_true,ma\_true;\\
-    x\_true=-3.65029; eta\_true=1.13067*M\_PI; r\_true=0.511325; ma\_true=3.71199e-3;\\
-    double M\_para[4],OSC\_para[6];\\
-    M\_para[0]=x\_true; M\_para[1]=eta\_true; M\_para[2]=r\_true; M\_para[3]=ma\_true;\\
-    MtoS(OSC\_para, M\_para);\\
-    double th12\_true=OSC\_para[0];\\
-    double th13\_true=OSC\_para[1];\\
-    double th23\_true=OSC\_para[2];\\
-    double dCP\_true=OSC\_para[3];\\
-    double DM21\_true=OSC\_para[4];\\
-    double DM31\_true=OSC\_para[5];\\
-    glb\_params true\_values = glbAllocParams();\\
-    glb\_params test\_values = glbAllocParams();\\
-    glb\_params input\_errors = glbAllocParams();\\
-    glb\_params centers = glbAllocParams();\\
-    \\
-    glbDefineParams(test\_values,x\_true,eta\_true,r\_true,ma\_true,0,0);\\
-    glbSetDensityParams(test\_values,1.0,GLB\_ALL);\\
-    glbDefineParams(true\_values,th12\_true,th13\_true,th23\_true,dCP\_true,DM21\_true,DM31\_true);\\
-    glbSetDensityParams(true\_values,1.0,GLB\_ALL); }\vspace{0.2cm}\\
-\texttt{ \{ ...  set up for prior ...\}}\vspace{0.2cm}\\
-\texttt{
-    float th23,dCP,dth23,ddCP,lower\_th23,upper\_th23,lower\_dCP,upper\_dCP;\\
-    FILE* File=fopen("data/ModelTest\_th23\_dCP\_test.dat", "w");\\
-    lower\_th23=40; upper\_th23=50; lower\_dCP=125; upper\_dCP=392;\\
-    dth23=(upper\_th23-lower\_th23)/100; ddCP=(upper\_dCP-lower\_dCP)/100;\\
-    glbSetProjection(free);\\
-    for (th23=lower\_th23;th23<=upper\_th23;th23=th23+dth23)\{\\
-    for (dCP=lower\_dCP;dCP<=upper\_dCP;dCP=dCP+ddCP)\{\\
-    glbSetOscParams(true\_values,th23*degree,GLB\_THETA\_23);\\
-    glbSetOscParams(true\_values,dCP*degree,GLB\_DELTA\_CP);\\
-    PARA=STAN; \\
-    glbSetOscillationParameters(true\_values);\\
-    glbSetRates();\\
-    PARA=MODEL;\\ 
-        float res=glbChiNP(test\_values,NULL,GLB\_ALL);\\
-            fprintf(File,"\%f \%f \%f $\backslash$n",th23,dCP,gsl\_cdf\_chisq\_Qinv(gsl\_cdf\_chisq\_Q(fabs(res),dof),1));\\
-         \} fprintf(File,"$\backslash$n");\\
-    \}
-}\vspace{0.2cm}\\
-\texttt{ \{ ...  destroy the pointer ...\}}\vspace{0.2cm}\\
 Finally, in the code we adopt Wilk's theorem \cite{Wilks:1938dza}.

### 2020-05-04 doc/paper.tex
update draft
update paper draft

@@
 %
-The oscillation parameters are based on
+The oscillation parameters are obtained in the way based on
 \begin{equation}\label{eq:MM}
@@
 But, oscillation and model parameters can be mixed up together in the using of prior. 
-
+%
 The values of $\theta^c_i$ and $\sigma_i$ need to be given by the user through three arrays: \texttt{Central\_prior}, \texttt{UPPER\_prior}, and \texttt{LOWER\_prior}, in which there are six components.
@@
 Finally, some restrictions are imposed by the studied flavour symmetry model.
-We set up these restrictions in the function \texttt{model\_restriction}, which is in \texttt{model-input\_diga.c} and \texttt{model-input.c}.
+We set up these restrictions in the function \texttt{model\_restriction}, which is in \texttt{model-input.c}.
 In the function \texttt{model\_restriction}, the user needs to \textit{return $0$} once the restriction is broken.
@@
 
-The user can use \textbf{FaSE-GLoBES} to study the constraint of model parameters.
-Here we take tri-direct littlest seesaw as an example to present how we can adopt \textbf{FaSE-GLoBES} to constrain two model parameters -- $x$ and $\eta$.
-The $\chi^2$ function is constructed based on a log-likelihood ratio,
+The user can use \textbf{FaSE-GLoBES} to study the constraint of model parameters. The $\chi^2$ function is constructed based on a log-likelihood ratio,
 \begin{equation}\label{eq:chi-squared}

### 2020-05-05 doc/paper.tex
update paper draft

@@
 \usepackage{color}
+\usepackage{xcolor}
 \usepackage{graphicx}
@@
 \begin{abstract}
+We present a supplemental tool \textbf{F}l\textbf{a}vour \textbf{S}ymmetry \textbf{E}mbedded (\textbf{FaSE}) for  \textbf{G}eneral \textbf{Lo}ng \textbf{B}aseline \textbf{E}xperiment \textbf{S}imulator (\textbf{GLoBES}).
+\textbf{FaSE}  works with \textbf{GLoBES} (\textbf{FaSE-GLoBES}) to analysis how flavour symmetry models can be examined with simulated neutrino oscillations.
+It can translate the model to oscillation parameters, and provides prior functions, in a user-friendly way.
+We demonstrate two examples for \textbf{FaSE-GLoBE}: how model parameters can be constrained and how a model can be excluded by an experiment.
+Finally, we emphasis as \textbf{GLoBES} is now a popular and power tool for neutrino oscillation physics, \textbf{FaSE} is convenient for flavour-symmetry model builders and neutrino oscillation phenomenologists.\\
 \textbf{Keywords: Neutrino Oscillations, Leptonic Flavour Symmetry}  
@@
 
-\textbf{F}l\textbf{a}vor \textbf{S}ymmetry \textbf{E}mbedded (\textbf{FaSE}) is a supplemental tool for General Long Baseline Experiment Simulator (\textbf{GLoBES}) in order to analysis how a leptonic flavour symmetry model can be tested in neutrino oscillation experiments.
+\textbf{F}l\textbf{a}vor \textbf{S}ymmetry \textbf{E}mbedded (\textbf{FaSE}) is a supplemental tool for \textbf{G}eneral \textbf{Lo}ng \textbf{B}aseline \textbf{E}xperiment \textbf{S}imulator (\textbf{GLoBES}) in order to analysis how a leptonic flavour symmetry model can be tested in neutrino oscillation experiments.
 \textbf{FaSE} is written in the \texttt{c/c++} language, and consist with three codes \textbf{FASE\_GLoBES.c} and \textbf{model-input.c}.
@@
 The idea behind this flow chart Fig.~\ref{fig:FASE} is that given a set of value for model parameter, the corresponding values for oscillation parameters are obtained by a translation, which is assigned by the user in \textbf{model-input.c}.
-And then, through \textbf{FASE\_GLoBES.c}, these oscillation-parameter values are passed in to \textbf{GLoBES} library to simulate the event spectrum for evaluating the $\chi^2$ value.
+And then, through \textbf{FASE\_GLoBES.c} these oscillation-parameter values are passed in to \textbf{GLoBES} library to simulate the event spectrum for evaluating the $\chi^2$ value.
 
-API functions to use \textbf{FaSE} are listed:
+API functions in \textbf{FaSE} are listed:
 \begin{enumerate}
@@
 \end{enumerate}
-The first one is to initialise \textbf{FaSE} with the parameter $N_{para}$ the number of input parameters.
-The next three functions need to be included to replace the default GLoBES probability engine by the one that can read the output from \textbf{model-input.c}, as follows\vspace{0.2cm}\\
+The first one is to initialise \textbf{FaSE} with the number of input parameters $N_{para}$.
+The next three functions need to be included to replace the default \textbf{GLoBES} probability engine by the one that can read the output from \textbf{model-input.c}, as follows.\vspace{0.2cm}\\
 \texttt{    glbRegisterProbabilityEngine(6,\\
@@
                                  NULL); }\vspace{0.2cm}\\ 
-This probability engine can work with the oscillation or model parameter.
+This probability engine can work with oscillation or model parameters.
 It can be set by the user with the parameter \texttt{PARA}.
 If \texttt{PARA=STAN} (\texttt{PARA=MODEL}) the probability engine works with oscillation (model) parameters.
-The final two functions are prior functions.
+The final two items on the API list are prior functions.
 Once the user gives the prior in oscillation (model) parameters, the user needs to call \texttt{FASE\_prior\_OSC} (\texttt{FASE\_prior\_model}) as follows.\vspace{0.2cm}\\
@@
 
-In the function \texttt{MtoS} in \textbf{model-input.c}, the user can assign the relation between the oscillation and model parameter sets, or define the mass matrix in model parameters, which will be diagonalised by the function \texttt{ModelTO} to obtain the corresponding oscillation-parameter values.
-The user needs give the input of \texttt{MtoS} -- a set of model parameters ($\vec{\theta}_{Model}$), and the output is the corresponding oscillation parameter $\vec{\theta}_{OSC.}$, of which components are $\theta_{12}$, $\theta_{13}$, $\theta_{23}$, $\delta$, $\Delta m_{21}^2$, and $\Delta m_{31}^2$.
+The function \texttt{MtoS} can do the translator from model parameters $\vec{\theta}_{Model}$ to oscillation parameters $\vec{\theta}_{OSC.}$.
+After the user gives the array $\vec{\theta}_{Model}$ to the function \texttt{MtoS}, the output is the corresponding oscillation parameter $\vec{\theta}_{OSC.}$, of which components are $\theta_{12}$, $\theta_{13}$, $\theta_{23}$, $\delta$, $\Delta m_{21}^2$, and $\Delta m_{31}^2$.
 For the first four components, values are given in the unit of \textbf{rad}, while the other two are in \textbf{eV$^2$}.
@@
 
-The relation between the oscillation and model parameter sets can be derived out by the user, 
-\begin{equation}
+To do the translation from $\vec{\theta}_{Model}$ to $\vec{\theta}_{OSC.}$, the user can assign the relation between the oscillation and model parameter sets, or define the mass matrix in model parameters, which will be diagonalised by the function \texttt{ModelTO} to obtain the corresponding oscillation-parameter values.
+%The relation between the oscillation and model parameter sets can be derived out by the user, 
+In the way of directly giving the relation between oscillation and model parameter sets, the user needs to provide
+\begin{equation}\label{eq:modelofOSC}
 \vec{\theta}_{Model}=\vec{f}(\vec{\theta}_{OSC.})
 \end{equation}
-and give in the function \texttt{MtoS}.
+ in the function \texttt{MtoS}.
 %
-The oscillation parameters are obtained in the way based on
+
+The oscillation parameters can also be obtained in the way based on
 \begin{equation}\label{eq:MM}
@@
 \end{equation}
-where $\mathcal{M}$ ($\mathbf{M}$) is the mass matrix in the flavour (mass) state.
-The matrix $\mathcal{M}$ is given by user with model parameters ($\vec{\theta}_{Model}$).
-The matrix $U$ is the mixing matrix, and can be used for getting mixing angles, and differences between any two diagonal elements of $\textbf{M}$ are the corresponding mass-squared differences.
-The diagnolisation will be done in the function \texttt{ModelTO}, which needs to be called in \texttt{MtoS} and outputs directly the vector $\vec{\theta}_{OSC.}$.
+where $\mathcal{M}$ ($\mathbf{M}$) is the neutrino mass matrix in the flavour (mass) state.
+The matrix $\mathcal{M}$ is given by user with model parameters $\vec{\theta}_{Model}$.
+The matrix $U$ is the neutrino mixing matrix, and can be used for getting mixing angles.
+The difference between any two diagonal elements of $\textbf{M}$ ($\textbf{M}_{ii}-\textbf{M}_{jj}$) is the mass-squared difference ($\Delta m_{ij}^2$).
+This diagnolisation Eq.~\ref{eq:MM} can be done with the function \texttt{ModelTO}, which needs to be called in \texttt{MtoS} and outputs directly the vector $\vec{\theta}_{OSC.}$.
 
 \section{Prior setting}\label{sec:prior}
-Given a set of values for model parameters, \textbf{FASE\_GLoBES.c} will obtain the corresponding oscillation-parameter values from \textbf{model-input.c}, and will pass these values to simulate the event spectrum and to give the prior value.
-Two gaussian prior functions are provided in \textbf{FASE} -- \texttt{FASE\_prior\_OSC} and \texttt{FASE\_prior\_model}.
+Given a set of values for model parameters, \textbf{FASE\_GLoBES.c} will obtain the corresponding oscillation-parameter values from \textbf{model-input.c}, and will pass these values to simulate event spectra and to compute the prior value.
+Two gaussian prior functions are provided in \textbf{FaSE} -- \texttt{FASE\_prior\_OSC} and \texttt{FASE\_prior\_model}.
 These two functions are for different purposes.
-If the user give the prior in oscillation (model) parameters, the user should register \texttt{FASE\_prior\_OSC} (\texttt{FASE\_prior\_model}) for the prior with the \textbf{GLoBES} function \texttt{glbRegisterPriorFunction}, as we introduced in the beginning of this section.
+If the user give the prior in oscillation (model) parameters, the user should register \texttt{FASE\_prior\_OSC} (\texttt{FASE\_prior\_model}) with the \textbf{GLoBES} function \texttt{glbRegisterPriorFunction}, as we introduced in the beginning of this section.
+The user also needs to assign the parameter \texttt{PARA=STAN} (\texttt{PARA=Model}), when the user prefers to give the prior in oscillation (model) parameters.
 The Gaussian prior is
@@
 \end{equation}
- where $\theta_i$ is one of parameters constrained by prior, $\theta^c_i$ ($\sigma_c$) is the central value (Gaussian width) of the prior for $\theta_i$.
+ where $\theta_i$ is one of parameters constrained by prior, $\theta^c_i$ ($\sigma_i$) is the central value (Gaussian width) of the prior for $\theta_i$.
 We note that $\theta_i$ can be either model ($\vec{\theta}_{Model}$) or oscillation parameters ($\vec{\theta}_{OSC.}$).
-But, oscillation and model parameters can be mixed up together in the using of prior. 
 %
 The values of $\theta^c_i$ and $\sigma_i$ need to be given by the user through three arrays: \texttt{Central\_prior}, \texttt{UPPER\_prior}, and \texttt{LOWER\_prior}, in which there are six components.
-To treat asymmetry of width for the upper and lower Gaussian widths, we give values in two arrays \texttt{UPPER\_prior}, and \texttt{LOWER\_prior}, respectively.
-If the user gives the prior in model parameters, the order of each component follow with the setup of input of the probability engine.
+To treat asymmetry of width for upper ($\theta_i>\theta_i^c$) and lower ($\theta_i<\theta_i^c$) Gaussian widths, we give values in two arrays \texttt{UPPER\_prior}, and \texttt{LOWER\_prior}, respectively.
+If the user gives the prior in model parameters, the order of each component follows with the setup of input of the probability engine.
 While the user gives the prior in oscillation parameters, the six components in order are $\theta_{12}$, $\theta_{13}$, $\theta_{23}$, $\delta$, $\Delta m_{21}^2$, and  $\Delta m_{31}^2$.
@@
 Finally, some restrictions are imposed by the studied flavour symmetry model.
-We set up these restrictions in the function \texttt{model\_restriction}, which is in \texttt{model-input.c}.
-In the function \texttt{model\_restriction}, the user needs to \textit{return $0$} once the restriction is broken.
+We set up these restrictions in the function \texttt{model\_restriction} in \texttt{model-input.c}.
+In the function \texttt{model\_restriction}, the user needs to \textit{return $1$} once the restriction is broken.
 For example, if the normal ordering is imposed, we give ``\texttt{ if (DMS31<0) \{ return 1;\} } '' in \texttt{model\_restriction}, where \texttt{DMS31} is the variable for $\Delta m_{31}^2$.
@@
 
-\section{The $\chi^2$ value}
+\section{The definition for $\chi^2$ (based on \textbf{GLoBES})}
+ {\color{red}CAN BE REMOVED}
 
-The user can use \textbf{FaSE-GLoBES} to study the constraint of model parameters. The $\chi^2$ function is constructed based on a log-likelihood ratio,
+The user can use \textbf{FaSE-GLoBES} to study the constraint of model parameters.
+The expression of $\chi^2$ is used as the default \textbf{GLoBES} setting.
+In more detail, the $\chi^2$ function is constructed based on a log-likelihood ratio,
 \begin{equation}\label{eq:chi-squared}
@@
 \end{equation}
-where $i$ runs over the number of bins, $\eta_i{\vec{\theta},\xi_s,\xi_b}$ is the hypothesis event rate for bin i and $E_i$ is the central bin energy.
-The vector $\vec{\theta}$ consist test model or oscillation parameters.
-Here, $\vec{\theta}=(x,\eta,r,m_a)$.
-The parameters $\xi_s$ and $\xi_b$ are introduced to account for the systematic uncertainty of normalisation for the signal (subscript $_s$) and background (subscript $_b$) components for the event rate, and are allowed to bary in the fit as nuisance parameters.
-For a given hypothesized set of parmaeters $\vec{\theta}$, the event rate for bin $i$ is calculated as\\
+where $i$ runs over the number of bins, $\eta_i(\vec{\theta},\xi_s,\xi_b)$ is the hypothesis event rate for bin i and $E_i$ is the central bin energy.
+The vector $\vec{\theta}$ consists of test model or oscillation parameters.
+The parameters $\xi_s$ and $\xi_b$ are introduced to account for the systematic uncertainty of normalisation for the signal (subscript $_s$) and background (subscript $_b$) components for the event rate, and are allowed to vary in the fit as nuisance parameters.
+For a given hypothesised set of parameters $\vec{\theta}$, the event rate for bin $i$ is calculated as\\
 \begin{equation}
@@
 
-To get the constraint of $x$ and $\eta$, we obtain the minimum of $\chi^2$ value.\\
+\textbf{FaSE-GloBES} can be used to study how the model parameter is constrained by simulated neutrino oscillation experiments.
+We take the tri-direct littlest seesaw (TDLS) model as example.
+Under this model, the light left-handed Majorana neutrino mass matrix is given by
+\begin{equation}
+\label{eq:mnu}  m_{\nu}=m_{a}\begin{pmatrix}
+ 1 &~ \omega  &~ \omega ^2 \\
+ \omega  &~ \omega ^2 &~ 1 \\
+ \omega ^2 &~ 1 &~ \omega  \\
+\end{pmatrix}+e^{i\eta}m_{s}
+\begin{pmatrix}
+ 1 &~  x &~  x \\
+ x &~ x^2 &~ x^2 \\
+ x &~ x^2 &~ x^2 \\
+\end{pmatrix}\,,
+\end{equation}
+where $x$, $\eta$, $m_a$, and the ratio $r\equiv m_s/m_a$ are four parameters and will be constrained by experimental data.
+We note that from Eq.~(\ref{eq:mnu}), $m_1=0$ and the normal mass ordering are imposed, and will need to be imposed in \textbf{FaSE-GLoBES}.
+Therefore, the restrictions in this model are $m_a>0$ and $r>0$.
+%\begin{figure}[!h]
+% \flushleft
+%\hspace{15mm}\includegraphics[width=0.32\textwidth]{figs/x_eta.pdf}$~~~~~~$\\
+%\hspace{15mm} \includegraphics[width=0.32\textwidth]{figs/x_r.pdf}\hspace{-11mm}
+% \includegraphics[width=0.32\textwidth]{figs/eta_r.pdf}$~~~~~~$\\
+%\hspace{15mm} \includegraphics[width=0.32\textwidth]{figs/x_ma.pdf}\hspace{-11mm}
+% \includegraphics[width=0.32\textwidth]{figs/eta_ma.pdf}\hspace{-11mm}
+% \includegraphics[width=0.32\textwidth]{figs/r_ma.pdf}
+% \caption{\label{fig:model_2D}Precision measurements of any two model parameters at 3$\sigma$ confidence level in the framework of three neutrino oscillations taking uncertainties of the current global fit results, for MOMENT, at $1\sigma$ (gray), $2\sigma$ (orange), $3\sigma$ (black).
+True values for the model parameters are used $(x,~\eta,~r,~M_a)=(-3.65,~1.13\pi,~0.511,~3.71~\text{meV})$.}
+%\end{figure}
 
 \begin{figure}[!h]
- \flushleft
-\hspace{15mm}\includegraphics[width=0.32\textwidth]{figs/x_eta.pdf}$~~~~~~$\\
-\hspace{15mm} \includegraphics[width=0.32\textwidth]{figs/x_r.pdf}\hspace{-11mm}
- \includegraphics[width=0.32\textwidth]{figs/eta_r.pdf}$~~~~~~$\\
-\hspace{15mm} \includegraphics[width=0.32\textwidth]{figs/x_ma.pdf}\hspace{-11mm}
- \includegraphics[width=0.32\textwidth]{figs/eta_ma.pdf}\hspace{-11mm}
- \includegraphics[width=0.32\textwidth]{figs/r_ma.pdf}
- \caption{\label{fig:model_2D}Precision measurements of any two model parameters at 3$\sigma$ confidence level in the framework of three neutrino oscillations taking uncertainties of the current global fit results, for MOMENT, at $1\sigma$ (gray), $2\sigma$ (orange), $3\sigma$ (black).
+ %\flushleft
+ \centering
+\hspace{15mm}\includegraphics[width=0.5\textwidth]{figs/x_eta.pdf}
+ \caption{\label{fig:x_eta}Precision measurements of any two model parameters in the framework of three neutrino oscillations taking uncertainties of the current global fit results, for MOMENT, at $1\sigma$ (gray), $2\sigma$ (orange), $3\sigma$ (black).
 True values for the model parameters are used $(x,~\eta,~r,~M_a)=(-3.65,~1.13\pi,~0.511,~3.71~\text{meV})$.}
@@
 
-We use the same code to obtain the constraint of any other combination of two parameters. Then, we can have the result as in Fig.~\ref{fig:model_2D}.
-
-%\texttt{
-%glbFreeParams(true\_values);\\
-%glbFreeParams(test\_values); \\
-%glbFreeParams(input\_errors); \\
-%glbFreeParams(centers);\\
-%glbFreeProjection(free);\\
-%glbFreeProjection(projection);\\
-%}
+In Fig.~\ref{fig:x_eta}, we study how parameters $x$ and $\eta$ can be constrained by the MuOn-decay MEdium baseline NeuTrino beam experiment (MOMENT).
+We input the model by giving model parameters as functions of oscillation parameters Eq.~\ref{eq:modelofOSC}.
+And, parameters $r$ and $ma$ are varied with the prior that is given in oscillation parameters, according to the global-fit result NUFIT4.0.
+More details are presented in the user manual.
+The code for this example is provided as \textbf{x\_eta.c} in the \textbf{FaSE} distribution.
 
@@
 
+\begin{figure}[!h]
+ \centering
+\includegraphics[width=0.5\textwidth]{figs/SR_th23_dCP.pdf}
+\caption{\label{fig:th23_delta}The 2-D exclusion contour for tri-direct littlest seesaw model on the plane of two true standard parameters $\theta_{23}$ and $\delta$, from $1\sigma$ to $5\sigma$.
+The range for each parameter is taken according to the $3\sigma$ uncertainty in NuFit4.0 results.
+The black dot denotes the best fit of NuFit4.0 results ($(\theta_{12},~\theta_{13},~\theta_{23},~\delta,~\Delta m_{21}^2,~\Delta m_{31}^2)=(33.82^\circ,~8.61^\circ,~49.6^\circ,~215^\circ,~7.39\times10^{-5}~\text{eV}^2,~2.525\times10^{-3}~\text{eV}^2)$), while the star is the prediction by the tri-direct littlest seesaw model with NuFit4.0 results ($(\theta_{12},~\theta_{13},~\theta_{23},~\delta,~\Delta m_{21}^2,~\Delta m_{31}^2)\sim(36.25^\circ,~8.63^\circ,~47^\circ,~279^\circ,~7.39\times10^{-5}~\text{eV}^2,~2.525\times10^{-3}~\text{eV}^2)$).}
+\end{figure}
+
 We can also study on excluding the model, assuming different true values for oscillation parameters.
-In this example, we present testing the tri-driect littlest seesaw model in various $\theta_{23}$ and $\delta$.
-To do so, we set the true value in oscillation parameters.
-We change values of $\theta_{23}$ and $\delta$ of the true theory, and compute the minimal $\chi^2$ value for the tested model with all four model parameters, free to be varied.
+In this example, we present testing the TDLS model in various true values of $\theta_{23}$ and $\delta$.
+We compute the minimal $\chi^2$ value for the tested model with all four model parameters, varied with the prior Eq.~\ref{eq:prior} according to NUFIT4.0 result.
 And, the studied statistics function is exactly Eq.~\ref{eq:chi-squared}, but the true event rate $n_i$ is predicted by a set of oscillation parameters, which will be varied in the code.
-And all four model parameter can be varied with the prior given by Eq.~\ref{eq:prior}.
 
@@
 And that is our output: \texttt{gsl\_cdf\_chisq\_Qinv(gsl\_cdf\_chisq\_Q(fabs(res),dof),1)}.
+We use the same code to analysis the exclusion ability for other oscillation-parameter combinations.
+Then, we have the results shown in Fig.~\ref{fig:th23_delta}.
+More details are presented in the user manual.
+The code for this example is provided as \textbf{th23\_delta.c} in the \textbf{FaSE} distribution.
 
-\begin{figure}[!h]
- \flushleft
+%\begin{figure}[!h]
+ %\flushleft
 %
-\includegraphics[width=0.32\textwidth]{figs/SR_th13_th23.pdf}$~~~~~~$\\
-\includegraphics[width=0.32\textwidth]{figs/SR_th13_dCP.pdf}
-\includegraphics[width=0.32\textwidth]{figs/SR_th23_dCP.pdf}$~~~~~~$\\
-\includegraphics[width=0.32\textwidth]{figs/SR_th13_ldm.pdf}
-\includegraphics[width=0.32\textwidth]{figs/SR_th23_ldm.pdf}
-\includegraphics[width=0.32\textwidth]{figs/SR_dCP_ldm.pdf}
- \caption{\label{fig:SR_2D}The 2-D exclusion contour for tri-direct littlest seesaw model on the plane of any two true standard parameters, from $1\sigma$ to $5\sigma$.
+%\includegraphics[width=0.32\textwidth]{figs/SR_th13_th23.pdf}$~~~~~~$\\
+%\includegraphics[width=0.32\textwidth]{figs/SR_th13_dCP.pdf}
+%\includegraphics[width=0.32\textwidth]{figs/SR_th23_dCP.pdf}$~~~~~~$\\
+%\includegraphics[width=0.32\textwidth]{figs/SR_th13_ldm.pdf}
+%\includegraphics[width=0.32\textwidth]{figs/SR_th23_ldm.pdf}
+%\includegraphics[width=0.32\textwidth]{figs/SR_dCP_ldm.pdf}
+ %\caption{\label{fig:SR_2D}The 2-D exclusion contour for tri-direct littlest seesaw model on the plane of any two true standard parameters, from $1\sigma$ to $5\sigma$.
 The range for each parameter is taken according to the $3\sigma$ uncertainty in NuFit4.0 results.
 The black dot denotes the best fit of NuFit4.0 results ($(\theta_{12},~\theta_{13},~\theta_{23},~\delta,~\Delta m_{21}^2,~\Delta m_{31}^2)=(33.82^\circ,~8.61^\circ,~49.6^\circ,~215^\circ,~7.39\times10^{-5}~\text{eV}^2,~2.525\times10^{-3}~\text{eV}^2)$), while the star is the prediction by the tri-direct littlest seesaw model with NuFit4.0 results ($(\theta_{12},~\theta_{13},~\theta_{23},~\delta,~\Delta m_{21}^2,~\Delta m_{31}^2)\sim(36.25^\circ,~8.63^\circ,~47^\circ,~279^\circ,~7.39\times10^{-5}~\text{eV}^2,~2.525\times10^{-3}~\text{eV}^2)$).}
-\end{figure}
-
-We use the same code to analysis the exclusion ability for other oscillation-parameter combinations. Then, we have the results shown in Fig.~\ref{fig:SR_2D}.
+%\end{figure}
 
@@
 However, all inputs of the user needs to be given in the code \textbf{model-input.c}.
-Given a set of model parameters $\vec{M}$, with \textbf{GLoBES}, the output can be the $\chi^2$ value for the hypothesis $\vec{M}$.
-{\color{red}\texttt{Makefile} is easy to include these two binary files (\textbf{model-input} and \textbf{FASE\_GLoBES}) in the \texttt{makefile} script for \textbf{GLoBES}.
-}
+Given a set of model parameters $\vec{\theta}_{Model}$, with \textbf{GLoBES}, the output can be the $\chi^2$ value for the hypothesis $\vec{\theta}_{Model}$.
+%{\color{red}\texttt{Makefile} is easy to include these two binary files (\textbf{model-input} and \textbf{FASE\_GLoBES}) in the \texttt{makefile} script for \textbf{GLoBES}. }
 

### 2020-05-06 doc/FAS-GLoBES.tex
update doc

@@
 %\title{FlAvour Symmetry with the GLoBES library}
-\title{The user manual: Flavour Symmetry Embedded - GLoBES (FaSE-GLoBES)} %JHEP%
+\title{\Large The user manual: Flavour Symmetry Embedded - GLoBES (FaSE-GLoBES)} %JHEP%
 %\maketitle %JHEP%
@@
 
-\begin{abstract}
-\textbf{Keywords: Neutrino Oscillations, Leptonic Flavour Symmetry}  
-\end{abstract}
+%\begin{abstract}
+%\textbf{Keywords: Neutrino Oscillations, Leptonic Flavour Symmetry}  
+%\end{abstract}
 
@@
 
-\textbf{F}l\textbf{a}vor \textbf{S}ymmetry \textbf{E}mbedded (\textbf{FaSE}) is a supplemental tool for General Long Baseline Experiment Simulator (\textbf{GLoBES}) in order to analysis how a leptonic flavour symmetry model can be tested in neutrino oscillation experiments.
-\textbf{FaSE} is written in the \texttt{c/c++} language, and consist with three codes \textbf{FASE\_GLoBES.c}, \textbf{model-input\_diag.c} and \textbf{model-input.c}.
-The user defines the model in to \textbf{model-input\_diag.c} or \textbf{model-input.c}, while \textbf{FASE\_GLoBES.c} does not need to be touched.
+\textbf{F}l\textbf{a}vor \textbf{S}ymmetry \textbf{E}mbedded (\textbf{FaSE}) is a supplemental tool for \textbf{G}eneral \textbf{Lo}ng \textbf{B}aseline \textbf{E}xperiment \textbf{S}imulator (\textbf{GLoBES}) in order to analysis how a leptonic flavour symmetry model can be tested in neutrino oscillation experiments.
+\textbf{FaSE} is written in the \texttt{c/c++} language, and consist with three codes \textbf{FASE\_GLoBES.c} and \textbf{model-input.c}.
+The user defines the model in to \textbf{model-input.c}, while \textbf{FASE\_GLoBES.c} does not need to be touched.
 
@@
 The concept of \textbf{FaSE-GLoBES} is shown in Fig.~\ref{fig:FASE}, in which three parts are shown: 1.~\textbf{the parameter translation} (the blue box), 2.~\textbf{giving oscillation-parameter values} (the green box), and 3.~\textbf{the $\chi^2$-value calculation} (the orange box).
-The idea behind this flow chart Fig.~\ref{fig:FASE} is that given a set of value for model parameter, the corresponding values for oscillation parameters are obtained by a translation, which is assigned by the user in \textbf{model-input\_diag.c} or \textbf{model-input.c}.
-And then, through \textbf{FASE\_GLoBES.c}, these oscillation-parameter values are passed in to \textbf{GLoBES} library to simulate the event spectrum for evaluating the $\chi^2$ value.
+The idea behind this flow chart Fig.~\ref{fig:FASE} is that given a set of value for model parameter, the corresponding values for oscillation parameters are obtained by a translation, which is assigned by the user in \textbf{model-input.c}.
+And then, through \textbf{FASE\_GLoBES.c} these oscillation-parameter values are passed in to \textbf{GLoBES} library to simulate the event spectrum for evaluating the $\chi^2$ value.
 
-API functions to use \textbf{FaSE} are listed:
+API functions in \textbf{FaSE} are listed:
 \begin{enumerate}
@@
 \end{enumerate}
-The first one is to initialise \textbf{FaSE} with the parameter $N_{para}$ the number of input parameters.
-The next three functions need to be included to replace the default GLoBES probability engine by the one that can read the output from  \textbf{model-input\_diag.c} or \textbf{model-input.c}, as follows\vspace{0.2cm}\\
+The first one is to initialise \textbf{FaSE} with the number of input parameters $N_{para}$.
+The next three functions need to be included to replace the default \textbf{GLoBES} probability engine by the one that can read the output from \textbf{model-input.c}, as follows.\vspace{0.2cm}\\
 \texttt{    glbRegisterProbabilityEngine(6,\\
@@
 
-FASE includes three \texttt{c++} files: \textbf{model-input\_diag.c}, \textbf{model-input.c}, and \textbf{FASE\_GLoBES.c}.
-As shown in the previous paragraph, these files are for different service.
-In \textbf{model-input\_diag.c} and \textbf{model-input.c}, the user can assign the relation between the oscillation and model parameter sets.
-The difference between these two code is that in \textbf{model-input.c}, the user give the relation between these two parameter sets directly, while in \textbf{model-input.c}, the mass matrix, which is provided by the user, can be diagonalised to obtain the corresponding oscillation-parameter values.
+The function \texttt{MtoS} can do the translator from model parameters $\vec{\theta}_{Model}$ to oscillation parameters $\vec{\theta}_{OSC.}$.
+After the user gives the array $\vec{\theta}_{Model}$ to the function \texttt{MtoS}, the output is the corresponding oscillation parameter $\vec{\theta}_{OSC.}$, of which components are $\theta_{12}$, $\theta_{13}$, $\theta_{23}$, $\delta$, $\Delta m_{21}^2$, and $\Delta m_{31}^2$.
+For the first four components, values are given in the unit of \textbf{rad}, while the other two are in \textbf{eV$^2$}.
+These values will be passed in to \textbf{FaSE\_GLoBES} to simulate
+the experimental spectra and compute the prior value.
 
-For different methods to include the model, we use different \texttt{c++} file.
-Adopting the mass matrix expressed by model parameters, we assign this model in \textbf{model-input\_diag.c}.
-In function \texttt{MtoS}, we give
-the mass matrix in the $3\times3$ complex matrix \texttt{Mass\_Matrix[]}.
+To do the translation from $\vec{\theta}_{Model}$ to $\vec{\theta}_{OSC.}$, the user can assign the relation between the oscillation and model parameter sets, or define the mass matrix in model parameters, which will be diagonalised by the function \texttt{ModelTO} to obtain the corresponding oscillation-parameter values.
+%The relation between the oscillation and model parameter sets can be derived out by the user, 
+In the way of directly giving the relation between oscillation and model parameter sets, the user needs to provide
+\begin{equation}\label{eq:modelofOSC}
+\vec{\theta}_{Model}=\vec{f}(\vec{\theta}_{OSC.})
+\end{equation}
+ in the function \texttt{MtoS}.
 %
-Passing the complex matrix \texttt{Mass\_Matrix[]} into the function \texttt{STAN\_OSC}, we will get the corresponding oscillation parameters in an array \texttt{OSC\_PARAMS}, components of which are the value for $\theta_{12}$, $\theta_{13}$, $\theta_{23}$, $\delta$, $\Delta m_{21}^2$, and $\Delta m_{31}^2$.
-The expression of \texttt{Mass\_Matrix[]} is given by the user.
-For the first four components, values are given in the unit of \textbf{rad}, while the other two are in \textbf{eV$^2$}.
-We can also assign the relation between oscillation and model parameters in \textbf{model-input.c}.
-The relations are given in \texttt{MtoS} as well.
+
+The oscillation parameters can also be obtained in the way based on
+\begin{equation}\label{eq:MM}
+U^\dagger\mathcal{M}\mathcal{M}^\dagger U = \mathbf{M}^2,~\text{where}~\mathbf{M}^2_{\alpha\beta}=m_\alpha^2\delta_{\alpha\beta},
+\end{equation}
+where $\mathcal{M}$ ($\mathbf{M}$) is the neutrino mass matrix in the flavour (mass) state.
+The matrix $\mathcal{M}$ is given by user with model parameters $\vec{\theta}_{Model}$.
+The matrix $U$ is the neutrino mixing matrix, and can be used for getting mixing angles.
+The difference between any two diagonal elements of $\textbf{M}$ ($\textbf{M}_{ii}-\textbf{M}_{jj}$) is the mass-squared difference ($\Delta m_{ij}^2$).
+This diagnolisation Eq.~\ref{eq:MM} can be done with the function \texttt{ModelTO}, which needs to be called in \texttt{MtoS} and outputs directly the vector $\vec{\theta}_{OSC.}$.
 
 \subsection{Prior setting}\label{sec:prior}
-Given a set of values for model parameters, \textbf{FASE\_GLoBES.c} will obtain the corresponding oscillation-parameter values from \textbf{model-input\_diga.c} or \textbf{model-input.c}, and will pass these values to simulate the event spectrum and to give the prior value.
-Two gaussian prior functions are provided in \textbf{FASE} -- \texttt{FASE\_prior\_OSC} and \texttt{FASE\_prior\_model}.
+Given a set of values for model parameters, \textbf{FASE\_GLoBES.c} will obtain the corresponding oscillation-parameter values from \textbf{model-input.c}, and will pass these values to simulate event spectra and to compute the prior value.
+Two gaussian prior functions are provided in \textbf{FaSE} -- \texttt{FASE\_prior\_OSC} and \texttt{FASE\_prior\_model}.
 These two functions are for different purposes.
-If the user give the prior in oscillation (model) parameters, the user should register \texttt{FASE\_prior\_OSC} (\texttt{FASE\_prior\_model}) for the prior with the \textbf{GLoBES} function \texttt{glbRegisterPriorFunction}, as we introduced in the beginning of this section.
+If the user give the prior in oscillation (model) parameters, the user should register \texttt{FASE\_prior\_OSC} (\texttt{FASE\_prior\_model}) with the \textbf{GLoBES} function \texttt{glbRegisterPriorFunction}, as we introduced in the beginning of this section.
+The user also needs to assign the parameter \texttt{PARA=STAN} (\texttt{PARA=Model}), when the user prefers to give the prior in oscillation (model) parameters.
 The Gaussian prior is
@@
 \end{equation}
- where $\theta_i$ is one of parameters constrained by prior, $\theta^c_i$ ($\sigma_c$) is the central value (Gaussian width) of the prior for $\theta_i$.
-We note that $\theta_i$ can be either model or oscillation parameter.
- But, oscillation and model parameters can be mixed up together in the using of prior.
-
+ where $\theta_i$ is one of parameters constrained by prior, $\theta^c_i$ ($\sigma_i$) is the central value (Gaussian width) of the prior for $\theta_i$.
+We note that $\theta_i$ can be either model ($\vec{\theta}_{Model}$) or oscillation parameters ($\vec{\theta}_{OSC.}$).
+%
 The values of $\theta^c_i$ and $\sigma_i$ need to be given by the user through three arrays: \texttt{Central\_prior}, \texttt{UPPER\_prior}, and \texttt{LOWER\_prior}, in which there are six components.
-To treat asymmetry of width for the upper and lower Gaussian widths, we give values in two arrays \texttt{UPPER\_prior}, and \texttt{LOWER\_prior}, respectively.
-If the user gives the prior in model parameters, the order of each component follow with the setup of input of the probability engine.
+To treat asymmetry of width for upper ($\theta_i>\theta_i^c$) and lower ($\theta_i<\theta_i^c$) Gaussian widths, we give values in two arrays \texttt{UPPER\_prior}, and \texttt{LOWER\_prior}, respectively.
+If the user gives the prior in model parameters, the order of each component follows with the setup of input of the probability engine.
 While the user gives the prior in oscillation parameters, the six components in order are $\theta_{12}$, $\theta_{13}$, $\theta_{23}$, $\delta$, $\Delta m_{21}^2$, and  $\Delta m_{31}^2$.
@@
 Finally, some restrictions are imposed by the studied flavour symmetry model.
-We set up these restrictions in the function \texttt{model\_restriction}, which is in \texttt{model-input\_diga.c} and \texttt{model-input.c}.
-In the function \texttt{model\_restriction}, the user needs to \textit{return $0$} once the restriction is broken.
-For example, if the normal ordering is imposed, we give ``\texttt{ if (DMS31<0) \{ return 1;\} } '' in \texttt{model\_restriction}, where \texttt{DMS31} is for $\Delta m_{31}^2$.
+We set up these restrictions in the function \texttt{model\_restriction} in \texttt{model-input.c}.
+In the function \texttt{model\_restriction}, the user needs to \textit{return $1$} once the restriction is broken.
+For example, if the normal ordering is imposed, we give ``\texttt{ if (DMS31<0) \{ return 1;\} } '' in \texttt{model\_restriction}, where \texttt{DMS31} is the variable for $\Delta m_{31}^2$.
 Then, when the restriction is broken, \texttt{model\_restriction} returns the value $1$ to the prior function \texttt{FASE\_prior\_OSC} or \texttt{FASE\_prior\_model}.
-In the following, the prior function will give $10^6$ for the $\chi^2$ value, and it will be selected out when we study the statistically reasonable region in the parameter space.
+%In the following, the prior function will give $10^6$ for the $\chi^2$ value, and it will be selected out when the user studies the statistically reasonable region in the parameter space.
 
@@
 The user can use \textbf{FaSE-GLoBES} to study the constraint of model parameters.
-Here we take tri-direct littlest seesaw as an example to present how we can adopt \textbf{FaSE-GLoBES} to constrain two model parameters -- $x$ and $\eta$.
-The $\chi^2$ function is constructed based on a log-likelihood ratio,
+The expression of $\chi^2$ is used as the default \textbf{GLoBES} setting.
+In more detail, the $\chi^2$ function is constructed based on a log-likelihood ratio,
 \begin{equation}\label{eq:chi-squared}
@@
 Finally, $\chi^2_{prior}$ is a set of Gaussian priors for hypothesis, and is expressed as Eq.~\ref{eq:prior}.
+After doing all minimisations, the user obtain the $\chi^2$ value for a specific hypothesis $\vec{\theta}^{hyp.}$, $\chi^2(\vec{\theta}^{hyp.})$.
+
+The user of \textbf{FaSE-GLoBES} is able to study how model parameters can be constrained by the simulated experiment.
+To do so, the user needs to define the true event spectrum $n_i$ with a set of model or oscillation parameters, \textit{i.e.}~$n_i(\vec{\theta}_{Model}^{true})$ or $n_i(\vec{\theta}_{OSC.}^{true})$.
+The hypothesis $\vec{\theta}_{Model}^{hyp.}$ predicts the tested event spectrum $\eta_i(\vec{\theta}_{Model}^{hyp.},\xi_s,\xi_b)$.
+With the default setting for $\chi^2$ function Eq.~\ref{eq:prior}, from \textbf{FaSE-GLoBES} the user computes the statistical quantity,
+\begin{equation}\label{eq:chi_model}
+\chi^2(\vec{\theta}_{Model}^{hyp.}),~~\text{with}~n_i(\vec{\theta}_{Model}^{true})~\text{or}~n_i(\vec{\theta}_{OSC.}^{true}).
+\end{equation}
+%
+We note that the minimum of $\chi^2$ in the whole parameter space ($\chi^2_{min.}$) may not be $0$.
+Therefore, to study the precision of model parameters, the user should use the value $\Delta\chi^2(\vec{\theta}_{Model}^{hyp.})\equiv \chi^2(\vec{\theta}_{Model}^{hyp.})-\chi^2_{min.}$, instead of $\chi^2$ itself.
+By varying different hypothesis $\vec{\theta}_{Model}^{hyp.}$, the user can obtain the allowed region of model parameters with the statistical quantity $\Delta\chi^2(\vec{\theta}_{Model}^{hyp.})$.
+
 To get the constraint of $x$ and $\eta$, we obtain the minimum of $\chi^2$ value,\vspace{0.2cm}\\
@@
 \subsection{Model testing}
+
+The user can also study how well a flavour symmetry model explains the computed data as predicting how the simulated experiment can exclude this model.
+In the other word, the user studies the minimum of $\chi^2$ for the flavour symmetry model $\vec{\theta}_{Model}$ as a hypothesis, assuming different true oscillation values, \textit{i.e.}~different $\vec{\theta}^{true}_{OSC}$.
+To do so, we compute the same statistical quantity Eq.~\ref{eq:chi_model}, while the true spectrum is varied with different true values $\vec{\theta}_{OSC}^{true}$.
+All model parameters are allowed to be varied with the user-defined prior.
+%
+Finally, the user needs to adopt Wilk's theorem \cite{Wilks:1938dza}.
+When comparing nested models, the $\Delta \chi^2$ test statistics is a random variable asymptotically distributed according to the $\chi^2$-distribution with the number of degrees of freedom, which is equal to the difference in the number of free model parameters \texttt{dof}.
 

### 2020-05-06 doc/paper.tex
update doc

@@
 Then, when the restriction is broken, \texttt{model\_restriction} returns the value $1$ to the prior function \texttt{FASE\_prior\_OSC} or \texttt{FASE\_prior\_model}.
-In the following, the prior function will give $10^6$ for the $\chi^2$ value, and it will be selected out when the user studies the statistically reasonable region in the parameter space.
+%In the following, the prior function will give $10^6$ for the $\chi^2$ value, and it will be selected out when the user studies the statistically reasonable region in the parameter space.
 
-\section{The definition for $\chi^2$ (based on \textbf{GLoBES})}
- {\color{red}CAN BE REMOVED}
+\section{The definition for $\chi^2$ (based on \textbf{GLoBES})}\label{sec:chi-squared}
+% {\color{red}CAN BE REMOVED}
 
@@
 \begin{equation}\label{eq:chi-squared}
-\chi^2(\vec{\theta},\xi_s,\xi_b)=2\sum_i\left(\eta_i(\vec{\theta},\xi_s,\xi_b)-n_i+n_i\ln\frac{n_i}{\eta_i(\vec{\theta},\xi_s,\xi_b)} \right)+p(\xi_s,\sigma_s)+p(\xi_b,\sigma_b)+\chi^2_{prior},
+\chi^2(\vec{\theta}^{hyp.},\xi_s,\xi_b)=2\sum_i\left(\eta_i(\vec{\theta}^{hyp.},\xi_s,\xi_b)-n_i+n_i\ln\frac{n_i}{\eta_i(\vec{\theta}^{hyp.},\xi_s,\xi_b)} \right)+p(\xi_s,\sigma_s)+p(\xi_b,\sigma_b)+\chi^2_{prior},
 \end{equation}
@@
 \begin{equation}
-\eta_i(\vec{\theta},\xi_s,\xi_b)=(1+\xi_s)\times n_i+(1+\xi_b)\times b_i,
+\eta_i(\vec{\theta}^{hyp.},\xi_s,\xi_b)=(1+\xi_s)\times s_i+(1+\xi_b)\times b_i,
 \end{equation}
-where $n_i$ and $b_i$ are the expected number of signal and background events in bin $i$, respectively.
+where $s_i$ and $b_i$ are the expected number of signal and background events in bin $i$, respectively.
 The nuisance parameters are constrained by the Gaussian prior $p(\xi,\sigma)=\xi^2/\sigma^2$ with corresponding uncertainties $\sigma_s$ and $\sigma_b$ for the signal and background, respectively.
 Finally, $\chi^2_{prior}$ is a set of Gaussian priors for hypothesis, and is expressed as Eq.~\ref{eq:prior}.
+After doing all minimisations, the user obtain the $\chi^2$ value for a specific hypothesis $\vec{\theta}^{hyp.}$, $\chi^2(\vec{\theta}^{hyp.})$.
+
+Based on the $\chi^2$ value Eq.~\ref{eq:chi-squared}, we can study how model parameters can be constrained and how a flavour-symmetry model can be tested by simulated experiments.
+In the following we will introduce how it works.
+
+\subsection*{Applications}
+
+The user of \textbf{FaSE-GLoBES} is able to study how model parameters can be constrained by the simulated experiment.
+To do so, the user needs to define the true event spectrum $n_i$ with a set of model or oscillation parameters, \textit{i.e.}~$n_i(\vec{\theta}_{Model}^{true})$ or $n_i(\vec{\theta}_{OSC.}^{true})$.
+The hypothesis $\vec{\theta}_{Model}^{hyp.}$ predicts the tested event spectrum $\eta_i(\vec{\theta}_{Model}^{hyp.},\xi_s,\xi_b)$.
+With the default setting for $\chi^2$ function Eq.~\ref{eq:prior}, from \textbf{FaSE-GLoBES} the user computes the statistical quantity,
+\begin{equation}\label{eq:chi_model}
+\chi^2(\vec{\theta}_{Model}^{hyp.}),~~\text{with}~n_i(\vec{\theta}_{Model}^{true})~\text{or}~n_i(\vec{\theta}_{OSC.}^{true}).
+\end{equation}
+%
+We note that the minimum of $\chi^2$ in the whole parameter space ($\chi^2_{min.}$) may not be $0$.
+Therefore, to study the precision of model parameters, the user should use the value $\Delta\chi^2(\vec{\theta}_{Model}^{hyp.})\equiv \chi^2(\vec{\theta}_{Model}^{hyp.})-\chi^2_{min.}$, instead of $\chi^2$ itself.
+By varying different hypothesis $\vec{\theta}_{Model}^{hyp.}$, the user can obtain the allowed region of model parameters with the statistical quantity $\Delta\chi^2(\vec{\theta}_{Model}^{hyp.})$.
+
+The user can also study how well a flavour symmetry model explains the computed data as predicting how the simulated experiment can exclude this model.
+In the other word, the user studies the minimum of $\chi^2$ for the flavour symmetry model $\vec{\theta}_{Model}$ as a hypothesis, assuming different true oscillation values, \textit{i.e.}~different $\vec{\theta}^{true}_{OSC}$.
+To do so, we compute the same statistical quantity Eq.~\ref{eq:chi_model}, while the true spectrum is varied with different true values $\vec{\theta}_{OSC}^{true}$.
+All model parameters are allowed to be varied with the user-defined prior.
+%
+Finally, the user needs to adopt Wilk's theorem \cite{Wilks:1938dza}.
+When comparing nested models, the $\Delta \chi^2$ test statistics is a random variable asymptotically distributed according to the $\chi^2$-distribution with the number of degrees of freedom, which is equal to the difference in the number of free model parameters \texttt{dof}.
 
@@
 
-Finally, in the code we adopt Wilk's theorem \cite{Wilks:1938dza}.
-When comparing nested models, the $\Delta \chi^2$ test statistics is a random variable asymptotically distributed according to the $\chi^2$-distribution with the number of degrees of freedom, which is equal to the difference in the number of free model parameters \texttt{dof}.
+Mentioned in Sec.~\ref{sec:chi-squared}, the user need to consider Wilk's theory with the different of degrees of freedom between the true theory and the hypothesis, \texttt{dof}.
 Here the number \texttt{dof} is $2$.
 And that is our output: \texttt{gsl\_cdf\_chisq\_Qinv(gsl\_cdf\_chisq\_Q(fabs(res),dof),1)}.
-We use the same code to analysis the exclusion ability for other oscillation-parameter combinations.
-Then, we have the results shown in Fig.~\ref{fig:th23_delta}.
+We show the result in Fig.~\ref{fig:th23_delta}.
 More details are presented in the user manual.
@@
 Considering the success of the flavour symmetry theory to explain the neutrino oscillations, \textbf{FaSE-GLoBES} should benefit model builders of leptonic flavour symmetry and phenomenologists for neutrino oscillation physics.
-We leave the flexibility for the user, and some other improvements and extensions might be done in the future.
+We leave the flexibility for the user, and some other improvements and extensions can be also expected in the future.
+
+ \begin{acknowledgements}
+\end{acknowledgements}
 

### 2020-05-07 FASE_GLoBES.c
update code

@@ -5,13 +5,14 @@
 #include <complex.h>
 #include <float.h>
 
+#include <gsl/gsl_math.h>
 #include <gsl/gsl_complex.h>
 #include <gsl/gsl_complex_math.h>
 #include <gsl/gsl_matrix.h>
 #include <gsl/gsl_blas.h>
-#include <gsl/gsl_statistics.h>
-#include <gsl/gsl_rng.h>
-#include <gsl/gsl_randist.h>
+//#include <gsl/gsl_statistics.h>
+//#include <gsl/gsl_rng.h>
+//#include <gsl/gsl_randist.h>
 #include <gsl/gsl_cblas.h>
 #include <gsl/gsl_eigen.h>
 #include <gsl/gsl_vector.h>
@@ -19,8 +20,8 @@
 
 #include <globes/globes.h>   /* GLoBES library */
 #include"FASE_GLoBES.h"
+//#include"model-input_diag.h"
 #include"model-input.h"
-//#include"model-input.h"
 
 extern char **glb_param_names;
 
@@ -71,6 +72,112 @@ gsl_vector *lambda=NULL;    /* Eigenvalues of Hamiltonian                       
 gsl_matrix_complex *S=NULL; /* The neutrino S-matrix                              */
 gsl_matrix_complex *H0_template=NULL;  /* Used in the construction of the vac. Hamiltonian */
 gsl_matrix_complex *S1=NULL, *T0=NULL; /* Temporary matrix storage                         */
+
+
+int STAN_OSC(double complex M[], double out[6])
+{
+    //https://github.com/daviddoria/Examples/blob/master/c%2B%2B/GSL/Test1/Test1.cpp
+    //http://linux.math.tifr.res.in/manuals/html/gsl-ref-html/gsl-ref_14.html
+    
+    
+    double complex MMsquare[] = { 1.0 + 0.0*I, 10.0 + 0.0*I, 3.0 + 0.0*I,
+        0.0 + 0.0*I, 2.0 + 0.0*I, 100.0 + 0.0*I,
+        1.0 + 0.0*I, 5.0 + 0.0*I, 3.0 + 0.0*I };
+    
+    
+    double complex beta = 0.0 + 0.0*I;
+    double complex alpha = 1.0 + 0.0*I;
+    
[…]

### 2020-05-07 FASE_GLoBES.h

@@ -39,16 +39,17 @@
 #include <gsl/gsl_complex_math.h>
 #include <gsl/gsl_matrix.h>
 #include <gsl/gsl_blas.h>
-#include <gsl/gsl_statistics.h>
-#include <gsl/gsl_rng.h>
-#include <gsl/gsl_randist.h>
+//#include <gsl/gsl_statistics.h>
+//#include <gsl/gsl_rng.h>
+//#include <gsl/gsl_randist.h>
 #include <gsl/gsl_cblas.h>
 #include <gsl/gsl_eigen.h>
 #include <gsl/gsl_vector.h>
 //#include <globes/globes.h>   /* GLoBES library */
 
 #include "model-input.h"
-//#include "model-input.h"
+//#include "model-input_diag.h"
+
 /*#define GLB_NU_FLAVOURS 3*/
 #define GLB_SIGMA_E 6        /* Index of non-standard parameter sigma_E */
 #define GLB_ETA 0
@@ -74,7 +75,6 @@
 /* which vacuum algorithms are used   */
 #define M_SQRT3  1.73205080756887729352744634151      /* sqrt(3) */
 
-
 /* Interface for non-standard implementations of the probability engine */
 
 //typedef struct OSC_PARAMS { double theta12; double theta13; double theta23; double delta; double alpha21; double alpha31; double Dm21; double Dm31; double m3; double m2; double m1; } OSC_PARAMS;
@@ -96,11 +96,8 @@ double x_in,eta_in,r_in,ma_in;
 
 double UPPER_prior[6],LOWER_prior[6],Central_prior[6];
 
-
-double randn (double mu, double sigma);
-int random_gaussian(int n, double sigma);
-int random_poisson_n(int n, double mu) ;
-int free_random();
+int STAN_OSC(double complex M[], double output[6]);
+int ModelTO( double OSC_PARAMS[6],double M_para[]);
 inline double square(double x);
 int sinsq(double complex U[], double * a);
 //double find_PMNS(double complex M[], OSC_PARAMS * output);

### 2020-05-07 model-input.c

@@ -6,9 +6,20 @@
 #include <gsl/gsl_complex.h>
 #include <gsl/gsl_math.h>
 #include <globes/globes.h>   /* GLoBES library */
+
+#include <gsl/gsl_complex_math.h>
+#include <gsl/gsl_matrix.h>
+#include <gsl/gsl_blas.h>
+//#include <gsl/gsl_statistics.h>
+//#include <gsl/gsl_rng.h>
+//#include <gsl/gsl_randist.h>
+#include <gsl/gsl_cblas.h>
+#include <gsl/gsl_eigen.h>
+#include <gsl/gsl_vector.h>
+#include "FASE_GLoBES.h"
 /* Macros */
-#define SQR(x)          ((x)*(x))                       /*x^2*/
-#define SQR_ABS(x)      (SQR(creal(x))+SQR(cimag(x)))   /*|x|^2*/
+//#define SQR(x)          ((x)*(x))                       /*x^2*/
+//#define SQR_ABS(x)      (SQR(creal(x))+SQR(cimag(x)))   /*|x|^2*/
 int N_M;
 
 /*Define the formula (5) in the working note provided by Ding.*/
@@ -195,24 +206,136 @@ double MODEL_init(int N) /*initialise the model-input*/
     return 0;
 }
 
+/*
+int STAN_OSC(double complex M[], double out[6])
+{
+    //https://github.com/daviddoria/Examples/blob/master/c%2B%2B/GSL/Test1/Test1.cpp
+    //http://linux.math.tifr.res.in/manuals/html/gsl-ref-html/gsl-ref_14.html
+    
+    
+    double complex MMsquare[] = { 1.0 + 0.0*I, 10.0 + 0.0*I, 3.0 + 0.0*I,
+        0.0 + 0.0*I, 2.0 + 0.0*I, 100.0 + 0.0*I,
+        1.0 + 0.0*I, 5.0 + 0.0*I, 3.0 + 0.0*I };
+    
+    
+    double complex beta = 0.0 + 0.0*I;
+    double complex alpha = 1.0 + 0.0*I;
+    
+    cblas_zgemm (CblasRowMajor, CblasConjTrans, CblasNoTrans, 3, 3, 3, &alpha, M, 3, M, 3, &beta, MMsquare, 3); //eq 4.5 page 107 Giunti
+    
+    
[…]

### 2020-05-07 model-input.h

@@ -8,16 +8,16 @@
 #include <gsl/gsl_complex_math.h>
 #include <gsl/gsl_matrix.h>
 #include <gsl/gsl_blas.h>
-#include <gsl/gsl_statistics.h>
-#include <gsl/gsl_rng.h>
-#include <gsl/gsl_randist.h>
+//#include <gsl/gsl_statistics.h>
+//#include <gsl/gsl_rng.h>
+//#include <gsl/gsl_randist.h>
 #include <gsl/gsl_cblas.h>
 #include <gsl/gsl_eigen.h>
 #include <gsl/gsl_vector.h>
-
+//#include "FASE_GLoBES.h"
 
 int N_M;
-
+/******************************************the user-defined relation*/
 double complex TDModelY(double x, double eta, double r, double Ma);
 double complex TDModelZ(double x, double eta, double r, double Ma);
 double complex TDModelW(double x, double eta, double r, double Ma);
@@ -31,6 +31,13 @@ double TDth23(double x, double eta, double r, double Ma);
 double TDdCP(double x, double eta, double r, double Ma);
 double TDdm21(double x, double eta, double r, double Ma);
 double TDdm31(double x, double eta, double r, double Ma);
+/*******************************************************************/
+
 double MODEL_init();
+/********************************************diagonaliser ********/
+//int STAN_OSC(double complex M[], double output[6]);
+//int ModelTO( double OSC_PARAMS[6],double M_para[]);
+/*******************************************************************/
+
 double MtoS(double osc_para[6], double M_para[]);
 double model_restriction(double model []);

### 2020-05-07 model-input_diag.c

@@ -1,228 +1,0 @@
-#include <stdio.h>
-#include <stdlib.h>
-#include <math.h>
-#include <string.h>
-#include <complex.h>
-#include <float.h>
-
-#include <gsl/gsl_complex.h>
-#include <gsl/gsl_complex_math.h>
-#include <gsl/gsl_matrix.h>
-#include <gsl/gsl_blas.h>
-#include <gsl/gsl_statistics.h>
-#include <gsl/gsl_rng.h>
-#include <gsl/gsl_randist.h>
-#include <gsl/gsl_cblas.h>
-#include <gsl/gsl_eigen.h>
-#include <gsl/gsl_vector.h>
-#include <globes/globes.h>   /* GLoBES library */
-/* Macros */
-#define SQR(x)          ((x)*(x))                       /*x^2*/
-#define SQR_ABS(x)      (SQR(creal(x))+SQR(cimag(x)))   /*|x|^2*/
-
-int N_M;
-typedef struct OSC_PARAMS { double theta12; double theta13; double theta23; double delta; double alpha21; double alpha31; double Dm21; double Dm31; double m3; double m2; double m1; } OSC_PARAMS;
-
-
-double MODEL_init(int N) /*initialise the model-input*/
-{
-    if (N>6){printf("the number of parameters cannot be larger than 6.\n");}
-    N_M=N;
-
-    return 0;
-}
-
-
-
-int STAN_OSC(double complex M[], double out[6])
-{
-/*https://github.com/daviddoria/Examples/blob/master/c%2B%2B/GSL/Test1/Test1.cpp
- http://linux.math.tifr.res.in/manuals/html/gsl-ref-html/gsl-ref_14.html
- */
-
-    double complex MMsquare[] = { 1.0 + 0.0*I, 10.0 + 0.0*I, 3.0 + 0.0*I,
-        0.0 + 0.0*I, 2.0 + 0.0*I, 100.0 + 0.0*I,
-        1.0 + 0.0*I, 5.0 + 0.0*I, 3.0 + 0.0*I };
-    
-    
-    double complex beta = 0.0 + 0.0*I;
-    double complex alpha = 1.0 + 0.0*I;
-    
[…]

### 2020-05-07 model-input_diag.h

@@ -1,78 +1,0 @@
-/* GLoBES -- General LOng Baseline Experiment Simulator
- * (C) 2002 - 2007,  The GLoBES Team
- *
- * GLoBES is mainly intended for academic purposes. Proper
- * credit must be given if you use GLoBES or parts of it. Please
- * read the section 'Credit' in the README file.
- *
- * This program is free software; you can redistribute it and/or modify
- * it under the terms of the GNU General Public License as published by
- * the Free Software Foundation; either version 2 of the License, or
- * (at your option) any later version.
- *
- * This program is distributed in the hope that it will be useful,
- * but WITHOUT ANY WARRANTY; without even the implied warranty of
- * MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
- * GNU General Public License for more details.
- *
- * You should have received a copy of the GNU General Public License
- * along with this program; if not, write to the Free Software
- * Foundation, Inc., 59 Temple Place, Suite 330, Boston, MA  02111-1307  USA
- */
- 
-/*
- Some simple output functions for GLoBES examples
- */
-
-
-//#ifndef TRI_DIRECT_PE_H
-//#define TRI_DIRECT_PE_H
-
-
-#include <stdio.h>
-#include <stdlib.h>
-#include <math.h>
-#include <string.h>
-#include <complex.h>
-#include <float.h>
-#include <gsl/gsl_complex.h>
-#include <gsl/gsl_complex_math.h>
-#include <gsl/gsl_matrix.h>
-#include <gsl/gsl_blas.h>
-#include <gsl/gsl_statistics.h>
-#include <gsl/gsl_rng.h>
-#include <gsl/gsl_randist.h>
-#include <gsl/gsl_cblas.h>
-#include <gsl/gsl_eigen.h>
-#include <gsl/gsl_vector.h>
-#include <globes/globes.h>   /* GLoBES library */
-
-
-/*#define GLB_NU_FLAVOURS 3*/
-//#define GLB_SIGMA_E 6
-//#define GLB_ETA 0
-//#define GLB_MA 1
-//#define GLB_MB 2
-//#define STAN 0
-//#define MODEL -100
-//#define SQR(x)      ((x)*(x))                        /* x^2   */
-//#define SQR_ABS(x)  (SQR(creal(x)) + SQR(cimag(x)))  /* |x|^2 */
-//#define GLB_NU_FLAVOURS 3
-//#define GLB_V_FACTOR        7.5e-14   /* Conversion factor for matter potentials */
-
[…]

### 2020-05-07 doc/FAS-GLoBES.tex
update documents

@@
 
+\begin{figure}[!h]
+ %\flushleft
+ \centering
+\hspace{15mm}\includegraphics[width=0.5\textwidth]{figs/x_eta.pdf}
+ \caption{\label{fig:x_eta}Precision measurements of any two model parameters in the framework of three neutrino oscillations taking uncertainties of the current global fit results, for MOMENT, at $1\sigma$ (gray), $2\sigma$ (orange), $3\sigma$ (black).
+True values for the model parameters are used $(x,~\eta,~r,~M_a)=(-3.65,~1.13\pi,~0.511,~3.71~\text{meV})$.}
+\end{figure}
+
 The user can use \textbf{FaSE-GLoBES} to study the constraint of model parameters.
@@
 The user of \textbf{FaSE-GLoBES} is able to study how model parameters can be constrained by the simulated experiment.
-To do so, the user needs to define the true event spectrum $n_i$ with a set of model or oscillation parameters, \textit{i.e.}~$n_i(\vec{\theta}_{Model}^{true})$ or $n_i(\vec{\theta}_{OSC.}^{true})$.
+To do so, the user needs to define the true event spectrum $n_i$ with a set of model ($\vec{\theta}_{Model}^{true}$) or oscillation parameters ($\vec{\theta}_{OSC.}^{true}$), \textit{i.e.}~set up $n_i(\vec{\theta}_{Model}^{true})$ or $n_i(\vec{\theta}_{OSC.}^{true})$.
 The hypothesis $\vec{\theta}_{Model}^{hyp.}$ predicts the tested event spectrum $\eta_i(\vec{\theta}_{Model}^{hyp.},\xi_s,\xi_b)$.
@@
 
-To get the constraint of $x$ and $\eta$, we obtain the minimum of $\chi^2$ value,\vspace{0.2cm}\\
+We take TDLS as an example model, to see how the model parameter can be constrained by MOMENT experiment.
+To get the constraint of $x$ and $\eta$, we obtain the minimum of $\chi^2$ value as the following script in the main code.\vspace{0.2cm}\\
 \texttt{
@@
 %
-Then, we set two loops to get the $\Delta \chi^2$ value for different $x$ and $\eta$\vspace{0.2cm}\\
+The \textbf{GLoBES} projector \texttt{free} allows all model parameters to vary, in order to find the value of \texttt{res0}, $\chi^2_{min}$.
+Then, we set two loops varying different values of $x$ and $\eta$ in $\vec{\theta}^{hyp}_{Model}$ to get $\Delta \chi^2$ values for different hypotheses.\vspace{0.2cm}\\
 %
@@
 
-\begin{figure}[!h]
- \flushleft
-\hspace{15mm}\includegraphics[width=0.32\textwidth]{figs/x_eta.pdf}$~~~~~~$\\
-\hspace{15mm} \includegraphics[width=0.32\textwidth]{figs/x_r.pdf}\hspace{-11mm}
- \includegraphics[width=0.32\textwidth]{figs/eta_r.pdf}$~~~~~~$\\
-\hspace{15mm} \includegraphics[width=0.32\textwidth]{figs/x_ma.pdf}\hspace{-11mm}
- \includegraphics[width=0.32\textwidth]{figs/eta_ma.pdf}\hspace{-11mm}
- \includegraphics[width=0.32\textwidth]{figs/r_ma.pdf}
- \caption{\label{fig:model_2D}Precision measurements of any two model parameters at 3$\sigma$ confidence level in the framework of three neutrino oscillations taking uncertainties of the current global fit results, for MOMENT, at $1\sigma$ (gray), $2\sigma$ (orange), $3\sigma$ (black).
+The output is a set of $\Delta \chi^2(\vec{\theta}^{hyp})$ (the third column) values with the changed $x$ (the first column), $\eta$ (the second column) in the file \texttt{data/contraint\_x\_eta.dat}.
+We use these data, and find the $1\sigma$, $2\sigma$, and $3\sigma$ constraints of $x$ and $\eta$ shown in Fig.~\ref{fig:x_eta}.
+
+%\begin{figure}[!h]
+% \flushleft
+%\hspace{15mm}\includegraphics[width=0.32\textwidth]{figs/x_eta.pdf}$~~~~~~$\\
+%\hspace{15mm} \includegraphics[width=0.32\textwidth]{figs/x_r.pdf}\hspace{-11mm}
+% \includegraphics[width=0.32\textwidth]{figs/eta_r.pdf}$~~~~~~$\\
+%\hspace{15mm} \includegraphics[width=0.32\textwidth]{figs/x_ma.pdf}\hspace{-11mm}
+% \includegraphics[width=0.32\textwidth]{figs/eta_ma.pdf}\hspace{-11mm}
+% \includegraphics[width=0.32\textwidth]{figs/r_ma.pdf}
+% \caption{\label{fig:model_2D}Precision measurements of any two model parameters at 3$\sigma$ confidence level in the framework of three neutrino oscillations taking uncertainties of the current global fit results, for MOMENT, at $1\sigma$ (gray), $2\sigma$ (orange), $3\sigma$ (black).
 True values for the model parameters are used $(x,~\eta,~r,~M_a)=(-3.65,~1.13\pi,~0.511,~3.71~\text{meV})$.}
-\end{figure}
-
-We use the same code to obtain the constraint of any other combination of two parameters. Then, we can have the result as in Fig.~\ref{fig:model_2D}.
+%\end{figure}
 

### 2020-05-08 doc/FAS-GLoBES.tex
update docs

@@
 
-The function \texttt{MtoS} can do the translator from model parameters $\vec{\theta}_{Model}$ to oscillation parameters $\vec{\theta}_{OSC.}$.
-After the user gives the array $\vec{\theta}_{Model}$ to the function \texttt{MtoS}, the output is the corresponding oscillation parameter $\vec{\theta}_{OSC.}$, of which components are $\theta_{12}$, $\theta_{13}$, $\theta_{23}$, $\delta$, $\Delta m_{21}^2$, and $\Delta m_{31}^2$.
+The function \texttt{MtoS} can do the translator from model parameters $\vec{\theta}_{Model}$ to oscillation parameters $\vec{\theta}_{OSC}$.
+After the user gives the array $\vec{\theta}_{Model}$ to the function \texttt{MtoS}, the output is the corresponding oscillation parameter $\vec{\theta}_{OSC}$, of which components are $\theta_{12}$, $\theta_{13}$, $\theta_{23}$, $\delta$, $\Delta m_{21}^2$, and $\Delta m_{31}^2$.
 For the first four components, values are given in the unit of \textbf{rad}, while the other two are in \textbf{eV$^2$}.
@@
 
-To do the translation from $\vec{\theta}_{Model}$ to $\vec{\theta}_{OSC.}$, the user can assign the relation between the oscillation and model parameter sets, or define the mass matrix in model parameters, which will be diagonalised by the function \texttt{ModelTO} to obtain the corresponding oscillation-parameter values.
+To do the translation from $\vec{\theta}_{Model}$ to $\vec{\theta}_{OSC}$, the user can assign the relation between the oscillation and model parameter sets, or define the mass matrix in model parameters, which will be diagonalised by the function \texttt{ModelTO} to obtain the corresponding oscillation-parameter values.
 %The relation between the oscillation and model parameter sets can be derived out by the user, 
@@
 \begin{equation}\label{eq:modelofOSC}
-\vec{\theta}_{Model}=\vec{f}(\vec{\theta}_{OSC.})
+\vec{\theta}_{Model}=\vec{f}(\vec{\theta}_{OSC})
 \end{equation}
@@
 The matrix $U$ is the neutrino mixing matrix, and can be used for getting mixing angles.
-The difference between any two diagonal elements of $\textbf{M}$ ($\textbf{M}_{ii}-\textbf{M}_{jj}$) is the mass-squared difference ($\Delta m_{ij}^2$).
-This diagnolisation Eq.~\ref{eq:MM} can be done with the function \texttt{ModelTO}, which needs to be called in \texttt{MtoS} and outputs directly the vector $\vec{\theta}_{OSC.}$.
+The difference between any two diagonal elements of $\textbf{M}$ ($\textbf{M}_{ii}-\textbf{M}_{jj}=m_i^2-m_j^2$) is the mass-squared difference ($\Delta m_{ij}^2$).
+This diagnolisation Eq.~\ref{eq:MM} can be done with the function \texttt{ModelTO}, which needs to be called in \texttt{MtoS} and outputs directly the vector $\vec{\theta}_{OSC}$.
 
@@
  where $\theta_i$ is one of parameters constrained by prior, $\theta^c_i$ ($\sigma_i$) is the central value (Gaussian width) of the prior for $\theta_i$.
-We note that $\theta_i$ can be either model ($\vec{\theta}_{Model}$) or oscillation parameters ($\vec{\theta}_{OSC.}$).
+We note that $\theta_i$ can be either model ($\vec{\theta}_{Model}$) or oscillation parameters ($\vec{\theta}_{OSC}$).
 %
@@
 Then, when the restriction is broken, \texttt{model\_restriction} returns the value $1$ to the prior function \texttt{FASE\_prior\_OSC} or \texttt{FASE\_prior\_model}.
+Therefore, if there is no any restrictions, we simply \textit{return $0$} in \texttt{model\_restriction} as follows.\vspace{0.2cm}\\
+\texttt{double model\_restriction(double model [])\{ return 0;\} }\vspace{0.2cm}\\
+
 %In the following, the prior function will give $10^6$ for the $\chi^2$ value, and it will be selected out when the user studies the statistically reasonable region in the parameter space.
@@
 \subsection{Setup for a model}
-We now take the littlest seesaw model in the tri-direct approach as an example.
+We now take the tri-direct littlest seesaw (TDLS)~\cite{King:2013iva,King:2015dvf,King:2016yvg} as an example.
 In this model, the atmospheric and solar flavon vacuum alignments are $\langle\phi_{\text{atm}}\rangle\propto\left(1, \omega^2, \omega\right)^T$ and $\langle\phi_{\text{sol}}\rangle\propto\left(1, x, x\right)^T$,
@@
 \\    
-    \texttt{double x\_in   = M\_para[0];}\\
-    \texttt{double eta\_in = M\_para[1];}\\
-    \texttt{double r\_in   = M\_para[2];}\\
-    \texttt{double ma\_in  = M\_para[3];}\\
+    \texttt{double x=M\_para[0];}\\
+    \texttt{double eta=M\_para[1];}\\
+    \texttt{double r=M\_para[2];}\\
+    \texttt{double ma=M\_para[3];}\\
 \\  
-    \texttt{osc\_para[0]=TDth12(x\_in,eta\_in,r\_in, ma\_in);}\\
-    \texttt{osc\_para[1]=TDth13(x\_in,eta\_in,r\_in, ma\_in);}\\
-    \texttt{osc\_para[2]=TDth23(x\_in,eta\_in,r\_in, ma\_in);}\\
-    \texttt{osc\_para[3]=TDdCP(x\_in,eta\_in,r\_in, ma\_in);}\\
-    \texttt{osc\_para[4]=TDdm21(x\_in,eta\_in,r\_in, ma\_in);}\\
-    \texttt{osc\_para[5]=TDdm31(x\_in,eta\_in,r\_in, ma\_in);}\\
+    \texttt{osc\_para[0]=TDth12(x,eta,r, ma);}\\
+    \texttt{osc\_para[1]=TDth13(x,eta,r, ma);}\\
+    \texttt{osc\_para[2]=TDth23(x,eta,r, ma);}\\
+    \texttt{osc\_para[3]=TDdCP(x,eta,r, ma);}\\
+    \texttt{osc\_para[4]=TDdm21(x,eta,r, ma);}\\
+    \texttt{osc\_para[5]=TDdm31(x,eta,r, ma);}\\
 \\    
@@
 \}\vspace{0.2cm}\\
-If there is no any restrictions, we simply \textit{return $0$} in \texttt{model\_restriction} as follows.\vspace{0.2cm}\\
-\texttt{double model\_restriction(double model [])\{ return 0;\} }\vspace{0.2cm}\\
 
 \subsection{Initialise the code}
-In the beginning of main code, we need to initialise GLoBES and FASE, and include the considered experiment (here we consider MOMENT experiment) as follows.\vspace{0.2cm}\\ 
+In the beginning of main code, we need to initialise GLoBES and FASE, and to include the AEDL file for the MuOn-decay MEdium baseline NeuTrino beam experiment (MOMENT)~\cite{Cao:2014bea} as follows.\vspace{0.2cm}\\
 \texttt{glbInit(argv[0]);}\\
@@
     glbSetDensityProjectionFlag(free, GLB\_FREE, GLB\_ALL);\\
-glbDefineProjection(projection,GLB\_FIXED,GLB\_FIXED,GLB\_FREE,GLB\_FREE,GLB\_FIXED,GLB\_FIXED);\\    
+glbDefineProjection(projection,GLB\_FIXED,GLB\_FIXED,GLB\_FREE,GLB\_FREE,GLB\_FIXED\\ ,GLB\_FIXED);\\    
 glbSetDensityProjectionFlag(projection, GLB\_FREE, GLB\_ALL);\\
@@
 Finally, $\chi^2_{prior}$ is a set of Gaussian priors for hypothesis, and is expressed as Eq.~\ref{eq:prior}.
-After doing all minimisations, the user obtain the $\chi^2$ value for a specific hypothesis $\vec{\theta}^{hyp.}$, $\chi^2(\vec{\theta}^{hyp.})$.
+After doing all minimisations, the user obtain the $\chi^2$ value for a specific hypothesis $\vec{\theta}^{hyp}$, $\chi^2(\vec{\theta}^{hyp})$.
 
 The user of \textbf{FaSE-GLoBES} is able to study how model parameters can be constrained by the simulated experiment.
-To do so, the user needs to define the true event spectrum $n_i$ with a set of model ($\vec{\theta}_{Model}^{true}$) or oscillation parameters ($\vec{\theta}_{OSC.}^{true}$), \textit{i.e.}~set up $n_i(\vec{\theta}_{Model}^{true})$ or $n_i(\vec{\theta}_{OSC.}^{true})$.
-The hypothesis $\vec{\theta}_{Model}^{hyp.}$ predicts the tested event spectrum $\eta_i(\vec{\theta}_{Model}^{hyp.},\xi_s,\xi_b)$.
+To do so, the user needs to define the true event spectrum $n_i$ with a set of model ($\vec{\theta}_{Model}^{true}$) or oscillation parameters ($\vec{\theta}_{OSC}^{true}$), \textit{i.e.}~set up $n_i(\vec{\theta}_{Model}^{true})$ or $n_i(\vec{\theta}_{OSC}^{true})$.
+The hypothesis $\vec{\theta}_{Model}^{hyp}$ predicts the tested event spectrum $\eta_i(\vec{\theta}_{Model}^{hyp},\xi_s,\xi_b)$.
 With the default setting for $\chi^2$ function Eq.~\ref{eq:prior}, from \textbf{FaSE-GLoBES} the user computes the statistical quantity,
 \begin{equation}\label{eq:chi_model}
-\chi^2(\vec{\theta}_{Model}^{hyp.}),~~\text{with}~n_i(\vec{\theta}_{Model}^{true})~\text{or}~n_i(\vec{\theta}_{OSC.}^{true}).
+\chi^2(\vec{\theta}_{Model}^{hyp}),~~\text{with}~n_i(\vec{\theta}_{Model}^{true})~\text{or}~n_i(\vec{\theta}_{OSC}^{true}).
 \end{equation}
@@
 We note that the minimum of $\chi^2$ in the whole parameter space ($\chi^2_{min.}$) may not be $0$.
-Therefore, to study the precision of model parameters, the user should use the value $\Delta\chi^2(\vec{\theta}_{Model}^{hyp.})\equiv \chi^2(\vec{\theta}_{Model}^{hyp.})-\chi^2_{min.}$, instead of $\chi^2$ itself.
-By varying different hypothesis $\vec{\theta}_{Model}^{hyp.}$, the user can obtain the allowed region of model parameters with the statistical quantity $\Delta\chi^2(\vec{\theta}_{Model}^{hyp.})$.
+Therefore, to study the precision of model parameters, the user should use the value $\Delta\chi^2(\vec{\theta}_{Model}^{hyp})\equiv \chi^2(\vec{\theta}_{Model}^{hyp})-\chi^2_{min.}$, instead of $\chi^2$ itself.
+By varying different hypothesis $\vec{\theta}_{Model}^{hyp}$, the user can obtain the allowed region of model parameters with the statistical quantity $\Delta\chi^2(\vec{\theta}_{Model}^{hyp})$.
 
-We take TDLS as an example model, to see how the model parameter can be constrained by MOMENT experiment.
-To get the constraint of $x$ and $\eta$, we obtain the minimum of $\chi^2$ value as the following script in the main code.\vspace{0.2cm}\\
+We take TDLS as an example model, to see how the model parameter can be constrained by MOMENT experiment, assuming the true model values $x=-3.65$, $\eta=1.13\pi$, $r=0.511$, and $m_a=3.71$~meV.
+To get the constraint of $x$ and $\eta$, we need to comput the minimum of $\chi^2$ value as the following script in the main code.\vspace{0.2cm}\\
 \texttt{
@@
 
-The output is a set of $\Delta \chi^2(\vec{\theta}^{hyp})$ (the third column) values with the changed $x$ (the first column), $\eta$ (the second column) in the file \texttt{data/contraint\_x\_eta.dat}.
-We use these data, and find the $1\sigma$, $2\sigma$, and $3\sigma$ constraints of $x$ and $\eta$ shown in Fig.~\ref{fig:x_eta}.
+The \textbf{GLoBES} projector \texttt{projection} fixes values of $x$ and $\eta$, but allows the other parameters to vary.
+The output (\texttt{data/contraint\_x\_eta.dat}) is a set of $\Delta \chi^2(\vec{\theta}^{hyp})$ (the third column) values with the changed $x$ (the first column), $\eta$ (the second column).
+We use these data, and obtain the predicted $1\sigma$, $2\sigma$, and $3\sigma$ constraints of $x$ and $\eta$ by MOMENT shown in Fig.~\ref{fig:x_eta}.
+The code for this example is provided as \textbf{x\_eta.c} in the \textbf{FaSE} distribution.
 
@@
 
-We can also study on excluding the model, assuming different true values for oscillation parameters.
-In this example, we present testing the tri-driect littlest seesaw model in various $\theta_{23}$ and $\delta$.
-To do so, we set the true value in oscillation parameters.
-We change values of $\theta_{23}$ and $\delta$ of the true theory, and compute the minimal $\chi^2$ value for the tested model with all four model parameters, free to be varied.
+\begin{figure}[!h]
+ \centering
+\includegraphics[width=0.5\textwidth]{figs/SR_th23_dCP.pdf}
+\caption{\label{fig:th23_delta}The 2-D exclusion contour for tri-direct littlest seesaw model on the plane of two true standard parameters $\theta_{23}$ and $\delta$, from $1\sigma$ to $5\sigma$.
+The range for each parameter is taken according to the $3\sigma$ uncertainty in NuFit4.0 results.
+The black dot denotes the best fit of NuFit4.0 results ($(\theta_{12},~\theta_{13},~\theta_{23},~\delta,~\Delta m_{21}^2,~\Delta m_{31}^2)=(33.82^\circ,~8.61^\circ,~49.6^\circ,~215^\circ,~7.39\times10^{-5}~\text{eV}^2,~2.525\times10^{-3}~\text{eV}^2)$), while the star is the prediction by the tri-direct littlest seesaw model with NuFit4.0 results ($(\theta_{12},~\theta_{13},~\theta_{23},~\delta,~\Delta m_{21}^2,~\Delta m_{31}^2)\sim(36.25^\circ,~8.63^\circ,~47^\circ,~279^\circ,~7.39\times10^{-5}~\text{eV}^2,~2.525\times10^{-3}~\text{eV}^2)$).}
+\end{figure}
+
+%We can also study on excluding the model, assuming different true values for oscillation parameters. 
+As an example, we present testing TDLS, assuming various true values of $\theta_{23}$ and $\delta$.
+The code for this example is provided as \textbf{th23\_delta.c}.
+in the \textbf{FaSE} distribution We change values of $\theta_{23}$ and $\delta$ of the true theory, and compute the minimal $\chi^2$ value for the tested model with all four model parameters, allowed to vary with priors.
 And, the studied statistics function is exactly Eq.~\ref{eq:chi-squared}, but the true event rate $n_i$ is predicted by a set of oscillation parameters, which will be varied in the code.
 And all four model parameter can be varied with the prior given by Eq.~\ref{eq:prior}.
+%
+Except for $\theta_{23}$ and $\delta$, which are varied between $40^\circ<\theta_{23}<52^\circ$ and $125^\circ<\delta<392^\circ$, we fix the other oscillation parameters at $\theta_{12}=36.25^\circ$, $\theta_{13}=8.63^\circ$, $\Delta m_{21}^2=7.39\times 10^{-5}$~eV$^2$ and $2.525\times10^{-3}$~eV$^2$ predicted by the model $x=-3.65$, $\eta=1.13\pi$, $r=0.511$, and $m_a=3.71$~meV.
 
-The example code is given below.\vspace{0.2cm}\\
+The example code is presented as follows.\vspace{0.2cm}\\
 \texttt{ \{ ...  initalize the code ...\}\\
@@
     glbSetDensityParams(test\_values,1.0,GLB\_ALL);\\
-    glbDefineParams(true\_values,th12\_true,th13\_true,th23\_true,dCP\_true,DM21\_true,DM31\_true);\\
+    glbDefineParams(true\_values,th12\_true,th13\_true,th23\_true,dCP\_true,\\
+    DM21\_true,DM31\_true);\\
     glbSetDensityParams(true\_values,1.0,GLB\_ALL); }\vspace{0.2cm}\\
@@
     FILE* File=fopen("data/ModelTest\_th23\_dCP\_test.dat", "w");\\
-    lower\_th23=40; upper\_th23=50; lower\_dCP=125; upper\_dCP=392;\\
+    lower\_th23=40; upper\_th23=52; lower\_dCP=125; upper\_dCP=392;\\
     dth23=(upper\_th23-lower\_th23)/100; ddCP=(upper\_dCP-lower\_dCP)/100;\\
@@
         float res=glbChiNP(test\_values,NULL,GLB\_ALL);\\
-            fprintf(File,"\%f \%f \%f $\backslash$n",th23,dCP,gsl\_cdf\_chisq\_Qinv(gsl\_cdf\_chisq\_Q(fabs(res),dof),1));\\
+            fprintf(File,"\%f \%f \%f $\backslash$n",th23,dCP,\\
+            gsl\_cdf\_chisq\_Qinv(gsl\_cdf\_chisq\_Q(fabs(res),dof),1));\\
          \} fprintf(File,"$\backslash$n");\\
@@
 \texttt{ \{ ...  destroy the pointer ...\}}\vspace{0.2cm}\\
-Finally, in the code we adopt Wilk's theorem \cite{Wilks:1938dza}.
-When comparing nested models, the $\Delta \chi^2$ test statistics is a random variable asymptotically distributed according to the $\chi^2$-distribution with the number of degrees of freedom, which is equal to the difference in the number of free model parameters \texttt{dof}.
-Here the number \texttt{dof} is $2$.
-And that is our output: \texttt{gsl\_cdf\_chisq\_Qinv(gsl\_cdf\_chisq\_Q(fabs(res),dof),1)}.
+Finally, in the code we adopt Wilk's theorem \cite{Wilks:1938dza}. Here the number \texttt{dof} is $2$. And that is our output: \texttt{gsl\_cdf\_chisq\_Qinv(gsl\_cdf\_chisq\_Q(fabs(res),dof),1)}.
 
-\begin{figure}[!h]
- \flushleft
+%\begin{figure}[!h]
+ %\flushleft
 %
-\includegraphics[width=0.32\textwidth]{figs/SR_th13_th23.pdf}$~~~~~~$\\
-\includegraphics[width=0.32\textwidth]{figs/SR_th13_dCP.pdf}
-\includegraphics[width=0.32\textwidth]{figs/SR_th23_dCP.pdf}$~~~~~~$\\
-\includegraphics[width=0.32\textwidth]{figs/SR_th13_ldm.pdf}
-\includegraphics[width=0.32\textwidth]{figs/SR_th23_ldm.pdf}
-\includegraphics[width=0.32\textwidth]{figs/SR_dCP_ldm.pdf}
- \caption{\label{fig:SR_2D}The 2-D exclusion contour for tri-direct littlest seesaw model on the plane of any two true standard parameters, from $1\sigma$ to $5\sigma$.
+%\includegraphics[width=0.32\textwidth]{figs/SR_th13_th23.pdf}$~~~~~~$\\
+%\includegraphics[width=0.32\textwidth]{figs/SR_th13_dCP.pdf}
+%\includegraphics[width=0.32\textwidth]{figs/SR_th23_dCP.pdf}$~~~~~~$\\
+%\includegraphics[width=0.32\textwidth]{figs/SR_th13_ldm.pdf}
+%\includegraphics[width=0.32\textwidth]{figs/SR_th23_ldm.pdf}
+%\includegraphics[width=0.32\textwidth]{figs/SR_dCP_ldm.pdf}
+% \caption{\label{fig:SR_2D}The 2-D exclusion contour for tri-direct littlest seesaw model on the plane of any two true standard parameters, from $1\sigma$ to $5\sigma$.
 The range for each parameter is taken according to the $3\sigma$ uncertainty in NuFit4.0 results.
 The black dot denotes the best fit of NuFit4.0 results ($(\theta_{12},~\theta_{13},~\theta_{23},~\delta,~\Delta m_{21}^2,~\Delta m_{31}^2)=(33.82^\circ,~8.61^\circ,~49.6^\circ,~215^\circ,~7.39\times10^{-5}~\text{eV}^2,~2.525\times10^{-3}~\text{eV}^2)$), while the star is the prediction by the tri-direct littlest seesaw model with NuFit4.0 results ($(\theta_{12},~\theta_{13},~\theta_{23},~\delta,~\Delta m_{21}^2,~\Delta m_{31}^2)\sim(36.25^\circ,~8.63^\circ,~47^\circ,~279^\circ,~7.39\times10^{-5}~\text{eV}^2,~2.525\times10^{-3}~\text{eV}^2)$).}
-\end{figure}
+%\end{figure}
 
-We use the same code to analysis the exclusion ability for other oscillation-parameter combinations. Then, we have the results shown in Fig.~\ref{fig:SR_2D}.
+The output \texttt{data/ModelTest\_th23\_dCP\_test.dat} contains true values of $\theta_{23}$ (the first column) and $\delta$ (the second column) with $\chi^2_{min}$ for TDLS (the third column).
+With these data, we then have the results shown in Fig.~\ref{fig:th23_delta}.
 

### 2020-05-08 doc/paper.tex
update docs

--- 2020-05-06 doc/paper.tex
@@
  where $\theta_i$ is one of parameters constrained by prior, $\theta^c_i$ ($\sigma_i$) is the central value (Gaussian width) of the prior for $\theta_i$.
-We note that $\theta_i$ can be either model ($\vec{\theta}_{Model}$) or oscillation parameters ($\vec{\theta}_{OSC.}$).
+We note that $\theta_i${OSC} can be either model ($\vec{\theta}_{Model}$) or oscillation parameters ($\vec{\theta}_{OSC}$).
 %
@@
 Then, when the restriction is broken, \texttt{model\_restriction} returns the value $1$ to the prior function \texttt{FASE\_prior\_OSC} or \texttt{FASE\_prior\_model}.
+Therefore, if there is no any restrictions, we simply \textit{return $0$} in \texttt{model\_restriction} as follows.\vspace{0.2cm}\\
+\texttt{double model\_restriction(double model [])\{ return 0;\} }\vspace{0.2cm}\\
 %In the following, the prior function will give $10^6$ for the $\chi^2$ value, and it will be selected out when the user studies the statistically reasonable region in the parameter space.
@@
 In more detail, the $\chi^2$ function is constructed based on a log-likelihood ratio,
-\begin{equation}\label{eq:chi-squared}
-\chi^2(\vec{\theta}^{hyp.},\xi_s,\xi_b)=2\sum_i\left(\eta_i(\vec{\theta}^{hyp.},\xi_s,\xi_b)-n_i+n_i\ln\frac{n_i}{\eta_i(\vec{\theta}^{hyp.},\xi_s,\xi_b)} \right)+p(\xi_s,\sigma_s)+p(\xi_b,\sigma_b)+\chi^2_{prior},
-\end{equation}
+%\begin{equation}\label{eq:chi-squared}
+\begin{align}\label{eq:chi-squared}
+\chi^2(\vec{\theta}^{hyp},\xi_s,\xi_b)=&2\sum_i\left(\eta_i(\vec{\theta}^{hyp},\xi_s,\xi_b)-n_i+n_i\ln\frac{n_i}{\eta_i(\vec{\theta}^{hyp},\xi_s,\xi_b)} \right)\nonumber\\
+&+p(\xi_s,\sigma_s)+p(\xi_b,\sigma_b)+\chi^2_{prior},
+\end{align}
+%\end{equation}
 where $i$ runs over the number of bins, $\eta_i(\vec{\theta},\xi_s,\xi_b)$ is the hypothesis event rate for bin i and $E_i$ is the central bin energy.
@@
 \begin{equation}
-\eta_i(\vec{\theta}^{hyp.},\xi_s,\xi_b)=(1+\xi_s)\times s_i+(1+\xi_b)\times b_i,
+\eta_i(\vec{\theta}^{hyp},\xi_s,\xi_b)=(1+\xi_s)\times s_i+(1+\xi_b)\times b_i,
 \end{equation}
@@
 Finally, $\chi^2_{prior}$ is a set of Gaussian priors for hypothesis, and is expressed as Eq.~\ref{eq:prior}.
-After doing all minimisations, the user obtain the $\chi^2$ value for a specific hypothesis $\vec{\theta}^{hyp.}$, $\chi^2(\vec{\theta}^{hyp.})$.
+After doing all minimisations, the user obtain the $\chi^2$ value for a specific hypothesis $\vec{\theta}^{hyp}$, $\chi^2(\vec{\theta}^{hyp})$.
 
@@
 The user of \textbf{FaSE-GLoBES} is able to study how model parameters can be constrained by the simulated experiment.
-To do so, the user needs to define the true event spectrum $n_i$ with a set of model or oscillation parameters, \textit{i.e.}~$n_i(\vec{\theta}_{Model}^{true})$ or $n_i(\vec{\theta}_{OSC.}^{true})$.
-The hypothesis $\vec{\theta}_{Model}^{hyp.}$ predicts the tested event spectrum $\eta_i(\vec{\theta}_{Model}^{hyp.},\xi_s,\xi_b)$.
+To do so, the user needs to define the true event spectrum $n_i$ with a set of model ($\vec{\theta}_{Model}^{true}$) or oscillation parameters ($\vec{\theta}_{OSC}^{true}$), \textit{i.e.}~set up $n_i(\vec{\theta}_{Model}^{true})$ or $n_i(\vec{\theta}_{OSC}^{true})$.
+The hypothesis $\vec{\theta}_{Model}^{hyp}$ predicts the tested event spectrum $\eta_i(\vec{\theta}_{Model}^{hyp},\xi_s,\xi_b)$.
 With the default setting for $\chi^2$ function Eq.~\ref{eq:prior}, from \textbf{FaSE-GLoBES} the user computes the statistical quantity,
 \begin{equation}\label{eq:chi_model}
-\chi^2(\vec{\theta}_{Model}^{hyp.}),~~\text{with}~n_i(\vec{\theta}_{Model}^{true})~\text{or}~n_i(\vec{\theta}_{OSC.}^{true}).
+\chi^2(\vec{\theta}_{Model}^{hyp}),~~\text{with}~n_i(\vec{\theta}_{Model}^{true})~\text{or}~n_i(\vec{\theta}_{OSC}^{true}).
 \end{equation}
@@
 We note that the minimum of $\chi^2$ in the whole parameter space ($\chi^2_{min.}$) may not be $0$.
-Therefore, to study the precision of model parameters, the user should use the value $\Delta\chi^2(\vec{\theta}_{Model}^{hyp.})\equiv \chi^2(\vec{\theta}_{Model}^{hyp.})-\chi^2_{min.}$, instead of $\chi^2$ itself.
-By varying different hypothesis $\vec{\theta}_{Model}^{hyp.}$, the user can obtain the allowed region of model parameters with the statistical quantity $\Delta\chi^2(\vec{\theta}_{Model}^{hyp.})$.
+Therefore, to study the precision of model parameters, the user should use the value $\Delta\chi^2(\vec{\theta}_{Model}^{hyp})\equiv \chi^2(\vec{\theta}_{Model}^{hyp})-\chi^2_{min.}$, instead of $\chi^2$ itself.
+By varying different hypothesis $\vec{\theta}_{Model}^{hyp}$, the user can obtain the allowed region of model parameters with the statistical quantity $\Delta\chi^2(\vec{\theta}_{Model}^{hyp})$.
 
@@
 \textbf{FaSE-GloBES} can be used to study how the model parameter is constrained by simulated neutrino oscillation experiments.
-We take the tri-direct littlest seesaw (TDLS) model as example.
+We take the tri-direct littlest seesaw (TDLS) model~\cite{King:2013iva,King:2015dvf,King:2016yvg} as example.
 Under this model, the light left-handed Majorana neutrino mass matrix is given by
@@
 
-In Fig.~\ref{fig:x_eta}, we study how parameters $x$ and $\eta$ can be constrained by the MuOn-decay MEdium baseline NeuTrino beam experiment (MOMENT).
+In Fig.~\ref{fig:x_eta}, we study how parameters $x$ and $\eta$ can be constrained by the MuOn-decay MEdium baseline NeuTrino beam experiment (MOMENT)~\cite{Cao:2014bea}.
 We input the model by giving model parameters as functions of oscillation parameters Eq.~\ref{eq:modelofOSC}.

### 2020-05-11 doc/FAS-GLoBES.tex
update docs

@@
 \centering
-\includegraphics[width=4.5in]{Figs/FASE-chart_1_v1.pdf}
+\includegraphics[width=4.5in]{Figs/FASE-chart_1_2.pdf}
 \caption{A scheme to correlate the model parameters with standard neutrino oscillation parameters. The error propagation is implemented in the simulation code up to the spectra analysis.}%
@@
 To do so, we include the script in the \texttt{Makefile},\vspace{0.2cm}\\
-\texttt{\{makefile\_execution\}: my\_program.o  FASE\_GLoBES.o model-input\_diag.o\\
-	gcc my\_program.o  FASE\_GLoBES.o model-input\_diag.o -o my\_executable  \$(LDFLAGS) \$(local\_LDFLAGS)}\\
-or\\
 \texttt{\{makefile\_execution\}: my\_program.o  FASE\_GLoBES.o model-input.o\\
@@
 And, the user can execute the program by typing the following commend on the terminal.\vspace{0.2cm}\\ 
-\texttt{./my\_executable}\vspace{0.2cm}\\
+\texttt{./my\_executable}%\vspace{0.2cm}\\
 
 The user can also compile the program without the \textbf{GLoBES} \texttt{Makefile} with the following script.\vspace{0.2cm}\\
-\texttt{gcc my\_program.o FASE\_GLoBES.o model-input\_diag.o -lglobes -LGLB\_DIR/lib/ -o my\_executable}\\
-or\\
 \texttt{gcc my\_program.o FASE\_GLoBES.o model-input.o -lglobes -LGLB\_DIR/lib/ -o my\_executable}\vspace{0.2cm}\\
@@
 The difference between any two diagonal elements of $\textbf{M}$ ($\textbf{M}_{ii}-\textbf{M}_{jj}=m_i^2-m_j^2$) is the mass-squared difference ($\Delta m_{ij}^2$).
-This diagnolisation Eq.~\ref{eq:MM} can be done with the function \texttt{ModelTO}, which needs to be called in \texttt{MtoS} and outputs directly the vector $\vec{\theta}_{OSC}$.
+This diagnolisation Eq.~\ref{eq:MM} can be done with the function \texttt{STAN\_OSC}, which outputs directly the vector $\vec{\theta}\_{OSC}$.
+The user needs to call it in \texttt{MtoS} with the script,\vspace{0.2cm}\\
+\texttt{STAN\_OSC(\{}$M$\texttt{\},\{}$\vec{\theta}_{OSC}$\texttt{\});},\\
+where \texttt{\{}$M$\texttt{\}} and \texttt{\{}$\vec{\theta}_{OSC}$\texttt{\}} are the input neutrino mass matrix and the output array of oscillation parameter values, respectively.
 
@@
 To treat asymmetry of width for upper ($\theta_i>\theta_i^c$) and lower ($\theta_i<\theta_i^c$) Gaussian widths, we give values in two arrays \texttt{UPPER\_prior}, and \texttt{LOWER\_prior}, respectively.
-If the user gives the prior in model parameters, the order of each component follows with the setup of input of the probability engine.
-While the user gives the prior in oscillation parameters, the six components in order are $\theta_{12}$, $\theta_{13}$, $\theta_{23}$, $\delta$, $\Delta m_{21}^2$, and  $\Delta m_{31}^2$.
+If the user gives the prior in model parameters, the order of each component follows with the setup of input for the probability engine.
+If the user gives the prior in oscillation parameters, the six components in order are $\theta_{12}$, $\theta_{13}$, $\theta_{23}$, $\delta$, $\Delta m_{21}^2$, and  $\Delta m_{31}^2$.
 The first four parameter are in \textbf{rad}, and the final two are in \textbf{eV$^2$}.
@@
 \subsection{Initialise the code}
-In the beginning of main code, we need to initialise GLoBES and FASE, and to include the AEDL file for the MuOn-decay MEdium baseline NeuTrino beam experiment (MOMENT)~\cite{Cao:2014bea} as follows.\vspace{0.2cm}\\
+In the beginning of main code, we need to initialise \textbf{GLoBES} and \textbf{FaSE}, and to include the AEDL file for the MuOn-decay MEdium baseline NeuTrino beam experiment (MOMENT)~\cite{Cao:2014bea} as follows.\vspace{0.2cm}\\
 \texttt{glbInit(argv[0]);}\\
@@
                                  NULL); }\vspace{0.2cm}\\                                 
-In the following we define the model-parameter values, and set the true value in model parameters.\vspace{0.2cm}\\
+In the following we define the model-parameter values ($x$, $\eta$, $r$, and $m_a$), and set the true value in model parameters \texttt{true\_values} to simulated the true event spectrum.\vspace{0.2cm}\\
 \texttt{     float degree   = M\_PI/180;}\\
@@
 We then finally set up the projection.
-The projection \texttt{free} is to set all four parameters free to find the minimal value of $\chi^2$, which \texttt{project} is used for studying the constraint on $x$ and $\eta$.\vspace{0.2cm}\\
+The projection \texttt{free} allows all four parameters to be varied for finding the minimal value of $\chi^2$, which \texttt{project} is used for studying the constraint on $x$ and $\eta$.\vspace{0.2cm}\\
 \texttt{glb\_projection projection = glbAllocProjection();\\
@@
 
-\subsection{Prior setup}
+\subsection{Prior setup {\color{red}[updating]}}
 
@@
 where $i$ runs over the number of bins, $\eta_i(\vec{\theta},\xi_s,\xi_b)$ is the hypothesis event rate for bin i and $E_i$ is the central bin energy.
-The vector $\vec{\theta}$ consists of test model or oscillation parameters.
+The vector $\vec{\theta}$ consists of tested model or oscillation parameters.
 The parameters $\xi_s$ and $\xi_b$ are introduced to account for the systematic uncertainty of normalisation for the signal (subscript $_s$) and background (subscript $_b$) components for the event rate, and are allowed to vary in the fit as nuisance parameters.
@@
 
-We have presented \textbf{FaSE}, which is a supplemental simulation tool for \textbf{GLoBES} to study the flavour symmetry with neutrino oscillation experiments.
-\textbf{FaSE} provides \texttt{c}-codes: \textbf{model-input.c} and \textbf{FASE\_GLoBES.c}.
-Shown in Fig.~\ref{fig:FASE}, \textbf{FASE\_GLoBES}, which calls functions in \textbf{model-input.c}, plays a role as a bridge between \textbf{FaSE} and \textbf{GLoBES} to simulate the expected spectra and compute the prior value.
+We have presented \textbf{FaSE}, which is a supplemental simulation tool for \textbf{GLoBES} to study the leptonic flavour symmetry with neutrino oscillation experiments in a user-friendly way.
+\textbf{FaSE} contains two \texttt{c}-codes: \textbf{model-input.c} and \textbf{FASE\_GLoBES.c}.
+Shown in Fig.~\ref{fig:FASE}, \textbf{FASE\_GLoBES}, which calls functions in \textbf{model-input.c}, plays a role as a bridge between \textbf{FaSE} and \textbf{GLoBES} to simulate the event spectrum and compute the prior value.
 It can be left to be untouched by users.
-However, all inputs of the user needs to be given in the code \textbf{model-input.c}.
-Given a set of model parameters $\vec{M}$, with \textbf{GLoBES}, the output can be the $\chi^2$ value for the hypothesis $\vec{M}$.
-{\color{red}\texttt{Makefile} is easy to include these two binary files (\textbf{model-input} and \textbf{FASE\_GLoBES}) in the \texttt{makefile} script for \textbf{GLoBES}.
-}
+However, all inputs from the user needs to be given in \textbf{model-input.c}.
+The user can provide the relation between model and oscillation parameters, or simply give the mass matrix predicted by the studied model.
+The prior can be assigned as a Gaussian distribution in model or oscillation parameters.
+Central values and widths are given by the user in the main code through three arrays.
+Given a set of model parameters $\vec{\theta}_{Model}$, with \textbf{GLoBES}, the output can be the $\chi^2$ value for the hypothesis $\vec{\theta}_{Model}$ in the simulated experiments.
 
-We also present two examples for \textbf{FaSE-GLoBES} with the flavour symmetry model -- tri-direct littlest seesaw (TDLS) -- and the future neutrino oscillaiton experiment -- MOMENT.
-We show the model can be assign in two ways: the relation between model and oscillation parameters or the form of mass matrix in model parameters.
-The input of the oscillation probability and prior value can be in model or oscillation parameters.
-We further demonstrate how to use \textbf{FaSE-GLoBES} to obtain the constraint of any two of model parameters, and to study the ability to TDLS by MOMENT experiment.
+We also present demonstrate examples for \textbf{FaSE-GLoBES} with the flavour symmetry model -- tri-direct littlest seesaw (TDLS) -- and the future neutrino oscillaiton experiment -- MOMENT.
+We demonstrate how to use \textbf{FaSE-GLoBES} to obtain the constraint of any two of model parameters, and to study the ability to TDLS by MOMENT experiment.
 
@@
 Considering the success of the flavour symmetry theory to explain the neutrino oscillations, \textbf{FaSE-GLoBES} should benefit model builders of leptonic flavour symmetry and phenomenologists for neutrino oscillation physics.
-We leave the flexibility for the user, and some other improvements and extensions might be done in the future.
+We leave the flexibility for the user, and some other improvements and extensions can be expected in the future.
 
@@
 % use BIBTEX if you want
-\bibliographystyle{JHEP}
-%\bibliographystyle{plain}
+%\bibliographystyle{JHEP}
+\bibliographystyle{plain}
 \bibliography{FAS-GLoBES.bib}

### 2020-05-11 doc/paper.tex
update docs

@@
 
-We have presented \textbf{FaSE}, which is a supplemental simulation tool for \textbf{GLoBES} to study the flavour symmetry with neutrino oscillation experiments.
-\textbf{FaSE} provides \texttt{c}-codes: \textbf{model-input.c} and \textbf{FASE\_GLoBES.c}.
-Shown in Fig.~\ref{fig:FASE}, \textbf{FASE\_GLoBES}, which calls functions in \textbf{model-input.c}, plays a role as a bridge between \textbf{FaSE} and \textbf{GLoBES} to simulate the expected spectra and compute the prior value.
+e have presented \textbf{FaSE}, which is a supplemental simulation tool for \textbf{GLoBES} to study the leptonic flavour symmetry with neutrino oscillation experiments in a user-friendly way.
+\textbf{FaSE} contains two \texttt{c}-codes: \textbf{model-input.c} and \textbf{FASE\_GLoBES.c}.
+Shown in Fig.~\ref{fig:FASE}, \textbf{FASE\_GLoBES}, which calls functions in \textbf{model-input.c}, plays a role as a bridge between \textbf{FaSE} and \textbf{GLoBES} to simulate the event spectrum and compute the prior value.
 It can be left to be untouched by users.
-However, all inputs of the user needs to be given in the code \textbf{model-input.c}.
-Given a set of model parameters $\vec{\theta}_{Model}$, with \textbf{GLoBES}, the output can be the $\chi^2$ value for the hypothesis $\vec{\theta}_{Model}$.
-%{\color{red}\texttt{Makefile} is easy to include these two binary files (\textbf{model-input} and \textbf{FASE\_GLoBES}) in the \texttt{makefile} script for \textbf{GLoBES}. }
+However, all inputs from the user needs to be given in \textbf{model-input.c}.
+The user can provide the relation between model and oscillation parameters, or simply give the mass matrix predicted by the studied model.
+The prior can be assigned as a Gaussian distribution in model or oscillation parameters.
+Central values and widths are given by the user in the main code through three arrays.
+Given a set of model parameters $\vec{\theta}_{Model}$, with \textbf{GLoBES}, the output can be the $\chi^2$ value for the hypothesis $\vec{\theta}_{Model}$ in the simulated experiments.
 
-We also present two examples for \textbf{FaSE-GLoBES} with the flavour symmetry model -- tri-direct littlest seesaw (TDLS) -- and the future neutrino oscillaiton experiment -- MOMENT.
-We show the model can be assign in two ways: the relation between model and oscillation parameters or the form of mass matrix in model parameters.
-The input of the oscillation probability and prior value can be in model or oscillation parameters.
-We further demonstrate how to use \textbf{FaSE-GLoBES} to obtain the constraint of any two of model parameters, and to study the ability to TDLS by MOMENT experiment.
+We also present demonstrate examples for \textbf{FaSE-GLoBES} with the flavour symmetry model -- tri-direct littlest seesaw (TDLS) -- and the future neutrino oscillaiton experiment -- MOMENT.
+We demonstrate how to use \textbf{FaSE-GLoBES} to obtain the constraint of any two of model parameters, and to study the ability to TDLS by MOMENT experiment.
 
@@
 Considering the success of the flavour symmetry theory to explain the neutrino oscillations, \textbf{FaSE-GLoBES} should benefit model builders of leptonic flavour symmetry and phenomenologists for neutrino oscillation physics.
-We leave the flexibility for the user, and some other improvements and extensions can be also expected in the future.
+We leave the flexibility for the user, and some other improvements and extensions can be expected in the future.
 

### 2020-05-12 doc/paper.tex
update draft

@@
 \textbf{FaSE-GloBES} can be used to study how the model parameter is constrained by simulated neutrino oscillation experiments.
-We take the tri-direct littlest seesaw (TDLS) model~\cite{King:2013iva,King:2015dvf,King:2016yvg} as example.
+We take \textit{the tri-direct littlest seesaw} (TDLS)~\cite{King:2013iva,King:2015dvf,King:2016yvg} as an example.
 Under this model, the light left-handed Majorana neutrino mass matrix is given by
@@
 
+{\color{red}To show the generality of \textbf{FaSE-GLoBES}, we present the similar result with another model -- \textit{the warped flavor symmetry} (WFS).
+This model predict the simplification that mixing angles and the CP phase are functions of two model parameters $\theta_\nu$ and $\phi_\nu$,
+\begin{align}
+\sin^2\theta_{12}&=\frac{1}{2-\sin2\theta_{\nu}\cos\phi_\nu},\nonumber\\
+\sin^2\theta_{13}&=\frac{1}{3}(1+\sin2\theta_\nu\cos\phi_\nu),\nonumber\\
+\sin^2\theta_{23}&=\frac{1-\sin2\theta_\nu\sin(\pi/6-\phi_\nu)}{2-\sin2\theta_\nu\cos\phi_\nu},\nonumber\\
+J_{CP}&=-\frac{1}{6\sqrt{3}}\cos2\theta_\nu.
+\end{align}
+The constraint of $\theta_\nu$ and $\phi_\nu$ is presented in Fig.
+}
+
 \section{Model testing}
@@
 More details are presented in the user manual.
-The code for this example is provided as \textbf{th23\_delta.c} in the \textbf{FaSE} distribution.
+The code for this example is provided as
+\textbf{th23\_delta.c} in the \textbf{FaSE} distribution.
+
+{\color{red}We also show the similar result for WFS, and present it in Fig.}
 

### 2020-05-12 doc/paper.tex
update paper draft

@@
 
+\begin{figure}[!h]
+ %\flushleft
+ \centering
+\hspace{15mm}\includegraphics[width=0.5\textwidth]{figs/theta_phi.pdf}
+ \caption{\label{fig:theta_phi} {\color{red}[formate will be further tuned]}}
+\end{figure}
+
 {\color{red}To show the generality of \textbf{FaSE-GLoBES}, we present the similar result with another model -- \textit{the warped flavor symmetry} (WFS).
@@
 \end{align}
-The constraint of $\theta_\nu$ and $\phi_\nu$ is presented in Fig.
-}
+The constraint of $\theta_\nu$ and $\phi_\nu$ is presented in Fig~\ref{fig:theta_phi}, in which we use the best fit of NUFIT 4.0 result as the true values ($(\theta_{12},~\theta_{13},~\theta_{23},~\delta,~\Delta m_{21}^2,~\Delta m_{31}^2)=(33.82^\circ,~8.61^\circ,~49.6^\circ,~215^\circ,~7.39\times10^{-5}~\text{eV}^2,~2.525\times10^{-3}~\text{eV}^2)$).}
 

### 2020-05-13 doc/FAS-GLoBES.tex
update docs and code

@@
 In this work, we will present our simulation tool \textbf{F}l\textbf{a}vour \textbf{S}ymmetry \textbf{E}mbedded - \textbf{GLoBES} (\textbf{FaSE-GloBES}) that is a simulation code based on GLoBES library for studying the flavour symmetry.
-\textbf{FaSE} is a supplemental tool for GLoBES, written in \texttt{c/c++} language, and FASE-GLoBES allows the user to assign the flavour symmetry model and analysis how a flavour symmetry model can be excluded by the simulated neutrino oscillation experiment.
+\textbf{FaSE} is a supplemental tool for GLoBES, written in \texttt{c/c++} language, and FASE-GLoBES allows the user to assign the flavour symmetry model and analyse how a flavour symmetry model can be excluded by the simulated neutrino oscillation experiment.
 
@@
 
-\textbf{F}l\textbf{a}vor \textbf{S}ymmetry \textbf{E}mbedded (\textbf{FaSE}) is a supplemental tool for \textbf{G}eneral \textbf{Lo}ng \textbf{B}aseline \textbf{E}xperiment \textbf{S}imulator (\textbf{GLoBES}) in order to analysis how a leptonic flavour symmetry model can be tested in neutrino oscillation experiments.
+\textbf{F}l\textbf{a}vor \textbf{S}ymmetry \textbf{E}mbedded (\textbf{FaSE}) is a supplemental tool for \textbf{G}eneral \textbf{Lo}ng \textbf{B}aseline \textbf{E}xperiment \textbf{S}imulator (\textbf{GLoBES}) in order to analyse how a leptonic flavour symmetry model can be tested in neutrino oscillation experiments.
 \textbf{FaSE} is written in the \texttt{c/c++} language, and consist with three codes \textbf{FASE\_GLoBES.c} and \textbf{model-input.c}.
@@
 
-Finally, \textbf{GLoBES} is a popular and powerful simulation tool to analysis the neutrino oscillation experiments in a simple language (AEDL), without losing too much detail.
+Finally, \textbf{GLoBES} is a popular and powerful simulation tool to analyse the neutrino oscillation experiments in a simple language (AEDL), without losing too much detail.
 Considering the success of the flavour symmetry theory to explain the neutrino oscillations, \textbf{FaSE-GLoBES} should benefit model builders of leptonic flavour symmetry and phenomenologists for neutrino oscillation physics.

### 2020-05-13 doc/paper.tex
update docs and code

@@
 We present a supplemental tool \textbf{F}l\textbf{a}vour \textbf{S}ymmetry \textbf{E}mbedded (\textbf{FaSE}) for  \textbf{G}eneral \textbf{Lo}ng \textbf{B}aseline \textbf{E}xperiment \textbf{S}imulator (\textbf{GLoBES}).
-\textbf{FaSE}  works with \textbf{GLoBES} (\textbf{FaSE-GLoBES}) to analysis how flavour symmetry models can be examined with simulated neutrino oscillations.
+\textbf{FaSE}  works with \textbf{GLoBES} (\textbf{FaSE-GLoBES}) to analyse how flavour symmetry models can be examined with simulated neutrino oscillations.
 It can translate the model to oscillation parameters, and provides prior functions, in a user-friendly way.
@@
 
-e have presented \textbf{FaSE}, which is a supplemental simulation tool for \textbf{GLoBES} to study the leptonic flavour symmetry with neutrino oscillation experiments in a user-friendly way.
+We have presented \textbf{FaSE}, which is a supplemental simulation tool for \textbf{GLoBES} to study the leptonic flavour symmetry with neutrino oscillation experiments in a user-friendly way.
 \textbf{FaSE} contains two \texttt{c}-codes: \textbf{model-input.c} and \textbf{FASE\_GLoBES.c}.

### 2020-05-13 th23_dCP.c

@@ -66,7 +66,7 @@ int main(int argc, char *argv[])
     glb_params test_values = glbAllocParams();
     glb_params input_errors = glbAllocParams();
     glb_params centers = glbAllocParams();
-    
+    glb_params out = glbAllocParams();
     /*define model parameter: true_values( x, eta, r, ma)*/
     glbDefineParams(test_values,x_true,eta_true,r_true,ma_true,0,0);
     glbSetDensityParams(test_values,1.0,GLB_ALL);
@@ -114,6 +114,10 @@ int main(int argc, char *argv[])
     dth23=(upper_th23-lower_th23)/100; ddCP=(upper_dCP-lower_dCP)/100;
     int dof=2;
     glbSetProjection(free);
+    
+    PARA=MODEL;
+    float res0=glbChiNP(test_values,out,GLB_ALL);
+
     for (th23=lower_th23;th23<=upper_th23;th23=th23+dth23){
     for (dCP=lower_dCP;dCP<=upper_dCP;dCP=dCP+ddCP){
     glbSetOscParams(true_values,th23*degree,GLB_THETA_23);
@@ -123,8 +127,11 @@ int main(int argc, char *argv[])
     glbSetRates();
     PARA=MODEL; /* if the user is interested in the sensitivity on Standard Oscillation parameters*/
         float res=glbChiNP(test_values,NULL,GLB_ALL);
-            fprintf(File,"%f %f %f\n",th23,dCP,gsl_cdf_chisq_Qinv(gsl_cdf_chisq_Q(fabs(res),dof),1));
-//            printf("%f %f %f\n",th23,dCP,res);
+//        float res2=glbChiNP(out,NULL,GLB_ALL);
+//        if(res2<res) {res=res2;}
+            fprintf(File,"%f %f %f\n",th23,dCP,gsl_cdf_chisq_Qinv(gsl_cdf_chisq_Q(fabs(res-res0),dof),1));
+//            printf("%f %f %f\n",th23,dCP,gsl_cdf_chisq_Qinv(gsl_cdf_chisq_Q(fabs(res),dof),1));
+//                    printf("%f %f %f %f\n",th23,dCP,res,res0);
          } fprintf(File,"\n");
     }
  

### 2020-05-15 doc/paper.tex
Polish the texts and add comments.

--- 2020-05-12 doc/paper.tex
@@
 \begin{abstract}
+Neutrino models based on flavour symmetries provide the natural way to explain the origin of tiny neutrino masses.
+At the dawn of precision measurements of neutrino mixing parameters, it is straightforward to constrain and examine neutrino mass models by on-going and next-generation neutrino experiments.
 We present a supplemental tool \textbf{F}l\textbf{a}vour \textbf{S}ymmetry \textbf{E}mbedded (\textbf{FaSE}) for \textbf{G}eneral \textbf{Lo}ng \textbf{B}aseline \textbf{E}xperiment \textbf{S}imulator (\textbf{GLoBES}).
-\textbf{FaSE}  works with \textbf{GLoBES} (\textbf{FaSE-GLoBES}) to analysis how flavour symmetry models can be examined with simulated neutrino oscillations.
-It can translate the model to oscillation parameters, and provides prior functions, in a user-friendly way.
-We demonstrate two examples for \textbf{FaSE-GLoBE}: how model parameters can be constrained and how a model can be excluded by an experiment.
-Finally, we emphasis as \textbf{GLoBES} is now a popular and power tool for neutrino oscillation physics, \textbf{FaSE} is convenient for flavour-symmetry model builders and neutrino oscillation phenomenologists.\\
+It can translate the neutrino mass model inputs to standard neutrino oscillation parameters, and offers prior functions in a user-friendly way.
+We demonstrate the robustness of \textbf{FaSE-GLoBE} with two examples on how the model parameters can be constrained and even whether the model is excluded by an experiment or not.
+We wish that this toolkit will facilitate the study of new neutrino mass models in an effecient and effective manner.\\
 \textbf{Keywords: Neutrino Oscillations, Leptonic Flavour Symmetry}  
@@
 Thanks to the great efforts in the past two decades, we almost have a complete understanding of such a neutrino oscillation framework.
-More data in the neutrino oscillation experiments is needed to determine the sign of $\Delta m_{31}^2$, to measure the value of $\sin\theta_{23}$, to discover the potential CP violation in the leptonic sector and even to constrain the size of $\delta$ \cite{Esteban:2018azc}.
+Nevertheless, more efforts in the neutrino oscillation experiments are needed to determine the sign of $\Delta m_{31}^2$, to measure the value of $\sin\theta_{23}$ more precisely, to discover the potential CP violation in the leptonic sector and even to constrain the size of $\delta$ \cite{Esteban:2018azc}.
 For these purposes, the on-going long baseline experiments (LBLs), such as the NuMI Off-axis $\nu_e$ Appearance experiment (NO$\nu$A)~\cite{Ayres:2007tu} and the Tokai-to-Kamioka experiment (T2K)~\cite{Abe:2011ks}, can answer these questions with the statistical significance $\gtrsim 3\sigma$ in most of the parameter space.
-Based on the analysis with their data, the normal mass ordering ($\Delta m_{31}^2>0$), the higher $\theta_{23}$ octant ($\theta_{23}>45^\circ$), and $\delta\sim270^\circ$ are preferred so far~\cite{Esteban:2018azc}.
+Based on the analysis in T2K and NO$\nu$A, the normal mass ordering ($\Delta m_{31}^2>0$), the higher $\theta_{23}$ octant ($\theta_{23}>45^\circ$), and $\delta\sim270^\circ$ are preferred so far~\cite{Esteban:2018azc}.
 The future LBLs, Deep Underground Neutrino Experiment (DUNE)~\cite{Acciarri:2015uup}, Tokai to Hyper-Kamiokande (T2HK)~\cite{Abe:2014oxa}, and the medium baseline reactor experiment, the Jiangmen Underground Neutrino Observatory (JUNO)~\cite{Djurcic:2015vqa,An:2015jdp} will further complete our knowledge of neutrino oscillations.
 
-Flavour symmetry models are used to explain the origin of the neutrino mixing, and to predict the value of oscillation parameters (some of useful review articles are~\cite{Altarelli:2010gt,Ishimori:2010au,King:2013eh,King:2014nza,King:2015aea,King:2015ata,King:2017guk}).
-These models are motivated by some interesting features, \textit{such as} $\theta_{12}\sim 33^\circ$, and $\theta_{23}\sim 45^\circ$.
-Before the discovery of non-zero $\theta_{13}$ measurement by Daya Bay experiment~\cite{An:2013zwz}, the `tri-bi-maximal' neutrino mixing (TBM) ansatz, which was proposed in 2002 by Horrison, Perkins, and Scott~\cite{Harrison:2002er}, fitted with the experimental data in a good agreement:
+It is clear that neutrinos carry the peculiar mass smaller than $\mathcal{O}(1)$ eV among the elementary particle, although the absolute value of each neutrino mass is unknown.
+In addition, one of the fundamental questions with regards to neutrino properties is how neutrino masses are generated naturally.
+The seesaw mechanism has been used to explain such a tiny mass in the neutrino sector with the help of neutrino flavor mixings.
+Anyhow new particles have to be introduced in such a mechanism.
+The more degrees of freedom in a theoretical model, the less predictivity of observables in experiments.
+Furthermore, flavour symmetries are employed to reduce degrees of freedom in the neutrino mass model.
+These models can explain the origin of the neutrino mixing, and predict correlations of oscillation parameters (some of recent review articles are~\cite{Altarelli:2010gt,Ishimori:2010au,King:2013eh,King:2014nza,King:2015aea,King:2015ata,King:2017guk}).
+Before the discovery of non-zero $\theta_{13}$ by Daya Bay reactor neutrino experiment~\cite{An:2013zwz}, the `tri-bi-maximal' neutrino mixing (TBM) ansatz, which was proposed in 2002 by Horrison, Perkins, and Scott~\cite{Harrison:2002er}, was in line with experimental data:
 \begin{equation*}
@@
 \end{equation*} 
-With the fact that $\theta_{13}\approx 8^\circ$, several ways to obtain such non-zero value of $\theta_{13}$ are proposed.
+Given $\theta_{13}\approx 8^\circ$ measured by several reactor neutrino experiments, we have to break the symmetry pattern to to obtain such non-zero value of $\theta_{13}$.
 One of popular proposals is to correct the tri-bi-maximal neutrino mixing such that
@@
 \end{equation*}
+It is relatively easy for model builders to check the validity of the neutrino mass model and constrain model parameters by the public nufit results [Ref:nufit website].
+However, there is no such a public toolkit to evaluate model predictions in future neutrino experiments.
+\textbf{G}eneral \textbf{Lo}ng \textbf{B}aseline \textbf{E}xperiment \textbf{S}imulator (\textbf{GLoBES}) \cite{Huber:2004ka,Huber:2007ji} is a convenient tool to simulate neutrino oscillation experiments via the Abstract Experiment Definition Language (AEDL) as one of the most popular and useful tools in the community of neutrino oscillation physics.
+Some AEDL files to describe experiments are also available in \textbf{GLoBES} website, while the working group in the DUNE experiment also releases their neutrino flux information and detector descriptions in AEDL files~\cite{Alion:2016uaj}.
+It is to be extended for the purpose of analysing flavour symmetry models in an universal way.
 
-Currently, some works discuss on how the future experiments can be used for testing these flavour symmetry models in the phenomenological point of view, \textit{e.g.}~Ref.~\cite{Ballett:2016yod,Chatterjee:2017xkb,Ding:2019zhn,Tang:2019edw}.
-A large number of these works are based on the \texttt{c}-library -- \textbf{G}eneral \textbf{Lo}ng \textbf{B}aseline \textbf{E}xperiment \textbf{S}imulator (\textbf{GLoBES}) \cite{Huber:2004ka,Huber:2007ji}, which is a convenient simulation tool to simulate neutrino oscillation experiments via the Abstract Experiment Definition Language (AEDL).
-Some AEDL files for experiments are also available on \textbf{GLoBES} website, while the working group of DUNE experiment also releases their AEDL files~\cite{Alion:2016uaj}.
-\textbf{GLoBES} can be taken as one of popular and useful tools in the community of neutrino oscillation physics.
-However, it has not yet to be extended for the purpose of analysing flavour symmetry models.
-In this work, we will present our simulation tool \textbf{F}l\textbf{a}vour \textbf{S}ymmetry \textbf{E}mbedded - \textbf{GLoBES} (\textbf{FaSE-GloBES}) that is a simulation code based on GLoBES library for studying the flavour symmetry.
-\textbf{FaSE} is a supplemental tool for GLoBES, written in \texttt{c/c++} language, and FASE-GLoBES allows the user to assign the flavour symmetry model and analysis how a flavour symmetry model can be excluded by the simulated neutrino oscillation experiment.
+As we approach the era of precision measurements in the neutrino oscillations, recent works pay more attentions to how the future neutrino experiments can be used to test these flavour-symmetry neutrino mass models, \textit{e.g.}~Ref.~\cite{Ballett:2016yod,Chatterjee:2017xkb, Ding:2019zhn, Tang:2019edw, Blennow:2020snb}.
+In this work, we will present our simulation toolkit \textbf{F}l\textbf{a}vour \textbf{S}ymmetry \textbf{E}mbedded - \textbf{GLoBES} (\textbf{FaSE-GloBES}) in a C-library to facilitate the study in the flavour symmetry neutrino models.
+\textbf{FaSE} is a supplemental tool for GLoBES, written in \texttt{c/c++} language, and allows users to assign any flavour symmetry model and analyze how a flavour symmetry model is constrained by the simulated neutrino oscillation experiments.
 
@@
 
-\textbf{F}l\textbf{a}vor \textbf{S}ymmetry \textbf{E}mbedded (\textbf{FaSE}) is a supplemental tool for \textbf{G}eneral \textbf{Lo}ng \textbf{B}aseline \textbf{E}xperiment \textbf{S}imulator (\textbf{GLoBES}) in order to analysis how a leptonic flavour symmetry model can be tested in neutrino oscillation experiments.
-\textbf{FaSE} is written in the \texttt{c/c++} language, and consist with three codes \textbf{FASE\_GLoBES.c} and \textbf{model-input.c}.
-The user defines the model in to \textbf{model-input.c}, while \textbf{FASE\_GLoBES.c} does not need to be touched.
+\textbf{FaSE-GLoBES} is written in the \texttt{c} language, and consists of two source codes \textbf{FASE\_GLoBES.c} and \textbf{model-input.c}.
+The user defines the correlations between model inputs and standard neutrino mixing parameters in \textbf{model-input.c}, while \textbf{FASE\_GLoBES.c} is an engine to perform analysis with user-specified experiments in a simulaton.
+Note that we define the standard neutrino mixing/oscillation parameters $\vec{\theta}_{OSC}$ ($\theta_{12}$, $\theta_{13}$, $\theta_{23}$, $\Delta m_{21}^2$, $\Delta m_{31}^2$, $\delta$) to separate from model parameters $\vec{\theta}_{Model}$ hereafter.
 
@@
 The concept of \textbf{FaSE-GLoBES} is shown in Fig.~\ref{fig:FASE}, in which three parts are shown: 1.~\textbf{the parameter translation} (the blue box), 2.~\textbf{giving oscillation-parameter values} (the green box), and 3.~\textbf{the $\chi^2$-value calculation} (the orange box).
-The idea behind this flow chart Fig.~\ref{fig:FASE} is that given a set of value for model parameter, the corresponding values for oscillation parameters are obtained by a translation, which is assigned by the user in \textbf{model-input.c}.
-And then, through \textbf{FASE\_GLoBES.c} these oscillation-parameter values are passed in to \textbf{GLoBES} library to simulate the event spectrum for evaluating the $\chi^2$ value.
+The idea behind this flow chart Fig.~\ref{fig:FASE} is that given a set of model parameters, the corresponding values in standard oscillation parameters are obtained by a translation, which is assigned by the user in \textbf{model-input.c}.
+And then, through \textbf{FASE\_GLoBES.c} these oscillation-parameter values are passed into \textbf{GLoBES} library to simulate the event spectra so that we can perform physics analysis in the newly-defined $\chi^2$.
 
-API functions in \textbf{FaSE} are listed:
+Application Programming Interface (API) functions in \textbf{FaSE-GLoBES} are listed:
 \begin{enumerate}
@@
 The first one is to initialise \textbf{FaSE} with the number of input parameters $N_{para}$.
-The next three functions need to be included to replace the default \textbf{GLoBES} probability engine by the one that can read the output from \textbf{model-input.c}, as follows.\vspace{0.2cm}\\
-\texttt{    glbRegisterProbabilityEngine(6,\\
-                                 \&FASE\_glb\_probability\_matrix,\\
-                                 \&FASE\_glb\_set\_oscillation\_parameters,\\
-                                 \&FASE\_glb\_get\_oscillation\_parameters,\\
-                                 NULL); }\vspace{0.2cm}\\ 
+The next three functions need to be included to replace the default \textbf{GLoBES} probability engine by the one that can read the output from \textbf{model-input.c}, as follows.
+% \vspace{0.2cm}\\
+% \texttt{    glbRegisterProbabilityEngine(6,\\
+%                                  \&FASE\_glb\_probability\_matrix,\\
+%                                  \&FASE\_glb\_set\_oscillation\_parameters,\\
+%                                  \&FASE\_glb\_get\_oscillation\_parameters,\\
+%                                  NULL); }\vspace{0.2cm}\\
+\begin{verbatim}
+ glbRegisterProbabilityEngine(6,
+                                 &FASE_glb_probability_matrix,
+                                 &FASE_glb_set_oscillation_parameters,
+                                 &FASE_glb_get_oscillation_parameters,
+                                 NULL);
+\end{verbatim}
+
 This probability engine can work with oscillation or model parameters.
@@
 The final two items on the API list are prior functions.
-Once the user gives the prior in oscillation (model) parameters, the user needs to call \texttt{FASE\_prior\_OSC} (\texttt{FASE\_prior\_model}) as follows.\vspace{0.2cm}\\
-\texttt{glbRegisterPriorFunction(FASE\_prior\_OSC,NULL,NULL,NULL); }  \\
-or\\
-\texttt{glbRegisterPriorFunction(FASE\_prior\_model,NULL,NULL,NULL); } \vspace{0.2cm}\\
+Once the user gives the prior in oscillation (model) parameters, the user needs to call \texttt{FASE\_prior\_OSC} (\texttt{FASE\_prior\_model}) as follows.
+% \vspace{0.2cm}\\
+% \texttt{glbRegisterPriorFunction(FASE\_prior\_OSC,NULL,NULL,NULL); }  
+% \\
+\begin{verbatim}
+ glbRegisterPriorFunction(FASE_prior_OSC,NULL,NULL,NULL);
+\end{verbatim}
+or
+% \\
+% \texttt{glbRegisterPriorFunction(FASE\_prior\_model,NULL,NULL,NULL); } \vspace{0.2cm}\\
+\begin{verbatim}
+ glbRegisterPriorFunction(FASE_prior_model,NULL,NULL,NULL);
+\end{verbatim}
+
 We note that except for setting the probability engine and the prior function, the other parts in the main code should follow with the GLoBES manual.
@@
 
-The function \texttt{MtoS} can do the translator from model parameters $\vec{\theta}_{Model}$ to oscillation parameters $\vec{\theta}_{OSC}$.
+The function \texttt{MtoS} can do the translation from model parameters $\vec{\theta}_{Model}$ to oscillation parameters $\vec{\theta}_{OSC}$.
 After the user gives the array $\vec{\theta}_{Model}$ to the function \texttt{MtoS}, the output is the corresponding oscillation parameter $\vec{\theta}_{OSC}$, of which components are $\theta_{12}$, $\theta_{13}$, $\theta_{23}$, $\delta$, $\Delta m_{21}^2$, and $\Delta m_{31}^2$.
 For the first four components, values are given in the unit of \textbf{rad}, while the other two are in \textbf{eV$^2$}.
-These values will be passed in to \textbf{FaSE\_GLoBES} to simulate
-the experimental spectra and compute the prior value.
+These values will be passed into \textbf{FaSE\_GLoBES} to simulate
+the experimental spectra and compute the prior values.
 
-To do the translation from $\vec{\theta}_{Model}$ to $\vec{\theta}_{OSC}$, the user can assign the relation between the oscillation and model parameter sets, or define the mass matrix in model parameters, which will be diagonalised by the function \texttt{ModelTO} to obtain the corresponding oscillation-parameter values.
+To transform from $\vec{\theta}_{Model}$ to $\vec{\theta}_{OSC}$, the user can assign the correlation between the standard oscillation and model parameter sets, or define the mass matrix in model parameters, which will be diagonalised by the function \texttt{ModelTO} to obtain the corresponding oscillation-parameter values.
 %The relation between the oscillation and model parameter sets can be derived out by the user, 
 In the way of directly giving the relation between oscillation and model parameter sets, the user needs to provide
-\begin{equation}\label{eq:modelofOSC}
-\vec{\theta}_{Model}=\vec{f}(\vec{\theta}_{OSC})
-\end{equation}
- in the function \texttt{MtoS}.
+$\vec{\theta}_{Model}=\vec{f}(\vec{\theta}_{OSC})$ in the function \texttt{MtoS}.
 %
@@
 The matrix $\mathcal{M}$ is given by user with model parameters $\vec{\theta}_{Model}$.
-The matrix $U$ is the neutrino mixing matrix, and can be used for getting mixing angles.
+The matrix $U$ is the neutrino mixing matrix, and can be used to get mixing angles, mass squared differences and the CP phase.
 The difference between any two diagonal elements of $\textbf{M}$ ($\textbf{M}_{ii}-\textbf{M}_{jj}=m_i^2-m_j^2$) is the mass-squared difference ($\Delta m_{ij}^2$).
-This diagnolisation Eq.~\ref{eq:MM} can be done with the function \texttt{ModelTO}, which needs to be called in \texttt{MtoS} and outputs directly the vector $\vec{\theta}_{OSC}$.
+This diagnolisation Eq.~(\ref{eq:MM}) can be done by the function \texttt{ModelTO}, which needs to be called in \texttt{MtoS} with outputs of the vector $\vec{\theta}_{OSC}$.
 
 \section{Prior setting}\label{sec:prior}
-Given a set of values for model parameters, \textbf{FASE\_GLoBES.c} will obtain the corresponding oscillation-parameter values from \textbf{model-input.c}, and will pass these values to simulate event spectra and to compute the prior value.
-Two gaussian prior functions are provided in \textbf{FaSE} -- \texttt{FASE\_prior\_OSC} and \texttt{FASE\_prior\_model}.
-These two functions are for different purposes.
-If the user give the prior in oscillation (model) parameters, the user should register \texttt{FASE\_prior\_OSC} (\texttt{FASE\_prior\_model}) with the \textbf{GLoBES} function \texttt{glbRegisterPriorFunction}, as we introduced in the beginning of this section.
-The user also needs to assign the parameter \texttt{PARA=STAN} (\texttt{PARA=Model}), when the user prefers to give the prior in oscillation (model) parameters.
+Given a set of values for model parameters, \textbf{FASE\_GLoBES.c} will obtain the corresponding oscillation-parameter values from \textbf{model-input.c}, and will pass these values to simulate event spectra and to compute the prior values.
+Two gaussian prior functions are provided in \textbf{FaSE}: \texttt{FASE\_prior\_OSC} and \texttt{FASE\_prior\_model}.
+These two functions are constructed for different purposes.
+If the user gives the prior in oscillation (model) parameters, the user should register \texttt{FASE\_prior\_OSC} (\texttt{FASE\_prior\_model}) with the \textbf{GLoBES} function \texttt{glbRegisterPriorFunction}, as we introduced in the previous section.
+The user also needs to assign the parameters \texttt{PARA=STAN} (\texttt{PARA=Model}), when the user prefers to give the prior in oscillation (model) parameters.
 The Gaussian prior is
@@
 
-Finally, some restrictions are imposed by the studied flavour symmetry model.
+Finally, some restrictions are imposed by the chosen flavour symmetry model.
 We set up these restrictions in the function \texttt{model\_restriction} in \texttt{model-input.c}.
@@
 Then, when the restriction is broken, \texttt{model\_restriction} returns the value $1$ to the prior function \texttt{FASE\_prior\_OSC} or \texttt{FASE\_prior\_model}.
-Therefore, if there is no any restrictions, we simply \textit{return $0$} in \texttt{model\_restriction} as follows.\vspace{0.2cm}\\
-\texttt{double model\_restriction(double model [])\{ return 0;\} }\vspace{0.2cm}\\
+Therefore, if there is no restriction, we simply \textit{return $0$} in \texttt{model\_restriction} as follows.
+% \vspace{0.2cm}\\
+% \texttt{double model\_restriction(double model [])\{ return 0;\} }\vspace{0.2cm}\\
+\begin{verbatim}
+ double model_restriction(double model []){ return 0;};
+\end{verbatim}
+
 %In the following, the prior function will give $10^6$ for the $\chi^2$ value, and it will be selected out when the user studies the statistically reasonable region in the parameter space.
@@
 
-The user can use \textbf{FaSE-GLoBES} to study the constraint of model parameters.
-The expression of $\chi^2$ is used as the default \textbf{GLoBES} setting.
-In more detail, the $\chi^2$ function is constructed based on a log-likelihood ratio,
+The user can use \textbf{FaSE-GLoBES} to constrain model parameters.
+The expression $\chi^2$ is used as the default \textbf{GLoBES} setting.
+\textcolor{red}{[JT: What is the meaning of this $\chi^2$ here?]} In more detail, the $\chi^2$ function is constructed based on a log-likelihood ratio,
 %\begin{equation}\label{eq:chi-squared}
@@
 %\end{equation}
-where $i$ runs over the number of bins, $\eta_i(\vec{\theta},\xi_s,\xi_b)$ is the hypothesis event rate for bin i and $E_i$ is the central bin energy.
-The vector $\vec{\theta}$ consists of tested model or oscillation parameters.
-The parameters $\xi_s$ and $\xi_b$ are introduced to account for the systematic uncertainty of normalisation for the signal (subscript $_s$) and background (subscript $_b$) components for the event rate, and are allowed to vary in the fit as nuisance parameters.
-For a given hypothesised set of parameters $\vec{\theta}$, the event rate for bin $i$ is calculated as\\
+where $i$ runs over the number of bins, $\eta_i(\vec{\theta},\xi_s,\xi_b)$ is the assumed event rate in the $i$th bin and $E_i$ is the central value in this energy bin.
+The vector $\vec{\theta}$ consists of model or oscillation parameters.
+The parameters $\xi_s$ and $\xi_b$ are introduced to account for the systematic uncertainties in the normalisation for the signal (subscript $_s$) and background (subscript $_b$) components of the event rate, and are allowed to vary in the fit as nuisance parameters.
+For a given set of parameters $\vec{\theta}$, the event rate in the $i$th energy bin is calculated as\\
 \begin{equation}
@@
 \end{equation}
-where $s_i$ and $b_i$ are the expected number of signal and background events in bin $i$, respectively.
+where $s_i$ and $b_i$ are the expected number of signal and background events in $i$th energy bin, respectively.
 The nuisance parameters are constrained by the Gaussian prior $p(\xi,\sigma)=\xi^2/\sigma^2$ with corresponding uncertainties $\sigma_s$ and $\sigma_b$ for the signal and background, respectively.
@@
 
-Based on the $\chi^2$ value Eq.~\ref{eq:chi-squared}, we can study how model parameters can be constrained and how a flavour-symmetry model can be tested by simulated experiments.
-In the following we will introduce how it works.
+Based on the $\chi^2$ value Eq.~\ref{eq:chi-squared}, we can study how model parameters can be constrained and whether a flavour-symmetry neutrino model is excluded by simulated experiments.
+In the following we will demonstrate with typical examples how it works.
 
@@
 
-The user of \textbf{FaSE-GLoBES} is able to study how model parameters can be constrained by the simulated experiment.
-To do so, the user needs to define the true event spectrum $n_i$ with a set of model ($\vec{\theta}_{Model}^{true}$) or oscillation parameters ($\vec{\theta}_{OSC}^{true}$), \textit{i.e.}~set up $n_i(\vec{\theta}_{Model}^{true})$ or $n_i(\vec{\theta}_{OSC}^{true})$.
+The user of \textbf{FaSE-GLoBES} is able to study how model parameters can be constrained by the simulated experiments.
+To do so, the user needs to simulate the true event spectrum $n_i$ with a set of model ($\vec{\theta}_{Model}^{true}$) or oscillation parameters ($\vec{\theta}_{OSC}^{true}$), \textit{i.e.}~set up $n_i(\vec{\theta}_{Model}^{true})$ or $n_i(\vec{\theta}_{OSC}^{true})$.
 The hypothesis $\vec{\theta}_{Model}^{hyp}$ predicts the tested event spectrum $\eta_i(\vec{\theta}_{Model}^{hyp},\xi_s,\xi_b)$.
-With the default setting for $\chi^2$ function Eq.~\ref{eq:prior}, from \textbf{FaSE-GLoBES} the user computes the statistical quantity,
+With the default settings for $\chi^2$ function as Eq.~(\ref{eq:prior}) in \textbf{FaSE-GLoBES}, the user computes the statistical quantity,
 \begin{equation}\label{eq:chi_model}
@@
 We note that the minimum of $\chi^2$ in the whole parameter space ($\chi^2_{min.}$) may not be $0$.
-Therefore, to study the precision of model parameters, the user should use the value $\Delta\chi^2(\vec{\theta}_{Model}^{hyp})\equiv \chi^2(\vec{\theta}_{Model}^{hyp})-\chi^2_{min.}$, instead of $\chi^2$ itself.
-By varying different hypothesis $\vec{\theta}_{Model}^{hyp}$, the user can obtain the allowed region of model parameters with the statistical quantity $\Delta\chi^2(\vec{\theta}_{Model}^{hyp})$.
+Therefore, to get the precision of model parameters, the user should use the value $\Delta\chi^2(\vec{\theta}_{Model}^{hyp})\equiv \chi^2(\vec{\theta}_{Model}^{hyp})-\chi^2_{min.}$, instead of $\chi^2$ itself.
+By varying different hypotheses $\vec{\theta}_{Model}^{hyp}$, we will obtain the allowed region of model parameters with the statistical quantity $\Delta\chi^2(\vec{\theta}_{Model}^{hyp})$.
 
-The user can also study how well a flavour symmetry model explains the computed data as predicting how the simulated experiment can exclude this model.
-In the other word, the user studies the minimum of $\chi^2$ for the flavour symmetry model $\vec{\theta}_{Model}$ as a hypothesis, assuming different true oscillation values, \textit{i.e.}~different $\vec{\theta}^{true}_{OSC}$.
-To do so, we compute the same statistical quantity Eq.~\ref{eq:chi_model}, while the true spectrum is varied with different true values $\vec{\theta}_{OSC}^{true}$.
+The user can also study how well a flavour symmetry model explains the computed data, or predict whether the simulated experiment can exclude this model or not.
+In other words, the user studies the minimum of $\chi^2$ for the flavour symmetry model $\vec{\theta}_{Model}$ as a hypothesis, by assuming different true oscillation values, \textit{i.e.}~different $\vec{\theta}^{true}_{OSC}$.
+To do so, one can compute the same statistical quantity Eq.~(\ref{eq:chi_model}), while the true spectrum is varied with different true values $\vec{\theta}_{OSC}^{true}$.
 All model parameters are allowed to be varied with the user-defined prior.
 %
-Finally, the user needs to adopt Wilk's theorem \cite{Wilks:1938dza}.
-When comparing nested models, the $\Delta \chi^2$ test statistics is a random variable asymptotically distributed according to the $\chi^2$-distribution with the number of degrees of freedom, which is equal to the difference in the number of free model parameters \texttt{dof}.
+Finally, the user might adopt Wilk's theorem to interpret results~\cite{Wilks:1938dza}.
+When we compare nested models, the $\Delta \chi^2$ test statistics is a random variable asymptotically distributed as a $\chi^2$-distribution with the number of degrees of freedom, which is equal to the difference in the number of free model parameters \texttt{dof}.
 
@@
 
-\textbf{FaSE-GloBES} can be used to study how the model parameter is constrained by simulated neutrino oscillation experiments.
+\textbf{FaSE-GloBES} can be used to study how model parameters are constrained by simulated neutrino oscillation experiments.
 We take \textit{the tri-direct littlest seesaw} (TDLS)~\cite{King:2013iva,King:2015dvf,King:2016yvg} as an example.
-Under this model, the light left-handed Majorana neutrino mass matrix is given by
+In this model, the light left-handed Majorana neutrino mass matrix is given by
 \begin{equation}
@@
 \end{equation}
-where $x$, $\eta$, $m_a$, and the ratio $r\equiv m_s/m_a$ are four parameters and will be constrained by experimental data.
+where $x$, $\eta$, $m_a$, and the ratio $r\equiv m_s/m_a$ are four parameters to be constrained by simulated data.
 We note that from Eq.~(\ref{eq:mnu}), $m_1=0$ and the normal mass ordering are imposed, and will need to be imposed in \textbf{FaSE-GLoBES}.
@@
  \centering
-\hspace{15mm}\includegraphics[width=0.5\textwidth]{figs/x_eta.pdf}
- \caption{\label{fig:x_eta}Precision measurements of any two model parameters in the framework of three neutrino oscillations taking uncertainties of the current global fit results, for MOMENT, at $1\sigma$ (gray), $2\sigma$ (orange), $3\sigma$ (black).
+\hspace{15mm}\includegraphics[width=0.5\textwidth]{Figs/x_eta.pdf}
+ \caption{\label{fig:x_eta}Precision measurements of two model parameters in the framework of three neutrino oscillations taking uncertainties of the current global fit results, for MOMENT, at $1\sigma$ (gray), $2\sigma$ (orange), $3\sigma$ (black).
 True values for the model parameters are used $(x,~\eta,~r,~M_a)=(-3.65,~1.13\pi,~0.511,~3.71~\text{meV})$.}
@@
 In Fig.~\ref{fig:x_eta}, we study how parameters $x$ and $\eta$ can be constrained by the MuOn-decay MEdium baseline NeuTrino beam experiment (MOMENT)~\cite{Cao:2014bea}.
-We input the model by giving model parameters as functions of oscillation parameters Eq.~\ref{eq:modelofOSC}.
-And, parameters $r$ and $ma$ are varied with the prior that is given in oscillation parameters, according to the global-fit result NUFIT4.0.
+We input the model by giving model parameters as functions of standard oscillation parameters Eq.~(\ref{eq:modelofOSC}).
+Besides, parameters $r$ and $ma$ are varied with the prior that is given in standard oscillation parameters, according to the global-fit result NUFIT4.0.
 More details are presented in the user manual.
@@
  \centering
-\hspace{15mm}\includegraphics[width=0.5\textwidth]{figs/theta_phi.pdf}
+\hspace{15mm}\includegraphics[width=0.5\textwidth]{Figs/theta_phi.pdf}
  \caption{\label{fig:theta_phi} {\color{red}[formate will be further tuned]}}
@@
 
-{\color{red}To show the generality of \textbf{FaSE-GLoBES}, we present the similar result with another model -- \textit{the warped flavor symmetry} (WFS).
-This model predict the simplification that mixing angles and the CP phase are functions of two model parameters $\theta_\nu$ and $\phi_\nu$,
+{\color{red}To show the generality of \textbf{FaSE-GLoBES}, we present the similar result with another model -- \textit{the warped flavor symmetry} (WFS) [Ref???].
+This model predict further simplified correlations that the standard oscillation parameters including mixing angles and the CP phase are functions of only two model parameters $\theta_\nu$ and $\phi_\nu$,
 \begin{align}
@@
  \centering
-\includegraphics[width=0.5\textwidth]{figs/SR_th23_dCP.pdf}
+\includegraphics[width=0.5\textwidth]{Figs/SR_th23_dCP.pdf}
 \caption{\label{fig:th23_delta}The 2-D exclusion contour for tri-direct littlest seesaw model on the plane of two true standard parameters $\theta_{23}$ and $\delta$, from $1\sigma$ to $5\sigma$.
@@
 
-We can also study on excluding the model, assuming different true values for oscillation parameters.
+We can also study on whether a neutrino mass model is excluded or not, assuming different true values for oscillation parameters.
 In this example, we present testing the TDLS model in various true values of $\theta_{23}$ and $\delta$.
-We compute the minimal $\chi^2$ value for the tested model with all four model parameters, varied with the prior Eq.~\ref{eq:prior} according to NUFIT4.0 result.
-And, the studied statistics function is exactly Eq.~\ref{eq:chi-squared}, but the true event rate $n_i$ is predicted by a set of oscillation parameters, which will be varied in the code.
+We compute the minimal $\chi^2$ value for the model with all four model parameters, varied with the prior Eq.~(\ref{eq:prior}) according to NUFIT4.0 results.
+In addition, the studied statistics function is exactly given by Eq.~(\ref{eq:chi-squared}), but the true event rate $n_i$ is predicted by a set of oscillation parameters, which will be varied in the code.
 
-Mentioned in Sec.~\ref{sec:chi-squared}, the user need to consider Wilk's theory with the different of degrees of freedom between the true theory and the hypothesis, \texttt{dof}.
-Here the number \texttt{dof} is $2$.
+As mentioned in Sec.~\ref{sec:chi-squared}, the user needs to consider Wilk's theorem with the different of degrees of freedom between the true theory and the hypothesis, \texttt{dof}.
+\textcolor{red}{[JT: what is the meaning of the true theory?]} Here the number \texttt{dof} is $2$.
 And that is our output: \texttt{gsl\_cdf\_chisq\_Qinv(gsl\_cdf\_chisq\_Q(fabs(res),dof),1)}.
-We show the result in Fig.~\ref{fig:th23_delta}.
+\textcolor{red}{[I don't understand this sentence.]} We show the result in Fig.~\ref{fig:th23_delta}.
 More details are presented in the user manual.
@@
 \section{Summary and conclusions}
+\textcolor{red}{[JT: This section has to be significantly improved.]}
 
-e have presented \textbf{FaSE}, which is a supplemental simulation tool for \textbf{GLoBES} to study the leptonic flavour symmetry with neutrino oscillation experiments in a user-friendly way.
+We have presented a simulation toolkit \textbf{FaSE-GLoBES} to study the leptonic flavour symmetry models with neutrino oscillation experiments in a user-friendly way.
 \textbf{FaSE} contains two \texttt{c}-codes: \textbf{model-input.c} and \textbf{FASE\_GLoBES.c}.
@@
 
- \begin{acknowledgements}
-\end{acknowledgements}
+\acknowledgements{
+This work was supported in part by Guangdong Basic and Applied Basic Research Foundation under Grant No.
+2019A1515012216, National Natural Science Foundation of China under Grant Nos.
+11505301 and 11881240247, the university funding based on National SuperComputer Center-Guangzhou.
+Jian Tang acknowledge the support from the CAS Center for Excellence in Particle Physics (CCEPP).
+Tse-Chun Wang was supported in part by Postdoctoral recruitment program in Guangdong province.
+}
 

### 2020-05-18 doc/paper.tex
update docs

@@
 \centering
-\includegraphics[width=4.5in]{Figs/FASE-chart_1_2.pdf}
+\includegraphics[width=7.5in]{Figs/FASE-chart_1_2.pdf}
 \caption{A scheme to correlate the model parameters with standard neutrino oscillation parameters. The error propagation is implemented in the simulation code up to the spectra analysis.}%
@@
 The user can use \textbf{FaSE-GLoBES} to constrain model parameters. 
+{\color{blue}Suppose we have the measurement $\vec{x}$ and the likelihood function $L(\vec{\theta})=P(\vec{x}|\vec{\theta})$ for a set of parameters $\vec{\theta}=(\theta_1,...,\theta_N)$, where $P(\vec{x}|\vec{\theta})$ is the probability function for data $\vec{x}$ in favour of the hypothesis $\vec{\theta}$.
+The constraint of model parameters can be obtained with the statistis parameter $\chi^2\equiv \ln L(\vec{\theta})$.}
 The expression $\chi^2$ is used as the default \textbf{GLoBES} setting.
-\textcolor{red}{[JT: What is the meaning of this $\chi^2$ here?]} In more detail, the $\chi^2$ function is constructed based on a log-likelihood ratio,
+\textcolor{red}{[JT: What is the meaning of this $\chi^2$ here?]} In more detail, the $\chi^2$ function{\color{blue}, following the Poisson distribution,} is constructed based on a log-likelihood ratio,
 %\begin{equation}\label{eq:chi-squared}
@@
 
-{\color{red}To show the generality of \textbf{FaSE-GLoBES}, we present the similar result with another model -- \textit{the warped flavor symmetry} (WFS) [Ref???].
+{\color{red}To show the generality of \textbf{FaSE-GLoBES}, we present the similar result with another model -- \textit{the warped flavor symmetry} (WFS)~\cite{Chen:2015jta}.
 This model predict further simplified correlations that the standard oscillation parameters including mixing angles and the CP phase are functions of only two model parameters $\theta_\nu$ and $\phi_\nu$,
@@
  \centering
-\includegraphics[width=0.5\textwidth]{Figs/SR_th23_dCP.pdf}
-\caption{\label{fig:th23_delta}The 2-D exclusion contour for tri-direct littlest seesaw model on the plane of two true standard parameters $\theta_{23}$ and $\delta$, from $1\sigma$ to $5\sigma$.
+\includegraphics[width=0.5\textwidth]{Figs/SR_th23_dCP_DUNE_MOMENT.pdf}
+\caption{\label{fig:th23_delta}The 2-D exclusion contour for sub-models of tri-direct littlest seesaw on the plane of two true standard parameters $\theta_{23}$ and $\delta$, from $1\sigma$ to $5\sigma$, for DUNE (dotted) and MOMENT (solid).
 The range for each parameter is taken according to the $3\sigma$ uncertainty in NuFit4.0 results.
@@
 We can also study on whether a neutrino mass model is excluded or not, assuming different true values for oscillation parameters.
-In this example, we present testing the TDLS model in various true values of $\theta_{23}$ and $\delta$.
-We compute the minimal $\chi^2$ value for the model with all four model parameters, varied with the prior Eq.~(\ref{eq:prior}) according to NUFIT4.0 results.
+In this example, we present testing sub-models of TDLS in various true values of $\theta_{23}$ and $\delta$.
+We compute the minimal $\chi^2$ value for the model with $r$ and $m_a$, varied with the prior Eq.~(\ref{eq:prior}) according to NUFIT4.0 results.
+Two parameters $x$ and $\eta$ are fixed at the best fit.
 In addition, the studied statistics function is exactly given by Eq.~(\ref{eq:chi-squared}), but the true event rate $n_i$ is predicted by a set of oscillation parameters, which will be varied in the code.
 
-As mentioned in Sec.~\ref{sec:chi-squared}, the user needs to consider Wilk's theorem with the different of degrees of freedom between the true theory and the hypothesis, \texttt{dof}.
-\textcolor{red}{[JT: what is the meaning of the true theory?]} Here the number \texttt{dof} is $2$.
-And that is our output: \texttt{gsl\_cdf\_chisq\_Qinv(gsl\_cdf\_chisq\_Q(fabs(res),dof),1)}.
-\textcolor{red}{[I don't understand this sentence.]} We show the result in Fig.~\ref{fig:th23_delta}.
-More details are presented in the user manual.
-The code for this example is provided as
+As mentioned in Sec.~\ref{sec:chi-squared}, the user needs to consider Wilk's theorem with the different of degrees of freedom between the {\color{blue}assumed} true theory and the hypothesis, \texttt{dof}.
+{\color{blue}`The assumed true theory' here means that the oscillation parameters assumed for predicting the true event spectrum.} \textcolor{red}{[JT: what is the meaning of the true theory?]}
+%Here the number \texttt{dof} is $2$. 
+%And that is our output: \texttt{gsl\_cdf\_chisq\_Qinv(gsl\_cdf\_chisq\_Q(fabs(res),dof),1)}. \textcolor{red}{[I don't understand this sentence.]} 
+We show the result in Fig.~\ref{fig:th23_delta}. More details are presented in the user manual. The code for this example is provided as 
 \textbf{th23\_delta.c} in the \textbf{FaSE} distribution.

### 2020-05-18 doc/paper.tex
update docs

@@
  \centering
-\hspace{15mm}\includegraphics[width=0.5\textwidth]{Figs/x_eta.pdf}
- \caption{\label{fig:x_eta}Precision measurements of two model parameters in the framework of three neutrino oscillations taking uncertainties of the current global fit results, for MOMENT, at $1\sigma$ (gray), $2\sigma$ (orange), $3\sigma$ (black).
+\includegraphics[width=0.48\textwidth]{Figs/x_eta.pdf}
+ \includegraphics[width=0.48\textwidth]{Figs/theta_phi.pdf}
+% \caption{\label{fig:constraint}Precision measurements of two model parameters in the framework of three neutrino oscillations taking uncertainties of the current global fit results, for MOMENT, at $1\sigma$ (gray), $2\sigma$ (orange), $3\sigma$ (black).
 True values for the model parameters are used $(x,~\eta,~r,~M_a)=(-3.65,~1.13\pi,~0.511,~3.71~\text{meV})$.}
+ %
+  \caption{\label{fig:constraint}Examples for using \textbf{FaSE-GLoBES} to obtain the constraints of model parameters for tri-direct littlest seesaw (left) and the warped flavor symmetry (right), with simulated DUNE and MOMENT data.
+{\color{blue}[the left panel will be updated]}}
 \end{figure}
 
-In Fig.~\ref{fig:x_eta}, we study how parameters $x$ and $\eta$ can be constrained by the MuOn-decay MEdium baseline NeuTrino beam experiment (MOMENT)~\cite{Cao:2014bea}.
+In Fig.~\ref{fig:constraint}, we study how parameters $x$ and $\eta$ can be constrained by the MuOn-decay MEdium baseline NeuTrino beam experiment (MOMENT)~\cite{Cao:2014bea}.
 We input the model by giving model parameters as functions of standard oscillation parameters Eq.~(\ref{eq:modelofOSC}).
@@
 
-\begin{figure}[!h]
- %\flushleft
- \centering
-\hspace{15mm}\includegraphics[width=0.5\textwidth]{Figs/theta_phi.pdf}
- \caption{\label{fig:theta_phi} {\color{red}[formate will be further tuned]}}
-\end{figure}
+%\begin{figure}[!h]
+% \centering
+%\hspace{15mm}\includegraphics[width=0.5\textwidth]{Figs/theta_phi.pdf}
+ %\caption{\label{fig:theta_phi} {\color{red}[formate will be further tuned]}}
+%\end{figure}
 
@@
 \end{align}
-The constraint of $\theta_\nu$ and $\phi_\nu$ is presented in Fig~\ref{fig:theta_phi}, in which we use the best fit of NUFIT 4.0 result as the true values ($(\theta_{12},~\theta_{13},~\theta_{23},~\delta,~\Delta m_{21}^2,~\Delta m_{31}^2)=(33.82^\circ,~8.61^\circ,~49.6^\circ,~215^\circ,~7.39\times10^{-5}~\text{eV}^2,~2.525\times10^{-3}~\text{eV}^2)$).}
+The constraint of $\theta_\nu$ and $\phi_\nu$ is presented in the right panel of Fig~\ref{fig:constraint}, in which we use the best fit of NUFIT 4.0 result as the true values ($(\theta_{12},~\theta_{13},~\theta_{23},~\delta,~\Delta m_{21}^2,~\Delta m_{31}^2)=(33.82^\circ,~8.61^\circ,~49.6^\circ,~215^\circ,~7.39\times10^{-5}~\text{eV}^2,~2.525\times10^{-3}~\text{eV}^2)$).}
 

### 2020-05-19 doc/paper.tex
update paper draft

@@
 \textbf{FaSE} contains two \texttt{c}-codes: \textbf{model-input.c} and \textbf{FASE\_GLoBES.c}.
-Shown in Fig.~\ref{fig:FASE}, \textbf{FASE\_GLoBES}, which calls functions in \textbf{model-input.c}, plays a role as a bridge between \textbf{FaSE} and \textbf{GLoBES} to simulate the event spectrum and compute the prior value.
-It can be left to be untouched by users.
-However, all inputs from the user needs to be given in \textbf{model-input.c}.
-The user can provide the relation between model and oscillation parameters, or simply give the mass matrix predicted by the studied model.
-The prior can be assigned as a Gaussian distribution in model or oscillation parameters.
-Central values and widths are given by the user in the main code through three arrays.
-Given a set of model parameters $\vec{\theta}_{Model}$, with \textbf{GLoBES}, the output can be the $\chi^2$ value for the hypothesis $\vec{\theta}_{Model}$ in the simulated experiments.
-
-We also present demonstrate examples for \textbf{FaSE-GLoBES} with the flavour symmetry model -- tri-direct littlest seesaw (TDLS) -- and the future neutrino oscillaiton experiment -- MOMENT.
-We demonstrate how to use \textbf{FaSE-GLoBES} to obtain the constraint of any two of model parameters, and to study the ability to TDLS by MOMENT experiment.
+While \textbf{FASE\_GLoBES.c} plays a role as a bridge between \textbf{FaSE} and \textbf{GLoBES}, all inputs from the user needs to be given in \textbf{model-input.c}.
+Two main functions provided by \textbf{FaSE} for users are a convenient way to assign a flavour symmetry model and to include Gaussian priors that can be in oscillation or model parameters.
+%
+With \textbf{FaSE-GLoBES}, users are able to study how a flavour model can be studied by the simulated experimental configuration in varieties of perspectives, \textit{e.g.} model parameter constraints, hypothesis testing.
 

### 2020-05-19 doc/paper.tex
update paper draft

@@
 
-It is clear that neutrinos carry the peculiar mass smaller than $\mathcal{O}(1)$ eV among the elementary particle, although the absolute value of each neutrino mass is unknown.
+It is clear that neutrinos carry the peculiar mass smaller than $\mathcal{O}(1)$ eV among elementary particles, although the absolute value of each neutrino mass is unknown.
 In addition, one of the fundamental questions with regards to neutrino properties is how neutrino masses are generated naturally.
-The seesaw mechanism has been used to explain such a tiny mass in the neutrino sector with the help of neutrino flavor mixings.
-Anyhow new particles have to be introduced in such a mechanism.
-The more degrees of freedom in a theoretical model, the less predictivity of observables in experiments.
+%The seesaw mechanism has been used to explain such a tiny mass in the neutrino sector with the help of neutrino flavor mixings. 
+The seesaw mechanism has been used to explain such a tiny mass in the neutrino sector. 
+%Anyhow new particles have to be introduced in such a mechanism. 
+More degrees of freedom in a theoretical model, the less predictivity of observables in experiments.
 Furthermore, flavour symmetries are employed to reduce degrees of freedom in the neutrino mass model.
@@
 \end{equation*}
-It is relatively easy for model builders to check the validity of the neutrino mass model and constrain model parameters by the public nufit results [Ref:nufit website].
+It is relatively easy for model builders to check the validity of the neutrino mass model and constrain model parameters by the public NUFIT results \cite{Esteban:2018azc}.
 However, there is no such a public toolkit to evaluate model predictions in future neutrino experiments.
-\textbf{G}eneral \textbf{Lo}ng \textbf{B}aseline \textbf{E}xperiment \textbf{S}imulator (\textbf{GLoBES}) \cite{Huber:2004ka,Huber:2007ji} is a convenient tool to simulate neutrino oscillation experiments via the Abstract Experiment Definition Language (AEDL) as one of the most popular and useful tools in the community of neutrino oscillation physics.
-Some AEDL files to describe experiments are also available in \textbf{GLoBES} website, while the working group in the DUNE experiment also releases their neutrino flux information and detector descriptions in AEDL files~\cite{Alion:2016uaj}.
+\textbf{G}eneral \textbf{Lo}ng \textbf{B}aseline \textbf{E}xperiment \textbf{S}imulator (\textbf{GLoBES}) \cite{Huber:2004ka,Huber:2007ji} is a convenient tool to simulate neutrino oscillation experiments via the Abstract Experiment Definition Language (AEDL) as one of the most popular and powerful tools in the community of neutrino oscillation physics.
+Some AEDL files to describe experiments are also available in \textbf{GLoBES} website, while the working group in the DUNE experiment also releases their neutrino flux information and detector descriptions in a AEDL file, provided in~\cite{Alion:2016uaj}.
 It is to be extended for the purpose of analysing flavour symmetry models in an universal way.
@@
 
-In Fig.~\ref{fig:constraint}, we study how parameters $x$ and $\eta$ can be constrained by the MuOn-decay MEdium baseline NeuTrino beam experiment (MOMENT)~\cite{Cao:2014bea}.
-We input the model by giving model parameters as functions of standard oscillation parameters Eq.~(\ref{eq:modelofOSC}).
-Besides, parameters $r$ and $ma$ are varied with the prior that is given in standard oscillation parameters, according to the global-fit result NUFIT4.0.
-More details are presented in the user manual.
-The code for this example is provided as \textbf{x\_eta.c} in the \textbf{FaSE} distribution.
+In left panel of Fig.~\ref{fig:constraint}, we study how parameters $x$ and $\eta$ can be constrained by the MuOn-decay MEdium baseline NeuTrino beam experiment (MOMENT)~\cite{Cao:2014bea}. 
+%We input the model by giving model parameters as functions of standard oscillation parameters Eq.~(\ref{eq:modelofOSC}). 
+Parameters $r$ and $ma$ are varied with the prior that is given in standard oscillation parameters, according to the global-fit result NUFIT4.0. More details are presented in the user manual. 
+%The code for this example is provided as \textbf{x\_eta.c} in the \textbf{FaSE} distribution.
 
@@
 
-{\color{red}To show the generality of \textbf{FaSE-GLoBES}, we present the similar result with another model -- \textit{the warped flavor symmetry} (WFS)~\cite{Chen:2015jta}.
+{\color{red}To show the generality of \textbf{FaSE-GLoBES}, we also present the similar result with another model -- \textit{the warped flavor symmetry} (WFS)~\cite{Chen:2015jta}.
 This model predict further simplified correlations that the standard oscillation parameters including mixing angles and the CP phase are functions of only two model parameters $\theta_\nu$ and $\phi_\nu$,
@@
 \end{align}
-The constraint of $\theta_\nu$ and $\phi_\nu$ is presented in the right panel of Fig~\ref{fig:constraint}, in which we use the best fit of NUFIT 4.0 result as the true values ($(\theta_{12},~\theta_{13},~\theta_{23},~\delta,~\Delta m_{21}^2,~\Delta m_{31}^2)=(33.82^\circ,~8.61^\circ,~49.6^\circ,~215^\circ,~7.39\times10^{-5}~\text{eV}^2,~2.525\times10^{-3}~\text{eV}^2)$).}
+The constraint of $\theta_\nu$ and $\phi_\nu$ for DUNE and MOMENT is presented in the right panel of Fig~\ref{fig:constraint}, in which we use the best fit of NUFIT 4.0 result as the true values ($(\theta_{12},~\theta_{13},~\theta_{23},~\delta,~\Delta m_{21}^2,~\Delta m_{31}^2)=(33.82^\circ,~8.61^\circ,~49.6^\circ,~215^\circ,~7.39\times10^{-5}~\text{eV}^2,~2.525\times10^{-3}~\text{eV}^2)$).}
 
@@
  \centering
-\includegraphics[width=0.5\textwidth]{Figs/SR_th23_dCP_DUNE_MOMENT.pdf}
-\caption{\label{fig:th23_delta}The 2-D exclusion contour for sub-models of tri-direct littlest seesaw on the plane of two true standard parameters $\theta_{23}$ and $\delta$, from $1\sigma$ to $5\sigma$, for DUNE (dotted) and MOMENT (solid).
+\includegraphics[width=0.48\textwidth]{Figs/SR_th23_dCP_DUNE_MOMENT.pdf}
+\includegraphics[width=0.48\textwidth]{Figs/SR_th23_dCP_WFS.pdf}
+\caption{\label{fig:th23_delta}Examples for using \textbf{FaSE-GLoBES} to obtain the 2-D exclusion contour on the plane of true values of $\theta_{23}$ and $\delta$ for sub-models of TDLS (left) and of WFS (right) with DUNE and MOMENT.
+{\color{red} [keep tuning plots]}}
+%\caption{\label{fig:th23_delta}The 2-D exclusion contour for sub-models of tri-direct littlest seesaw on the plane of two true standard parameters $\theta_{23}$ and $\delta$, from $1\sigma$ to $5\sigma$, for DUNE (dotted) and MOMENT (solid).
 The range for each parameter is taken according to the $3\sigma$ uncertainty in NuFit4.0 results.
@@
 In addition, the studied statistics function is exactly given by Eq.~(\ref{eq:chi-squared}), but the true event rate $n_i$ is predicted by a set of oscillation parameters, which will be varied in the code.
-
-As mentioned in Sec.~\ref{sec:chi-squared}, the user needs to consider Wilk's theorem with the different of degrees of freedom between the {\color{blue}assumed} true theory and the hypothesis, \texttt{dof}.
-{\color{blue}`The assumed true theory' here means that the oscillation parameters assumed for predicting the true event spectrum.} \textcolor{red}{[JT: what is the meaning of the true theory?]}
+%
+%As mentioned in Sec.~\ref{sec:chi-squared}, the user needs to consider Wilk's theorem with the different of degrees of freedom between the {\color{blue}assumed} true theory {\color{blue}($\vec{\theta}^{true}_{OSC}$)} and the hypothesis {\color{blue}($\vec{\theta}^{hyp}_{Model}$)}, \texttt{dof}.
+%{\color{blue}`The assumed true theory' here means that the oscillation parameters assumed for predicting the true event spectrum.} \textcolor{red}{[JT: what is the meaning of the true theory?]} 
 %Here the number \texttt{dof} is $2$. 
 %And that is our output: \texttt{gsl\_cdf\_chisq\_Qinv(gsl\_cdf\_chisq\_Q(fabs(res),dof),1)}. \textcolor{red}{[I don't understand this sentence.]} 
-We show the result in Fig.~\ref{fig:th23_delta}. More details are presented in the user manual. The code for this example is provided as 
-\textbf{th23\_delta.c} in the \textbf{FaSE} distribution.
+We show the result in Fig.~\ref{fig:th23_delta}. More details are presented in the user manual. 
+%The code for this example is provided as \textbf{th23\_delta.c} in the \textbf{FaSE} distribution.
 
@@
 \textcolor{red}{[JT: This section has to be significantly improved.]}
-
+{\color{blue}[updated]}
 We have presented a simulation toolkit \textbf{FaSE-GLoBES} to study the leptonic flavour symmetry models with neutrino oscillation experiments in a user-friendly way.

### 2020-05-19 doc/paper.tex
update docs

@@
 
-{\color{red}To show the generality of \textbf{FaSE-GLoBES}, we also present the similar result with another model -- \textit{the warped flavor symmetry} (WFS)~\cite{Chen:2015jta}.
-This model predict further simplified correlations that the standard oscillation parameters including mixing angles and the CP phase are functions of only two model parameters $\theta_\nu$ and $\phi_\nu$,
+{\color{red}To show the generality of \textbf{FaSE-GLoBES}, we also present the similar result for another model -- \textit{the warped flavor symmetry} (WFS)~\cite{Chen:2015jta}.
+This model predicts further simplified correlations that the standard oscillation parameters including mixing angles and the CP phase are functions of only two model parameters $\theta_\nu$ and $\phi_\nu$,
 \begin{align}
@@
 \end{align}
-The constraint of $\theta_\nu$ and $\phi_\nu$ for DUNE and MOMENT is presented in the right panel of Fig~\ref{fig:constraint}, in which we use the best fit of NUFIT 4.0 result as the true values ($(\theta_{12},~\theta_{13},~\theta_{23},~\delta,~\Delta m_{21}^2,~\Delta m_{31}^2)=(33.82^\circ,~8.61^\circ,~49.6^\circ,~215^\circ,~7.39\times10^{-5}~\text{eV}^2,~2.525\times10^{-3}~\text{eV}^2)$).}
+The constraint of $\theta_\nu$ and $\phi_\nu$ for DUNE and MOMENT is presented in the right panel of Fig~\ref{fig:constraint}, in which we use the best fit of NUFIT 4.0 result as the true values $(\theta_{12},~\theta_{13},~\theta_{23},~\delta,~\Delta m_{21}^2,~\Delta m_{31}^2)=(33.82^\circ,~8.61^\circ,~49.6^\circ,~215^\circ,~7.39\times10^{-5}~\text{eV}^2,~2.525\times10^{-3}~\text{eV}^2)$.}
 

### 2020-05-19 doc/paper.tex
update docs

@@
 
-{\color{red}To show the generality of \textbf{FaSE-GLoBES}, we also present the similar result for another model -- \textit{the warped flavor symmetry} (WFS)~\cite{Chen:2015jta}.
+{\color{blue}To show the generality of \textbf{FaSE-GLoBES}, we also present the similar result for another model -- \textit{the warped flavor symmetry} (WFS)~\cite{Chen:2015jta}.
 This model predicts further simplified correlations that the standard oscillation parameters including mixing angles and the CP phase are functions of only two model parameters $\theta_\nu$ and $\phi_\nu$,
-\begin{align}
+\begin{align}\label{eq:WFS}
 \sin^2\theta_{12}&=\frac{1}{2-\sin2\theta_{\nu}\cos\phi_\nu},\nonumber\\
@@
 \end{align}
-The constraint of $\theta_\nu$ and $\phi_\nu$ for DUNE and MOMENT is presented in the right panel of Fig~\ref{fig:constraint}, in which we use the best fit of NUFIT 4.0 result as the true values $(\theta_{12},~\theta_{13},~\theta_{23},~\delta,~\Delta m_{21}^2,~\Delta m_{31}^2)=(33.82^\circ,~8.61^\circ,~49.6^\circ,~215^\circ,~7.39\times10^{-5}~\text{eV}^2,~2.525\times10^{-3}~\text{eV}^2)$.}
+The constraint of $\theta_\nu$ and $\phi_\nu$ for DUNE and MOMENT is presented in the right panel of Fig~\ref{fig:constraint}, in which we use the best fit of NUFIT 4.0 result as the true values $(\theta_{12},~\theta_{13},~\theta_{23},~\delta,~\Delta m_{21}^2,~\Delta m_{31}^2)=(33.82^\circ,~8.61^\circ,~49.6^\circ,~215^\circ,~7.39\times10^{-5}~\text{eV}^2,~2.525\times10^{-3}~\text{eV}^2)$.
+To reproduce the result show in \cite{Chatterjee:2017xkb}, we do not include any priors.}
 
@@
 \includegraphics[width=0.48\textwidth]{Figs/SR_th23_dCP_WFS.pdf}
-\caption{\label{fig:th23_delta}Examples for using \textbf{FaSE-GLoBES} to obtain the 2-D exclusion contour on the plane of true values of $\theta_{23}$ and $\delta$ for sub-models of TDLS (left) and of WFS (right) with DUNE and MOMENT.
+\caption{\label{fig:th23_delta}Examples for using \textbf{FaSE-GLoBES} to obtain the 2-D exclusion contour at $99\%$ C.L.
+on the plane of true values of $\theta_{23}$ and $\delta$ for sub-models of TDLS (left) and of WFS (right) with DUNE and MOMENT.
 {\color{red} [keep tuning plots]}}
@@
 %
+{\color{blue}We present this result in the left panel of Fig.~\ref{fig:th23_delta}.
+We further show the generality of \textbf{FaSE-GLoBES} by demonstrating the similar result for another model -- WFS Eq.~(\ref{eq:WFS}) for DUNE and MOMENT, in right panel of Fig.~\ref{fig:th23_delta}.
+In this result, two mass-squared differences are fixed at the true values without including any priors.
+%
 %As mentioned in Sec.~\ref{sec:chi-squared}, the user needs to consider Wilk's theorem with the different of degrees of freedom between the {\color{blue}assumed} true theory {\color{blue}($\vec{\theta}^{true}_{OSC}$)} and the hypothesis {\color{blue}($\vec{\theta}^{hyp}_{Model}$)}, \texttt{dof}.
@@
 %And that is our output: \texttt{gsl\_cdf\_chisq\_Qinv(gsl\_cdf\_chisq\_Q(fabs(res),dof),1)}. \textcolor{red}{[I don't understand this sentence.]} 
-We show the result in Fig.~\ref{fig:th23_delta}. More details are presented in the user manual. 
+More details are presented in the user manual. 
 %The code for this example is provided as \textbf{th23\_delta.c} in the \textbf{FaSE} distribution.
 
-{\color{red}We also show the similar result for WFS, and present it in Fig.}
+}
 

### 2020-05-20 doc/paper.tex
update docs

@@
 The nuisance parameters are constrained by the Gaussian prior $p(\xi,\sigma)=\xi^2/\sigma^2$ with corresponding uncertainties $\sigma_s$ and $\sigma_b$ for the signal and background, respectively.
-Finally, $\chi^2_{prior}$ is a set of Gaussian priors for hypothesis, and is expressed as Eq.~\ref{eq:prior}.
+Finally, $\chi^2_{prior}$ is a set of Gaussian priors for hypothesis, and is expressed as Eq.~(\ref{eq:prior}).
 After doing all minimisations, the user obtain the $\chi^2$ value for a specific hypothesis $\vec{\theta}^{hyp}$, $\chi^2(\vec{\theta}^{hyp})$.
 
-Based on the $\chi^2$ value Eq.~\ref{eq:chi-squared}, we can study how model parameters can be constrained and whether a flavour-symmetry neutrino model is excluded by simulated experiments.
-In the following we will demonstrate with typical examples how it works.
+Based on the $\chi^2$ function Eq.~(\ref{eq:chi-squared}), we can study how model parameters can be constrained and whether a flavour-symmetry neutrino model is excluded by simulated experiments.
+In the following we will demonstrate with typical examples how it works, {\color{blue} before presenting some demonstrations in next two sections.}
 
@@
  %
-  \caption{\label{fig:constraint}Examples for using \textbf{FaSE-GLoBES} to obtain the constraints of model parameters for tri-direct littlest seesaw (left) and the warped flavor symmetry (right), with simulated DUNE and MOMENT data.
-{\color{blue}[the left panel will be updated]}}
+  \caption{\label{fig:constraint}Examples for using \textbf{FaSE-GLoBES} to obtain the constraints of model parameters for tri-direct littlest seesaw (left) and the warped flavor symmetry (right), with simulated DUNE and MOMENT data.}
 \end{figure}
@@
 The constraint of $\theta_\nu$ and $\phi_\nu$ for DUNE and MOMENT is presented in the right panel of Fig~\ref{fig:constraint}, in which we use the best fit of NUFIT 4.0 result as the true values $(\theta_{12},~\theta_{13},~\theta_{23},~\delta,~\Delta m_{21}^2,~\Delta m_{31}^2)=(33.82^\circ,~8.61^\circ,~49.6^\circ,~215^\circ,~7.39\times10^{-5}~\text{eV}^2,~2.525\times10^{-3}~\text{eV}^2)$.
-To reproduce the result show in \cite{Chatterjee:2017xkb}, we do not include any priors.}
+To reproduce the result shown in \cite{Chatterjee:2017xkb}, we do not include any priors.}
 
@@
 on the plane of true values of $\theta_{23}$ and $\delta$ for sub-models of TDLS (left) and of WFS (right) with DUNE and MOMENT.
-{\color{red} [keep tuning plots]}}
+}
 %\caption{\label{fig:th23_delta}The 2-D exclusion contour for sub-models of tri-direct littlest seesaw on the plane of two true standard parameters $\theta_{23}$ and $\delta$, from $1\sigma$ to $5\sigma$, for DUNE (dotted) and MOMENT (solid).
@@
 \textcolor{red}{[JT: This section has to be significantly improved.]}
-{\color{blue}[updated]}
+
 We have presented a simulation toolkit \textbf{FaSE-GLoBES} to study the leptonic flavour symmetry models with neutrino oscillation experiments in a user-friendly way.
@@
 
-Finally, \textbf{GLoBES} is a popular and powerful simulation tool to analysis the neutrino oscillation experiments in a simple language (AEDL), without losing too much detail.
-Considering the success of the flavour symmetry theory to explain the neutrino oscillations, \textbf{FaSE-GLoBES} should benefit model builders of leptonic flavour symmetry and phenomenologists for neutrino oscillation physics.
-We leave the flexibility for the user, and some other improvements and extensions can be expected in the future.
+{\color{blue}With the progression of the precision measurements in the neutrino physics, and considering the success of the flavour symmetry theory in explaining neutrino oscillations, \textbf{FaSE-GLoBES} should benefit model builders of leptonic flavour symmetry and phenomenologists for neutrino oscillation physics.
+Finally, we leave the flexibility for the user, and some other improvements and extensions can be expected in the future.}
 

### 2020-05-21 doc/paper.tex
update docs

@@
 Neutrino models based on flavour symmetries provide the natural way to explain the origin of tiny neutrino masses.
-At the dawn of precision measurements of neutrino mixing parameters, it is straightforward to constrain and examine neutrino mass models by on-going and next-generation neutrino experiments.
+At the dawn of precision measurements of neutrino mixing parameters, neutrino mass models can be constrained and examined by on-going and up-coming neutrino experiments.
 We present a supplemental tool \textbf{F}l\textbf{a}vour \textbf{S}ymmetry \textbf{E}mbedded (\textbf{FaSE}) for \textbf{G}eneral \textbf{Lo}ng \textbf{B}aseline \textbf{E}xperiment \textbf{S}imulator (\textbf{GLoBES}).
@@
 
-The discovery of neutrino oscillations points out the fact that neutrinos have mass, and provides evidence beyond the Standard Model (BSM).
+The discovery of neutrino oscillations points out the fact that neutrinos have mass, and provides an evidence beyond the Standard Model (BSM).
 This phenomenon is successfully described by a theoretical framework with the help of three neutrino mixing angles ($\theta_{12}$, $\theta_{13}$, $\theta_{23}$), two mass-square splittings ($\Delta m_{21}^2$, $\Delta m_{31}^2$), and one Dirac CP phase ($\delta$) \cite{Pontecorvo:1967fh,Maki:1962mu,Pontecorvo:1957qd,Esteban:2018azc}.
@@
 \end{equation*} 
-Given $\theta_{13}\approx 8^\circ$ measured by several reactor neutrino experiments, we have to break the symmetry pattern to to obtain such non-zero value of $\theta_{13}$.
+Given $\theta_{13}\approx 8^\circ$ measured by several reactor neutrino experiments, we have to break this mixing pattern to to obtain such non-zero value of $\theta_{13}$.
 One of popular proposals is to correct the tri-bi-maximal neutrino mixing such that
@@
 
-As we approach the era of precision measurements in the neutrino oscillations, recent works pay more attentions to how the future neutrino experiments can be used to test these flavour-symmetry neutrino mass models, \textit{e.g.}~Ref.~\cite{Ballett:2016yod,Chatterjee:2017xkb, Ding:2019zhn, Tang:2019edw, Blennow:2020snb}.
+As we are entering the era of precision measurements in the neutrino oscillations, recent works pay more attentions to how the future neutrino experiments can be used to test these flavour-symmetry neutrino mass models, \textit{e.g.}~Ref.~\cite{Ballett:2016yod,Chatterjee:2017xkb, Ding:2019zhn, Tang:2019edw, Blennow:2020snb}.
 In this work, we will present our simulation toolkit \textbf{F}l\textbf{a}vour \textbf{S}ymmetry \textbf{E}mbedded - \textbf{GLoBES} (\textbf{FaSE-GloBES}) in a C-library to facilitate the study in the flavour symmetry neutrino models.
@@
 
-\section{Overview FASE-GloBES}
+\section{Overview FASE-GloBES}\label{sec:overview}
 
 \textbf{FaSE-GLoBES} is written in the \texttt{c} language, and consists of two source codes \textbf{FASE\_GLoBES.c} and \textbf{model-input.c}.
-The user defines the correlations between model inputs and standard neutrino mixing parameters in \textbf{model-input.c}, while \textbf{FASE\_GLoBES.c} is an engine to perform analysis with user-specified experiments in a simulaton.
+About these two \texttt{c}-codes, the user defines the correlations between model inputs and standard neutrino mixing parameters in \textbf{model-input.c}, while \textbf{FASE\_GLoBES.c} is an engine to perform analysis with user-specified experiments in a simulaton.
 Note that we define the standard neutrino mixing/oscillation parameters $\vec{\theta}_{OSC}$ ($\theta_{12}$, $\theta_{13}$, $\theta_{23}$, $\Delta m_{21}^2$, $\Delta m_{31}^2$, $\delta$) to separate from model parameters $\vec{\theta}_{Model}$ hereafter.
@@
 
-The concept of \textbf{FaSE-GLoBES} is shown in Fig.~\ref{fig:FASE}, in which three parts are shown: 1.~\textbf{the parameter translation} (the blue box), 2.~\textbf{giving oscillation-parameter values} (the green box), and 3.~\textbf{the $\chi^2$-value calculation} (the orange box).
-The idea behind this flow chart Fig.~\ref{fig:FASE} is that given a set of model parameters, the corresponding values in standard oscillation parameters are obtained by a translation, which is assigned by the user in \textbf{model-input.c}.
+The concept of \textbf{FaSE-GLoBES} is shown in Fig.~\ref{fig:FASE}, in which three parts are shown: 1.~\textbf{the parameter translation}, 2.~\textbf{giving oscillation-parameter values}, and 3.~\textbf{the $\chi^2$-value calculation}.
+The idea behind this flow chart Fig.~\ref{fig:FASE} is that given a set of model parameters, the corresponding values in standard oscillation parameters are obtained by a translation function, which is assigned by the user in \textbf{model-input.c}.
 And then, through \textbf{FASE\_GLoBES.c} these oscillation-parameter values are passed into \textbf{GLoBES} library to simulate the event spectra so that we can perform physics analysis in the newly-defined $\chi^2$.
@@
 This probability engine can work with oscillation or model parameters.
-It can be set by the user with the parameter \texttt{PARA}.
+It can be set by the user with the parameter \texttt{PARA} in the main code.
 If \texttt{PARA=STAN} (\texttt{PARA=MODEL}) the probability engine works with oscillation (model) parameters.
@@
 For the first four components, values are given in the unit of \textbf{rad}, while the other two are in \textbf{eV$^2$}.
-These values will be passed into \textbf{FaSE\_GLoBES} to simulate
-the experimental spectra and compute the prior values.
+These values will be passed into \textbf{FaSE\_GLoBES} to simulate experimental spectra and compute prior values.
 
-To transform from $\vec{\theta}_{Model}$ to $\vec{\theta}_{OSC}$, the user can assign the correlation between the standard oscillation and model parameter sets, or define the mass matrix in model parameters, which will be diagonalised by the function \texttt{ModelTO} to obtain the corresponding oscillation-parameter values.
+To translate from $\vec{\theta}_{Model}$ to $\vec{\theta}_{OSC}$, the user can assign the correlation between the standard oscillation and model parameter sets, or define the mass matrix in model parameters, which will be diagonalised by the function \texttt{STAN\_OSC} to obtain the corresponding oscillation-parameter values.
 %The relation between the oscillation and model parameter sets can be derived out by the user, 
@@
 where $\mathcal{M}$ ($\mathbf{M}$) is the neutrino mass matrix in the flavour (mass) state.
-The matrix $\mathcal{M}$ is given by user with model parameters $\vec{\theta}_{Model}$.
-The matrix $U$ is the neutrino mixing matrix, and can be used to get mixing angles, mass squared differences and the CP phase.
+The matrix $\mathcal{M}$ is given by the user with model parameters $\vec{\theta}_{Model}$.
+The matrix $U$ is the neutrino mixing matrix, and can be used to get mixing angles and the CP phase.
 The difference between any two diagonal elements of $\textbf{M}$ ($\textbf{M}_{ii}-\textbf{M}_{jj}=m_i^2-m_j^2$) is the mass-squared difference ($\Delta m_{ij}^2$).
-This diagnolisation Eq.~(\ref{eq:MM}) can be done by the function \texttt{ModelTO}, which needs to be called in \texttt{MtoS} with outputs of the vector $\vec{\theta}_{OSC}$.
+This diagnolisation Eq.~(\ref{eq:MM}) can be done by the function \texttt{STAN\_OSC}, which needs to be called in \texttt{MtoS} with outputs of the vector $\vec{\theta}_{OSC}$.
 
@@
 These two functions are constructed for different purposes.
-If the user gives the prior in oscillation (model) parameters, the user should register \texttt{FASE\_prior\_OSC} (\texttt{FASE\_prior\_model}) with the \textbf{GLoBES} function \texttt{glbRegisterPriorFunction}, as we introduced in the previous section.
+If the user gives the prior in oscillation (model) parameters, the user should register \texttt{FASE\_prior\_OSC} (\texttt{FASE\_prior\_model}) with the \textbf{GLoBES} function \texttt{glbRegisterPriorFunction}, as we introduced in Sec.~\ref{sec:overview}.
 The user also needs to assign the parameters \texttt{PARA=STAN} (\texttt{PARA=Model}), when the user prefers to give the prior in oscillation (model) parameters.
@@
  where $\theta_i$ is one of parameters constrained by prior, $\theta^c_i$ ($\sigma_i$) is the central value (Gaussian width) of the prior for $\theta_i$.
-We note that $\theta_i${OSC} can be either model ($\vec{\theta}_{Model}$) or oscillation parameters ($\vec{\theta}_{OSC}$).
+We note that $\theta_i$ can be either model ($\vec{\theta}_{Model}$) or oscillation parameters ($\vec{\theta}_{OSC}$).
 %
-The values of $\theta^c_i$ and $\sigma_i$ need to be given by the user through three arrays: \texttt{Central\_prior}, \texttt{UPPER\_prior}, and \texttt{LOWER\_prior}, in which there are six components.
+The values of $\theta^c_i$ and $\sigma_i$ need to be given by the user in the main code through three arrays: \texttt{Central\_prior}, \texttt{UPPER\_prior}, and \texttt{LOWER\_prior}, in which there are six components.
 To treat asymmetry of width for upper ($\theta_i>\theta_i^c$) and lower ($\theta_i<\theta_i^c$) Gaussian widths, we give values in two arrays \texttt{UPPER\_prior}, and \texttt{LOWER\_prior}, respectively.
 If the user gives the prior in model parameters, the order of each component follows with the setup of input of the probability engine.
-While the user gives the prior in oscillation parameters, the six components in order are $\theta_{12}$, $\theta_{13}$, $\theta_{23}$, $\delta$, $\Delta m_{21}^2$, and  $\Delta m_{31}^2$.
+While the user gives the prior in oscillation parameters, the six components of these three arrays in order are $\theta_{12}$, $\theta_{13}$, $\theta_{23}$, $\delta$, $\Delta m_{21}^2$, and  $\Delta m_{31}^2$.
 The first four parameter are in \textbf{rad}, and the final two are in \textbf{eV$^2$}.
@@
 For example, if the normal ordering is imposed, we give ``\texttt{ if (DMS31<0) \{ return 1;\} } '' in \texttt{model\_restriction}, where \texttt{DMS31} is the variable for $\Delta m_{31}^2$.
-Then, when the restriction is broken, \texttt{model\_restriction} returns the value $1$ to the prior function \texttt{FASE\_prior\_OSC} or \texttt{FASE\_prior\_model}.
-Therefore, if there is no restriction, we simply \textit{return $0$} in \texttt{model\_restriction} as follows.
+%Then, when the restriction is broken, \texttt{model\_restriction} returns the value $1$ to the prior function \texttt{FASE\_prior\_OSC} or \texttt{FASE\_prior\_model}.
+And, if there is no restriction, we simply \textit{return $0$} in \texttt{model\_restriction} as follows.
 % \vspace{0.2cm}\\

### 2020-05-21 doc/paper.tex
update docs

@@
 \end{equation*}
-It is relatively easy for model builders to check the validity of the neutrino mass model and constrain model parameters by the public NUFIT results \cite{Esteban:2018azc}.
+It is relatively easy for model builders to check the validity of the neutrino mass model and constrain model parameters by the public NuFit results \cite{Esteban:2018azc}.
 However, there is no such a public toolkit to evaluate model predictions in future neutrino experiments.
@@
 The user can use \textbf{FaSE-GLoBES} to constrain model parameters. 
-{\color{blue}Suppose we have the measurement $\vec{x}$ and the likelihood function $L(\vec{\theta})=P(\vec{x}|\vec{\theta})$ for a set of parameters $\vec{\theta}=(\theta_1,...,\theta_N)$, where $P(\vec{x}|\vec{\theta})$ is the probability function for data $\vec{x}$ in favour of the hypothesis $\vec{\theta}$.
-The constraint of model parameters can be obtained with the statistis parameter $\chi^2\equiv \ln L(\vec{\theta})$.}
+Suppose we have the measurement $\vec{x}$ and the likelihood function $L(\vec{\theta})=P(\vec{x}|\vec{\theta})$ for a set of parameters $\vec{\theta}=(\theta_1,...,\theta_N)$, where $P(\vec{x}|\vec{\theta})$ is the probability function for data $\vec{x}$ in favour of the hypothesis $\vec{\theta}$.
+The constraint of model parameters can be obtained with the statistis parameter $\chi^2\equiv \ln L(\vec{\theta})$.
 The expression $\chi^2$ is used as the default \textbf{GLoBES} setting.
-\textcolor{red}{[JT: What is the meaning of this $\chi^2$ here?]} In more detail, the $\chi^2$ function{\color{blue}, following the Poisson distribution,} is constructed based on a log-likelihood ratio,
+\textcolor{red}{[JT: What is the meaning of this $\chi^2$ here?]} In more detail, the $\chi^2$ function, following the Poisson distribution, is constructed based on a log-likelihood ratio,
 %\begin{equation}\label{eq:chi-squared}
@@
 Finally, $\chi^2_{prior}$ is a set of Gaussian priors for hypothesis, and is expressed as Eq.~(\ref{eq:prior}).
-After doing all minimisations, the user obtain the $\chi^2$ value for a specific hypothesis $\vec{\theta}^{hyp}$, $\chi^2(\vec{\theta}^{hyp})$.
+After doing all minimisations, the user obtains the $\chi^2$ value for a specific hypothesis $\vec{\theta}^{hyp}$, $\chi^2(\vec{\theta}^{hyp})$.
 
 Based on the $\chi^2$ function Eq.~(\ref{eq:chi-squared}), we can study how model parameters can be constrained and whether a flavour-symmetry neutrino model is excluded by simulated experiments.
-In the following we will demonstrate with typical examples how it works, {\color{blue} before presenting some demonstrations in next two sections.}
+In the following we will demonstrate with typical examples how it works, before presenting some demonstrations in next two sections.
 
@@
 We note that the minimum of $\chi^2$ in the whole parameter space ($\chi^2_{min.}$) may not be $0$.
-Therefore, to get the precision of model parameters, the user should use the value $\Delta\chi^2(\vec{\theta}_{Model}^{hyp})\equiv \chi^2(\vec{\theta}_{Model}^{hyp})-\chi^2_{min.}$, instead of $\chi^2$ itself.
+Therefore, to get the precision of model parameters, the user should use the value $\Delta\chi^2(\vec{\theta}_{Model}^{hyp})\equiv \chi^2(\vec{\theta}_{Model}^{hyp})-\chi^2_{min.}$, instead of $\chi^2(\vec{\theta}_{Model}^{hyp})$ itself.
 By varying different hypotheses $\vec{\theta}_{Model}^{hyp}$, we will obtain the allowed region of model parameters with the statistical quantity $\Delta\chi^2(\vec{\theta}_{Model}^{hyp})$.
@@
 Finally, the user might adopt Wilk's theorem to interpret results~\cite{Wilks:1938dza}.
-When we compare nested models, the $\Delta \chi^2$ test statistics is a random variable asymptotically distributed as a $\chi^2$-distribution with the number of degrees of freedom, which is equal to the difference in the number of free model parameters \texttt{dof}.
+When we compare nested models, the $\Delta \chi^2$ test statistics is a random variable asymptotically distributed as a $\chi^2$-distribution with the number of degrees of freedom, which is equal to the difference in the number of free model parameters.
+
+In following two sections, we will present examples to demonstrate how the user can do with \textbf{FaSE-GLoBES} to constrain the model parameter and to exclude a model by the simulated experiment configuration.
 
@@
 
-\textbf{FaSE-GloBES} can be used to study how model parameters are constrained by simulated neutrino oscillation experiments.
+\textbf{FaSE-GloBES} can be used to study how model parameters are constrained by simulated neutrino oscillation experiments as we introduced in Sec.~\ref{sec:chi-squared}.
 We take \textit{the tri-direct littlest seesaw} (TDLS)~\cite{King:2013iva,King:2015dvf,King:2016yvg} as an example.
@@
  %
-  \caption{\label{fig:constraint}Examples for using \textbf{FaSE-GLoBES} to obtain the constraints of model parameters for tri-direct littlest seesaw (left) and the warped flavor symmetry (right), with simulated DUNE and MOMENT data.}
+  \caption{\label{fig:constraint}Examples for using \textbf{FaSE-GLoBES} to obtain the constraints of model parameters for tri-direct littlest seesaw (left) and the warped flavor symmetry (right), with simulated DUNE and MOMENT data.
+In the left panel, the dot)denotes the prediction by the tri-direct littlest seesaw model with NuFit4.0 results.}
 \end{figure}
 
-In left panel of Fig.~\ref{fig:constraint}, we study how parameters $x$ and $\eta$ can be constrained by the MuOn-decay MEdium baseline NeuTrino beam experiment (MOMENT)~\cite{Cao:2014bea}. 
+In left panel of Fig.~\ref{fig:constraint}, we study how parameters $x$ and $\eta$ can be constrained at $3\sigma$ by the MuOn-decay MEdium baseline NeuTrino beam experiment (MOMENT)~\cite{Cao:2014bea} and DUNE experiment.
 %We input the model by giving model parameters as functions of standard oscillation parameters Eq.~(\ref{eq:modelofOSC}). 
-Parameters $r$ and $ma$ are varied with the prior that is given in standard oscillation parameters, according to the global-fit result NUFIT4.0. More details are presented in the user manual. 
+Parameters $r$ and $ma$ are varied with the prior that is given in standard oscillation parameters, according to the global-fit result NuFit4.0. 
 %The code for this example is provided as \textbf{x\_eta.c} in the \textbf{FaSE} distribution.
@@
 
-{\color{blue}To show the generality of \textbf{FaSE-GLoBES}, we also present the similar result for another model -- \textit{the warped flavor symmetry} (WFS)~\cite{Chen:2015jta}.
+To show the generality of \textbf{FaSE-GLoBES}, we also present the similar result for another model -- \textit{the warped flavor symmetry} (WFS)~\cite{Chen:2015jta}.
 This model predicts further simplified correlations that the standard oscillation parameters including mixing angles and the CP phase are functions of only two model parameters $\theta_\nu$ and $\phi_\nu$,
@@
 \end{align}
-The constraint of $\theta_\nu$ and $\phi_\nu$ for DUNE and MOMENT is presented in the right panel of Fig~\ref{fig:constraint}, in which we use the best fit of NUFIT 4.0 result as the true values $(\theta_{12},~\theta_{13},~\theta_{23},~\delta,~\Delta m_{21}^2,~\Delta m_{31}^2)=(33.82^\circ,~8.61^\circ,~49.6^\circ,~215^\circ,~7.39\times10^{-5}~\text{eV}^2,~2.525\times10^{-3}~\text{eV}^2)$.
-To reproduce the result shown in \cite{Chatterjee:2017xkb}, we do not include any priors.}
+The constraint of $\theta_\nu$ and $\phi_\nu$ for DUNE and MOMENT is presented in the right panel of Fig~\ref{fig:constraint}, in which we use the best fit of NuFit 4.0 result as the true values $(\theta_{12},~\theta_{13},~\theta_{23},~\delta,~\Delta m_{21}^2,~\Delta m_{31}^2)=(33.82^\circ,~8.61^\circ,~49.6^\circ,~215^\circ,~7.39\times10^{-5}~\text{eV}^2,~2.525\times10^{-3}~\text{eV}^2)$.
+To reproduce the result shown in \cite{Chatterjee:2017xkb}, we do not include any priors.
+More details about these codes are presented in the user manual.
 
@@
 on the plane of true values of $\theta_{23}$ and $\delta$ for sub-models of TDLS (left) and of WFS (right) with DUNE and MOMENT.
-}
+In the left panel, the star (dot) denotes the prediction by the tri-direct littlest seesaw model with NuFit4.0 results (best fit of NuFit4.0).}
 %\caption{\label{fig:th23_delta}The 2-D exclusion contour for sub-models of tri-direct littlest seesaw on the plane of two true standard parameters $\theta_{23}$ and $\delta$, from $1\sigma$ to $5\sigma$, for DUNE (dotted) and MOMENT (solid).
@@
 In this example, we present testing sub-models of TDLS in various true values of $\theta_{23}$ and $\delta$.
-We compute the minimal $\chi^2$ value for the model with $r$ and $m_a$, varied with the prior Eq.~(\ref{eq:prior}) according to NUFIT4.0 results.
+We compute the minimal $\chi^2$ value for the model with $r$ and $m_a$, varied with the prior Eq.~(\ref{eq:prior}) according to NuFit4.0 results.
 Two parameters $x$ and $\eta$ are fixed at the best fit.
@@
 %
-{\color{blue}We present this result in the left panel of Fig.~\ref{fig:th23_delta}.
+We present this result in the left panel of Fig.~\ref{fig:th23_delta}.
 We further show the generality of \textbf{FaSE-GLoBES} by demonstrating the similar result for another model -- WFS Eq.~(\ref{eq:WFS}) for DUNE and MOMENT, in right panel of Fig.~\ref{fig:th23_delta}.
@@
 %The code for this example is provided as \textbf{th23\_delta.c} in the \textbf{FaSE} distribution.
-
-}
 

### 2020-05-21 doc/paper.tex
Polish the conclusion in the FASE-GLoBES project.

@@
 \section{Summary and conclusions}
-\textcolor{red}{[JT: This section has to be significantly improved.]}
 
+With the progress of precision measurements in the neutrino experiments, and the success of numerous flavour symmetry theories to explain tiny neutrino masses, there are strong motivations to test and discriminate theoretical models by the next-generation neutrino oscillation experiments.
 We have presented a simulation toolkit \textbf{FaSE-GLoBES} to study the leptonic flavour symmetry models with neutrino oscillation experiments in a user-friendly way.
-\textbf{FaSE} contains two \texttt{c}-codes: \textbf{model-input.c} and \textbf{FASE\_GLoBES.c}.
-While \textbf{FASE\_GLoBES.c} plays a role as a bridge between \textbf{FaSE} and \textbf{GLoBES}, all inputs from the user needs to be given in \textbf{model-input.c}.
-Two main functions provided by \textbf{FaSE} for users are a convenient way to assign a flavour symmetry model and to include Gaussian priors that can be in oscillation or model parameters.
-%
-With \textbf{FaSE-GLoBES}, users are able to study how a flavour model can be studied by the simulated experimental configuration in varieties of perspectives, \textit{e.g.} model parameter constraints, hypothesis testing.
-
-{\color{blue}With the progression of the precision measurements in the neutrino physics, and considering the success of the flavour symmetry theory in explaining neutrino oscillations, \textbf{FaSE-GLoBES} should benefit model builders of leptonic flavour symmetry and phenomenologists for neutrino oscillation physics.
-Finally, we leave the flexibility for the user, and some other improvements and extensions can be expected in the future.}
+\textbf{FaSE-GLoBES} contains two \texttt{c}-codes: \textbf{model-input.c} and \textbf{FASE\_GLoBES.c}.
+While \textbf{FASE\_GLoBES.c} works as a bridge between models and standard neutrino mixings, all inputs from the user need to be given in \textbf{model-input.c}.
+With the help of two main functions provided by \textbf{FaSE}, it is convenient to assign a flavour symmetry model and include Gaussian priors associated with oscillation or model parameters.
+Users are able to study how a flavour model can be studied by the simulated experimental configuration in various perspectives, \textit{e.g.} model parameter constraints, hypothesis testing.
+{\color{blue} \textbf{FaSE-GLoBES} will contribute to the selection and screening of underlying neutrino mass models by oscillation experiments.
+Further improvements and extensions can be envisioned as more requests are made by users.}
 

### 2020-05-21 doc/paper.tex
Polish the texts with comments in red font.

@@
 The concept of \textbf{FaSE-GLoBES} is shown in Fig.~\ref{fig:FASE}, in which three parts are shown: 1.~\textbf{the parameter translation}, 2.~\textbf{giving oscillation-parameter values}, and 3.~\textbf{the $\chi^2$-value calculation}.
-The idea behind this flow chart Fig.~\ref{fig:FASE} is that given a set of model parameters, the corresponding values in standard oscillation parameters are obtained by a translation function, which is assigned by the user in \textbf{model-input.c}.
+The idea behind this flow chart in Fig.~\ref{fig:FASE} is that given a set of model parameters, the corresponding values in standard oscillation parameters are obtained by a translation function, which is assigned by the user in \textbf{model-input.c}.
 And then, through \textbf{FASE\_GLoBES.c} these oscillation-parameter values are passed into \textbf{GLoBES} library to simulate the event spectra so that we can perform physics analysis in the newly-defined $\chi^2$.
@@
 The difference between any two diagonal elements of $\textbf{M}$ ($\textbf{M}_{ii}-\textbf{M}_{jj}=m_i^2-m_j^2$) is the mass-squared difference ($\Delta m_{ij}^2$).
-This diagnolisation Eq.~(\ref{eq:MM}) can be done by the function \texttt{STAN\_OSC}, which needs to be called in \texttt{MtoS} with outputs of the vector $\vec{\theta}_{OSC}$.
+This diagnolisation in Eq.~(\ref{eq:MM}) can be done by the function \texttt{STAN\_OSC}, which needs to be called in \texttt{MtoS} with outputs of the vector $\vec{\theta}_{OSC}$.
 
@@
 The constraint of model parameters can be obtained with the statistis parameter $\chi^2\equiv \ln L(\vec{\theta})$.
-The expression $\chi^2$ is used as the default \textbf{GLoBES} setting.
-\textcolor{red}{[JT: What is the meaning of this $\chi^2$ here?]} In more detail, the $\chi^2$ function, following the Poisson distribution, is constructed based on a log-likelihood ratio,
+The expression $\chi^2$ is used as the default \textbf{GLoBES} setting. In more detail, the $\chi^2$ function, following the Poisson distribution, is constructed based on a log-likelihood ratio,
 %\begin{equation}\label{eq:chi-squared}
@@
 In other words, the user studies the minimum of $\chi^2$ for the flavour symmetry model $\vec{\theta}_{Model}$ as a hypothesis, by assuming different true oscillation values, \textit{i.e.}~different $\vec{\theta}^{true}_{OSC}$.
-To do so, one can compute the same statistical quantity Eq.~(\ref{eq:chi_model}), while the true spectrum is varied with different true values $\vec{\theta}_{OSC}^{true}$.
+To do so, one can compute the same statistical quantity in Eq.~(\ref{eq:chi_model}), while the true spectrum is varied with different true values $\vec{\theta}_{OSC}^{true}$.
 All model parameters are allowed to be varied with the user-defined prior.
@@
   \caption{\label{fig:constraint}Examples for using \textbf{FaSE-GLoBES} to obtain the constraints of model parameters for tri-direct littlest seesaw (left) and the warped flavor symmetry (right), with simulated DUNE and MOMENT data.
-In the left panel, the dot)denotes the prediction by the tri-direct littlest seesaw model with NuFit4.0 results.}
+In the left panel, the dot)denotes the prediction by the tri-direct littlest seesaw model with NuFit4.0 results.
+\textcolor{red}{No best-fit values in the right panel?
+NH is assumed here?}}
 \end{figure}
@@
 The constraint of $\theta_\nu$ and $\phi_\nu$ for DUNE and MOMENT is presented in the right panel of Fig~\ref{fig:constraint}, in which we use the best fit of NuFit 4.0 result as the true values $(\theta_{12},~\theta_{13},~\theta_{23},~\delta,~\Delta m_{21}^2,~\Delta m_{31}^2)=(33.82^\circ,~8.61^\circ,~49.6^\circ,~215^\circ,~7.39\times10^{-5}~\text{eV}^2,~2.525\times10^{-3}~\text{eV}^2)$.
-To reproduce the result shown in \cite{Chatterjee:2017xkb}, we do not include any priors.
+To reproduce results shown in \cite{Chatterjee:2017xkb}, we do not include any priors.
 More details about these codes are presented in the user manual.
@@
 on the plane of true values of $\theta_{23}$ and $\delta$ for sub-models of TDLS (left) and of WFS (right) with DUNE and MOMENT.
-In the left panel, the star (dot) denotes the prediction by the tri-direct littlest seesaw model with NuFit4.0 results (best fit of NuFit4.0).}
+In the left panel, the star (dot) denotes the prediction by the tri-direct littlest seesaw model with NuFit4.0 results (best fit of NuFit4.0).
+\textcolor{red}{No best-fit values in the right panel?
+NH is assumed here?}}
 %\caption{\label{fig:th23_delta}The 2-D exclusion contour for sub-models of tri-direct littlest seesaw on the plane of two true standard parameters $\theta_{23}$ and $\delta$, from $1\sigma$ to $5\sigma$, for DUNE (dotted) and MOMENT (solid).
@@
 In this example, we present testing sub-models of TDLS in various true values of $\theta_{23}$ and $\delta$.
-We compute the minimal $\chi^2$ value for the model with $r$ and $m_a$, varied with the prior Eq.~(\ref{eq:prior}) according to NuFit4.0 results.
+We compute the minimal $\chi^2$ value for the model with $r$ and $m_a$, varied with the prior in Eq.~(\ref{eq:prior}) according to NuFit4.0 results.
 Two parameters $x$ and $\eta$ are fixed at the best fit.
@@
 We present this result in the left panel of Fig.~\ref{fig:th23_delta}.
-We further show the generality of \textbf{FaSE-GLoBES} by demonstrating the similar result for another model -- WFS Eq.~(\ref{eq:WFS}) for DUNE and MOMENT, in right panel of Fig.~\ref{fig:th23_delta}.
+We further show the generality of \textbf{FaSE-GLoBES} by demonstrating the similar result for another model -- WFS in Eq.~(\ref{eq:WFS}) for DUNE and MOMENT, in right panel of Fig.~\ref{fig:th23_delta}.
 In this result, two mass-squared differences are fixed at the true values without including any priors.
@@
 
+\textcolor{red}{In the references, the arXiv number is chopped by one digit. Could you please check the reason?}
+
 \acknowledgements{

### 2020-05-22 doc/paper.tex
update plot and docs

@@
 
-\documentclass[aps,prd,nofootinbib,preprint]{revtex4}
+%\documentclass[aps,prd,nofootinbib,preprint]{revtex4}
+\documentclass[preprint]{revtex4}
+%\documentclass[a4paper]{article}
 
@@
 ,epsfig}
-
-%JHEP%
-%\title{\boldmath  Flavour Symmetry Embedded - GLoBES (FaSE-GLoBES)}
-
-%JHEP%
-%\author[a]{Jian Tang,}
-%\author[a]{Tse-Chun Wang}
-%\affiliation[a]{School of Physics, Sun Yat-Sen University, Guangzhou 510275, China}
-%\emailAdd{tangjian5@mail.sysu.edu.cn}
-%\emailAdd{wangzejun@mail.sysu.edu.cn}
-%\abstract{Abstract...}
 
@@
   \caption{\label{fig:constraint}Examples for using \textbf{FaSE-GLoBES} to obtain the constraints of model parameters for tri-direct littlest seesaw (left) and the warped flavor symmetry (right), with simulated DUNE and MOMENT data.
-In the left panel, the dot)denotes the prediction by the tri-direct littlest seesaw model with NuFit4.0 results.
-\textcolor{red}{No best-fit values in the right panel?
+{\color{blue}Two results are assumed the normal ordering.
+And, the dot denotes the model prediction with with NuFit4.0 results.} \textcolor{red}{No best-fit values in the right panel?
 NH is assumed here?}}
@@
 on the plane of true values of $\theta_{23}$ and $\delta$ for sub-models of TDLS (left) and of WFS (right) with DUNE and MOMENT.
-In the left panel, the star (dot) denotes the prediction by the tri-direct littlest seesaw model with NuFit4.0 results (best fit of NuFit4.0).
-\textcolor{red}{No best-fit values in the right panel?
+{\color{blue}Two results are assumed the normal ordering.
+And, the dot (star) denotes the model prediction with NuFit4.0 results (best fit of NuFit4.0).} \textcolor{red}{No best-fit values in the right panel?
 NH is assumed here?}}
@@
 In this result, two mass-squared differences are fixed at the true values without including any priors.
+%
+%{\color{blue}And, true values of the other oscillation parameters are fixed at the best fit of NuFit4.0, and this setup is different from the left panel, in which we fix the other oscillation parameters at the model prediction for the true value.}
 %
@@
 % use BIBTEX if you want
-\bibliographystyle{JHEP}
-%\bibliographystyle{plain}
+%\bibliographystyle{JHEP}
+\bibliographystyle{plain}
+%\bibliographystyle{ksfh_nat}
 \bibliography{FAS-GLoBES.bib}

### 2020-05-22 WFS/FASE_GLoBES.c
update code and docs

@@ -1,0 +1,927 @@
+#include <stdio.h>
+#include <stdlib.h>
+#include <math.h>
+#include <string.h>
+#include <complex.h>
+#include <float.h>
+#include <gsl/gsl_math.h>
+#include <gsl/gsl_complex.h>
+#include <gsl/gsl_complex_math.h>
+#include <gsl/gsl_matrix.h>
+#include <gsl/gsl_blas.h>
+#include <gsl/gsl_cblas.h>
+#include <gsl/gsl_eigen.h>
+#include <gsl/gsl_vector.h>
+#include <globes/globes.h>   /* GLoBES library */
+#include"FASE_GLoBES.h"
+#include"model-input.h"
+
+extern char **glb_param_names;
+
+typedef struct {
+    double *osc_params;
+    size_t length;
+} glb_osc_type;
+
+typedef struct {
+    double *density_params;
+    size_t length;
+} glb_density_type;
+
+struct glb_params_type {
+    glb_osc_type *osc;
+    glb_density_type *density;
+    int iterations;
+};
+
+typedef struct {
+    int *osc_params;
+    size_t length;
+} glb_osc_proj_type;
+
+typedef struct {
+    int *density_params;
+    size_t length;
+} glb_density_proj_type;
+
+struct glb_projection_type {
+    glb_osc_proj_type *osc;
+    glb_density_proj_type *density;
+};
+
+/* Interface for non-standard implementations of the probability engine */
+int glb_oscp;
+glb_probability_matrix_function glb_hook_probability_matrix;
+glb_set_oscillation_parameters_function glb_hook_set_oscillation_parameters;
+glb_get_oscillation_parameters_function glb_hook_get_oscillation_parameters;
+void *glb_probability_user_data=NULL;
+/* Internal temporary variables */
+gsl_matrix_complex *U=NULL; /* The vacuum mixing matrix                           */
+gsl_matrix_complex *H=NULL; /* Neutrino Hamiltonian                               */
+gsl_matrix_complex *Q=NULL; /* Eigenvectors of Hamiltonian (= eff. mixing matrix) */
+gsl_vector *lambda=NULL;    /* Eigenvalues of Hamiltonian                         */
+gsl_matrix_complex *S=NULL; /* The neutrino S-matrix                              */
[…]

### 2020-05-22 WFS/FASE_GLoBES.h

@@ -1,0 +1,71 @@
+#include <stdio.h>
+#include <stdlib.h>
+#include <math.h>
+#include <string.h>
+#include <complex.h>
+#include <float.h>
+#include <gsl/gsl_complex.h>
+#include <gsl/gsl_complex_math.h>
+#include <gsl/gsl_matrix.h>
+#include <gsl/gsl_blas.h>
+#include <gsl/gsl_cblas.h>
+#include <gsl/gsl_eigen.h>
+#include <gsl/gsl_vector.h>
+#include "model-input.h"
+
+#define STAN 0
+#define MODEL -100
+#define SQR(x)      ((x)*(x))                        /* x^2   */
+#define SQR_ABS(x)  (SQR(creal(x)) + SQR(cimag(x)))  /* |x|^2 */
+#define GLB_NU_FLAVOURS 3
+#define GLB_V_FACTOR        7.5e-14   /* Conversion factor for matter potentials */
+//#define GLB_Ne_MANTLE       0.497      /* Effective electron numbers for calculation */
+#define GLB_Ne_MANTLE       0.5        /* Effective electron numbers for calculation */
+#define GLB_Ne_CORE         0.468      /*   of MSW potentials                        */
+#define V_THRESHOLD 0.001*GLB_V_FACTOR*GLB_Ne_MANTLE  /* The minimum matter potential below */
+#define M_SQRT3  1.73205080756887729352744634151      /* sqrt(3) */
+
+double th12;
+double th13;
+double th23;
+double deltacp;
+double sdm;
+double ldm;
+double sigma_E;
+double delta;
+int N_in;
+static double mq[3];
+int    PARA,PARA_in,ran,ran_in,n_ram,FIT,PRIOR;
+double x_in,eta_in,r_in,ma_in;
+
+double UPPER_prior[6],LOWER_prior[6],Central_prior[6];
+
+int STAN_OSC(double complex M[], double output[6]);
+inline double square(double x);
+int sinsq(double complex U[], double * a);
+int glb_free_probability_engine();
+int glb_init_probability_engine();
+int zheevc3(double complex A[3][3], double w[3]);
+void zhetrd3(double complex A[3][3], double complex Q[3][3],
+             double d[3], double e[2]);
+int zheevq3(double complex A[3][3], double complex Q[3][3], double w[3]);
+int FASE_glb_set_oscillation_parameters(glb_params p, void *user_data);
[…]

### 2020-05-22 WFS/model-input.c

@@ -1,0 +1,78 @@
+#include <stdio.h>
+#include <stdlib.h>
+#include <math.h>
+#include <string.h>
+#include <complex.h>
+#include <gsl/gsl_complex.h>
+#include <gsl/gsl_math.h>
+#include <globes/globes.h>   /* GLoBES library */
+
+#include <gsl/gsl_complex_math.h>
+#include <gsl/gsl_matrix.h>
+#include <gsl/gsl_blas.h>
+#include <gsl/gsl_statistics.h>
+#include <gsl/gsl_rng.h>
+#include <gsl/gsl_randist.h>
+#include <gsl/gsl_cblas.h>
+#include <gsl/gsl_eigen.h>
+#include <gsl/gsl_vector.h>
+#include "FASE_GLoBES.h"
+int N_M;
+
+double MODEL_init(int N) /*initialise the model-input*/
+{
+    if (N>6){printf("the number of parameters cannot be larger than 6.\n");}
+    N_M=N;
+    return 0;
+}
+
+double MtoS(double osc_para[6], double M_para[])
+/*revert model parameters to
+ the standard oscillation parameters */
+{// set up for normal ordering according to arXiv:1509.06683
+    /*example: tri-direct*/
+    
+    double theta_nu   = M_para[0];
+    double phi_nu     = M_para[1];
+    double sdm        = M_para[2];
+    double ldm        = M_para[3];
+    
+    osc_para[4]=sdm;
+    osc_para[5]=ldm;
+    
+    double sin2the= sin(2*theta_nu);
+    double cosphi = cos(phi_nu);
+    double s12= sqrt(1/(2-sin2the*cosphi));
+    double s13= sqrt((1+sin2the*cosphi)/3);
+    double s23= sqrt((1-sin2the*sin(M_PI/6-phi_nu))/(2-sin2the*cosphi));
+    double JCP= -1*cos(2*theta_nu)/(6*sqrt(3));
+    
+    double theta12=asin(s12);
+    double theta13=asin(s13);
+    double theta23=asin(s23);
+    
+    double sindCP=JCP/(cos(theta12)*s12*cos(theta23)*s23*cos(theta13)*cos(theta13)*s13);
+    double deltaCP=asin(sindCP);
+  
+    
+    osc_para[0]=theta12;
+    osc_para[1]=theta13;
+    osc_para[2]=theta23;
+    osc_para[3]=deltaCP;
+    return 0;
+}
+
+double model_restriction(double M_para [])
[…]

### 2020-05-22 WFS/model-input.h

@@ -1,0 +1,18 @@
+#include <stdio.h>
+#include <stdlib.h>
+#include <math.h>
+#include <string.h>
+#include <complex.h>
+#include <float.h>
+#include <gsl/gsl_complex.h>
+#include <gsl/gsl_complex_math.h>
+#include <gsl/gsl_matrix.h>
+#include <gsl/gsl_blas.h>
+#include <gsl/gsl_cblas.h>
+#include <gsl/gsl_eigen.h>
+#include <gsl/gsl_vector.h>
+
+int N_M;
+double MODEL_init();
+double MtoS(double osc_para[6], double M_para[]);
+double model_restriction(double model []);

### 2020-05-22 WFS/th23_dCP_WFS.c

@@ -1,0 +1,125 @@
+#include <stdio.h>
+#include <stdlib.h>
+#include <math.h>
+#include <string.h>
+#include <complex.h>
+#include <float.h>
+#include <gsl/gsl_cdf.h>
+#include <globes/globes.h>   /* GLoBES library */
+#include "FASE_GLoBES.h"
+#include "model-input.h"
+
+/***************************************************************************
+ *                            M A I N   P R O G R A M                      *
+ ***************************************************************************/
+
+int main(int argc, char *argv[])
+{
+    /* Initialize libglobes */
+    glbInit(argv[0]);
+    glbInitExperiment("exp/MOMENT_FIX_FLUX_150KM_addATM_NC.glb",&glb_experiment_list[0],&glb_num_of_exps);
+    /*Initialize FASE*/
+    MODEL_init(4);
+    
+    /* Register non-standard probability engine. This has to be done
+     * before any calls to glbAllocParams() or glbAllocProjections() */
+    glb_init_probability_engine();
+    glbRegisterProbabilityEngine(6,
+                                 &FASE_glb_probability_matrix,
+                                 &FASE_glb_set_oscillation_parameters,
+                                 &FASE_glb_get_oscillation_parameters,
+                                 NULL);
+    /*define the true value*/
+    float degree   = M_PI/180;
+    double th12_true=33.82*degree;
+    double th13_true=8.61*degree;
+    double th23_true=49.6*degree;
+    double dCP_true=215*degree;
+    double DM21_true=7.39e-5;
+    double DM31_true=2.525e-3;
+    double phi_test=1*M_PI;
+    double theta_test=0.19*M_PI;
+    
+    /* Initialize parameter and projection vector(s) */
+    glb_params true_values = glbAllocParams();
+    glb_params test_values = glbAllocParams();
+    glb_params input_errors = glbAllocParams();
+    glb_params centers = glbAllocParams();
+    
+    /*define model parameter: true_values( x, eta, r, ma)*/
+    glbDefineParams(test_values,theta_test,phi_test,DM21_true,DM31_true,0,0);
[…]

### 2020-05-22 WFS/theta_phi.c

@@ -1,0 +1,117 @@
+#include <stdio.h>
+#include <stdlib.h>
+#include <math.h>
+#include <string.h>
+#include <complex.h>
+#include <float.h>
+#include <globes/globes.h>   /* GLoBES library */
+#include "FASE_GLoBES.h"
+#include "model-input.h"
+
+/***************************************************************************
+ *                            M A I N   P R O G R A M                      *
+ ***************************************************************************/
+
+int main(int argc, char *argv[])
+{
+    /* Initialize libglobes */
+    glbInit(argv[0]);
+    glbInitExperiment("exp/MOMENT_FIX_FLUX_150KM_addATM_NC.glb",&glb_experiment_list[0],&glb_num_of_exps);
+    
+    /*Initialize FASE*/
+    MODEL_init(4);
+    
+    /* Register non-standard probability engine. This has to be done
+     * before any calls to glbAllocParams() or glbAllocProjections() */
+    glb_init_probability_engine();
+    glbRegisterProbabilityEngine(6,
+                                 &FASE_glb_probability_matrix,
+                                 &FASE_glb_set_oscillation_parameters,
+                                 &FASE_glb_get_oscillation_parameters,
+                                 NULL);
+    /*define the true value*/
+    float degree   = M_PI/180;
+    double th12_true=33.82*degree;
+    double th13_true=8.61*degree;
+    double th23_true=49.6*degree;
+    double dCP_true=215*degree;
+    double DM21_true=7.39e-5;
+    double DM31_true=2.525e-3;
+    double phi_test=1*M_PI;
+    double theta_test=0.19*M_PI;
+    /* Initialize parameter and projection vector(s) */
+    glb_params true_values = glbAllocParams();
+    glb_params test_values = glbAllocParams();
+    glb_params input_errors = glbAllocParams();
+    glb_params centers = glbAllocParams();
+    
+    /*define model parameter: true_values( x, eta, r, ma)*/
+    glbDefineParams(true_values,th12_true,th13_true,th23_true,dCP_true,DM21_true,DM31_true);
[…]

### 2020-05-22 doc/paper.tex
update docs

@@
 
-%\documentclass[aps,prd,nofootinbib,preprint]{revtex4}
-\documentclass[preprint]{revtex4}
+\documentclass[aps,prd,nofootinbib,preprint]{revtex4}
+%\documentclass[preprint]{revtex4}
 %\documentclass[a4paper]{article}
@@
   \caption{\label{fig:constraint}Examples for using \textbf{FaSE-GLoBES} to obtain the constraints of model parameters for tri-direct littlest seesaw (left) and the warped flavor symmetry (right), with simulated DUNE and MOMENT data.
-{\color{blue}Two results are assumed the normal ordering.
-And, the dot denotes the model prediction with with NuFit4.0 results.} \textcolor{red}{No best-fit values in the right panel?
-NH is assumed here?}}
+Two results are assumed the normal ordering.
+And, the dot denotes the model prediction with with NuFit4.0 results.}
 \end{figure}
@@
 on the plane of true values of $\theta_{23}$ and $\delta$ for sub-models of TDLS (left) and of WFS (right) with DUNE and MOMENT.
-{\color{blue}Two results are assumed the normal ordering.
-And, the dot (star) denotes the model prediction with NuFit4.0 results (best fit of NuFit4.0).} \textcolor{red}{No best-fit values in the right panel?
-NH is assumed here?}}
+Two results are assumed the normal ordering.
+And, the dot (star) denotes the model prediction with NuFit4.0 results (best fit of NuFit4.0).}
 %\caption{\label{fig:th23_delta}The 2-D exclusion contour for sub-models of tri-direct littlest seesaw on the plane of two true standard parameters $\theta_{23}$ and $\delta$, from $1\sigma$ to $5\sigma$, for DUNE (dotted) and MOMENT (solid).
@@
 We further show the generality of \textbf{FaSE-GLoBES} by demonstrating the similar result for another model -- WFS in Eq.~(\ref{eq:WFS}) for DUNE and MOMENT, in right panel of Fig.~\ref{fig:th23_delta}.
-In this result, two mass-squared differences are fixed at the true values without including any priors.
+In this result, two mass-squared differences are fixed at the true values.
 %
@@
 Users are able to study how a flavour model can be studied by the simulated experimental configuration in various perspectives, \textit{e.g.} model parameter constraints, hypothesis testing.
-{\color{blue} \textbf{FaSE-GLoBES} will contribute to the selection and screening of underlying neutrino mass models by oscillation experiments.
-Further improvements and extensions can be envisioned as more requests are made by users.}
+\textbf{FaSE-GLoBES} will contribute to the selection and screening of underlying neutrino mass models by oscillation experiments.
+Further improvements and extensions can be envisioned as more requests are made by users.
 
-\textcolor{red}{In the references, the arXiv number is chopped by one digit. Could you please check the reason?}
+%\textcolor{red}{In the references, the arXiv number is chopped by one digit. Could you please check the reason?}
 
@@
 %\bibliographystyle{JHEP}
-\bibliographystyle{plain}
+%\bibliographystyle{plain}
 %\bibliographystyle{ksfh_nat}

### 2020-05-25 examples(TDLS)/FASE_GLoBES.c
update codes

@@ -4,16 +4,23 @@
 #include <string.h>
 #include <complex.h>
 #include <float.h>
+
 #include <gsl/gsl_math.h>
 #include <gsl/gsl_complex.h>
 #include <gsl/gsl_complex_math.h>
 #include <gsl/gsl_matrix.h>
 #include <gsl/gsl_blas.h>
+//#include <gsl/gsl_statistics.h>
+//#include <gsl/gsl_rng.h>
+//#include <gsl/gsl_randist.h>
 #include <gsl/gsl_cblas.h>
 #include <gsl/gsl_eigen.h>
 #include <gsl/gsl_vector.h>
+
+
 #include <globes/globes.h>   /* GLoBES library */
 #include"FASE_GLoBES.h"
+//#include"model-input_diag.h"
 #include"model-input.h"
 
 extern char **glb_param_names;

### 2020-05-25 examples(TDLS)/FASE_GLoBES.h

@@ -1,3 +1,34 @@
+/* GLoBES -- General LOng Baseline Experiment Simulator
+ * (C) 2002 - 2007,  The GLoBES Team
+ *
+ * GLoBES is mainly intended for academic purposes. Proper
+ * credit must be given if you use GLoBES or parts of it. Please
+ * read the section 'Credit' in the README file.
+ *
+ * This program is free software; you can redistribute it and/or modify
+ * it under the terms of the GNU General Public License as published by
+ * the Free Software Foundation; either version 2 of the License, or
+ * (at your option) any later version.
+ *
+ * This program is distributed in the hope that it will be useful,
+ * but WITHOUT ANY WARRANTY; without even the implied warranty of
+ * MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+ * GNU General Public License for more details.
+ *
+ * You should have received a copy of the GNU General Public License
+ * along with this program; if not, write to the Free Software
+ * Foundation, Inc., 59 Temple Place, Suite 330, Boston, MA  02111-1307  USA
+ */
+ 
+/*
+ Some simple output functions for GLoBES examples
+ */
+
+
+//#ifndef TRI_DIRECT_PE_H
+//#define TRI_DIRECT_PE_H
+
+
 #include <stdio.h>
 #include <stdlib.h>
 #include <math.h>
@@ -8,10 +39,16 @@
 #include <gsl/gsl_complex_math.h>
 #include <gsl/gsl_matrix.h>
 #include <gsl/gsl_blas.h>
+//#include <gsl/gsl_statistics.h>
+//#include <gsl/gsl_rng.h>
+//#include <gsl/gsl_randist.h>
 #include <gsl/gsl_cblas.h>
 #include <gsl/gsl_eigen.h>
 #include <gsl/gsl_vector.h>
+//#include <globes/globes.h>   /* GLoBES library */
+
 #include "model-input.h"
+//#include "model-input_diag.h"
 
 /*#define GLB_NU_FLAVOURS 3*/
 #define GLB_SIGMA_E 6        /* Index of non-standard parameter sigma_E */
@@ -39,6 +76,8 @@
 #define M_SQRT3  1.73205080756887729352744634151      /* sqrt(3) */
 
 /* Interface for non-standard implementations of the probability engine */
+
[…]

### 2020-05-25 examples(TDLS)/model-input.c

@@ -1,0 +1,358 @@
+#include <stdio.h>
+#include <stdlib.h>
+#include <math.h>
+#include <string.h>
+#include <complex.h>
+#include <gsl/gsl_complex.h>
+#include <gsl/gsl_math.h>
+#include <globes/globes.h>   /* GLoBES library */
+
+#include <gsl/gsl_complex_math.h>
+#include <gsl/gsl_matrix.h>
+#include <gsl/gsl_blas.h>
+#include <gsl/gsl_statistics.h>
+#include <gsl/gsl_rng.h>
+#include <gsl/gsl_randist.h>
+#include <gsl/gsl_cblas.h>
+#include <gsl/gsl_eigen.h>
+#include <gsl/gsl_vector.h>
+#include "FASE_GLoBES.h"
+/* Macros */
+//#define SQR(x)          ((x)*(x))                       /*x^2*/
+//#define SQR_ABS(x)      (SQR(creal(x))+SQR(cimag(x)))   /*|x|^2*/
+int N_M;
+
+/*Define the formula (5) in the working note provided by Ding.*/
+double complex TDModelY(double x, double eta, double r, double Ma){
+    double Ms=Ma*r;
+    
+    double complex result;
+    result = (5*SQR(x) + 2*x + 2)*(Ma + cexp(I*eta)*Ms)/(SQR(x) + x +1)*1/2;
+    
+    return result;
+    
+} //Checked!
+
+/*Define the formula (5) in the working note provided by Ding.*/
+double complex TDModelZ(double x, double eta, double r, double Ma){
+    double Ms=Ma*r;
+    
+    double complex result;
+    result = (-1)*sqrt(5*SQR(x) + 2*x + 2)/(SQR(x) + x + 1) * 1/2 * ((x+2)*Ma - x*(2*x+1) * cexp(I*eta)*Ms);
+    
+    return result;
+} //Checked!
+
+/*Define the formula (5) in the working note provided by Ding.*/
+double complex TDModelW(double x, double eta, double r, double Ma){
+    double Ms=Ma*r;
+    
+    double complex result;
+    result = 1/(SQR(x) + x + 1) * 1/2 * ( SQR(x+2)*Ma + SQR(x)*SQR(2*x+1) * cexp(I*eta)*Ms);
+    
[…]

### 2020-05-25 examples(TDLS)/model-input.h

@@ -1,0 +1,43 @@
+#include <stdio.h>
+#include <stdlib.h>
+#include <math.h>
+#include <string.h>
+#include <complex.h>
+#include <float.h>
+#include <gsl/gsl_complex.h>
+#include <gsl/gsl_complex_math.h>
+#include <gsl/gsl_matrix.h>
+#include <gsl/gsl_blas.h>
+//#include <gsl/gsl_statistics.h>
+//#include <gsl/gsl_rng.h>
+//#include <gsl/gsl_randist.h>
+#include <gsl/gsl_cblas.h>
+#include <gsl/gsl_eigen.h>
+#include <gsl/gsl_vector.h>
+//#include "FASE_GLoBES.h"
+
+int N_M;
+/******************************************the user-defined relation*/
+double complex TDModelY(double x, double eta, double r, double Ma);
+double complex TDModelZ(double x, double eta, double r, double Ma);
+double complex TDModelW(double x, double eta, double r, double Ma);
+double TDpsi(double x, double eta, double r, double Ma);
+double TDsinpsi(double x, double eta, double r, double Ma);
+double TDcospsi(double x, double eta, double r, double Ma);
+double TDtheta(double x, double eta, double r, double Ma);
+double TDth12(double x, double eta, double r, double Ma);
+double TDth13(double x, double eta, double r, double Ma);
+double TDth23(double x, double eta, double r, double Ma);
+double TDdCP(double x, double eta, double r, double Ma);
+double TDdm21(double x, double eta, double r, double Ma);
+double TDdm31(double x, double eta, double r, double Ma);
+/*******************************************************************/
+
+double MODEL_init();
+/********************************************diagonaliser ********/
+//int STAN_OSC(double complex M[], double output[6]);
+//int ModelTO( double OSC_PARAMS[6],double M_para[]);
+/*******************************************************************/
+
+double MtoS(double osc_para[6], double M_para[]);
+double model_restriction(double model []);

### 2020-05-25 examples(TDLS)/th23_dCP.c

@@ -1,30 +1,12 @@
-#if HAVE_CONFIG_H   /* config.h should come before any other includes */
-#  include "config.h"
-#endif
-
-
 #include <stdio.h>
 #include <stdlib.h>
 #include <math.h>
 #include <string.h>
 #include <complex.h>
 #include <float.h>
-
-#include <gsl/gsl_complex.h>
-#include <gsl/gsl_complex_math.h>
-#include <gsl/gsl_matrix.h>
-#include <gsl/gsl_blas.h>
-#include <gsl/gsl_statistics.h>
-#include <gsl/gsl_rng.h>
-#include <gsl/gsl_randist.h>
-#include <gsl/gsl_cblas.h>
-#include <gsl/gsl_eigen.h>
-#include <gsl/gsl_vector.h>
-
-
+#include <gsl/gsl_cdf.h>
 #include <globes/globes.h>   /* GLoBES library */
 #include "FASE_GLoBES.h"
-//#include "model-input_diag.h"
 #include "model-input.h"
 
 /***************************************************************************
@@ -35,7 +17,8 @@ int main(int argc, char *argv[])
 {
     /* Initialize libglobes */
     glbInit(argv[0]);
-    glbInitExperiment("exp/MOMENT_FIX_FLUX_150KM_addATM_NC.glb",&glb_experiment_list[0],&glb_num_of_exps);
+    glbInitExperiment("exp/MOMENT_150KM_addATM_NC.glb",&glb_experiment_list[0],&glb_num_of_exps);
+
     /*Initialize FASE*/
     MODEL_init(4);
     
@@ -51,76 +34,100 @@ int main(int argc, char *argv[])
     float degree   = M_PI/180;
     float x_true,eta_true,r_true,ma_true;
     x_true=-3.65029; eta_true=1.13067*M_PI; r_true=0.511325; ma_true=3.71199e-3;
+    double M_para[4],OSC_para[6];
+    M_para[0]=x_true; M_para[1]=eta_true; M_para[2]=r_true; M_para[3]=ma_true;
     
+    MtoS(OSC_para, M_para);
+    double th12_true=OSC_para[0];
+    double th13_true=OSC_para[1];
+    double th23_true=OSC_para[2];
+    double dCP_true=OSC_para[3];
+    double DM21_true=OSC_para[4];
+    double DM31_true=OSC_para[5];
+
     /* Initialize parameter and projection vector(s) */
[…]

### 2020-05-25 examples(TDLS)/x_eta.c

@@ -4,7 +4,6 @@
 #include <string.h>
 #include <complex.h>
 #include <float.h>
-#include <gsl/gsl_cdf.h>
 #include <globes/globes.h>   /* GLoBES library */
 #include "FASE_GLoBES.h"
 #include "model-input.h"
@@ -31,41 +30,35 @@ int main(int argc, char *argv[])
                                  NULL);
     /*define the true value*/
     float degree   = M_PI/180;
-    double th12_true=33.82*degree;
-    double th13_true=8.61*degree;
-    double th23_true=49.6*degree;
-    double dCP_true=215*degree;
-    double DM21_true=7.39e-5;
-    double DM31_true=2.525e-3;
-    double phi_test=1*M_PI;
-    double theta_test=0.19*M_PI;
+    float x_true,eta_true,r_true,ma_true;
+    x_true=-3.65029; eta_true=1.13067*M_PI; r_true=0.511325; ma_true=3.71199e-3;
     
     /* Initialize parameter and projection vector(s) */
     glb_params true_values = glbAllocParams();
     glb_params test_values = glbAllocParams();
     glb_params input_errors = glbAllocParams();
     glb_params centers = glbAllocParams();
-    
+    glb_params out = glbAllocParams();
+    glb_params out_temp = glbAllocParams();
     /*define model parameter: true_values( x, eta, r, ma)*/
-    glbDefineParams(test_values,theta_test,phi_test,DM21_true,DM31_true,0,0);
+    glbDefineParams(true_values,x_true,eta_true,r_true,ma_true,0,0);
     glbSetDensityParams(true_values,1.0,GLB_ALL);
-    int i;
-    
-    glbDefineParams(true_values,th12_true,th13_true,th23_true,dCP_true,DM21_true,DM31_true);
-    glbSetDensityParams(true_values,1.0,GLB_ALL);
-
+    glbCopyParams(true_values,test_values);
     
     /*assign the parameter set*/
+    PARA=STAN; /* if the user is interested in the sensitivity on Standard Oscillation parameters*/ /*Mark4*/
     PARA=MODEL; /* if the user is interested in the sensitivity on model parameters*/
[…]

### 2020-05-25 model-input.c

@@ -6,197 +6,18 @@
 #include <gsl/gsl_complex.h>
 #include <gsl/gsl_math.h>
 #include <globes/globes.h>   /* GLoBES library */
-
 #include <gsl/gsl_complex_math.h>
 #include <gsl/gsl_matrix.h>
 #include <gsl/gsl_blas.h>
-//#include <gsl/gsl_statistics.h>
-//#include <gsl/gsl_rng.h>
-//#include <gsl/gsl_randist.h>
+#include <gsl/gsl_statistics.h>
+#include <gsl/gsl_rng.h>
+#include <gsl/gsl_randist.h>
 #include <gsl/gsl_cblas.h>
 #include <gsl/gsl_eigen.h>
 #include <gsl/gsl_vector.h>
 #include "FASE_GLoBES.h"
 /* Macros */
-//#define SQR(x)          ((x)*(x))                       /*x^2*/
-//#define SQR_ABS(x)      (SQR(creal(x))+SQR(cimag(x)))   /*|x|^2*/
 int N_M;
-
-/*Define the formula (5) in the working note provided by Ding.*/
-double complex TDModelY(double x, double eta, double r, double Ma){
-    double Ms=Ma*r;
-    
-    double complex result;
-    result = (5*SQR(x) + 2*x + 2)*(Ma + cexp(I*eta)*Ms)/(SQR(x) + x +1)*1/2;
-    
-    return result;
-    
-} //Checked!
-
-/*Define the formula (5) in the working note provided by Ding.*/
-double complex TDModelZ(double x, double eta, double r, double Ma){
-    double Ms=Ma*r;
-    
-    double complex result;
-    result = (-1)*sqrt(5*SQR(x) + 2*x + 2)/(SQR(x) + x + 1) * 1/2 * ((x+2)*Ma - x*(2*x+1) * cexp(I*eta)*Ms);
-    
-    return result;
-} //Checked!
-
-/*Define the formula (5) in the working note provided by Ding.*/
-double complex TDModelW(double x, double eta, double r, double Ma){
-    double Ms=Ma*r;
-    
-    double complex result;
-    result = 1/(SQR(x) + x + 1) * 1/2 * ( SQR(x+2)*Ma + SQR(x)*SQR(2*x+1) * cexp(I*eta)*Ms);
-    
[…]

### 2020-05-25 model-input.h

@@ -8,9 +8,6 @@
 #include <gsl/gsl_complex_math.h>
 #include <gsl/gsl_matrix.h>
 #include <gsl/gsl_blas.h>
-//#include <gsl/gsl_statistics.h>
-//#include <gsl/gsl_rng.h>
-//#include <gsl/gsl_randist.h>
 #include <gsl/gsl_cblas.h>
 #include <gsl/gsl_eigen.h>
 #include <gsl/gsl_vector.h>
@@ -18,19 +15,6 @@
 
 int N_M;
 /******************************************the user-defined relation*/
-double complex TDModelY(double x, double eta, double r, double Ma);
-double complex TDModelZ(double x, double eta, double r, double Ma);
-double complex TDModelW(double x, double eta, double r, double Ma);
-double TDpsi(double x, double eta, double r, double Ma);
-double TDsinpsi(double x, double eta, double r, double Ma);
-double TDcospsi(double x, double eta, double r, double Ma);
-double TDtheta(double x, double eta, double r, double Ma);
-double TDth12(double x, double eta, double r, double Ma);
-double TDth13(double x, double eta, double r, double Ma);
-double TDth23(double x, double eta, double r, double Ma);
-double TDdCP(double x, double eta, double r, double Ma);
-double TDdm21(double x, double eta, double r, double Ma);
-double TDdm31(double x, double eta, double r, double Ma);
 /*******************************************************************/
 
 double MODEL_init();

### 2020-05-25 model_constrain_xxx_v1.c

@@ -1,179 +1,0 @@
-/* GLoBES -- General LOng Baseline Experiment Simulator
- * (C) 2002 - 2007,  The GLoBES Team
- *
- * GLoBES is mainly intended for academic purposes. Proper
- * credit must be given if you use GLoBES or parts of it. Please
- * read the section 'Credit' in the README file.
- *
- * This program is free software; you can redistribute it and/or modify
- * it under the terms of the GNU General Public License as published by
- * the Free Software Foundation; either version 2 of the License, or
- * (at your option) any later version.
- *
- * This program is distributed in the hope that it will be useful,
- * but WITHOUT ANY WARRANTY; without even the implied warranty of
- * MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
- * GNU General Public License for more details.
- *
- * You should have received a copy of the GNU General Public License
- * along with this program; if not, write to the Free Software
- * Foundation, Inc., 59 Temple Place, Suite 330, Boston, MA  02111-1307  USA
- */
-
-/*
- * Example: Non-Standard-Interactions and user-defined priors
- * Compile with ``make example6''
- *
- * This example is similar to Chapter 4 of hep-ph/0502147
- */
-#if HAVE_CONFIG_H   /* config.h should come before any other includes */
-#  include "config.h"
-#endif
-
-
-#include <stdio.h>
-#include <stdlib.h>
-#include <math.h>
-#include <string.h>
-#include <complex.h>
-#include <float.h>
-
-#include <gsl/gsl_complex.h>
-#include <gsl/gsl_complex_math.h>
-#include <gsl/gsl_matrix.h>
-#include <gsl/gsl_blas.h>
-#include <gsl/gsl_statistics.h>
-#include <gsl/gsl_rng.h>
-#include <gsl/gsl_randist.h>
-#include <gsl/gsl_cblas.h>
-#include <gsl/gsl_eigen.h>
-#include <gsl/gsl_vector.h>
-
-
-#include <globes/globes.h>   /* GLoBES library */
-#include "FASE_GLoBES.h"
-//#include "model-input_diag.h"
-#include "model-input.h"
-
-/***************************************************************************
[…]

### 2020-05-25 th23_dCP.c

@@ -1,146 +1,0 @@
-#if HAVE_CONFIG_H   /* config.h should come before any other includes */
-#  include "config.h"
-#endif
-
-
-#include <stdio.h>
-#include <stdlib.h>
-#include <math.h>
-#include <string.h>
-#include <complex.h>
-#include <float.h>
-
-/*
-#include <gsl/gsl_complex.h>
-#include <gsl/gsl_complex_math.h>
-#include <gsl/gsl_matrix.h>
-#include <gsl/gsl_blas.h>
-#include <gsl/gsl_statistics.h>
-#include <gsl/gsl_rng.h>
-#include <gsl/gsl_randist.h>
-#include <gsl/gsl_cblas.h>
-#include <gsl/gsl_eigen.h>
-#include <gsl/gsl_vector.h>
-*/
-#include <gsl/gsl_cdf.h>
-#include <globes/globes.h>   /* GLoBES library */
-#include "FASE_GLoBES.h"
-//#include "model-input_diag.h"
-#include "model-input.h"
-
-/***************************************************************************
- *                            M A I N   P R O G R A M                      *
- ***************************************************************************/
-
-int main(int argc, char *argv[])
-{
-    /* Initialize libglobes */
-    glbInit(argv[0]);
-    glbInitExperiment("exp/MOMENT_FIX_FLUX_150KM_addATM_NC.glb",&glb_experiment_list[0],&glb_num_of_exps);
-    /*Initialize FASE*/
-    MODEL_init(4);
-    
-    /* Register non-standard probability engine. This has to be done
-     * before any calls to glbAllocParams() or glbAllocProjections() */
-    glb_init_probability_engine();
-    glbRegisterProbabilityEngine(6,
-                                 &FASE_glb_probability_matrix,
-                                 &FASE_glb_set_oscillation_parameters,
-                                 &FASE_glb_get_oscillation_parameters,
-                                 NULL);
-    /*define the true value*/
-    float degree   = M_PI/180;
-    float x_true,eta_true,r_true,ma_true;
-    x_true=-3.65029; eta_true=1.13067*M_PI; r_true=0.511325; ma_true=3.71199e-3;
-    double M_para[4],OSC_para[6];
[…]

### 2020-05-25 doc/FAS-GLoBES.tex
update manual

@@
 \section{Introduction}\label{sec:intro}
-
+{\color{red}[updating]} 
 The discovery of neutrino oscillations points out the fact that neutrinos have mass, and provides evidence beyond the Standard Model (BSM).
@@
 \textbf{F}l\textbf{a}vor \textbf{S}ymmetry \textbf{E}mbedded (\textbf{FaSE}) is a supplemental tool for \textbf{G}eneral \textbf{Lo}ng \textbf{B}aseline \textbf{E}xperiment \textbf{S}imulator (\textbf{GLoBES}) in order to analyse how a leptonic flavour symmetry model can be tested in neutrino oscillation experiments.
-\textbf{FaSE} is written in the \texttt{c/c++} language, and consist with three codes \textbf{FASE\_GLoBES.c} and \textbf{model-input.c}.
+\textbf{FaSE} is written in the \texttt{c/c++} language, and consist with two codes \textbf{FASE\_GLoBES.c} and \textbf{model-input.c}.
 The user defines the model in to \textbf{model-input.c}, while \textbf{FASE\_GLoBES.c} does not need to be touched.
@@
 \centering
-\includegraphics[width=4.5in]{Figs/FASE-chart_1_2.pdf}
+\includegraphics[width=7in]{Figs/FASE-chart_1_2.pdf}
 \caption{A scheme to correlate the model parameters with standard neutrino oscillation parameters. The error propagation is implemented in the simulation code up to the spectra analysis.}%
@@
 
-The concept of \textbf{FaSE-GLoBES} is shown in Fig.~\ref{fig:FASE}, in which three parts are shown: 1.~\textbf{the parameter translation} (the blue box), 2.~\textbf{giving oscillation-parameter values} (the green box), and 3.~\textbf{the $\chi^2$-value calculation} (the orange box).
-The idea behind this flow chart Fig.~\ref{fig:FASE} is that given a set of value for model parameter, the corresponding values for oscillation parameters are obtained by a translation, which is assigned by the user in \textbf{model-input.c}.
-And then, through \textbf{FASE\_GLoBES.c} these oscillation-parameter values are passed in to \textbf{GLoBES} library to simulate the event spectrum for evaluating the $\chi^2$ value.
+The concept of \textbf{FaSE-GLoBES} is shown in Fig.~\ref{fig:FASE}, in which three parts are shown: 1.~\textbf{the parameter translation}, 2.~\textbf{giving oscillation-parameter values}, and 3.~\textbf{the $\chi^2$-value calculation}.
+%
+The idea behind this flow chart in Fig.~\ref{fig:FASE} is that given a set of model parameters $\vec{\theta}_{Model}$, the corresponding values in standard oscillation parameters $\vec{\theta}_{OSC}$ are obtained by a translation function, which is assigned by the user in \textbf{model-input.c}.
+And then, through \textbf{FASE\_GLoBES.c} these oscillation-parameter values are passed into \textbf{GLoBES} library to simulate the event spectra so that we can perform physics analysis in the newly-defined $\chi^2$.
 
@@
 
-To do the translation from $\vec{\theta}_{Model}$ to $\vec{\theta}_{OSC}$, the user can assign the relation between the oscillation and model parameter sets, or define the mass matrix in model parameters, which will be diagonalised by the function \texttt{ModelTO} to obtain the corresponding oscillation-parameter values.
+To do the translation from $\vec{\theta}_{Model}$ to $\vec{\theta}_{OSC}$, the user can assign the relation between the oscillation and model parameter sets, or define the mass matrix in model parameters, which will be diagonalised by the function \texttt{STAN\_OSC} to obtain the corresponding oscillation-parameter values.
 %The relation between the oscillation and model parameter sets can be derived out by the user, 
@@
 The difference between any two diagonal elements of $\textbf{M}$ ($\textbf{M}_{ii}-\textbf{M}_{jj}=m_i^2-m_j^2$) is the mass-squared difference ($\Delta m_{ij}^2$).
-This diagnolisation Eq.~\ref{eq:MM} can be done with the function \texttt{STAN\_OSC}, which outputs directly the vector $\vec{\theta}\_{OSC}$.
-The user needs to call it in \texttt{MtoS} with the script,\vspace{0.2cm}\\
+This diagnolisation Eq.~(\ref{eq:MM}) can be done with the function \texttt{STAN\_OSC}, which outputs directly the vector $\vec{\theta}_{OSC}$.
+The user needs to call it in \texttt{MtoS} with\vspace{0.2cm}\\
 \texttt{STAN\_OSC(\{}$M$\texttt{\},\{}$\vec{\theta}_{OSC}$\texttt{\});},\\
 where \texttt{\{}$M$\texttt{\}} and \texttt{\{}$\vec{\theta}_{OSC}$\texttt{\}} are the input neutrino mass matrix and the output array of oscillation parameter values, respectively.
+More details about how to assign a model will be introduced in Sec.~\ref{sec:ex_set_model}.
 
@@
 Given a set of values for model parameters, \textbf{FASE\_GLoBES.c} will obtain the corresponding oscillation-parameter values from \textbf{model-input.c}, and will pass these values to simulate event spectra and to compute the prior value.
-Two gaussian prior functions are provided in \textbf{FaSE} -- \texttt{FASE\_prior\_OSC} and \texttt{FASE\_prior\_model}.
+Two gaussian prior functions are provided in \textbf{FaSE}: \texttt{FASE\_prior\_OSC} and \texttt{FASE\_prior\_model}.
 These two functions are for different purposes.
@@
 For example, if the normal ordering is imposed, we give ``\texttt{ if (DMS31<0) \{ return 1;\} } '' in \texttt{model\_restriction}, where \texttt{DMS31} is the variable for $\Delta m_{31}^2$.
-Then, when the restriction is broken, \texttt{model\_restriction} returns the value $1$ to the prior function \texttt{FASE\_prior\_OSC} or \texttt{FASE\_prior\_model}.
-Therefore, if there is no any restrictions, we simply \textit{return $0$} in \texttt{model\_restriction} as follows.\vspace{0.2cm}\\
+If there is no any restrictions, we simply \textit{return $0$} in \texttt{model\_restriction} as follows.\vspace{0.2cm}\\
 \texttt{double model\_restriction(double model [])\{ return 0;\} }\vspace{0.2cm}\\
@@
 
+\subsection{The definition of $\chi^2$ function}
+
+The user can use \textbf{FaSE-GLoBES} to constrain model parameters. 
+Suppose we have the measurement $\vec{x}$ and the likelihood function $L(\vec{\theta})=P(\vec{x}|\vec{\theta})$ for a set of parameters $\vec{\theta}=(\theta_1,...,\theta_N)$, where $P(\vec{x}|\vec{\theta})$ is the probability function for data $\vec{x}$ in favour of the hypothesis $\vec{\theta}$.
+The constraint of model parameters can be obtained with the statistis parameter $\chi^2\equiv \ln L(\vec{\theta})$.
+The expression $\chi^2$ is used as the default \textbf{GLoBES} setting. In more detail, the $\chi^2$ function, following the Poisson distribution, is constructed based on a log-likelihood ratio,
+%\begin{equation}\label{eq:chi-squared}
+\begin{align}\label{eq:chi-squared}
+\chi^2(\vec{\theta}^{hyp},\xi_s,\xi_b)=&2\sum_i\left(\eta_i(\vec{\theta}^{hyp},\xi_s,\xi_b)-n_i+n_i\ln\frac{n_i}{\eta_i(\vec{\theta}^{hyp},\xi_s,\xi_b)} \right)\nonumber\\
+&+p(\xi_s,\sigma_s)+p(\xi_b,\sigma_b)+\chi^2_{prior},
+\end{align}
+%\end{equation}
+where $i$ runs over the number of bins, $\eta_i(\vec{\theta},\xi_s,\xi_b)$ is the assumed event rate in the $i$th bin and $E_i$ is the central value in this energy bin.
+The vector $\vec{\theta}$ consists of model or oscillation parameters.
+The parameters $\xi_s$ and $\xi_b$ are introduced to account for the systematic uncertainties in the normalisation for the signal (subscript $_s$) and background (subscript $_b$) components of the event rate, and are allowed to vary in the fit as nuisance parameters.
+For a given set of parameters $\vec{\theta}$, the event rate in the $i$th energy bin is calculated as\\
+\begin{equation}
+\eta_i(\vec{\theta}^{hyp},\xi_s,\xi_b)=(1+\xi_s)\times s_i+(1+\xi_b)\times b_i,
+\end{equation}
+where $s_i$ and $b_i$ are the expected number of signal and background events in $i$th energy bin, respectively.
+The nuisance parameters are constrained by the Gaussian prior $p(\xi,\sigma)=\xi^2/\sigma^2$ with corresponding uncertainties $\sigma_s$ and $\sigma_b$ for the signal and background, respectively.
+Finally, $\chi^2_{prior}$ is a set of Gaussian priors for hypothesis, and is expressed as Eq.~(\ref{eq:prior}).
+After doing all minimisations, the user obtains the $\chi^2$ value for a specific hypothesis $\vec{\theta}^{hyp}$, $\chi^2(\vec{\theta}^{hyp})$.
+
+Based on the $\chi^2$ function Eq.~(\ref{eq:chi-squared}), we can study how model parameters can be constrained and whether a flavour-symmetry neutrino model is excluded by simulated experiments.
+In the following we will demonstrate how it works.
+
+\subsubsection*{Applications}
+
+The user of \textbf{FaSE-GLoBES} is able to study how model parameters can be constrained by the simulated experiments.
+To do so, the user needs to simulate the true event spectrum $n_i$ with a set of model ($\vec{\theta}_{Model}^{true}$) or oscillation parameters ($\vec{\theta}_{OSC}^{true}$), \textit{i.e.}~set up $n_i(\vec{\theta}_{Model}^{true})$ or $n_i(\vec{\theta}_{OSC}^{true})$.
+The hypothesis $\vec{\theta}_{Model}^{hyp}$ predicts the tested event spectrum $\eta_i(\vec{\theta}_{Model}^{hyp},\xi_s,\xi_b)$.
+With the default settings for $\chi^2$ function as Eq.~(\ref{eq:prior}) in \textbf{FaSE-GLoBES}, the user computes the statistical quantity,
+\begin{equation}\label{eq:chi_model}
+\chi^2(\vec{\theta}_{Model}^{hyp}),~~\text{with}~n_i(\vec{\theta}_{Model}^{true})~\text{or}~n_i(\vec{\theta}_{OSC}^{true}).
+\end{equation}
+%
+We note that the minimum of $\chi^2$ in the whole parameter space ($\chi^2_{min.}$) may not be $0$.
+Therefore, to get the precision of model parameters, the user should use the value $\Delta\chi^2(\vec{\theta}_{Model}^{hyp})\equiv \chi^2(\vec{\theta}_{Model}^{hyp})-\chi^2_{min.}$, instead of $\chi^2(\vec{\theta}_{Model}^{hyp})$ itself.
+By varying different hypotheses $\vec{\theta}_{Model}^{hyp}$, we will obtain the allowed region of model parameters with the statistical quantity $\Delta\chi^2(\vec{\theta}_{Model}^{hyp})$.
+
+The user can also study how well a flavour symmetry model explains the computed data, or predict whether the simulated experiment can exclude this model or not.
+In other words, the user studies the minimum of $\chi^2$ for the flavour symmetry model $\vec{\theta}_{Model}$ as a hypothesis, by assuming different true oscillation values, \textit{i.e.}~different $\vec{\theta}^{true}_{OSC}$.
+To do so, one can compute the same statistical quantity in Eq.~(\ref{eq:chi_model}), while the true spectrum is varied with different true values $\vec{\theta}_{OSC}^{true}$.
+All model parameters are allowed to be varied with the user-defined prior.
+%
+Finally, the user might adopt Wilk's theorem to interpret results~\cite{Wilks:1938dza}.
+When we compare nested models, the $\Delta \chi^2$ test statistics is a random variable asymptotically distributed as a $\chi^2$-distribution with the number of degrees of freedom, which is equal to the difference in the number of free model parameters.
+
+In Secs.~\ref{sec:ex_MC} and \ref{sec:ex_MT}, we will present examples to demonstrate how the user can do with \textbf{FaSE-GLoBES} to constrain the model parameter and to exclude a model by the simulated experiment configuration, respectively.
+
 \section{Examples}
-\subsection{Setup for a model}
-We now take the tri-direct littlest seesaw (TDLS)~\cite{King:2013iva,King:2015dvf,King:2016yvg} as an example.
-In this model, the atmospheric and solar flavon vacuum alignments are $\langle\phi_{\text{atm}}\rangle\propto\left(1, \omega^2, \omega\right)^T$ and $\langle\phi_{\text{sol}}\rangle\propto\left(1, x, x\right)^T$,
-where  stands for a cube root of unity and the parameter $x$ is real because of the imposed CP symmetry. Under this model, the light left-handed Majorana neutrino mass matrix is given by
-\begin{equation}
-\label{eq:mnu}  m_{\nu}=m_{a}\begin{pmatrix}
- 1 &~ \omega  &~ \omega ^2 \\
- \omega  &~ \omega ^2 &~ 1 \\
- \omega ^2 &~ 1 &~ \omega  \\
-\end{pmatrix}+e^{i\eta}m_{s}
-\begin{pmatrix}
- 1 &~  x &~  x \\
- x &~ x^2 &~ x^2 \\
- x &~ x^2 &~ x^2 \\
-\end{pmatrix}\,,
-\end{equation}
-where $x$, $\eta$, $m_a$, and the ratio $r\equiv m_s/m_a$ are four parameters and will be constrained by experimental data.
-We note that from Eq.~(\ref{eq:mnu}), $m_1=0$ and the normal mass ordering are imposed, and will need to be imposed in \textbf{FaSE-GLoBES}.
-Therefore, the restrictions in this model are $m_a>0$ and $r>0$.
 
@@
 
+We now take the tri-direct littlest seesaw (TDLS)~\cite{King:2013iva,King:2015dvf,King:2016yvg} as an example, and simulate the event spectra for DUNE and the MuOn-decay MEdium baseline NeuTrino beam experiment (MOMENT)~\cite{Cao:2014bea} by GLoBES.
+In this flavour model, the atmospheric and solar flavon vacuum alignments are $\langle\phi_{\text{atm}}\rangle\propto\left(1, \omega^2, \omega\right)^T$ and $\langle\phi_{\text{sol}}\rangle\propto\left(1, x, x\right)^T$,
+where $\omega$ stands for a cube root of unity and the parameter $x$ is real because of the imposed CP symmetry. Under this model, the light left-handed Majorana neutrino mass matrix is given by
+\begin{equation}
+\label{eq:mnu}  m_{\nu}=m_{a}\begin{pmatrix}
+ 1 &~ \omega  &~ \omega ^2 \\
+ \omega  &~ \omega ^2 &~ 1 \\
+ \omega ^2 &~ 1 &~ \omega  \\
+\end{pmatrix}+e^{i\eta}m_{s}
+\begin{pmatrix}
+ 1 &~  x &~  x \\
+ x &~ x^2 &~ x^2 \\
+ x &~ x^2 &~ x^2 \\
+\end{pmatrix}\,,
+\end{equation}
+where $x$, $\eta$, $m_a$, and the ratio $r\equiv m_s/m_a$ are four parameters and will be constrained by experimental data.
+And based on Eq.~(\ref{eq:mnu}), the relation between the model and oscillation parameters are predicted as Table.~\ref{tab:TD_parameters}.
+We note that from Eq.~(\ref{eq:mnu}), $m_1=0$ and the normal mass ordering are imposed, and will need to be imposed in \textbf{FaSE-GLoBES}.
+Therefore, the restrictions in this model are $m_a>0$ and $r>0$.
+
+In the following, all examples are presented for TDLS.
+However, we remind the user that though we use TDLS as an example, \textbf{FaSE-GLoBES} should not be limited in any flavour model.
+We therefore in the \textbf{FaSE} distribution,  show the warped flavour symmetry (WSF) for the other example, which will not be further introduced in this manual.
+
+\subsection{Setup for a model}\label{sec:ex_set_model}
+
+If the user prefers to assign the model with the mass matrix, the user will need to define the complex matrix \texttt{Mass\_Matrix} with Eq.~(\ref{eq:mnu}) in the function \texttt{MtoS}.
+The user can therefore assign the model as follows.
+
 \texttt{int MtoS(double OSC\_PARAMS[6],~double M\_para[])}\\
@@
 \texttt{\} }
+
+The user can also provide the relation between model and oscillation parameters Eq.~(\ref{eq:modelofOSC}), such as Table.~\ref{tab:TD_parameters}.
+The user, who prefers to do so, can assign a model as follows.
 
@@
 \subsection{Initialise the code}
-In the beginning of main code, we need to initialise \textbf{GLoBES} and \textbf{FaSE}, and to include the AEDL file for the MuOn-decay MEdium baseline NeuTrino beam experiment (MOMENT)~\cite{Cao:2014bea} as follows.\vspace{0.2cm}\\
+In the beginning of main code, we need to initialise \textbf{GLoBES} and \textbf{FaSE}, and to include the AEDL file for MOMENTas follows.\vspace{0.2cm}\\ 
 \texttt{glbInit(argv[0]);}\\
-\texttt{glbInitExperiment("expMOMENT\_FIX\_FLUX\_150KM\_addATM\_NC.glb",\&glb\_experiment\_list[0],}\\
+\texttt{glbInitExperiment("exp/MOMENT\_FIX\_FLUX\_150KM\_addATM\_NC.glb",\&glb\_experiment\_list[0],}\\
 \texttt{\&glb\_num\_of\_exps);}\\
@@
                                  NULL); }\vspace{0.2cm}\\                                 
-In the following we define the model-parameter values ($x$, $\eta$, $r$, and $m_a$), and set the true value in model parameters \texttt{true\_values} to simulated the true event spectrum.\vspace{0.2cm}\\
-\texttt{     float degree   = M\_PI/180;}\\
+In the following we define the model-parameter values ($x$, $\eta$, $r$, and $m_a$), and set the true value in model parameters \texttt{true\_values} to simulated the true event spectrum.
+Here we note that for setting up the true spectrum with model (oscillation) parameters, the user needs to make \texttt{PARA} equal to \texttt{MODEL} (\texttt{STAN}).\vspace{0.2cm}\\
+%\texttt{     float degree   = M\_PI/180;}\\
 \texttt{     float x\_true,eta\_true,r\_true,ma\_true;}\\
@@
 \texttt{glb\_params true\_values = glbAllocParams();}\\
-\texttt{glb\_params test\_values = glbAllocParams();}\\
-\texttt{glb\_params input\_errors  = glbAllocParams();}\\
-\texttt{glb\_params centers         = glbAllocParams();}\\
+%\texttt{glb\_params test\_values = glbAllocParams();}\\
+%\texttt{glb\_params input\_errors  = glbAllocParams();}\\
+%\texttt{glb\_params centers         = glbAllocParams();}\\
 \texttt{glbDefineParams(true\_values,x\_true,eta\_true,r\_true,ma\_true,0,0);}\\
 \texttt{    glbSetDensityParams(true\_values,1.0,GLB\_ALL);}\\
-\texttt{glbCopyParams(true\_values,test\_values);}\\
+%\texttt{glbCopyParams(true\_values,test\_values);}\\
 \texttt{PARA=MODEL;\\
@@
     glbSetRates();}\vspace{0.2cm}\\
-We then finally set up the projection.
+%We then finally set up the projection.
 The projection \texttt{free} allows all four parameters to be varied for finding the minimal value of $\chi^2$, which \texttt{project} is used for studying the constraint on $x$ and $\eta$.\vspace{0.2cm}\\
-\texttt{glb\_projection projection = glbAllocProjection();\\
-    glb\_projection free = glbAllocProjection();  \\
-     glbDefineProjection(free,GLB\_FREE,GLB\_FREE,GLB\_FREE,GLB\_FREE,GLB\_FIXED,GLB\_FIXED);\\
-    glbSetDensityProjectionFlag(free, GLB\_FREE, GLB\_ALL);\\
-glbDefineProjection(projection,GLB\_FIXED,GLB\_FIXED,GLB\_FREE,GLB\_FREE,GLB\_FIXED\\ ,GLB\_FIXED);\\    
-glbSetDensityProjectionFlag(projection, GLB\_FREE, GLB\_ALL);\\
-    }
+%\texttt{glb\_projection projection = glbAllocProjection();\\
+%    glb\_projection free = glbAllocProjection();  \\
+%     glbDefineProjection(free,GLB\_FREE,GLB\_FREE,GLB\_FREE,GLB\_FREE,GLB\_FIXED,GLB\_FIXED);\\
+%    glbSetDensityProjectionFlag(free, GLB\_FREE, GLB\_ALL);\\
+%glbDefineProjection(projection,GLB\_FIXED,GLB\_FIXED,GLB\_FREE,GLB\_FREE,GLB\_FIXED\\ ,GLB\_FIXED);\\    
+%glbSetDensityProjectionFlag(projection, GLB\_FREE, GLB\_ALL);\\
+%    }
 
-\subsection{Prior setup {\color{red}[updating]}}
+\subsection{Prior setup}
 
@@
 
-\subsection{Constraint of model parameters}
+\subsection{Constraint of model parameters}\label{sec:ex_MC}
 
@@
 \hspace{15mm}\includegraphics[width=0.5\textwidth]{figs/x_eta.pdf}
- \caption{\label{fig:x_eta}Precision measurements of any two model parameters in the framework of three neutrino oscillations taking uncertainties of the current global fit results, for MOMENT, at $1\sigma$ (gray), $2\sigma$ (orange), $3\sigma$ (black).
+% \caption{\label{fig:x_eta}Precision measurements of any two model parameters in the framework of three neutrino oscillations taking uncertainties of the current global fit results, for MOMENT, at $1\sigma$ (gray), $2\sigma$ (orange), $3\sigma$ (black).
 True values for the model parameters are used $(x,~\eta,~r,~M_a)=(-3.65,~1.13\pi,~0.511,~3.71~\text{meV})$.}
+   \caption{\label{fig:constraint}Examples for using \textbf{FaSE-GLoBES} to obtain the constraints of model parameters for tri-direct littlest seesaw, with simulated DUNE and MOMENT data.
+The result is assumed the normal ordering.
+And, the dot denotes the model prediction with with NuFit4.0 results.}
 \end{figure}
 
-The user can use \textbf{FaSE-GLoBES} to study the constraint of model parameters.
-The expression of $\chi^2$ is used as the default \textbf{GLoBES} setting.
-In more detail, the $\chi^2$ function is constructed based on a log-likelihood ratio,
-\begin{equation}\label{eq:chi-squared}
-\chi^2(\vec{\theta},\xi_s,\xi_b)=2\sum_i\left(\eta_i(\vec{\theta},\xi_s,\xi_b)-n_i+n_i\ln\frac{n_i}{\eta_i(\vec{\theta},\xi_s,\xi_b)} \right)+p(\xi_s,\sigma_s)+p(\xi_b,\sigma_b)+\chi^2_{prior},
-\end{equation}
-where $i$ runs over the number of bins, $\eta_i(\vec{\theta},\xi_s,\xi_b)$ is the hypothesis event rate for bin i and $E_i$ is the central bin energy.
-The vector $\vec{\theta}$ consists of tested model or oscillation parameters.
-The parameters $\xi_s$ and $\xi_b$ are introduced to account for the systematic uncertainty of normalisation for the signal (subscript $_s$) and background (subscript $_b$) components for the event rate, and are allowed to vary in the fit as nuisance parameters.
-For a given hypothesised set of parameters $\vec{\theta}$, the event rate for bin $i$ is calculated as\\
-\begin{equation}
-\eta_i(\vec{\theta},\xi_s,\xi_b)=(1+\xi_s)\times n_i+(1+\xi_b)\times b_i,
-\end{equation}
-where $n_i$ and $b_i$ are the expected number of signal and background events in bin $i$, respectively.
-The nuisance parameters are constrained by the Gaussian prior $p(\xi,\sigma)=\xi^2/\sigma^2$ with corresponding uncertainties $\sigma_s$ and $\sigma_b$ for the signal and background, respectively.
-Finally, $\chi^2_{prior}$ is a set of Gaussian priors for hypothesis, and is expressed as Eq.~\ref{eq:prior}.
-After doing all minimisations, the user obtain the $\chi^2$ value for a specific hypothesis $\vec{\theta}^{hyp}$, $\chi^2(\vec{\theta}^{hyp})$.
-
-The user of \textbf{FaSE-GLoBES} is able to study how model parameters can be constrained by the simulated experiment.
-To do so, the user needs to define the true event spectrum $n_i$ with a set of model ($\vec{\theta}_{Model}^{true}$) or oscillation parameters ($\vec{\theta}_{OSC}^{true}$), \textit{i.e.}~set up $n_i(\vec{\theta}_{Model}^{true})$ or $n_i(\vec{\theta}_{OSC}^{true})$.
-The hypothesis $\vec{\theta}_{Model}^{hyp}$ predicts the tested event spectrum $\eta_i(\vec{\theta}_{Model}^{hyp},\xi_s,\xi_b)$.
-With the default setting for $\chi^2$ function Eq.~\ref{eq:prior}, from \textbf{FaSE-GLoBES} the user computes the statistical quantity,
-\begin{equation}\label{eq:chi_model}
-\chi^2(\vec{\theta}_{Model}^{hyp}),~~\text{with}~n_i(\vec{\theta}_{Model}^{true})~\text{or}~n_i(\vec{\theta}_{OSC}^{true}).
-\end{equation}
-%
-We note that the minimum of $\chi^2$ in the whole parameter space ($\chi^2_{min.}$) may not be $0$.
-Therefore, to study the precision of model parameters, the user should use the value $\Delta\chi^2(\vec{\theta}_{Model}^{hyp})\equiv \chi^2(\vec{\theta}_{Model}^{hyp})-\chi^2_{min.}$, instead of $\chi^2$ itself.
-By varying different hypothesis $\vec{\theta}_{Model}^{hyp}$, the user can obtain the allowed region of model parameters with the statistical quantity $\Delta\chi^2(\vec{\theta}_{Model}^{hyp})$.
-
-We take TDLS as an example model, to see how the model parameter can be constrained by MOMENT experiment, assuming the true model values $x=-3.65$, $\eta=1.13\pi$, $r=0.511$, and $m_a=3.71$~meV.
-To get the constraint of $x$ and $\eta$, we need to comput the minimum of $\chi^2$ value as the following script in the main code.\vspace{0.2cm}\\
+We show an example for how the model parameter can be constrained by MOMENT experiment, assuming the true model values $x=-3.65$, $\eta=1.13\pi$, $r=0.511$, and $m_a=3.71$~meV.
+To get the constraint of $x$ and $\eta$, we need to compute the minimum of $\chi^2$ value as the following script in the main code.\vspace{0.2cm}\\
 \texttt{
@@
 %
-The \textbf{GLoBES} projector \texttt{free} allows all model parameters to vary, in order to find the value of \texttt{res0}, $\chi^2_{min}$.
-Then, we set two loops varying different values of $x$ and $\eta$ in $\vec{\theta}^{hyp}_{Model}$ to get $\Delta \chi^2$ values for different hypotheses.\vspace{0.2cm}\\
+The \textbf{GLoBES} projector \texttt{free} allows all model parameters to vary, in order to find the value of \texttt{res0}, which is for $\chi^2_{min}$.
+Then, we set two loops varying different values of $x$ and $\eta$ in $\vec{\theta}^{hyp}_{Model}$ to get $\Delta \chi^2$ values for different hypotheses.
+We note here there is degenerate solutions where $x\sim-8$, $\eta\sim1.8\pi$, $r\sim 0.1$, and $m_a\sim3.8$~meV.
+To find this degenerate solutions we set the entry with $r=0$.\vspace{0.2cm}\\
 %
@@
      glbSetOscParams(test\_values,x,0); glbSetOscParams(test\_values,eta,1);\\
+                glbSetOscParams(test\_values,r\_true,2);\\
         float res=glbChiNP(test\_values,NULL,GLB\_ALL);\\
+        glbSetOscParams(test\_values,0.,2);\\
+        float res2=glbChiNP(test\_values,NULL,GLB\_ALL);\\
+        if(res2<res) \{res=res2;\}\\
             fprintf(File,"\%f \%f  \%f $\backslash$n",x,eta/M\_PI,res-res0);\\
@@
 
-\subsection{Model testing}
+\subsection{Model testing}\label{sec:ex_MT}
 
-The user can also study how well a flavour symmetry model explains the computed data as predicting how the simulated experiment can exclude this model.
-In the other word, the user studies the minimum of $\chi^2$ for the flavour symmetry model $\vec{\theta}_{Model}$ as a hypothesis, assuming different true oscillation values, \textit{i.e.}~different $\vec{\theta}^{true}_{OSC}$.
-To do so, we compute the same statistical quantity Eq.~\ref{eq:chi_model}, while the true spectrum is varied with different true values $\vec{\theta}_{OSC}^{true}$.
-All model parameters are allowed to be varied with the user-defined prior.
-%
-Finally, the user needs to adopt Wilk's theorem \cite{Wilks:1938dza}.
-When comparing nested models, the $\Delta \chi^2$ test statistics is a random variable asymptotically distributed according to the $\chi^2$-distribution with the number of degrees of freedom, which is equal to the difference in the number of free model parameters \texttt{dof}.
+%\begin{figure}[!h]
+ %\centering
+%\includegraphics[width=0.5\textwidth]{figs/SR_th23_dCP.pdf}
+%\caption{\label{fig:th23_delta}The 2-D exclusion contour for tri-direct littlest seesaw model on the plane of two true standard parameters $\theta_{23}$ and $\delta$, from $1\sigma$ to $5\sigma$.
+The range for each parameter is taken according to the $3\sigma$ uncertainty in NuFit4.0 results.
+The black dot denotes the best fit of NuFit4.0 results ($(\theta_{12},~\theta_{13},~\theta_{23},~\delta,~\Delta m_{21}^2,~\Delta m_{31}^2)=(33.82^\circ,~8.61^\circ,~49.6^\circ,~215^\circ,~7.39\times10^{-5}~\text{eV}^2,~2.525\times10^{-3}~\text{eV}^2)$), while the star is the prediction by the tri-direct littlest seesaw model with NuFit4.0 results ($(\theta_{12},~\theta_{13},~\theta_{23},~\delta,~\Delta m_{21}^2,~\Delta m_{31}^2)\sim(36.25^\circ,~8.63^\circ,~47^\circ,~279^\circ,~7.39\times10^{-5}~\text{eV}^2,~2.525\times10^{-3}~\text{eV}^2)$).}
+%\end{figure}
 
@@
  \centering
-\includegraphics[width=0.5\textwidth]{figs/SR_th23_dCP.pdf}
-\caption{\label{fig:th23_delta}The 2-D exclusion contour for tri-direct littlest seesaw model on the plane of two true standard parameters $\theta_{23}$ and $\delta$, from $1\sigma$ to $5\sigma$.
+\includegraphics[width=0.48\textwidth]{Figs/SR_th23_dCP_DUNE_MOMENT.pdf}
+\caption{\label{fig:th23_delta}Examples for using \textbf{FaSE-GLoBES} to obtain the 2-D exclusion contour at $99\%$ C.L.
+on the plane of true values of $\theta_{23}$ and $\delta$ for sub-models of TDLS with DUNE and MOMENT.
+The result is assumed the normal ordering.
+And, the dot (star) denotes the model prediction with NuFit4.0 results (best fit of NuFit4.0).}
+%\caption{\label{fig:th23_delta}The 2-D exclusion contour for sub-models of tri-direct littlest seesaw on the plane of two true standard parameters $\theta_{23}$ and $\delta$, from $1\sigma$ to $5\sigma$, for DUNE (dotted) and MOMENT (solid).
 The range for each parameter is taken according to the $3\sigma$ uncertainty in NuFit4.0 results.
@@
 %We can also study on excluding the model, assuming different true values for oscillation parameters. 
-As an example, we present testing TDLS, assuming various true values of $\theta_{23}$ and $\delta$.
-The code for this example is provided as \textbf{th23\_delta.c}.
-in the \textbf{FaSE} distribution We change values of $\theta_{23}$ and $\delta$ of the true theory, and compute the minimal $\chi^2$ value for the tested model with all four model parameters, allowed to vary with priors.
-And, the studied statistics function is exactly Eq.~\ref{eq:chi-squared}, but the true event rate $n_i$ is predicted by a set of oscillation parameters, which will be varied in the code.
-And all four model parameter can be varied with the prior given by Eq.~\ref{eq:prior}.
+The user can also study how well a flavour symmetry model explains the computed data as predicting how the simulated experiment can exclude this model.
+As an example, we present testing sub-models of TDLS, assuming various true values of $\theta_{23}$ and $\delta$.
+The code for this example is provided as \textbf{th23\_delta.c} in the \textbf{FaSE} distribution.
+We compute the minimal $\chi^2$ value for the model with $r$ and $m_a$, varied with the prior in Eq.~(\ref{eq:prior}) according to NuFit4.0 results.
+Two parameters $x$ and $\eta$ are fixed at the best fit.
+The studied statistics function is exactly Eq.~(\ref{eq:chi-squared}), but the true event rate $n_i$ is predicted by a set of oscillation parameters, which will be varied in the code.
+And all four model parameter can be varied with the prior given by Eq.~(\ref{eq:prior}).
 %
 Except for $\theta_{23}$ and $\delta$, which are varied between $40^\circ<\theta_{23}<52^\circ$ and $125^\circ<\delta<392^\circ$, we fix the other oscillation parameters at $\theta_{12}=36.25^\circ$, $\theta_{13}=8.63^\circ$, $\Delta m_{21}^2=7.39\times 10^{-5}$~eV$^2$ and $2.525\times10^{-3}$~eV$^2$ predicted by the model $x=-3.65$, $\eta=1.13\pi$, $r=0.511$, and $m_a=3.71$~meV.
-
-The example code is presented as follows.\vspace{0.2cm}\\
-\texttt{ \{ ...  initalize the code ...\}\\
-\{ ...  register the probability engine ...\}    }\vspace{0.2cm}\\
-\texttt{    
-    float degree   = M\_PI/180;\\
-    float x\_true,eta\_true,r\_true,ma\_true;\\
-    x\_true=-3.65029; eta\_true=1.13067*M\_PI; r\_true=0.511325; ma\_true=3.71199e-3;\\
-    double M\_para[4],OSC\_para[6];\\
-    M\_para[0]=x\_true; M\_para[1]=eta\_true; M\_para[2]=r\_true; M\_para[3]=ma\_true;\\
-    MtoS(OSC\_para, M\_para);\\
-    double th12\_true=OSC\_para[0];\\
-    double th13\_true=OSC\_para[1];\\
-    double th23\_true=OSC\_para[2];\\
-    double dCP\_true=OSC\_para[3];\\
-    double DM21\_true=OSC\_para[4];\\
-    double DM31\_true=OSC\_para[5];\\
-    glb\_params true\_values = glbAllocParams();\\
-    glb\_params test\_values = glbAllocParams();\\
-    glb\_params input\_errors = glbAllocParams();\\
-    glb\_params centers = glbAllocParams();\\
-    \\
-    glbDefineParams(test\_values,x\_true,eta\_true,r\_true,ma\_true,0,0);\\
-    glbSetDensityParams(test\_values,1.0,GLB\_ALL);\\
-    glbDefineParams(true\_values,th12\_true,th13\_true,th23\_true,dCP\_true,\\
-    DM21\_true,DM31\_true);\\
-    glbSetDensityParams(true\_values,1.0,GLB\_ALL); }\vspace{0.2cm}\\
-\texttt{ \{ ...  set up for prior ...\}}\vspace{0.2cm}\\
+Finally, in the code we adopt Wilk's theorem \cite{Wilks:1938dza}: texttt{gsl\_cdf\_chisq\_Qinv(gsl\_cdf\_chisq\_Q(fabs(res),dof),1)}.\vspace{0.2cm}\\
+%
+%
+%The example code is presented as follows.\vspace{0.2cm}\\
+%\texttt{ \{ ...  initalize the code ...\}\\
+%\{ ...  register the probability engine ...\}    }\vspace{0.2cm}\\
+%\texttt{    
+%    float degree   = M\_PI/180;\\
+%    float x\_true,eta\_true,r\_true,ma\_true;\\
+%    x\_true=-3.65029; eta\_true=1.13067*M\_PI; r\_true=0.511325; ma\_true=3.71199e-3;\\
+%    double M\_para[4],OSC\_para[6];\\
+%    M\_para[0]=x\_true; M\_para[1]=eta\_true; M\_para[2]=r\_true; M\_para[3]=ma\_true;\\
+%    MtoS(OSC\_para, M\_para);\\
+%    double th12\_true=OSC\_para[0];\\
+%    double th13\_true=OSC\_para[1];\\
+%    double th23\_true=OSC\_para[2];\\
+%    double dCP\_true=OSC\_para[3];\\
+%    double DM21\_true=OSC\_para[4];\\
+%    double DM31\_true=OSC\_para[5];\\
+%    glb\_params true\_values = glbAllocParams();\\
+%    glb\_params test\_values = glbAllocParams();\\
+%    glb\_params input\_errors = glbAllocParams();\\
+%    glb\_params centers = glbAllocParams();\\
+%    \\
+%    glbDefineParams(test\_values,x\_true,eta\_true,r\_true,ma\_true,0,0);\\
+%    glbSetDensityParams(test\_values,1.0,GLB\_ALL);\\
+%    glbDefineParams(true\_values,th12\_true,th13\_true,th23\_true,dCP\_true,\\
+%    DM21\_true,DM31\_true);\\
+%    glbSetDensityParams(true\_values,1.0,GLB\_ALL); }\vspace{0.2cm}\\
+%\texttt{ \{ ...  set up for prior ...\}}\vspace{0.2cm}\\
 \texttt{
@@
 }\vspace{0.2cm}\\
-\texttt{ \{ ...  destroy the pointer ...\}}\vspace{0.2cm}\\
-Finally, in the code we adopt Wilk's theorem \cite{Wilks:1938dza}. Here the number \texttt{dof} is $2$. And that is our output: \texttt{gsl\_cdf\_chisq\_Qinv(gsl\_cdf\_chisq\_Q(fabs(res),dof),1)}.
-
+%\texttt{ \{ ...  destroy the pointer ...\}}\vspace{0.2cm}\\
+%
 %\begin{figure}[!h]
@@
 %\end{figure}
-
 The output \texttt{data/ModelTest\_th23\_dCP\_test.dat} contains true values of $\theta_{23}$ (the first column) and $\delta$ (the second column) with $\chi^2_{min}$ for TDLS (the third column).
@@
 
-\section{Summary and conclusions}
-
+\section{Summary and conclusions }
+{\color{red}[updating]} 
 We have presented \textbf{FaSE}, which is a supplemental simulation tool for \textbf{GLoBES} to study the leptonic flavour symmetry with neutrino oscillation experiments in a user-friendly way.
@@
 %\bibliographystyle{JHEP}
-\bibliographystyle{plain}
 \bibliography{FAS-GLoBES.bib}

### 2020-05-26 doc/paper.tex
update manual
update code and paper

@@
 
-To translate from $\vec{\theta}_{Model}$ to $\vec{\theta}_{OSC}$, the user can assign the correlation between the standard oscillation and model parameter sets, or define the mass matrix in model parameters, which will be diagonalised by the function \texttt{STAN\_OSC} to obtain the corresponding oscillation-parameter values.
+{\color{blue}There are three methods to translate from $\vec{\theta}_{Model}$ to $\vec{\theta}_{OSC}$ in \textbf{FaSE-GLoBES}:} the user can assign the correlation between the standard oscillation and model parameter sets{\color{blue}, give the mixing matrix in model parameter $U$}, or define the mass matrix in model parameters, which will be diagonalised by the function \texttt{STAN\_OSC} to obtain the corresponding oscillation-parameter values.
 %The relation between the oscillation and model parameter sets can be derived out by the user, 
 In the way of directly giving the relation between oscillation and model parameter sets, the user needs to provide
-$\vec{\theta}_{Model}=\vec{f}(\vec{\theta}_{OSC})$ in the function \texttt{MtoS}.
+{\color{blue}
+\begin{equation}
+\vec{\theta}_{Model}=\vec{f}(\vec{\theta}_{OSC}), 
+\end{equation}
+in the function \texttt{MtoS}.}
 %
+
+{\color{blue}When the user give the mixing matrix $U$ in model parameters, the corresponding mixing angles can be obtained easily through,
+\begin{eqnarray}\label{eq:U_angle}
+\tan\theta_{12}=\left|\frac{U_{e2}}{U_{e1}}\right|,& \tan\theta_{23} = \left|\frac{U_{\mu 3}}{U_{\tau 3}}\right|,&  \sin\theta_{13}=|U_{e3}|.
+\end{eqnarray}
+After getting these mixing angles, we can easily get the Dirac CP phase $\delta$ with Jarlskog invariant $J_{CP}$,\
+\begin{equation}\label{eq:U_phase}
+J_{CP}=c_{12}s_{12}c_{23}s_{23}c_{13}^2s_{13}\sin\delta,
+\end{equation}
+where $c_{ij}$ and $s_{ij}$ are $\cos \theta_{ij}$ and $\sin\theta_{ij}$, respectively.
+In \texttt{MtoS}, the user can pass the mixing matrix $U$ to the function  \texttt{STAN\_OSC\_U}, and can obtain the corresponding mixing matrix and the CP phase.
+}
 
@@
 The matrix $\mathcal{M}$ is given by the user with model parameters $\vec{\theta}_{Model}$.
-The matrix $U$ is the neutrino mixing matrix, and can be used to get mixing angles and the CP phase.
+The mixing matrix $U$ can be used to get mixing angles and the CP phase, as Eqs.
+(\ref{eq:U_angle}) and (\ref{eq:U_phase}).
 The difference between any two diagonal elements of $\textbf{M}$ ($\textbf{M}_{ii}-\textbf{M}_{jj}=m_i^2-m_j^2$) is the mass-squared difference ($\Delta m_{ij}^2$).
@@
 \section{The definition for $\chi^2$ (based on \textbf{GLoBES})}\label{sec:chi-squared}
-% {\color{red}CAN BE REMOVED}
 

### 2020-05-26 FASE_GLoBES.c

@@ -84,8 +84,6 @@ int STAN_OSC(double complex M[], double out[6])
     cblas_zgemm (CblasRowMajor, CblasConjTrans, CblasNoTrans, 3, 3, 3, &alpha, M, 3, M, 3, &beta, MMsquare, 3); //eq 4.5 page 107 Giunti
     
     
-    
-    
     gsl_matrix_complex *MM = gsl_matrix_complex_alloc(3, 3);
     int i,j;
     for(i=0;i<3;i++)
@@ -144,32 +142,25 @@ int STAN_OSC(double complex M[], double out[6])
 }
 
 
-
-int ModelTO( double OSC_PARAMS[6],double M_para[])
+int STAN_OSC_U(double complex U[], double out[4])
 {
     
+    double s13 = cabs(U[2]);       double the13=asin(s13);
+    double t12 = cabs(U[1])/cabs(U[0]);           double the12=atan(t12);
+    double t23 = cabs(U[5])/cabs(U[8]);           double the23=atan(t23);
     
-    //for the 2 heavy sterile case keep these zero.
-    double alpha = 0.0;
-    double mc = 0.0;
-    double gamma = 0.0;
+    double s12=sin(the12);
+    double c12=cos(the12);
+    double s23=sin(the23);
+    double c13=cos(the13);
+    double dCP=carg(U[1]*conj(U[2])*conj(U[4])*U[5]+s12*s12*s13*s13*c13*c13*s23*s23);
     
-    
-    
-    double x=M_para[0];
-    double eta=M_para[1];
-    double r=M_para[2];
-    double ma=M_para[3];
-    
-    double ms=ma*r;
-    
[…]

### 2020-05-26 FASE_GLoBES.h

@@ -53,9 +53,8 @@ int    PARA,PARA_in,ran,ran_in,n_ram,FIT,PRIOR;
 double x_in,eta_in,r_in,ma_in;
 
 double UPPER_prior[6],LOWER_prior[6],Central_prior[6];
-
 int STAN_OSC(double complex M[], double output[6]);
-int ModelTO( double OSC_PARAMS[6],double M_para[]);
+int STAN_OSC_U(double complex U[], double out[6]);
 inline double square(double x);
 int sinsq(double complex U[], double * a);
 int glb_free_probability_engine();

### 2020-05-26 doc/paper.tex
update docs

@@
 We present a supplemental tool \textbf{F}l\textbf{a}vour \textbf{S}ymmetry \textbf{E}mbedded (\textbf{FaSE}) for \textbf{G}eneral \textbf{Lo}ng \textbf{B}aseline \textbf{E}xperiment \textbf{S}imulator (\textbf{GLoBES}).
-It can translate the neutrino mass model inputs to standard neutrino oscillation parameters, and offers prior functions in a user-friendly way.
+It can translate the neutrino mass model {\color{blue}parameters} to standard neutrino oscillation parameters, and offers prior functions in a user-friendly way.
 We demonstrate the robustness of \textbf{FaSE-GLoBE} with two examples on how the model parameters can be constrained and even whether the model is excluded by an experiment or not.
 We wish that this toolkit will facilitate the study of new neutrino mass models in an effecient and effective manner.\\
-\textbf{Keywords: Neutrino Oscillations, Leptonic Flavour Symmetry}  
+\textbf{Keywords:} Neutrino Oscillations, Leptonic Flavour Symmetry 
 \end{abstract}
@@
 These models can explain the origin of the neutrino mixing, and predict correlations of oscillation parameters (some of recent review articles are~\cite{Altarelli:2010gt,Ishimori:2010au,King:2013eh,King:2014nza,King:2015aea,King:2015ata,King:2017guk}).
-Before the discovery of non-zero $\theta_{13}$ by Daya Bay reactor neutrino experiment~\cite{An:2013zwz}, the `tri-bi-maximal' neutrino mixing (TBM) ansatz, which was proposed in 2002 by Horrison, Perkins, and Scott~\cite{Harrison:2002er}, was in line with experimental data:
+Before the discovery of non-zero $\theta_{13}$ by Daya Bay reactor neutrino experiment~\cite{An:2013zwz}, the `tri-bi-maximal' neutrino mixing (TBM) ansatz, which was proposed in 2002 by Horrison, Perkins, and Scott~\cite{Harrison:2002er,Xing:2002sw}, was in line with experimental data:
 \begin{equation*}
@@
 We take \textit{the tri-direct littlest seesaw} (TDLS)~\cite{King:2013iva,King:2015dvf,King:2016yvg} as an example.
-In this model, the light left-handed Majorana neutrino mass matrix is given by
+In this model, the light left-handed Majorana neutrino mass matrix {\color{blue}in the flavor basis} is given by
 \begin{equation}
@@
 %We input the model by giving model parameters as functions of standard oscillation parameters Eq.~(\ref{eq:modelofOSC}). 
-Parameters $r$ and $ma$ are varied with the prior that is given in standard oscillation parameters, according to the global-fit result NuFit4.0. 
+Parameters $r$ and $m_a$ are varied with the prior that is given in standard oscillation parameters, according to the global-fit result NuFit4.0. 
 %The code for this example is provided as \textbf{x\_eta.c} in the \textbf{FaSE} distribution.
@@
 \acknowledgements{
+{\color{blue}We thank Gui-Jun Ding and Ye-Ling Zhou for helpful discussions.}
 This work was supported in part by Guangdong Basic and Applied Basic Research Foundation under Grant No.

### 2020-05-26 doc/paper.tex
update docs
update tex

@@
 \end{equation}
-in the function \texttt{MtoS}.}
+in the function \texttt{MtoS}. }
 %
 
-{\color{blue}When the user give the mixing matrix $U$ in model parameters, the corresponding mixing angles can be obtained easily through,
+{\color{blue}When the user give the mixing matrix $U$ in model parameters, the corresponding mixing angles can be obtained through relations,
 \begin{eqnarray}\label{eq:U_angle}
-\tan\theta_{12}=\left|\frac{U_{e2}}{U_{e1}}\right|,& \tan\theta_{23} = \left|\frac{U_{\mu 3}}{U_{\tau 3}}\right|,&  \sin\theta_{13}=|U_{e3}|.
+\tan\theta_{12}=\left|\frac{U_{e2}}{U_{e1}}\right|,&  \sin\theta_{13}=|U_{e3}|,& \tan\theta_{23} = \left|\frac{U_{\mu 3}}{U_{\tau 3}}\right|.
 \end{eqnarray}
-After getting these mixing angles, we can easily get the Dirac CP phase $\delta$ with Jarlskog invariant $J_{CP}$,\
+After getting these mixing angles, we can easily get the Dirac CP phase $\delta$ with the Jarlskog invariant $J_{CP}$,\
 \begin{equation}\label{eq:U_phase}
@@
 This diagnolisation in Eq.~(\ref{eq:MM}) can be done by the function \texttt{STAN\_OSC}, which needs to be called in \texttt{MtoS} with outputs of the vector $\vec{\theta}_{OSC}$.
+{\color{blue}We note that with non-diagonal mass matrix for charged leptons, this translation method is not suggested.}
 

### 2020-05-26 doc/paper.tex
update docs

@@
 
-{\color{blue}There are three methods to translate from $\vec{\theta}_{Model}$ to $\vec{\theta}_{OSC}$ in \textbf{FaSE-GLoBES}:} the user can assign the correlation between the standard oscillation and model parameter sets{\color{blue}, give the mixing matrix in model parameter $U$}, or define the mass matrix in model parameters, which will be diagonalised by the function \texttt{STAN\_OSC} to obtain the corresponding oscillation-parameter values.
+{\color{blue}There are three methods to translate from $\vec{\theta}_{Model}$ to $\vec{\theta}_{OSC}$ in \textbf{FaSE-GLoBES}:} 1).~the user can assign the correlation between the standard oscillation and model parameter sets{\color{blue}, 2).~give the mixing matrix in model parameter $U$}, or 3).~define the mass matrix in model parameters.
 %The relation between the oscillation and model parameter sets can be derived out by the user, 

### 2020-05-27 doc/paper.tex
upload the working note
update manucript

@@
 
-It is clear that neutrinos carry the peculiar mass smaller than $\mathcal{O}(1)$ eV among elementary particles, although the absolute value of each neutrino mass is unknown.
-In addition, one of the fundamental questions with regards to neutrino properties is how neutrino masses are generated naturally.
+{\color{blue}
+The mass of neutrinos is still a mystery in particle physics.  
+Though the last cosmological result shows the smallness of neutrino mass $\sum m_\nu<0.12$~eV~\cite{Aghanim:2018eyx}, the mass of each neutrinos is not clear.
+In addition, the true theory that explains the origin of neutrino mass is waiting to be determined. 
+%It is clear that neutrinos carry the peculiar mass smaller than $\mathcal{O}(1)$ eV among elementary particles, although the absolute value of each neutrino mass is unknown. 
+%In addition, one of the fundamental questions with regards to neutrino properties is how neutrino masses are generated naturally. 
 %The seesaw mechanism has been used to explain such a tiny mass in the neutrino sector with the help of neutrino flavor mixings. 
-The seesaw mechanism has been used to explain such a tiny mass in the neutrino sector. 
+One of these models, the seesaw mechanism has been used to explain such a tiny mass in the neutrino sector.}
 %Anyhow new particles have to be introduced in such a mechanism. 
-More degrees of freedom in a theoretical model, the less predictivity of observables in experiments.
+%More degrees of freedom in a theoretical model, the less predictivity of observables in experiments. 
 Furthermore, flavour symmetries are employed to reduce degrees of freedom in the neutrino mass model.
 These models can explain the origin of the neutrino mixing, and predict correlations of oscillation parameters (some of recent review articles are~\cite{Altarelli:2010gt,Ishimori:2010au,King:2013eh,King:2014nza,King:2015aea,King:2015ata,King:2017guk}).
-Before the discovery of non-zero $\theta_{13}$ by Daya Bay reactor neutrino experiment~\cite{An:2013zwz}, the `tri-bi-maximal' neutrino mixing (TBM) ansatz, which was proposed in 2002 by Horrison, Perkins, and Scott~\cite{Harrison:2002er,Xing:2002sw}, was in line with experimental data:
-\begin{equation*}
-U_{\text{TBM}}=\left(
-\begin{array}{ccc}
-2/\sqrt{6} & 1/\sqrt{3} & 0\\
--1/\sqrt{6} & 1/\sqrt{3} & 1/\sqrt{2}\\
-1/\sqrt{6}  & -1/\sqrt{3} & 1/\sqrt{2}
-\end{array}\right).
-\end{equation*} 
-Given $\theta_{13}\approx 8^\circ$ measured by several reactor neutrino experiments, we have to break this mixing pattern to to obtain such non-zero value of $\theta_{13}$.
-One of popular proposals is to correct the tri-bi-maximal neutrino mixing such that
-\begin{equation*}
-\sin\theta_{12}=(1+s)/\sqrt{3},~\sin\theta_{13}=r/\sqrt{2},~\text{and}~\sin\theta_{23}=(1+a)/\sqrt{2}.
-\end{equation*}
+{\color{blue}
+Several neutrino mixing patterns have been proposed, such as tribimaximal (TB)~\cite{Harrison:2002er,Xing:2002sw}, bimaximal (BM)~\cite{Fukugita:1998vn,Barger:1998ta,Davidson:1998bi}, and golden ratio (GR)~\cite{Datta:2003qg,Everett:2008et,Feruglio:2011qq} mixings.
+After the measurement of non-zero $\theta_{13}$, which excludes TB, BM, GR mixings, the surviving extension of TB mixing is mainly discussed~\cite{Harrison:2002er,King:2007pr,Pakvasa:2007zj}.
+%\begin{equation*}
+%\sin\theta_{12}=(1+s)/\sqrt{3},~\sin\theta_{13}=r/\sqrt{2},~\text{and}~\sin\theta_{23}=(1+a)/\sqrt{2}.
+%\end{equation*}
+%As some well-known models, such as non-Abelian discrete symmetries $A_4$ and $S_4$, can realise the TB mixing, the high-energy symmetry $G_f$ contains these symmetries.
+To explain the Dirac CP phase in the neutrino sector, $G_f$ is together with a non-commuting CP $H_{CP}$.
+The high energy symmetry $G_f$ is slightly broken in the lower energy. As a consequence, the mixing pattern is realised, and the size of CP phase $\delta$ is predicted. 
+As some well-known models such as $A_4$ and $S_4$ can realise the TB mixing, $G_f$ contains at least one of these symmetries.
+There are several approaches for the breaking from the high energy: direct~(\textit{e.g.}~Ref.~\cite{King:2013eh}), indirect~(\textit{e.g.}~Ref.~\cite{King:2013eh}), semi-direct(\textit{e.g.}~Ref.~\cite{Holthausen:2012dk,Feruglio:2012cw,Feruglio:2013hia,Ding:2013hpa,Ding:2013bpa}), tri-direct~(\textit{e.g.}~Ref.~\cite{Ding:2018fyz,Ding:2018tuj}) models.
+All of they can explain the current data well.
+Moreover, there are also different theories for the origin of the symmetry $G_f$ as well: continuous non-Abelian gauge theories \textit{such as} $SO(3)$ (\textit{e.g.}~Ref.~\cite{King:2005bj}) or $SU(3)$ (\textit{e.g.}~Ref.~\cite{King:2001uz,King:2003rf}), and the discrete symmetry from extra dimensions (\textit{e.g.}~Ref.~\cite{Feruglio:2017spp,Criado:2018thu,Penedo:2018nmg}).
+%
+We do not discuss each of these models, but we recommend the users, who are not familiar with these models, to visit these references.
+ }
+
 It is relatively easy for model builders to check the validity of the neutrino mass model and constrain model parameters by the public NuFit results \cite{Esteban:2018azc}.

### 2020-05-27 doc/paper.tex
update paper manuscript

@@
 To explain the Dirac CP phase in the neutrino sector, $G_f$ is together with a non-commuting CP $H_{CP}$.
-The high energy symmetry $G_f$ is slightly broken in the lower energy. As a consequence, the mixing pattern is realised, and the size of CP phase $\delta$ is predicted. 
+While the high energy symmetry $G_f$ is slightly broken in the lower energy, the mixing pattern is realised, and the size of CP phase $\delta$ is predicted. 
 As some well-known models such as $A_4$ and $S_4$ can realise the TB mixing, $G_f$ contains at least one of these symmetries.
 There are several approaches for the breaking from the high energy: direct~(\textit{e.g.}~Ref.~\cite{King:2013eh}), indirect~(\textit{e.g.}~Ref.~\cite{King:2013eh}), semi-direct(\textit{e.g.}~Ref.~\cite{Holthausen:2012dk,Feruglio:2012cw,Feruglio:2013hia,Ding:2013hpa,Ding:2013bpa}), tri-direct~(\textit{e.g.}~Ref.~\cite{Ding:2018fyz,Ding:2018tuj}) models.
-All of they can explain the current data well.
-Moreover, there are also different theories for the origin of the symmetry $G_f$ as well: continuous non-Abelian gauge theories \textit{such as} $SO(3)$ (\textit{e.g.}~Ref.~\cite{King:2005bj}) or $SU(3)$ (\textit{e.g.}~Ref.~\cite{King:2001uz,King:2003rf}), and the discrete symmetry from extra dimensions (\textit{e.g.}~Ref.~\cite{Feruglio:2017spp,Criado:2018thu,Penedo:2018nmg}).
+All of they can explain the current data well, and predict the size of $\delta$, which will be measured with the high precision.
+Moreover, there are also different theories explaining the origin of the symmetry $G_f$ as well: continuous non-Abelian gauge theories \textit{such as} $SO(3)$ (\textit{e.g.}~Ref.~\cite{King:2005bj}) or $SU(3)$ (\textit{e.g.}~Ref.~\cite{King:2001uz,King:2003rf}), and the discrete symmetry from extra dimensions (\textit{e.g.}~Ref.~\cite{Feruglio:2017spp,Criado:2018thu,Penedo:2018nmg}).
 %
-We do not discuss each of these models, but we recommend the users, who are not familiar with these models, to visit these references.
+Though we do not discuss each of these models in detail, we still recommend the users, who are not familiar with these models, to visit these references.
  }

### 2020-05-29 doc/paper.tex
update docs

@@
 
+\begin{table}[h!]
+\caption{\label{tab:exp}Summary of available AEDL files for some of most-discussed experiments.}
+\centering
+\begin{tabular}{l|c|r}
+exp.   & source & ref. \\\hline\hline
+T2K    &     T2K.glb on \cite{GLoBES}  &    \cite{Huber:2002mx}  \\
+NOvA   &     NOvA.glb on \cite{GLoBES}   &   \cite{Ambats:2004js}   \\
+T2HK   & sys-T2HK.glb on \cite{GLoBES}  &   \cite{Huber:2007xx}   \\
+DUNE   &    \cite{Alion:2016uaj}    &  \cite{Alion:2016uaj}    \\
+MOMENT &   on FaSE website    &     \cite{Cao:2014bea}
+\end{tabular}
+\end{table}
+
 It is relatively easy for model builders to check the validity of the neutrino mass model and constrain model parameters by the public NuFit results \cite{Esteban:2018azc}.
@@
 \textbf{G}eneral \textbf{Lo}ng \textbf{B}aseline \textbf{E}xperiment \textbf{S}imulator (\textbf{GLoBES}) \cite{Huber:2004ka,Huber:2007ji} is a convenient tool to simulate neutrino oscillation experiments via the Abstract Experiment Definition Language (AEDL) as one of the most popular and powerful tools in the community of neutrino oscillation physics.
-Some AEDL files to describe experiments are also available in \textbf{GLoBES} website, while the working group in the DUNE experiment also releases their neutrino flux information and detector descriptions in a AEDL file, provided in~\cite{Alion:2016uaj}.
-It is to be extended for the purpose of analysing flavour symmetry models in an universal way.
+Some AEDL files to describe experiments are also available in \textbf{GLoBES} website~\cite{GLoBES}, while the working group in the DUNE experiment also releases their neutrino flux information and detector descriptions in a AEDL file, provided in~\cite{Alion:2016uaj}.
+{\color{blue}We summarise AEDL files for some of most-discussed experiments in Table.~\ref{tab:exp}, including their source and reference.} It is to be extended for the purpose of analysing flavour symmetry models in an universal way.
 

### 2020-05-29 doc/paper.tex
update tex

@@
 
-\textbf{FaSE-GLoBES} is written in the \texttt{c} language, and consists of two source codes \textbf{FASE\_GLoBES.c} and \textbf{model-input.c}.
+\textbf{FaSE} is written in the \texttt{c} language, and consists of two source codes \textbf{FASE\_GLoBES.c} and \textbf{model-input.c}.
 About these two \texttt{c}-codes, the user defines the correlations between model inputs and standard neutrino mixing parameters in \textbf{model-input.c}, while \textbf{FASE\_GLoBES.c} is an engine to perform analysis with user-specified experiments in a simulaton.
 Note that we define the standard neutrino mixing/oscillation parameters $\vec{\theta}_{OSC}$ ($\theta_{12}$, $\theta_{13}$, $\theta_{23}$, $\Delta m_{21}^2$, $\Delta m_{31}^2$, $\delta$) to separate from model parameters $\vec{\theta}_{Model}$ hereafter.
-
 \begin{figure}[!h]%
@@
 
-The concept of \textbf{FaSE-GLoBES} is shown in Fig.~\ref{fig:FASE}, in which three parts are shown: 1.~\textbf{the parameter translation}, 2.~\textbf{giving oscillation-parameter values}, and 3.~\textbf{the $\chi^2$-value calculation}.
+{\color{blue}Combining \textbf{GLoBES} with \textbf{Fase} (we call it `\textbf{FaSE-GLoBES}'),  the user can analyse flavour symmetry models with the simulated experimental configuration.} The concept of \textbf{FaSE-GLoBES} is shown in Fig.~\ref{fig:FASE}, in which three parts are shown: 1.~\textbf{the parameter translation}, 2.~\textbf{giving oscillation-parameter values}, and 3.~\textbf{the $\chi^2$-value calculation}.
 The idea behind this flow chart in Fig.~\ref{fig:FASE} is that given a set of model parameters, the corresponding values in standard oscillation parameters are obtained by a translation function, which is assigned by the user in \textbf{model-input.c}.
@@
 
-Application Programming Interface (API) functions in \textbf{FaSE-GLoBES} are listed:
+Application Programming Interface (API) functions in \textbf{FaSE} are listed:
 \begin{enumerate}
@@
 
-We note that except for setting the probability engine and the prior function, the other parts in the main code should follow with the GLoBES manual.
+We note that except for setting the probability engine and the prior function, the other parts in the main code should follow with the \textbf{GLoBES} manual.
 
@@
 For the first four components, values are given in the unit of \textbf{rad}, while the other two are in \textbf{eV$^2$}.
-These values will be passed into \textbf{FaSE\_GLoBES} to simulate experimental spectra and compute prior values.
+These values will be passed into \textbf{FaSE\_GLoBES.c} to simulate experimental spectra and compute prior values.
 

### 2020-06-02 doc/paper.tex
update paper

@@
 
-{\color{blue}There are three methods to translate from $\vec{\theta}_{Model}$ to $\vec{\theta}_{OSC}$ in \textbf{FaSE-GLoBES}:} 1).~the user can assign the correlation between the standard oscillation and model parameter sets{\color{blue}, 2).~give the mixing matrix in model parameter $U$}, or 3).~define the mass matrix in model parameters.
+{\color{blue}There are three methods to translate from $\vec{\theta}_{Model}$ to $\vec{\theta}_{OSC}$ in \textbf{FaSE-GLoBES}:} 1.~the user can assign the correlation between the standard oscillation and model parameter sets{\color{blue}, 2.~give the mixing matrix in model parameter $U$}, or 3.~define the mass matrix in model parameters.
 %The relation between the oscillation and model parameter sets can be derived out by the user, 
@@
 \section{Model testing}
-
+{\color{blue}[changing models for demo]}
 \begin{figure}[!h]

### 2020-06-02 doc/paper.tex
update new result

@@
  \centering
-\includegraphics[width=0.48\textwidth]{Figs/SR_th23_dCP_DUNE_MOMENT.pdf}
+\includegraphics[width=0.48\textwidth]{Figs/TM1_th23_dCP.pdf}
 \includegraphics[width=0.48\textwidth]{Figs/SR_th23_dCP_WFS.pdf}
@@
 
-We can also study on whether a neutrino mass model is excluded or not, assuming different true values for oscillation parameters.
-In this example, we present testing sub-models of TDLS in various true values of $\theta_{23}$ and $\delta$.
+{\color{blue}We can also study on how much a neutrino mass model  or a sum rule can be excluded, assuming different true values for oscillation parameters.}
+In this example, we present testing {\color{blue}atmospherical sum rule TM1~[cite]} in various true values of $\theta_{23}$ and $\delta$.
 We compute the minimal $\chi^2$ value for the model with $r$ and $m_a$, varied with the prior in Eq.~(\ref{eq:prior}) according to NuFit4.0 results.

### 2020-06-02 doc/paper.tex
update docs

@@
 {\color{blue}We can also study on how much a neutrino mass model  or a sum rule can be excluded, assuming different true values for oscillation parameters.}
-In this example, we present testing {\color{blue}atmospherical sum rule TM1~[cite]} in various true values of $\theta_{23}$ and $\delta$.
+In this example, we present testing {\color{blue}atmospherical sum rule TM1~[cite] and a supersymmetric flavour model $\Gamma_3$~[cite]} in various true values of $\theta_{23}$ and $\delta$.
 We compute the minimal $\chi^2$ value for the model with $r$ and $m_a$, varied with the prior in Eq.~(\ref{eq:prior}) according to NuFit4.0 results.

### 2020-06-04 example3/FASE_GLoBES.c
update code

@@ -1,0 +1,1005 @@
+#include <stdio.h>
+#include <stdlib.h>
+#include <math.h>
+#include <string.h>
+#include <complex.h>
+#include <float.h>
+
+#include <gsl/gsl_math.h>
+#include <gsl/gsl_complex.h>
+#include <gsl/gsl_complex_math.h>
+#include <gsl/gsl_matrix.h>
+#include <gsl/gsl_blas.h>
+//#include <gsl/gsl_statistics.h>
+//#include <gsl/gsl_rng.h>
+//#include <gsl/gsl_randist.h>
+#include <gsl/gsl_cblas.h>
+#include <gsl/gsl_eigen.h>
+#include <gsl/gsl_vector.h>
+
+
+#include <globes/globes.h>   /* GLoBES library */
+#include"FASE_GLoBES.h"
+//#include"model-input_diag.h"
+#include"model-input.h"
+
+extern char **glb_param_names;
+
+typedef struct {
+    double *osc_params;
+    size_t length;
+} glb_osc_type;
+
+typedef struct {
+    double *density_params;
+    size_t length;
+} glb_density_type;
+
+struct glb_params_type {
+    glb_osc_type *osc;
+    glb_density_type *density;
+    int iterations;
+};
+
+typedef struct {
+    int *osc_params;
+    size_t length;
+} glb_osc_proj_type;
+
+typedef struct {
+    int *density_params;
+    size_t length;
+} glb_density_proj_type;
+
+struct glb_projection_type {
+    glb_osc_proj_type *osc;
+    glb_density_proj_type *density;
+};
+
+//typedef struct OSC_PARAMS { double theta12; double theta13; double theta23; double delta; double alpha21; double alpha31; double Dm21; double Dm31; double m3; double m2; double m1; } OSC_PARAMS;
+
+/* Interface for non-standard implementations of the probability engine */
+int glb_oscp;
+glb_probability_matrix_function glb_hook_probability_matrix;
+glb_set_oscillation_parameters_function glb_hook_set_oscillation_parameters;
+glb_get_oscillation_parameters_function glb_hook_get_oscillation_parameters;
+void *glb_probability_user_data=NULL;
+/* Internal temporary variables */
[…]

### 2020-06-04 example3/FASE_GLoBES.h

@@ -1,0 +1,130 @@
+/* GLoBES -- General LOng Baseline Experiment Simulator
+ * (C) 2002 - 2007,  The GLoBES Team
+ *
+ * GLoBES is mainly intended for academic purposes. Proper
+ * credit must be given if you use GLoBES or parts of it. Please
+ * read the section 'Credit' in the README file.
+ *
+ * This program is free software; you can redistribute it and/or modify
+ * it under the terms of the GNU General Public License as published by
+ * the Free Software Foundation; either version 2 of the License, or
+ * (at your option) any later version.
+ *
+ * This program is distributed in the hope that it will be useful,
+ * but WITHOUT ANY WARRANTY; without even the implied warranty of
+ * MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+ * GNU General Public License for more details.
+ *
+ * You should have received a copy of the GNU General Public License
+ * along with this program; if not, write to the Free Software
+ * Foundation, Inc., 59 Temple Place, Suite 330, Boston, MA  02111-1307  USA
+ */
+ 
+/*
+ Some simple output functions for GLoBES examples
+ */
+
+
+//#ifndef TRI_DIRECT_PE_H
+//#define TRI_DIRECT_PE_H
+
+
+#include <stdio.h>
+#include <stdlib.h>
+#include <math.h>
+#include <string.h>
+#include <complex.h>
+#include <float.h>
+#include <gsl/gsl_complex.h>
+#include <gsl/gsl_complex_math.h>
+#include <gsl/gsl_matrix.h>
+#include <gsl/gsl_blas.h>
+//#include <gsl/gsl_statistics.h>
+//#include <gsl/gsl_rng.h>
+//#include <gsl/gsl_randist.h>
+#include <gsl/gsl_cblas.h>
+#include <gsl/gsl_eigen.h>
+#include <gsl/gsl_vector.h>
+//#include <globes/globes.h>   /* GLoBES library */
+
+#include "model-input.h"
+//#include "model-input_diag.h"
+
+/*#define GLB_NU_FLAVOURS 3*/
+#define GLB_SIGMA_E 6        /* Index of non-standard parameter sigma_E */
+#define GLB_ETA 0
+#define GLB_MA 1
+#define GLB_MB 2
+#define STAN 0
+#define MODEL -100
+#define DUNE_nu 0
+#define DUNE_anu 1
+#define DUNE_app 0
[…]

### 2020-06-04 example3/model-input.c

@@ -1,0 +1,104 @@
+#include <stdio.h>
+#include <stdlib.h>
+#include <math.h>
+#include <string.h>
+#include <complex.h>
+#include <gsl/gsl_complex.h>
+#include <gsl/gsl_math.h>
+#include <globes/globes.h>   /* GLoBES library */
+
+#include <gsl/gsl_complex_math.h>
+#include <gsl/gsl_matrix.h>
+#include <gsl/gsl_blas.h>
+#include <gsl/gsl_statistics.h>
+#include <gsl/gsl_rng.h>
+#include <gsl/gsl_randist.h>
+#include <gsl/gsl_cblas.h>
+#include <gsl/gsl_eigen.h>
+#include <gsl/gsl_vector.h>
+#include "FASE_GLoBES.h"
+/* Macros */
+//#define SQR(x)          ((x)*(x))                       /*x^2*/
+//#define SQR_ABS(x)      (SQR(creal(x))+SQR(cimag(x)))   /*|x|^2*/
+int N_M;
+
+double MODEL_init(int N) /*initialise the model-input*/
+{
+    if (N>6){printf("the number of parameters cannot be larger than 6.\n");}
+    N_M=N;
+    return 0;
+}
+
+double MtoS(double osc_para[6], double M_para[])
+/*revert model parameters to
+ the standard oscillation parameters */
+{// set up for normal ordering according to arXiv:1509.06683
+    /*example: atmospheric sum rule
+     Lambda=1 TM1
+     Lambda=2 TM2 */
+    double Lambda= 1;
+    double a0=0;
+    
+    double th13          = M_para[0]; //
+    double th23          = M_para[1];
+    double sdm        = M_para[2];
+    double ldm        = M_para[3];
+    double Sign_sind        = M_para[4];
+    
+    double s13=sin(th13);
+    double ssq13=s13*s13;
+    double ct223=cos(2*th23)/sin(2*th23);
+    double s12=sqrt(1-ssq13)/(sqrt(3)*cos(th13));
+    double th12=asin(s12);
+    
+    double cosd=-ct223*(1-5*ssq13)/(2*sqrt(2)*s13*sqrt(1-3*ssq13));
+    double dCP=acos(cosd);
+    if(Sign_sind<0) dCP=-dCP;
+    
+    
+    osc_para[0]=th12;
+    osc_para[1]=th13;
[…]

### 2020-06-04 example3/th23_dCP.c

@@ -1,0 +1,144 @@
+#if HAVE_CONFIG_H   /* config.h should come before any other includes */
+#  include "config.h"
+#endif
+
+
+#include <stdio.h>
+#include <stdlib.h>
+#include <math.h>
+#include <string.h>
+#include <complex.h>
+#include <float.h>
+
+/*
+#include <gsl/gsl_complex.h>
+#include <gsl/gsl_complex_math.h>
+#include <gsl/gsl_matrix.h>
+#include <gsl/gsl_blas.h>
+#include <gsl/gsl_statistics.h>
+#include <gsl/gsl_rng.h>
+#include <gsl/gsl_randist.h>
+#include <gsl/gsl_cblas.h>
+#include <gsl/gsl_eigen.h>
+#include <gsl/gsl_vector.h>
+*/
+#include <gsl/gsl_cdf.h>
+#include <globes/globes.h>   /* GLoBES library */
+#include "FASE_GLoBES.h"
+//#include "model-input_diag.h"
+#include "model-input.h"
+
+/***************************************************************************
+ *                            M A I N   P R O G R A M                      *
+ ***************************************************************************/
+
+int main(int argc, char *argv[])
+{
+    /* Initialize libglobes */
+    glbInit(argv[0]);
+    glbInitExperiment("exp/DUNE_GLoBES.glb",&glb_experiment_list[0],&glb_num_of_exps);
+//    glbInitExperiment("exp/MOMENT_FIX_FLUX_150KM_addATM_NC.glb",&glb_experiment_list[0],&glb_num_of_exps);
+    /*Initialize FASE*/
+    MODEL_init(5);
+    
+    /* Register non-standard probability engine. This has to be done
+     * before any calls to glbAllocParams() or glbAllocProjections() */
+    glb_init_probability_engine();
+    glbRegisterProbabilityEngine(6,
+                                 &FASE_glb_probability_matrix,
+                                 &FASE_glb_set_oscillation_parameters,
+                                 &FASE_glb_get_oscillation_parameters,
+                                 NULL);
+    /*define the true value*/
+    float degree   = M_PI/180;
+    double th12_true=33.82*degree;
+    double th13_true=8.61*degree;
[…]

### 2020-06-04 doc/paper.tex
update plot and text

--- 2020-06-02 doc/paper.tex
@@
 \includegraphics[width=0.48\textwidth]{Figs/TM1_th23_dCP.pdf}
-\includegraphics[width=0.48\textwidth]{Figs/SR_th23_dCP_WFS.pdf}
+\includegraphics[width=0.48\textwidth]{Figs/OP_th23_dCP.pdf}
 \caption{\label{fig:th23_delta}Examples for using \textbf{FaSE-GLoBES} to obtain the 2-D exclusion contour at $99\%$ C.L.
-on the plane of true values of $\theta_{23}$ and $\delta$ for sub-models of TDLS (left) and of WFS (right) with DUNE and MOMENT.
-Two results are assumed the normal ordering.
-And, the dot (star) denotes the model prediction with NuFit4.0 results (best fit of NuFit4.0).}
+on the plane of true values of $\theta_{23}$ and $\delta$ for TM1 sum rule (left) and a $S_4\otimes H_\text{CP}$ model (right) with DUNE and MOMENT.
+}
 %\caption{\label{fig:th23_delta}The 2-D exclusion contour for sub-models of tri-direct littlest seesaw on the plane of two true standard parameters $\theta_{23}$ and $\delta$, from $1\sigma$ to $5\sigma$, for DUNE (dotted) and MOMENT (solid).
@@
 {\color{blue}We can also study on how much a neutrino mass model  or a sum rule can be excluded, assuming different true values for oscillation parameters.}
-In this example, we present testing {\color{blue}atmospherical sum rule TM1~[cite]} in various true values of $\theta_{23}$ and $\delta$.
-We compute the minimal $\chi^2$ value for the model with $r$ and $m_a$, varied with the prior in Eq.~(\ref{eq:prior}) according to NuFit4.0 results.
-Two parameters $x$ and $\eta$ are fixed at the best fit.
+In Fig.~\ref{fig:th23_delta}, we present testing {\color{blue}atmospherical sum rule TM1~[cite] (left) and a $S_4\otimes H_\text{CP}$ model broken to $G_e=Z_3$ and $G_\nu=Z_2\otimes H_{\text{CP}}$~[cite] (right)} in various true values of $\theta_{23}$ and $\delta$.
+We compute the minimal $\chi^2$ value for the model, and allowed all model parameters varied.
+In the left panel, we include the prior in Eq.~(\ref{eq:prior}) according to NuFit4.0 results, while in the other one, we do not include priors.
 In addition, the studied statistics function is exactly given by Eq.~(\ref{eq:chi-squared}), but the true event rate $n_i$ is predicted by a set of oscillation parameters, which will be varied in the code.
 %
-We present this result in the left panel of Fig.~\ref{fig:th23_delta}.
-We further show the generality of \textbf{FaSE-GLoBES} by demonstrating the similar result for another model -- WFS in Eq.~(\ref{eq:WFS}) for DUNE and MOMENT, in right panel of Fig.~\ref{fig:th23_delta}.
-In this result, two mass-squared differences are fixed at the true values.
 %

### 2020-06-05 doc/paper.tex
update tex

@@
 \section{Model testing}
-{\color{blue}[changing models for demo]}
 \begin{figure}[!h]
@@
 \caption{\label{fig:th23_delta}Examples for using \textbf{FaSE-GLoBES} to obtain the 2-D exclusion contour at $99\%$ C.L.
-on the plane of true values of $\theta_{23}$ and $\delta$ for TM1 sum rule (left) and a $S_4\otimes H_\text{CP}$ model (right) with DUNE and MOMENT.
+on the plane of true values of $\theta_{23}$ and $\delta$ for TM1 sum rule (left) and a $S_4$ modular symmetry model (right) with DUNE and MOMENT.
 }
-%\caption{\label{fig:th23_delta}The 2-D exclusion contour for sub-models of tri-direct littlest seesaw on the plane of two true standard parameters $\theta_{23}$ and $\delta$, from $1\sigma$ to $5\sigma$, for DUNE (dotted) and MOMENT (solid).
-The range for each parameter is taken according to the $3\sigma$ uncertainty in NuFit4.0 results.
-The black dot denotes the best fit of NuFit4.0 results ($(\theta_{12},~\theta_{13},~\theta_{23},~\delta,~\Delta m_{21}^2,~\Delta m_{31}^2)=(33.82^\circ,~8.61^\circ,~49.6^\circ,~215^\circ,~7.39\times10^{-5}~\text{eV}^2,~2.525\times10^{-3}~\text{eV}^2)$), while the star is the prediction by the tri-direct littlest seesaw model with NuFit4.0 results ($(\theta_{12},~\theta_{13},~\theta_{23},~\delta,~\Delta m_{21}^2,~\Delta m_{31}^2)\sim(36.25^\circ,~8.63^\circ,~47^\circ,~279^\circ,~7.39\times10^{-5}~\text{eV}^2,~2.525\times10^{-3}~\text{eV}^2)$).}
 \end{figure}
@@
 {\color{blue}We can also study on how much a neutrino mass model  or a sum rule can be excluded, assuming different true values for oscillation parameters.}
-In Fig.~\ref{fig:th23_delta}, we present testing {\color{blue}atmospherical sum rule TM1~[cite] (left) and a $S_4\otimes H_\text{CP}$ model broken to $G_e=Z_3$ and $G_\nu=Z_2\otimes H_{\text{CP}}$~[cite] (right)} in various true values of $\theta_{23}$ and $\delta$.
-We compute the minimal $\chi^2$ value for the model, and allowed all model parameters varied.
-In the left panel, we include the prior in Eq.~(\ref{eq:prior}) according to NuFit4.0 results, while in the other one, we do not include priors.
+In Fig.~\ref{fig:th23_delta}, we present testing {\color{blue}trimaximal mixing TM1~\cite{Albright:2008rp} (left) and a $S_4$ modular symmetry model~\cite{deMedeirosVarzielas:2019cyj} (right) in various true values of $\theta_{23}$ and $\delta$.
+TM1 implies three equivalent relations between $\theta_{12}$ and $\theta_{13}$~\cite{Albright:2008rp} :
+\begin{eqnarray}\label{eq:TM1}
+\tan\theta_{12}=\frac{1}{2}\sqrt{1-3s^2_{13}},&\sin\theta_{12}=\frac{1}{3}\frac{\sqrt{1-3s_{13}^2}}{c_13},&\text{or}~\cos\theta_{12}=\sqrt{\frac{2}{3}}\frac{1}{c_{13}}.
+\end{eqnarray}
+and also the dependence of $\delta$ on $\theta_{13}$ and $\theta_{23}$:
+\begin{eqnarray}\label{eq:TM1_dCP}
+\cos\delta=-\frac{\cot 2\theta_{23}(1-5s_{13}^2)}{2\sqrt{2}s_{13}\sqrt{1-3s_{13}^2}}.
+\end{eqnarray}
+The other model, we use for demonstration, is based on three moduli with finite modular symmetries $S_4^A$, $S_4^B$, and $S_4^C$, associated with two right-handed neutrinos and the charged lepton sector, respectively~\cite{deMedeirosVarzielas:2019cyj}.
+This model predicts the neutrino mass matrix:
+\begin{eqnarray}
+m_\nu=&(\mu_1\hat{c}_R^2+\mu_2\hat{s}_R^{*2})\left(
+\begin{array}{ccc}
+1& -2\omega^2& -2\omega\\
+-2\omega^2&4\omega&4\\
+-2\omega&4&4\omega^2
+\end{array}
+\right)+
+(\mu_1\hat{s}^2_R+\mu_2\hat{c}_R^{*2})\left(
+\begin{array}{ccc}
+0& 0& 0\\
+0&1&-1\\
+0&-1&1
+\end{array}
+\right) \nonumber \\
+&+(\mu_1\hat{c}_R\hat{s}_R-\mu_2\hat{c}^*_R\hat{s}_R^*)\left(
+\begin{array}{ccc}
+0& -1& 1\\
+-1&4\omega^2&2i\sqrt{3}\\
+1&2i\sqrt{3}&-4\omega
+\end{array}
+\right),
+\end{eqnarray}
+where $\hat{c}_R$ and $\hat{s}_R$ are $\cos\theta_R\times \mathrm{e}^{i\alpha_2}$ and $\sin\theta_R\times \mathrm{e}^{i\alpha_3}$, respectively.
+As $\omega$ is fixed at $-\frac{1}{2}+i\frac{\sqrt{3}}{2}$, this model has 5 model parameters: $\mu_1,~\mu_2,~\theta_R,~\alpha_2,~\alpha_3$.
+}
+
+We compute the minimal $\chi^2$ value for the model, and allowed all model parameters varied, with the prior in Eq.~(\ref{eq:prior}) according to NuFit4.0 results.
+%In the left panel, we include the prior in Eq.~(\ref{eq:prior}) according to NuFit4.0 results, while in the other one, we do not include priors.
 In addition, the studied statistics function is exactly given by Eq.~(\ref{eq:chi-squared}), but the true event rate $n_i$ is predicted by a set of oscillation parameters, which will be varied in the code.

### 2020-06-05 FASE_GLoBES.c
update code

@@ -135,8 +135,8 @@ int STAN_OSC(double complex M[], double out[6])
     
     
     out[0]=the12; out[1]=the13; out[2]=the23;
-    out[3]=dCP;   out[4]=m2*m2-m1*m1;
-    out[5]=m3*m3-m1*m1;
+    out[3]=dCP;   out[4]=gsl_vector_get(eval,1)-gsl_vector_get(eval,0);
+    out[5]=gsl_vector_get(eval,1)-gsl_vector_get(eval,0);
     
     return 0;
 }
@@ -983,101 +983,3 @@ double FASE_prior_model(const glb_params in, void* user_data)
     glbFreeParams(input_errors);
     return pv;
 }
-
-double TD_prior_NUFIT4(const glb_params in, void* user_data) /*the prior is always used in the standard parameterisation*/
-{
-    glb_params central_values = glbAllocParams();
-    glb_params input_errors = glbAllocParams();
-    glb_projection p = glbAllocProjection();
-    /*glbGetOscillationParameters(central_values);*/
-    glbGetCentralValues(central_values);
-    glbGetInputErrors(input_errors);
-    glbGetProjection(p);
-    int i;
-    double x,eta,r,ma;
-    double central_STAN[6];
-    double pv = 0.0;
-    double fitvalue,centralvalue,inputerror;
-    /* Add oscillation parameter priors */
-    r=.1; ma=.1;
-    if(PARA==MODEL){
-        x   = glbGetOscParams(in,0);
-        eta = glbGetOscParams(in,1);
-        r   = glbGetOscParams(in,2);
-        ma  = glbGetOscParams(in,3);
-        //        printf("x=%f  eta=%f  r=%f  ma=%f ");
-        glbSetOscParams(in,TDth12(x,eta,r, ma),0);
-        glbSetOscParams(in,TDth13(x,eta,r, ma),1);
-        glbSetOscParams(in,TDth23(x,eta,r, ma),2);
-        glbSetOscParams(in,TDdCP(x,eta,r, ma) ,3);
-        glbSetOscParams(in,TDdm21(x,eta,r, ma),4);
-        glbSetOscParams(in,TDdm31(x,eta,r, ma),5);
-        
-        if(ma<0) {return 1e8;}
-        if(r<0) {return 1e8;}
-        
-    }
-    
-    
-    
-    
[…]

### 2020-06-05 FASE_GLoBES.h

@@ -83,4 +83,3 @@ double glbChiSpectrumTilt3(int exp, int rule, int n_params, double *x, double *e
                            void *user_data);
 double FASE_prior_OSC(const glb_params in, void* user_data);
 double FASE_prior_model(const glb_params in, void* user_data);
-double TD_prior_NUFIT4(const glb_params in, void* user_data);

### 2020-06-05 example1/FASE_GLoBES.c

@@ -4,23 +4,16 @@
 #include <string.h>
 #include <complex.h>
 #include <float.h>
-
 #include <gsl/gsl_math.h>
 #include <gsl/gsl_complex.h>
 #include <gsl/gsl_complex_math.h>
 #include <gsl/gsl_matrix.h>
 #include <gsl/gsl_blas.h>
-//#include <gsl/gsl_statistics.h>
-//#include <gsl/gsl_rng.h>
-//#include <gsl/gsl_randist.h>
 #include <gsl/gsl_cblas.h>
 #include <gsl/gsl_eigen.h>
 #include <gsl/gsl_vector.h>
-
-
 #include <globes/globes.h>   /* GLoBES library */
 #include"FASE_GLoBES.h"
-//#include"model-input_diag.h"
 #include"model-input.h"
 
 extern char **glb_param_names;
@@ -91,8 +84,6 @@ int STAN_OSC(double complex M[], double out[6])
     cblas_zgemm (CblasRowMajor, CblasConjTrans, CblasNoTrans, 3, 3, 3, &alpha, M, 3, M, 3, &beta, MMsquare, 3); //eq 4.5 page 107 Giunti
     
     
-    
-    
     gsl_matrix_complex *MM = gsl_matrix_complex_alloc(3, 3);
     int i,j;
     for(i=0;i<3;i++)
@@ -144,39 +135,32 @@ int STAN_OSC(double complex M[], double out[6])
     
     
     out[0]=the12; out[1]=the13; out[2]=the23;
-    out[3]=dCP;   out[4]=m2*m2-m1*m1;
-    out[5]=m3*m3-m1*m1;
+    out[3]=dCP;   out[4]=gsl_vector_get(eval,1)-gsl_vector_get(eval,0);
+    out[5]=gsl_vector_get(eval,1)-gsl_vector_get(eval,0);
     
     return 0;
 }
 
 
-
-int ModelTO( double OSC_PARAMS[6],double M_para[])
+int STAN_OSC_U(double complex U[], double out[4])
 {
     
+    double s13 = cabs(U[2]);       double the13=asin(s13);
+    double t12 = cabs(U[1])/cabs(U[0]);           double the12=atan(t12);
+    double t23 = cabs(U[5])/cabs(U[8]);           double the23=atan(t23);
     
-    //for the 2 heavy sterile case keep these zero.
-    double alpha = 0.0;
-    double mc = 0.0;
-    double gamma = 0.0;
[…]

### 2020-06-05 example1/FASE_GLoBES.h

@@ -1,34 +1,3 @@
-/* GLoBES -- General LOng Baseline Experiment Simulator
- * (C) 2002 - 2007,  The GLoBES Team
- *
- * GLoBES is mainly intended for academic purposes. Proper
- * credit must be given if you use GLoBES or parts of it. Please
- * read the section 'Credit' in the README file.
- *
- * This program is free software; you can redistribute it and/or modify
- * it under the terms of the GNU General Public License as published by
- * the Free Software Foundation; either version 2 of the License, or
- * (at your option) any later version.
- *
- * This program is distributed in the hope that it will be useful,
- * but WITHOUT ANY WARRANTY; without even the implied warranty of
- * MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
- * GNU General Public License for more details.
- *
- * You should have received a copy of the GNU General Public License
- * along with this program; if not, write to the Free Software
- * Foundation, Inc., 59 Temple Place, Suite 330, Boston, MA  02111-1307  USA
- */
- 
-/*
- Some simple output functions for GLoBES examples
- */
-
-
-//#ifndef TRI_DIRECT_PE_H
-//#define TRI_DIRECT_PE_H
-
-
 #include <stdio.h>
 #include <stdlib.h>
 #include <math.h>
@@ -39,16 +8,10 @@
 #include <gsl/gsl_complex_math.h>
 #include <gsl/gsl_matrix.h>
 #include <gsl/gsl_blas.h>
-//#include <gsl/gsl_statistics.h>
-//#include <gsl/gsl_rng.h>
-//#include <gsl/gsl_randist.h>
 #include <gsl/gsl_cblas.h>
 #include <gsl/gsl_eigen.h>
 #include <gsl/gsl_vector.h>
-//#include <globes/globes.h>   /* GLoBES library */
-
 #include "model-input.h"
-//#include "model-input_diag.h"
 
 /*#define GLB_NU_FLAVOURS 3*/
 #define GLB_SIGMA_E 6        /* Index of non-standard parameter sigma_E */
@@ -76,8 +39,6 @@
 #define M_SQRT3  1.73205080756887729352744634151      /* sqrt(3) */
 
 /* Interface for non-standard implementations of the probability engine */
-
[…]

### 2020-06-05 example1/th23_dCP.c

@@ -1,133 +1,0 @@
-#include <stdio.h>
-#include <stdlib.h>
-#include <math.h>
-#include <string.h>
-#include <complex.h>
-#include <float.h>
-#include <gsl/gsl_cdf.h>
-#include <globes/globes.h>   /* GLoBES library */
-#include "FASE_GLoBES.h"
-#include "model-input.h"
-
-/***************************************************************************
- *                            M A I N   P R O G R A M                      *
- ***************************************************************************/
-
-int main(int argc, char *argv[])
-{
-    /* Initialize libglobes */
-    glbInit(argv[0]);
-    glbInitExperiment("exp/MOMENT_150KM_addATM_NC.glb",&glb_experiment_list[0],&glb_num_of_exps);
-
-    /*Initialize FASE*/
-    MODEL_init(4);
-    
-    /* Register non-standard probability engine. This has to be done
-     * before any calls to glbAllocParams() or glbAllocProjections() */
-    glb_init_probability_engine();
-    glbRegisterProbabilityEngine(6,
-                                 &FASE_glb_probability_matrix,
-                                 &FASE_glb_set_oscillation_parameters,
-                                 &FASE_glb_get_oscillation_parameters,
-                                 NULL);
-    /*define the true value*/
-    float degree   = M_PI/180;
-    float x_true,eta_true,r_true,ma_true;
-    x_true=-3.65029; eta_true=1.13067*M_PI; r_true=0.511325; ma_true=3.71199e-3;
-    double M_para[4],OSC_para[6];
-    M_para[0]=x_true; M_para[1]=eta_true; M_para[2]=r_true; M_para[3]=ma_true;
-    
-    MtoS(OSC_para, M_para);
-    double th12_true=OSC_para[0];
-    double th13_true=OSC_para[1];
-    double th23_true=OSC_para[2];
-    double dCP_true=OSC_para[3];
-    double DM21_true=OSC_para[4];
-    double DM31_true=OSC_para[5];
-
-    /* Initialize parameter and projection vector(s) */
-    glb_params true_values = glbAllocParams();
-    glb_params test_values = glbAllocParams();
[…]

### 2020-06-05 example2/FASE_GLoBES.c

@@ -49,6 +49,8 @@ struct glb_projection_type {
     glb_density_proj_type *density;
 };
 
+//typedef struct OSC_PARAMS { double theta12; double theta13; double theta23; double delta; double alpha21; double alpha31; double Dm21; double Dm31; double m3; double m2; double m1; } OSC_PARAMS;
+
 /* Interface for non-standard implementations of the probability engine */
 int glb_oscp;
 glb_probability_matrix_function glb_hook_probability_matrix;
@@ -81,12 +83,14 @@ int STAN_OSC(double complex M[], double out[6])
     
     cblas_zgemm (CblasRowMajor, CblasConjTrans, CblasNoTrans, 3, 3, 3, &alpha, M, 3, M, 3, &beta, MMsquare, 3); //eq 4.5 page 107 Giunti
     
+    
     gsl_matrix_complex *MM = gsl_matrix_complex_alloc(3, 3);
     int i,j;
     for(i=0;i<3;i++)
     {
         for(j=0;j<3;j++)
         {
+            //            gsl_matrix_complex_set(MM, i, j, gsl_complex_rect(creal(M[i*3+j]),cimag(M[i*3+j])));
             gsl_matrix_complex_set(MM, i, j, gsl_complex_rect(creal(MMsquare[i*3+j]),cimag(MMsquare[i*3+j])));
         }
     }
@@ -131,11 +135,33 @@ int STAN_OSC(double complex M[], double out[6])
     
     
     out[0]=the12; out[1]=the13; out[2]=the23;
-    out[3]=dCP;   out[4]=m2*m2-m1*m1;
-    out[5]=m3*m3-m1*m1;
+    out[3]=dCP;   out[4]=gsl_vector_get(eval,1)-gsl_vector_get(eval,0);
+    out[5]=gsl_vector_get(eval,1)-gsl_vector_get(eval,0);
     
     return 0;
 }
+
+
+int STAN_OSC_U(double complex U[], double out[4])
+{
+    
+    double s13 = cabs(U[2]);       double the13=asin(s13);
+    double t12 = cabs(U[1])/cabs(U[0]);           double the12=atan(t12);
+    double t23 = cabs(U[5])/cabs(U[8]);           double the23=atan(t23);
+    
+    double s12=sin(the12);
+    double c12=cos(the12);
+    double s23=sin(the23);
+    double c13=cos(the13);
[…]

### 2020-06-05 example2/FASE_GLoBES.h

@@ -13,8 +13,20 @@
 #include <gsl/gsl_vector.h>
 #include "model-input.h"
 
+/*#define GLB_NU_FLAVOURS 3*/
+#define GLB_SIGMA_E 6        /* Index of non-standard parameter sigma_E */
+#define GLB_ETA 0
+#define GLB_MA 1
+#define GLB_MB 2
 #define STAN 0
 #define MODEL -100
+#define DUNE_nu 0
+#define DUNE_anu 1
+#define DUNE_app 0
+#define DUNE_disapp 1
+#define T2HK 2
+#define RAM 100
+#define    top_bin_number 10000
 #define SQR(x)      ((x)*(x))                        /* x^2   */
 #define SQR_ABS(x)  (SQR(creal(x)) + SQR(cimag(x)))  /* |x|^2 */
 #define GLB_NU_FLAVOURS 3
@@ -23,8 +35,10 @@
 #define GLB_Ne_MANTLE       0.5        /* Effective electron numbers for calculation */
 #define GLB_Ne_CORE         0.468      /*   of MSW potentials                        */
 #define V_THRESHOLD 0.001*GLB_V_FACTOR*GLB_Ne_MANTLE  /* The minimum matter potential below */
+/* which vacuum algorithms are used   */
 #define M_SQRT3  1.73205080756887729352744634151      /* sqrt(3) */
 
+/* Interface for non-standard implementations of the probability engine */
 double th12;
 double th13;
 double th23;
@@ -39,8 +53,8 @@ int    PARA,PARA_in,ran,ran_in,n_ram,FIT,PRIOR;
 double x_in,eta_in,r_in,ma_in;
 
 double UPPER_prior[6],LOWER_prior[6],Central_prior[6];
-
 int STAN_OSC(double complex M[], double output[6]);
+int STAN_OSC_U(double complex U[], double out[6]);
 inline double square(double x);
 int sinsq(double complex U[], double * a);
 int glb_free_probability_engine();

### 2020-06-05 example3/FASE_GLoBES.c

@@ -4,23 +4,16 @@
 #include <string.h>
 #include <complex.h>
 #include <float.h>
-
 #include <gsl/gsl_math.h>
 #include <gsl/gsl_complex.h>
 #include <gsl/gsl_complex_math.h>
 #include <gsl/gsl_matrix.h>
 #include <gsl/gsl_blas.h>
-//#include <gsl/gsl_statistics.h>
-//#include <gsl/gsl_rng.h>
-//#include <gsl/gsl_randist.h>
 #include <gsl/gsl_cblas.h>
 #include <gsl/gsl_eigen.h>
 #include <gsl/gsl_vector.h>
-
-
 #include <globes/globes.h>   /* GLoBES library */
 #include"FASE_GLoBES.h"
-//#include"model-input_diag.h"
 #include"model-input.h"
 
 extern char **glb_param_names;
@@ -91,8 +84,6 @@ int STAN_OSC(double complex M[], double out[6])
     cblas_zgemm (CblasRowMajor, CblasConjTrans, CblasNoTrans, 3, 3, 3, &alpha, M, 3, M, 3, &beta, MMsquare, 3); //eq 4.5 page 107 Giunti
     
     
-    
-    
     gsl_matrix_complex *MM = gsl_matrix_complex_alloc(3, 3);
     int i,j;
     for(i=0;i<3;i++)
@@ -144,39 +135,32 @@ int STAN_OSC(double complex M[], double out[6])
     
     
     out[0]=the12; out[1]=the13; out[2]=the23;
-    out[3]=dCP;   out[4]=m2*m2-m1*m1;
-    out[5]=m3*m3-m1*m1;
+    out[3]=dCP;   out[4]=gsl_vector_get(eval,1)-gsl_vector_get(eval,0);
+    out[5]=gsl_vector_get(eval,1)-gsl_vector_get(eval,0);
     
     return 0;
 }
 
 
-
-int ModelTO( double OSC_PARAMS[6],double M_para[])
+int STAN_OSC_U(double complex U[], double out[4])
 {
     
+    double s13 = cabs(U[2]);       double the13=asin(s13);
+    double t12 = cabs(U[1])/cabs(U[0]);           double the12=atan(t12);
+    double t23 = cabs(U[5])/cabs(U[8]);           double the23=atan(t23);
     
-    //for the 2 heavy sterile case keep these zero.
[…]

### 2020-06-05 example3/FASE_GLoBES.h

@@ -1,34 +1,3 @@
-/* GLoBES -- General LOng Baseline Experiment Simulator
- * (C) 2002 - 2007,  The GLoBES Team
- *
- * GLoBES is mainly intended for academic purposes. Proper
- * credit must be given if you use GLoBES or parts of it. Please
- * read the section 'Credit' in the README file.
- *
- * This program is free software; you can redistribute it and/or modify
- * it under the terms of the GNU General Public License as published by
- * the Free Software Foundation; either version 2 of the License, or
- * (at your option) any later version.
- *
- * This program is distributed in the hope that it will be useful,
- * but WITHOUT ANY WARRANTY; without even the implied warranty of
- * MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
- * GNU General Public License for more details.
- *
- * You should have received a copy of the GNU General Public License
- * along with this program; if not, write to the Free Software
- * Foundation, Inc., 59 Temple Place, Suite 330, Boston, MA  02111-1307  USA
- */
- 
-/*
- Some simple output functions for GLoBES examples
- */
-
-
-//#ifndef TRI_DIRECT_PE_H
-//#define TRI_DIRECT_PE_H
-
-
 #include <stdio.h>
 #include <stdlib.h>
 #include <math.h>
@@ -39,16 +8,10 @@
 #include <gsl/gsl_complex_math.h>
 #include <gsl/gsl_matrix.h>
 #include <gsl/gsl_blas.h>
-//#include <gsl/gsl_statistics.h>
-//#include <gsl/gsl_rng.h>
-//#include <gsl/gsl_randist.h>
 #include <gsl/gsl_cblas.h>
 #include <gsl/gsl_eigen.h>
 #include <gsl/gsl_vector.h>
-//#include <globes/globes.h>   /* GLoBES library */
-
 #include "model-input.h"
-//#include "model-input_diag.h"
 
 /*#define GLB_NU_FLAVOURS 3*/
 #define GLB_SIGMA_E 6        /* Index of non-standard parameter sigma_E */
@@ -76,8 +39,6 @@
 #define M_SQRT3  1.73205080756887729352744634151      /* sqrt(3) */
 
 /* Interface for non-standard implementations of the probability engine */
-
[…]

### 2020-06-05 example3/model-input.c

@@ -17,9 +17,6 @@
 #include <gsl/gsl_eigen.h>
 #include <gsl/gsl_vector.h>
 #include "FASE_GLoBES.h"
-/* Macros */
-//#define SQR(x)          ((x)*(x))                       /*x^2*/
-//#define SQR_ABS(x)      (SQR(creal(x))+SQR(cimag(x)))   /*|x|^2*/
 int N_M;
 
 double MODEL_init(int N) /*initialise the model-input*/
@@ -32,12 +29,8 @@ double MODEL_init(int N) /*initialise the model-input*/
 double MtoS(double osc_para[6], double M_para[])
 /*revert model parameters to
  the standard oscillation parameters */
-{// set up for normal ordering according to arXiv:1509.06683
-    /*example: atmospheric sum rule
-     Lambda=1 TM1
-     Lambda=2 TM2 */
-    double Lambda= 1;
-    double a0=0;
+{// set up for normal ordering according to arXiv:1904.06660v3
+    /*example: atmospheric sum rule TM1 */
     
     double th13          = M_para[0]; //
     double th23          = M_para[1];
@@ -62,23 +55,11 @@ double MtoS(double osc_para[6], double M_para[])
     osc_para[3]=dCP;
     osc_para[4]=sdm;
     osc_para[5]=ldm;
-    
- 
-    
-    
-//    printf("in model %g %g %g %g %g\n",M_para[0],M_para[1],M_para[2]*180/M_PI,M_para[3],M_para[4]);
-//    printf("%g %g %g\n",s12,s13,s23);
-
-//    printf("in %g %g %g %g %g %g\n",osc_para[0]*180/M_PI,osc_para[1]*180/M_PI,osc_para[2]*180/M_PI,osc_para[3]*180/M_PI,osc_para[4],osc_para[5]);
     return 0;
 }
 
 double model_restriction(double M_para [])
-{// set up for normal ordering according to arXiv:1509.06683
-    
-    double Lambda= 1;
-    double a0=0;
-
+{// set up for normal ordering according to arXiv:1904.06660v3
     double th13          = M_para[0];
     double th23          = M_para[1];
     double s13=sin(th13);
@@ -90,14 +71,6 @@ double model_restriction(double M_para [])
     double cosd=-ct223*(1-5*ssq13)/(2*sqrt(2)*s13*sqrt(1-3*ssq13));
     
[…]

### 2020-06-05 example3/model-input.h

@@ -8,36 +8,11 @@
 #include <gsl/gsl_complex_math.h>
 #include <gsl/gsl_matrix.h>
 #include <gsl/gsl_blas.h>
-//#include <gsl/gsl_statistics.h>
-//#include <gsl/gsl_rng.h>
-//#include <gsl/gsl_randist.h>
 #include <gsl/gsl_cblas.h>
 #include <gsl/gsl_eigen.h>
 #include <gsl/gsl_vector.h>
-//#include "FASE_GLoBES.h"
 
 int N_M;
-/******************************************the user-defined relation*/
-double complex TDModelY(double x, double eta, double r, double Ma);
-double complex TDModelZ(double x, double eta, double r, double Ma);
-double complex TDModelW(double x, double eta, double r, double Ma);
-double TDpsi(double x, double eta, double r, double Ma);
-double TDsinpsi(double x, double eta, double r, double Ma);
-double TDcospsi(double x, double eta, double r, double Ma);
-double TDtheta(double x, double eta, double r, double Ma);
-double TDth12(double x, double eta, double r, double Ma);
-double TDth13(double x, double eta, double r, double Ma);
-double TDth23(double x, double eta, double r, double Ma);
-double TDdCP(double x, double eta, double r, double Ma);
-double TDdm21(double x, double eta, double r, double Ma);
-double TDdm31(double x, double eta, double r, double Ma);
-/*******************************************************************/
-
 double MODEL_init();
-/********************************************diagonaliser ********/
-//int STAN_OSC(double complex M[], double output[6]);
-//int ModelTO( double OSC_PARAMS[6],double M_para[]);
-/*******************************************************************/
-
 double MtoS(double osc_para[6], double M_para[]);
 double model_restriction(double model []);

### 2020-06-05 example3/th23_dCP.c

@@ -1,31 +1,12 @@
-#if HAVE_CONFIG_H   /* config.h should come before any other includes */
-#  include "config.h"
-#endif
-
-
 #include <stdio.h>
 #include <stdlib.h>
 #include <math.h>
 #include <string.h>
 #include <complex.h>
 #include <float.h>
-
-/*
-#include <gsl/gsl_complex.h>
-#include <gsl/gsl_complex_math.h>
-#include <gsl/gsl_matrix.h>
-#include <gsl/gsl_blas.h>
-#include <gsl/gsl_statistics.h>
-#include <gsl/gsl_rng.h>
-#include <gsl/gsl_randist.h>
-#include <gsl/gsl_cblas.h>
-#include <gsl/gsl_eigen.h>
-#include <gsl/gsl_vector.h>
-*/
 #include <gsl/gsl_cdf.h>
 #include <globes/globes.h>   /* GLoBES library */
 #include "FASE_GLoBES.h"
-//#include "model-input_diag.h"
 #include "model-input.h"
 
 /***************************************************************************
@@ -37,9 +18,8 @@ int main(int argc, char *argv[])
     /* Initialize libglobes */
     glbInit(argv[0]);
     glbInitExperiment("exp/DUNE_GLoBES.glb",&glb_experiment_list[0],&glb_num_of_exps);
-//    glbInitExperiment("exp/MOMENT_FIX_FLUX_150KM_addATM_NC.glb",&glb_experiment_list[0],&glb_num_of_exps);
     /*Initialize FASE*/
-    MODEL_init(5);
+    MODEL_init(4);
     
     /* Register non-standard probability engine. This has to be done
      * before any calls to glbAllocParams() or glbAllocProjections() */
@@ -62,11 +42,6 @@ int main(int argc, char *argv[])
     glb_params test_values = glbAllocParams();
     glb_params input_errors = glbAllocParams();
     glb_params centers = glbAllocParams();
-    double osc_para[6];
-    double M_para[5];
-    M_para[0]=0; M_para[1]=0; M_para[2]=dCP_true; M_para[3]=DM21_true; M_para[4]=DM31_true;
-    MtoS(osc_para, M_para);
-    /*define model parameter: true_values( x, eta, r, ma)*/
     glbDefineParams(test_values,th13_true,th23_true,DM21_true,DM31_true,-1,0);
[…]

### 2020-06-05 example1/model-input.c
update codes

@@ -17,9 +17,6 @@
 #include <gsl/gsl_eigen.h>
 #include <gsl/gsl_vector.h>
 #include "FASE_GLoBES.h"
-/* Macros */
-//#define SQR(x)          ((x)*(x))                       /*x^2*/
-//#define SQR_ABS(x)      (SQR(creal(x))+SQR(cimag(x)))   /*|x|^2*/
 int N_M;
 
 /*Define the formula (5) in the working note provided by Ding.*/
@@ -206,111 +203,6 @@ double MODEL_init(int N) /*initialise the model-input*/
     return 0;
 }
 
-/*
-int STAN_OSC(double complex M[], double out[6])
-{
-    //https://github.com/daviddoria/Examples/blob/master/c%2B%2B/GSL/Test1/Test1.cpp
-    //http://linux.math.tifr.res.in/manuals/html/gsl-ref-html/gsl-ref_14.html
-    
-    
-    double complex MMsquare[] = { 1.0 + 0.0*I, 10.0 + 0.0*I, 3.0 + 0.0*I,
-        0.0 + 0.0*I, 2.0 + 0.0*I, 100.0 + 0.0*I,
-        1.0 + 0.0*I, 5.0 + 0.0*I, 3.0 + 0.0*I };
-    
-    
-    double complex beta = 0.0 + 0.0*I;
-    double complex alpha = 1.0 + 0.0*I;
-    
-    cblas_zgemm (CblasRowMajor, CblasConjTrans, CblasNoTrans, 3, 3, 3, &alpha, M, 3, M, 3, &beta, MMsquare, 3); //eq 4.5 page 107 Giunti
-    
-    
-    
-    
-    gsl_matrix_complex *MM = gsl_matrix_complex_alloc(3, 3);
-    int i,j;
-    for(i=0;i<3;i++)
-    {
-        for(j=0;j<3;j++)
-        {
-            //            gsl_matrix_complex_set(MM, i, j, gsl_complex_rect(creal(M[i*3+j]),cimag(M[i*3+j])));
-            gsl_matrix_complex_set(MM, i, j, gsl_complex_rect(creal(MMsquare[i*3+j]),cimag(MMsquare[i*3+j])));
-        }
-    }
-    
-    
-    gsl_eigen_hermv_workspace * w = gsl_eigen_hermv_alloc(3);
-    
[…]

### 2020-06-05 example1/model-input.h

@@ -34,10 +34,5 @@ double TDdm31(double x, double eta, double r, double Ma);
 /*******************************************************************/
 
 double MODEL_init();
-/********************************************diagonaliser ********/
-//int STAN_OSC(double complex M[], double output[6]);
-//int ModelTO( double OSC_PARAMS[6],double M_para[]);
-/*******************************************************************/
-
 double MtoS(double osc_para[6], double M_para[]);
 double model_restriction(double model []);

### 2020-06-05 example3/FASE_GLoBES.h

@@ -13,7 +13,6 @@
 #include <gsl/gsl_vector.h>
 #include "model-input.h"
 
-/*#define GLB_NU_FLAVOURS 3*/
 #define GLB_SIGMA_E 6        /* Index of non-standard parameter sigma_E */
 #define GLB_ETA 0
 #define GLB_MA 1
@@ -31,7 +30,6 @@
 #define SQR_ABS(x)  (SQR(creal(x)) + SQR(cimag(x)))  /* |x|^2 */
 #define GLB_NU_FLAVOURS 3
 #define GLB_V_FACTOR        7.5e-14   /* Conversion factor for matter potentials */
-//#define GLB_Ne_MANTLE       0.497      /* Effective electron numbers for calculation */
 #define GLB_Ne_MANTLE       0.5        /* Effective electron numbers for calculation */
 #define GLB_Ne_CORE         0.468      /*   of MSW potentials                        */
 #define V_THRESHOLD 0.001*GLB_V_FACTOR*GLB_Ne_MANTLE  /* The minimum matter potential below */

### 2020-06-05 example4/FASE_GLoBES.c

@@ -1,0 +1,985 @@
+#include <stdio.h>
+#include <stdlib.h>
+#include <math.h>
+#include <string.h>
+#include <complex.h>
+#include <float.h>
+#include <gsl/gsl_math.h>
+#include <gsl/gsl_complex.h>
+#include <gsl/gsl_complex_math.h>
+#include <gsl/gsl_matrix.h>
+#include <gsl/gsl_blas.h>
+#include <gsl/gsl_cblas.h>
+#include <gsl/gsl_eigen.h>
+#include <gsl/gsl_vector.h>
+#include <globes/globes.h>   /* GLoBES library */
+#include"FASE_GLoBES.h"
+#include"model-input.h"
+
+extern char **glb_param_names;
+
+typedef struct {
+    double *osc_params;
+    size_t length;
+} glb_osc_type;
+
+typedef struct {
+    double *density_params;
+    size_t length;
+} glb_density_type;
+
+struct glb_params_type {
+    glb_osc_type *osc;
+    glb_density_type *density;
+    int iterations;
+};
+
+typedef struct {
+    int *osc_params;
+    size_t length;
+} glb_osc_proj_type;
+
+typedef struct {
+    int *density_params;
+    size_t length;
+} glb_density_proj_type;
+
+struct glb_projection_type {
+    glb_osc_proj_type *osc;
+    glb_density_proj_type *density;
+};
+
+//typedef struct OSC_PARAMS { double theta12; double theta13; double theta23; double delta; double alpha21; double alpha31; double Dm21; double Dm31; double m3; double m2; double m1; } OSC_PARAMS;
+
+/* Interface for non-standard implementations of the probability engine */
+int glb_oscp;
+glb_probability_matrix_function glb_hook_probability_matrix;
+glb_set_oscillation_parameters_function glb_hook_set_oscillation_parameters;
+glb_get_oscillation_parameters_function glb_hook_get_oscillation_parameters;
+void *glb_probability_user_data=NULL;
+/* Internal temporary variables */
+gsl_matrix_complex *U=NULL; /* The vacuum mixing matrix                           */
+gsl_matrix_complex *H=NULL; /* Neutrino Hamiltonian                               */
[…]

### 2020-06-05 example4/model-input.c

@@ -1,0 +1,68 @@
+#include <stdio.h>
+#include <stdlib.h>
+#include <math.h>
+#include <string.h>
+#include <complex.h>
+#include <gsl/gsl_complex.h>
+#include <gsl/gsl_math.h>
+#include <globes/globes.h>   /* GLoBES library */
+#include <gsl/gsl_complex_math.h>
+#include <gsl/gsl_matrix.h>
+#include <gsl/gsl_blas.h>
+#include <gsl/gsl_statistics.h>
+#include <gsl/gsl_rng.h>
+#include <gsl/gsl_randist.h>
+#include <gsl/gsl_cblas.h>
+#include <gsl/gsl_eigen.h>
+#include <gsl/gsl_vector.h>
+#include "FASE_GLoBES.h"
+int N_M;
+
+double MODEL_init(int N) /*initialise the model-input*/
+{
+    if (N>6){printf("the number of parameters cannot be larger than 6.\n");}
+    N_M=N;
+    return 0;
+}
+
+double MtoS(double osc_para[6], double M_para[])
+/*revert model parameters to
+ the standard oscillation parameters */
+{// set up according to arXiv:1906.02208*/
+    
+    double mu1          = M_para[0]; //
+    double mu2          = M_para[1];
+    double theta_R      = M_para[2];
+    double alpha1       = M_para[3];
+    double alpha2       = M_para[4];
+    double complex cR=cos(theta_R)*cos(alpha1)+I*cos(theta_R)*sin(alpha1);
+    double complex sR=sin(theta_R)*cos(alpha2)+I*sin(theta_R)*sin(alpha2);
+    
+    double complex sR_con=sin(theta_R)*cos(alpha2)-I*sin(theta_R)*sin(alpha2);
+    double complex cR_con=cos(theta_R)*cos(alpha1)-I*cos(theta_R)*sin(alpha1);
+    double complex cRs=cR*cR;
+    double complex sRs=sR*sR;
+    double complex cRs_con=cR_con*cR_con;
+    double complex sRs_con=sR_con*sR_con;
+    
+    
+    double complex A=mu1*cRs+mu2*sRs_con;
+    double complex B=mu1*sRs+mu2*cRs_con;
+    double complex C=mu1*cR*sR-mu2*cR_con*sR_con;
+    
+    double complex omega= -.5+I*.5*sqrt(3);
[…]

### 2020-06-05 example4/model-input.h

@@ -1,0 +1,19 @@
+#include <stdio.h>
+#include <stdlib.h>
+#include <math.h>
+#include <string.h>
+#include <complex.h>
+#include <float.h>
+#include <gsl/gsl_complex.h>
+#include <gsl/gsl_complex_math.h>
+#include <gsl/gsl_matrix.h>
+#include <gsl/gsl_blas.h>
+#include <gsl/gsl_cblas.h>
+#include <gsl/gsl_eigen.h>
+#include <gsl/gsl_vector.h>
+
+int N_M;
+
+double MODEL_init();
+double MtoS(double osc_para[6], double M_para[]);
+double model_restriction(double model []);

### 2020-06-05 example4/th23_dCP.c

@@ -1,0 +1,122 @@
+#include <stdio.h>
+#include <stdlib.h>
+#include <math.h>
+#include <string.h>
+#include <complex.h>
+#include <float.h>
+#include <gsl/gsl_cdf.h>
+#include <globes/globes.h>   /* GLoBES library */
+#include "FASE_GLoBES.h"
+#include "model-input.h"
+
+/***************************************************************************
+ *                            M A I N   P R O G R A M                      *
+ ***************************************************************************/
+
+int main(int argc, char *argv[])
+{
+    /* Initialize libglobes */
+    glbInit(argv[0]);
+    glbInitExperiment("exp/MOMENT_FIX_FLUX_150KM_addATM_NC.glb",&glb_experiment_list[0],&glb_num_of_exps);
+    /*Initialize FASE*/
+    MODEL_init(5);
+    
+    /* Register non-standard probability engine. This has to be done
+     * before any calls to glbAllocParams() or glbAllocProjections() */
+    glb_init_probability_engine();
+    glbRegisterProbabilityEngine(6,
+                                 &FASE_glb_probability_matrix,
+                                 &FASE_glb_set_oscillation_parameters,
+                                 &FASE_glb_get_oscillation_parameters,
+                                 NULL);
+    /*define the true value*/
+    float degree   = M_PI/180;
+    double th12_true=33.82*degree;
+    double th13_true=8.61*degree;
+    double th23_true=49.6*degree;
+    double dCP_true=215*degree;
+    double DM21_true=7.39e-5;
+    double DM31_true=2.525e-3;
+    double mu1=0.00633;
+    double mu2=0.0114;
+    double theta_R=43.01*degree;
+    double alpha1=64.53*degree;
+    double alpha2=20.38*degree;
+    /* Initialize parameter and projection vector(s) */
+    glb_params true_values = glbAllocParams();
+    glb_params test_values = glbAllocParams();
+    glb_params input_errors = glbAllocParams();
+    glb_params centers = glbAllocParams();
+
+    /*define model parameter*/
[…]

### 2020-06-08 doc/FAS-GLoBES.tex
update manual draft

@@
 %JHEP%
-%\title{\boldmath  Flavour Symmetry Embedded - GLoBES (FaSE-GLoBES)}
+%\title{\boldmath  flavor Symmetry Embedded - GLoBES (FaSE-GLoBES)}
 
@@
 \begin{document} 
-%\title{The user manual: FlAvour Symmetry with the GLoBES library}
-%\title{FlAvour Symmetry with the GLoBES library}
-\title{\Large The user manual: Flavour Symmetry Embedded - GLoBES (FaSE-GLoBES)} %JHEP%
+%\title{The user manual: flavor Symmetry with the GLoBES library}
+%\title{flavor Symmetry with the GLoBES library}
+\title{\Large The user manual: flavor Symmetry Embedded - GLoBES (FaSE-GLoBES)} %JHEP%
 %\maketitle %JHEP%
@@
 %\begin{abstract}
-%\textbf{Keywords: Neutrino Oscillations, Leptonic Flavour Symmetry}  
+%\textbf{Keywords: Neutrino Oscillations, Leptonic flavor Symmetry}  
 %\end{abstract}
@@
 
-\section{Introduction}\label{sec:intro}
-{\color{red}[updating]} 
-The discovery of neutrino oscillations points out the fact that neutrinos have mass, and provides evidence beyond the Standard Model (BSM).
+%\section{Introduction}\label{sec:intro}
+%{\color{red}[updating]} 
+%The discovery of neutrino oscillations points out the fact that neutrinos have mass, and provides evidence beyond the Standard Model (BSM).
 This phenomenon is successfully described by a theoretical framework with the help of three neutrino mixing angles ($\theta_{12}$, $\theta_{13}$, $\theta_{23}$), two mass-square splittings ($\Delta m_{21}^2$, $\Delta m_{31}^2$), and one Dirac CP phase ($\delta$) \cite{Pontecorvo:1967fh,Maki:1962mu,Pontecorvo:1957qd,Esteban:2018azc}.
@@
 
-Flavour symmetry models are used to explain the origin of the neutrino mixing, and to predict the value of oscillation parameters (some of useful review articles are~\cite{Altarelli:2010gt,Ishimori:2010au,King:2013eh,King:2014nza,King:2015aea,King:2015ata,King:2017guk}).
+%flavor symmetry models are used to explain the origin of the neutrino mixing, and to predict the value of oscillation parameters (some of useful review articles are~\cite{Altarelli:2010gt,Ishimori:2010au,King:2013eh,King:2014nza,King:2015aea,King:2015ata,King:2017guk}).
 These models are motivated by some interesting features, \textit{such as} $\theta_{12}\sim 33^\circ$, and $\theta_{23}\sim 45^\circ$.
-Before the discovery of non-zero $\theta_{13}$ measurement by Daya Bay experiment~\cite{An:2013zwz}, the `tri-bi-maximal' neutrino mixing (TBM) ansatz, which was proposed in 2002 by Horrison, Perkins, and Scott~\cite{Harrison:2002er}, fitted with the experimental data in a good agreement:
-\begin{equation*}
-U_{\text{TBM}}=\left(
-\begin{array}{ccc}
-2/\sqrt{6} & 1/\sqrt{3} & 0\\
--1/\sqrt{6} & 1/\sqrt{3} & 1/\sqrt{2}\\
-1/\sqrt{6}  & -1/\sqrt{3} & 1/\sqrt{2}
-\end{array}\right).
-\end{equation*} 
-With the fact that $\theta_{13}\approx 8^\circ$, several ways to obtain such non-zero value of $\theta_{13}$ are proposed.
-One of popular proposals is to correct the tri-bi-maximal neutrino mixing such that
-\begin{equation*}
-\sin\theta_{12}=(1+s)/\sqrt{3},~\sin\theta_{13}=r/\sqrt{2},~\text{and}~\sin\theta_{23}=(1+a)/\sqrt{2}.
-\end{equation*}
 Th neutrino mixing ansatz can be realised by high-energy symmetries $G_f$.
@@
 The symmetries need to be broken at the low energy.
-Otherwise, the flavour of leptons cannot be distinguished.
-There are several approaches for the symmetry breaking, including the direct, indirect, and semi approaches.
-Direct approach preserves the residual symmetries of $G_f$ in the charged-lepton or neutrino sector.
-On the other hand, there is no residual symmetry preserved in neither charged-lepton nor neutrino sector in the indirect approach.
-In the semi approach, the charged-lepton and neutrino sectors preserve different residual symmetries, respectively.
-This symmetry is broken by extending the Higgs sector or introducing the flavons.
-%As a result, these models do not only simplify the theoretical framework for neutrino oscillations, but also provide a theoretical reason for this phenomenon.
-Many of these models can well describe the current neutrino-oscillation data.
-%
+Otherwise, the flavor of leptons cannot be distinguished.
 To achieve the $\delta$ prediction, many models are based on a discrete family symmetry $G_f$ together with a non-commuting CP symmetry $H_\mathrm{CP}$.
 Broken in different approaches, the symmetry $G_f\otimes H_\mathrm{CP}$ can predict different patterns for the neutrino mixing.
-For example, in the semi-direct approach, $S_4$ is preserved in the leading order, and leads the bimaximal (MB) or tri-bimaximal (TB) neutrino mixing, while the higher order terms bring the correction to the neutrino mixing.
 
-Currently, some works discuss on how the future experiments can be used for testing these flavour symmetry models in the phenomenological point of view, \textit{e.g.}~Ref.~\cite{Ballett:2016yod,Chatterjee:2017xkb,Ding:2019zhn,Tang:2019edw}.
+%Currently, some works discuss on how the future experiments can be used for testing these flavor symmetry models in the phenomenological point of view, \textit{e.g.}~Ref.~\cite{Ballett:2016yod,Chatterjee:2017xkb,Ding:2019zhn,Tang:2019edw}.
 A large number of these works are based on the \texttt{c}-library -- \textbf{G}eneral \textbf{Lo}ng \textbf{B}aseline \textbf{E}xperiment \textbf{S}imulator (\textbf{GLoBES}) \cite{Huber:2004ka,Huber:2007ji}, which is a convenient simulation tool to simulate neutrino oscillation experiments via the Abstract Experiment Definition Language (AEDL).
@@
 \textbf{GLoBES} can be taken as one of popular and useful tools in the community of neutrino oscillation physics.
-However, it has not yet to be extended for the purpose of analysing flavour symmetry models.
-In this work, we will present our simulation tool \textbf{F}l\textbf{a}vour \textbf{S}ymmetry \textbf{E}mbedded - \textbf{GLoBES} (\textbf{FaSE-GloBES}) that is a simulation code based on GLoBES library for studying the flavour symmetry.
-\textbf{FaSE} is a supplemental tool for GLoBES, written in \texttt{c/c++} language, and FASE-GLoBES allows the user to assign the flavour symmetry model and analyse how a flavour symmetry model can be excluded by the simulated neutrino oscillation experiment.
+However, it has not yet to be extended for the purpose of analysing flavor symmetry models.
+We present our simulation tool \textbf{F}l\textbf{a}vour \textbf{S}ymmetry \textbf{E}mbedded - \textbf{GLoBES} (\textbf{FaSE-GloBES}) that is a simulation code based on GLoBES library for studying the flavor symmetry.
+\textbf{FaSE} is a supplemental tool for GLoBES, written in \texttt{c/c++} language, and FASE-GLoBES allows the user to assign the flavor symmetry model and analyse how a flavor symmetry model can be excluded by the simulated neutrino oscillation experiment.
 
-%One of the most predictive flavour-symmetry models is the littlest seesaw model (LSS), which includes two massive right-handed neutrinos: one corresponds to the atmospheric-mass term, while the other is included for the solar-mass term~\cite{King:2013iva,King:2015dvf,King:2016yvg}.
+%One of the most predictive flavor-symmetry models is the littlest seesaw model (LSS), which includes two massive right-handed neutrinos: one corresponds to the atmospheric-mass term, while the other is included for the solar-mass term~\cite{King:2013iva,King:2015dvf,King:2016yvg}.
 The littlest seesaw model in the tri-direct approach (TDLS) has been proposed and succeeds in describing the current global-fit results~\cite{Ding:2018fyz,Ding:2018tuj}.
@@
 
-\textbf{F}l\textbf{a}vor \textbf{S}ymmetry \textbf{E}mbedded (\textbf{FaSE}) is a supplemental tool for \textbf{G}eneral \textbf{Lo}ng \textbf{B}aseline \textbf{E}xperiment \textbf{S}imulator (\textbf{GLoBES}) in order to analyse how a leptonic flavour symmetry model can be tested in neutrino oscillation experiments.
+\textbf{F}l\textbf{a}vor \textbf{S}ymmetry \textbf{E}mbedded (\textbf{FaSE}) is a supplemental tool for \textbf{G}eneral \textbf{Lo}ng \textbf{B}aseline \textbf{E}xperiment \textbf{S}imulator (\textbf{GLoBES})~\cite{Huber:2004ka,Huber:2007ji} in order to analyse how a leptonic flavor symmetry model can be tested in neutrino oscillation experiments.
 \textbf{FaSE} is written in the \texttt{c/c++} language, and consist with two codes \textbf{FASE\_GLoBES.c} and \textbf{model-input.c}.
@@
 
-The concept of \textbf{FaSE-GLoBES} is shown in Fig.~\ref{fig:FASE}, in which three parts are shown: 1.~\textbf{the parameter translation}, 2.~\textbf{giving oscillation-parameter values}, and 3.~\textbf{the $\chi^2$-value calculation}.
+{\color{blue}Combining \textbf{GLoBES} with \textbf{Fase} (we call it `\textbf{FaSE-GLoBES}'),  the user can analyse flavor symmetry models with the simulated experimental configuration.} The concept of \textbf{FaSE-GLoBES} is shown in Fig.~\ref{fig:FASE}, in which three parts are shown: 1.~\textbf{the parameter translation}, 2.~\textbf{giving oscillation-parameter values}, and 3.~\textbf{the $\chi^2$-value calculation}.
 %
@@
 We note that except for setting the probability engine and the prior function, the other parts in the main code should follow with the GLoBES manual. 
+%
+%
+{\color{blue}Many simulation packages are provided on internet.
+Some of them are also available in \textbf{GLoBES} website~\cite{GLoBES}, while the working group in the DUNE experiment also releases their neutrino flux information and detector descriptions in a AEDL file, provided in~\cite{Alion:2016uaj}.
+We summarise AEDL files for some of most-discussed experiments in Table.~\ref{tab:exp}, including their source and reference.}
+
+\begin{table}[h!]
+\caption{\label{tab:exp}Summary of available AEDL files for some of most-discussed experiments.}
+\centering
+\begin{tabular}{l|c|r}
+exp.   & source & ref. \\\hline\hline
+T2K    &     T2K.glb on \cite{GLoBES}  &    \cite{Huber:2002mx}  \\
+NOvA   &     NOvA.glb on \cite{GLoBES}   &   \cite{Ambats:2004js}   \\
+T2HK   & sys-T2HK.glb on \cite{GLoBES}  &   \cite{Huber:2007xx}   \\
+DUNE   &    \cite{Alion:2016uaj}    &  \cite{Alion:2016uaj}    \\
+MOMENT &   on FaSE website    &     \cite{Cao:2014bea}
+\end{tabular}
+\end{table}
 
@@
 \end{equation}
-where $\mathcal{M}$ ($\mathbf{M}$) is the neutrino mass matrix in the flavour (mass) state.
+where $\mathcal{M}$ ($\mathbf{M}$) is the neutrino mass matrix in the flavor (mass) state.
 The matrix $\mathcal{M}$ is given by user with model parameters $\vec{\theta}_{Model}$.
@@
 
-Finally, some restrictions are imposed by the studied flavour symmetry model.
+Finally, some restrictions are imposed by the studied flavor symmetry model.
 We set up these restrictions in the function \texttt{model\_restriction} in \texttt{model-input.c}.
@@
 
-Based on the $\chi^2$ function Eq.~(\ref{eq:chi-squared}), we can study how model parameters can be constrained and whether a flavour-symmetry neutrino model is excluded by simulated experiments.
+Based on the $\chi^2$ function Eq.~(\ref{eq:chi-squared}), we can study how model parameters can be constrained and whether a flavor-symmetry neutrino model is excluded by simulated experiments.
 In the following we will demonstrate how it works.
@@
 
-The user can also study how well a flavour symmetry model explains the computed data, or predict whether the simulated experiment can exclude this model or not.
-In other words, the user studies the minimum of $\chi^2$ for the flavour symmetry model $\vec{\theta}_{Model}$ as a hypothesis, by assuming different true oscillation values, \textit{i.e.}~different $\vec{\theta}^{true}_{OSC}$.
+The user can also study how well a flavor symmetry model explains the computed data, or predict whether the simulated experiment can exclude this model or not.
+In other words, the user studies the minimum of $\chi^2$ for the flavor symmetry model $\vec{\theta}_{Model}$ as a hypothesis, by assuming different true oscillation values, \textit{i.e.}~different $\vec{\theta}^{true}_{OSC}$.
 To do so, one can compute the same statistical quantity in Eq.~(\ref{eq:chi_model}), while the true spectrum is varied with different true values $\vec{\theta}_{OSC}^{true}$.
@@
 
-We now take the tri-direct littlest seesaw (TDLS)~\cite{King:2013iva,King:2015dvf,King:2016yvg} as an example, and simulate the event spectra for DUNE and the MuOn-decay MEdium baseline NeuTrino beam experiment (MOMENT)~\cite{Cao:2014bea} by GLoBES.
-In this flavour model, the atmospheric and solar flavon vacuum alignments are $\langle\phi_{\text{atm}}\rangle\propto\left(1, \omega^2, \omega\right)^T$ and $\langle\phi_{\text{sol}}\rangle\propto\left(1, x, x\right)^T$,
-where $\omega$ stands for a cube root of unity and the parameter $x$ is real because of the imposed CP symmetry. Under this model, the light left-handed Majorana neutrino mass matrix is given by
+In this manual, we now take the tri-direct littlest seesaw (TDLS)~\cite{King:2013iva,King:2015dvf,King:2016yvg} {\color{blue}and a $S_4$ modular flavor symmetry model~\cite{deMedeirosVarzielas:2019cyj} as examples}, and simulate the event spectra for {\color{blue}Deep Underground Neutrino Experiment (DUNE)~\cite{Acciarri:2015uup}} and the MuOn-decay MEdium baseline NeuTrino beam experiment (MOMENT)~\cite{Cao:2014bea} by GLoBES.
+In TDLS model, the atmospheric and solar flavon vacuum alignments are $\langle\phi_{\text{atm}}\rangle\propto\left(1, \omega^2, \omega\right)^T$ and $\langle\phi_{\text{sol}}\rangle\propto\left(1, x, x\right)^T$,
+where $\omega$ stands for a cube root of unity and the parameter $x$ is real because of the imposed CP symmetry.
+Under this model, the light left-handed Majorana neutrino mass matrix {\color{blue}in the flavor basis} is given by
 \begin{equation}
@@
 
-In the following, all examples are presented for TDLS.
-However, we remind the user that though we use TDLS as an example, \textbf{FaSE-GLoBES} should not be limited in any flavour model.
-We therefore in the \textbf{FaSE} distribution,  show the warped flavour symmetry (WSF) for the other example, which will not be further introduced in this manual.
+{\color{blue}In the $S_4$ modular model, the neutrino mass is predicted:
+\begin{eqnarray}\label{eq:S4_mnu}
+m_\nu=&(\mu_1\hat{c}_R^2+\mu_2\hat{s}_R^{*2})\left(
+\begin{array}{ccc}
+1& -2\omega^2& -2\omega\\
+-2\omega^2&4\omega&4\\
+-2\omega&4&4\omega^2
+\end{array}
+\right)+
+(\mu_1\hat{s}^2_R+\mu_2\hat{c}_R^{*2})\left(
+\begin{array}{ccc}
+0& 0& 0\\
+0&1&-1\\
+0&-1&1
+\end{array}
+\right) \nonumber \\
+&+(\mu_1\hat{c}_R\hat{s}_R-\mu_2\hat{c}^*_R\hat{s}_R^*)\left(
+\begin{array}{ccc}
+0& -1& 1\\
+-1&4\omega^2&2i\sqrt{3}\\
+1&2i\sqrt{3}&-4\omega
+\end{array}
+\right),
+\end{eqnarray}
+where $\hat{c}_R$ and $\hat{s}_R$ are $\cos\theta_R\times \mathrm{e}^{i\alpha_2}$ and $\sin\theta_R\times \mathrm{e}^{i\alpha_3}$, respectively.
+As $\omega$ is fixed at $-\frac{1}{2}+i\frac{\sqrt{3}}{2}$, this model has 5 model parameters: $\mu_1,~\mu_2,~\theta_R,~\alpha_2,~\alpha_3$.
+}
+
+{\color{blue}In the following, all examples are mainly presented for TDLS, except for Sec.~\ref{sec:ex_MT}.
+However, we remind the user that though we use TDLS as an example, \textbf{FaSE-GLoBES} should not be limited in any flavor model.
+We therefore in the \textbf{FaSE} distribution, show the warped flavor symmetry (WSF)~\cite{Chen:2015jta}, trimaximal mixing sum rule (TM1)~\cite{Albright:2008rp}  as examples, which will not be further introduced in this manual.
+}
 
@@
 \texttt{\}}\\
+
+%{\color{blue}For the $S_4$ modular model, we simply include the mass matrix Eq.~\ref{eq:S4_mnu}.}
 
@@
 True values for the model parameters are used $(x,~\eta,~r,~M_a)=(-3.65,~1.13\pi,~0.511,~3.71~\text{meV})$.}
-   \caption{\label{fig:constraint}Examples for using \textbf{FaSE-GLoBES} to obtain the constraints of model parameters for tri-direct littlest seesaw, with simulated DUNE and MOMENT data.
+   \caption{\label{fig:constraint}Example for using \textbf{FaSE-GLoBES} to obtain the constraints of model parameters for tri-direct littlest seesaw, with simulated DUNE and MOMENT data.
 The result is assumed the normal ordering.
@@
 The output (\texttt{data/contraint\_x\_eta.dat}) is a set of $\Delta \chi^2(\vec{\theta}^{hyp})$ (the third column) values with the changed $x$ (the first column), $\eta$ (the second column).
-We use these data, and obtain the predicted $1\sigma$, $2\sigma$, and $3\sigma$ constraints of $x$ and $\eta$ by MOMENT shown in Fig.~\ref{fig:x_eta}.
-The code for this example is provided as \textbf{x\_eta.c} in the \textbf{FaSE} distribution.
+We use these data, and obtain the predicted $1\sigma$, $2\sigma$, and $3\sigma$ constraints of $x$ and $\eta$ by MOMENT shown in Fig.~\ref{fig:constraint}.
+The code for this example is provided as \textbf{x\_eta.c} in {\color{blue}\textbf{example1}} of the \textbf{FaSE} distribution.
 
@@
  \centering
-\includegraphics[width=0.48\textwidth]{Figs/SR_th23_dCP_DUNE_MOMENT.pdf}
-\caption{\label{fig:th23_delta}Examples for using \textbf{FaSE-GLoBES} to obtain the 2-D exclusion contour at $99\%$ C.L.
-on the plane of true values of $\theta_{23}$ and $\delta$ for sub-models of TDLS with DUNE and MOMENT.
+\includegraphics[width=0.48\textwidth]{Figs/MM_th23_dCP.pdf}
+\caption{\label{fig:th23_delta}Example for using \textbf{FaSE-GLoBES} to obtain the 2-D exclusion contour at $99\%$ C.L.
+on the plane of true values of $\theta_{23}$ and $\delta$ for a $S_4$ modular symmetry model with DUNE and MOMENT.
 The result is assumed the normal ordering.
@@
 %We can also study on excluding the model, assuming different true values for oscillation parameters. 
-The user can also study how well a flavour symmetry model explains the computed data as predicting how the simulated experiment can exclude this model.
-As an example, we present testing sub-models of TDLS, assuming various true values of $\theta_{23}$ and $\delta$.
-The code for this example is provided as \textbf{th23\_delta.c} in the \textbf{FaSE} distribution.
-We compute the minimal $\chi^2$ value for the model with $r$ and $m_a$, varied with the prior in Eq.~(\ref{eq:prior}) according to NuFit4.0 results.
-Two parameters $x$ and $\eta$ are fixed at the best fit.
+The user can also study how well a flavor symmetry model explains the computed data as predicting how the simulated experiment can exclude this model.
+As an example, we present testing {\color{blue}a $S_4$ modular symmetry model}, assuming various true values of $\theta_{23}$ and $\delta$.
+{\color{blue}The code for this example is provided as \textbf{th23\_delta.c} in the \textbf{example4} of \textbf{FaSE} distribution.} We compute the minimal $\chi^2$ value for {\color{blue}this $S_4$ modular model} with all model parameters, varied with the prior in Eq.~(\ref{eq:prior}) according to NuFit4.0 results.
 The studied statistics function is exactly Eq.~(\ref{eq:chi-squared}), but the true event rate $n_i$ is predicted by a set of oscillation parameters, which will be varied in the code.
@@
 %
-Except for $\theta_{23}$ and $\delta$, which are varied between $40^\circ<\theta_{23}<52^\circ$ and $125^\circ<\delta<392^\circ$, we fix the other oscillation parameters at $\theta_{12}=36.25^\circ$, $\theta_{13}=8.63^\circ$, $\Delta m_{21}^2=7.39\times 10^{-5}$~eV$^2$ and $2.525\times10^{-3}$~eV$^2$ predicted by the model $x=-3.65$, $\eta=1.13\pi$, $r=0.511$, and $m_a=3.71$~meV.
+Except for $\theta_{23}$ and $\delta$, which are varied between $40^\circ<\theta_{23}<52^\circ$ and $125^\circ<\delta<392^\circ$, we fix the other oscillation parameters at the current best fit result Table~\ref{tab:nufit4.0}.
 Finally, in the code we adopt Wilk's theorem \cite{Wilks:1938dza}: texttt{gsl\_cdf\_chisq\_Qinv(gsl\_cdf\_chisq\_Q(fabs(res),dof),1)}.\vspace{0.2cm}\\
-%
-%
-%The example code is presented as follows.\vspace{0.2cm}\\
-%\texttt{ \{ ...  initalize the code ...\}\\
-%\{ ...  register the probability engine ...\}    }\vspace{0.2cm}\\
-%\texttt{    
-%    float degree   = M\_PI/180;\\
-%    float x\_true,eta\_true,r\_true,ma\_true;\\
-%    x\_true=-3.65029; eta\_true=1.13067*M\_PI; r\_true=0.511325; ma\_true=3.71199e-3;\\
-%    double M\_para[4],OSC\_para[6];\\
-%    M\_para[0]=x\_true; M\_para[1]=eta\_true; M\_para[2]=r\_true; M\_para[3]=ma\_true;\\
-%    MtoS(OSC\_para, M\_para);\\
-%    double th12\_true=OSC\_para[0];\\
-%    double th13\_true=OSC\_para[1];\\
-%    double th23\_true=OSC\_para[2];\\
-%    double dCP\_true=OSC\_para[3];\\
-%    double DM21\_true=OSC\_para[4];\\
-%    double DM31\_true=OSC\_para[5];\\
-%    glb\_params true\_values = glbAllocParams();\\
-%    glb\_params test\_values = glbAllocParams();\\
-%    glb\_params input\_errors = glbAllocParams();\\
-%    glb\_params centers = glbAllocParams();\\
-%    \\
-%    glbDefineParams(test\_values,x\_true,eta\_true,r\_true,ma\_true,0,0);\\
-%    glbSetDensityParams(test\_values,1.0,GLB\_ALL);\\
-%    glbDefineParams(true\_values,th12\_true,th13\_true,th23\_true,dCP\_true,\\
-%    DM21\_true,DM31\_true);\\
-%    glbSetDensityParams(true\_values,1.0,GLB\_ALL); }\vspace{0.2cm}\\
-%\texttt{ \{ ...  set up for prior ...\}}\vspace{0.2cm}\\
-\texttt{
-    float th23,dCP,dth23,ddCP,lower\_th23,upper\_th23,lower\_dCP,upper\_dCP;\\
-    FILE* File=fopen("data/ModelTest\_th23\_dCP\_test.dat", "w");\\
-    lower\_th23=40; upper\_th23=52; lower\_dCP=125; upper\_dCP=392;\\
-    dth23=(upper\_th23-lower\_th23)/100; ddCP=(upper\_dCP-lower\_dCP)/100;\\
-    glbSetProjection(free);\\
-    for (th23=lower\_th23;th23<=upper\_th23;th23=th23+dth23)\{\\
-    for (dCP=lower\_dCP;dCP<=upper\_dCP;dCP=dCP+ddCP)\{\\
-    glbSetOscParams(true\_values,th23*degree,GLB\_THETA\_23);\\
-    glbSetOscParams(true\_values,dCP*degree,GLB\_DELTA\_CP);\\
-    PARA=STAN; \\
-    glbSetOscillationParameters(true\_values);\\
-    glbSetRates();\\
-    PARA=MODEL;\\ 
-        float res=glbChiNP(test\_values,NULL,GLB\_ALL);\\
-            fprintf(File,"\%f \%f \%f $\backslash$n",th23,dCP,\\
-            gsl\_cdf\_chisq\_Qinv(gsl\_cdf\_chisq\_Q(fabs(res),dof),1));\\
-         \} fprintf(File,"$\backslash$n");\\
-    \}
-}\vspace{0.2cm}\\
+\begin{verbatim}
+float th23,dCP,dth23,ddCP,lower_th23,upper_th23,lower_dCP,upper_dCP;
+FILE* File=fopen("data/S4Modular_th23_dCP(DUNE)_v3.dat", "w");
+lower_th23=40; upper_th23=52.5; lower_dCP=125; upper_dCP=395;
+dth23=.5; ddCP=5.;
+
+int dof=1;
+glbSetProjection(free);
+for (th23=lower_th23;th23<=upper_th23;th23=th23+dth23){
+for (dCP=lower_dCP;dCP<=upper_dCP;dCP=dCP+ddCP){
+glbSetOscParams(true_values,th23*degree,GLB_THETA_23);
+glbSetOscParams(true_values,dCP*degree,GLB_DELTA_CP);
+PARA=STAN;
+glbSetOscillationParameters(true_values);
+glbSetRates();
+PARA=MODEL;
+glbDefineParams(test_values,mu1,mu2,theta_R,alpha1,alpha2,0);
+float res=glbChiNP(test_values,out,GLB_ALL);
+
+for(double alpha2_test=25; alpha2_test<400; alpha2_test=alpha2_test+300){
+glbSetOscParams(test_values,alpha2_test*degree,4);
+
+for(double alpha1_test=60; alpha1_test<400; alpha1_test=alpha1_test+300){
+glbSetOscParams(test_values,alpha1_test*degree,3);
+
+glbSetOscParams(test_values,40*degree,2);
+float res2=glbChiNP(test_values,out2,GLB_ALL);
+if(res>res2) res=res2; glbCopyParams(out2,out);
+
+glbSetOscParams(test_values,20*degree,2);
+res2=glbChiNP(test_values,out2,GLB_ALL);
+if(res>res2) res=res2; glbCopyParams(out2,out);
+}}
+
+ fprintf(File,"%f %f %f\n",th23,dCP,\
+ gsl_cdf_chisq_Qinv(gsl_cdf_chisq_Q(fabs(res),dof),1));
+ } fprintf(File,"\n");}
+        \end{verbatim}
 %\texttt{ \{ ...  destroy the pointer ...\}}\vspace{0.2cm}\\
@@
 %\end{figure}
-The output \texttt{data/ModelTest\_th23\_dCP\_test.dat} contains true values of $\theta_{23}$ (the first column) and $\delta$ (the second column) with $\chi^2_{min}$ for TDLS (the third column).
+{\color{blue}We note that hoops for variables \texttt{alpha2\_text}, \texttt{alpha1\_test}, and switch the entry value of $\theta_R$ between $20^\circ$ and $40^\circ$ is for finding the degenerate solutions, according to Ref.~\cite{deMedeirosVarzielas:2019cyj}.
+}
+The output \texttt{data/S4Modular\_th23\_dCP\_test.dat} contains true values of $\theta_{23}$ (the first column) and $\delta$ (the second column) with $\chi^2_{min}$ for TDLS (the third column).
 With these data, we then have the results shown in Fig.~\ref{fig:th23_delta}.
 
-\section{Summary and conclusions }
-{\color{red}[updating]} 
-We have presented \textbf{FaSE}, which is a supplemental simulation tool for \textbf{GLoBES} to study the leptonic flavour symmetry with neutrino oscillation experiments in a user-friendly way.
+%\section{Summary and conclusions }
+%{\color{red}[updating]} 
+%We have presented \textbf{FaSE}, which is a supplemental simulation tool for \textbf{GLoBES} to study the leptonic flavor symmetry with neutrino oscillation experiments in a user-friendly way.
 \textbf{FaSE} contains two \texttt{c}-codes: \textbf{model-input.c} and \textbf{FASE\_GLoBES.c}.
@@
 
-We also present demonstrate examples for \textbf{FaSE-GLoBES} with the flavour symmetry model -- tri-direct littlest seesaw (TDLS) -- and the future neutrino oscillaiton experiment -- MOMENT.
+%We also present demonstrate examples for \textbf{FaSE-GLoBES} with the flavor symmetry model -- tri-direct littlest seesaw (TDLS) -- and the future neutrino oscillaiton experiment -- MOMENT.
 We demonstrate how to use \textbf{FaSE-GLoBES} to obtain the constraint of any two of model parameters, and to study the ability to TDLS by MOMENT experiment.
 
-Finally, \textbf{GLoBES} is a popular and powerful simulation tool to analyse the neutrino oscillation experiments in a simple language (AEDL), without losing too much detail.
-Considering the success of the flavour symmetry theory to explain the neutrino oscillations, \textbf{FaSE-GLoBES} should benefit model builders of leptonic flavour symmetry and phenomenologists for neutrino oscillation physics.
+%Finally, \textbf{GLoBES} is a popular and powerful simulation tool to analyse the neutrino oscillation experiments in a simple language (AEDL), without losing too much detail.
+Considering the success of the flavor symmetry theory to explain the neutrino oscillations, \textbf{FaSE-GLoBES} should benefit model builders of leptonic flavor symmetry and phenomenologists for neutrino oscillation physics.
 We leave the flexibility for the user, and some other improvements and extensions can be expected in the future.

### 2020-06-08 example4/th23_dCP.c

@@ -17,6 +17,7 @@ int main(int argc, char *argv[])
 {
     /* Initialize libglobes */
     glbInit(argv[0]);
+//    glbInitExperiment("exp/DUNE_GLoBES.glb",&glb_experiment_list[0],&glb_num_of_exps);
     glbInitExperiment("exp/MOMENT_FIX_FLUX_150KM_addATM_NC.glb",&glb_experiment_list[0],&glb_num_of_exps);
     /*Initialize FASE*/
     MODEL_init(5);
@@ -37,8 +38,8 @@ int main(int argc, char *argv[])
     double dCP_true=215*degree;
     double DM21_true=7.39e-5;
     double DM31_true=2.525e-3;
-    double mu1=0.00633;
-    double mu2=0.0114;
+    double mu1=0.006;
+    double mu2=0.015;
     double theta_R=43.01*degree;
     double alpha1=64.53*degree;
     double alpha2=20.38*degree;
@@ -47,7 +48,8 @@ int main(int argc, char *argv[])
     glb_params test_values = glbAllocParams();
     glb_params input_errors = glbAllocParams();
     glb_params centers = glbAllocParams();
-
+    glb_params out = glbAllocParams();
+    glb_params out2 = glbAllocParams();
     /*define model parameter*/
     glbDefineParams(test_values,mu1,mu2,theta_R,alpha1,alpha2,0);
     glbSetDensityParams(test_values,1.0,GLB_ALL);
@@ -81,7 +83,7 @@ int main(int argc, char *argv[])
     
     for (i=0;i<6;i++) {UPPER_prior[i]=fabs(UPPER_prior[i]-Central_prior[i])/3;
         LOWER_prior[i]=fabs(LOWER_prior[i]-Central_prior[i])/3;}
-
+    
     /* centers and input_errors will not be used, but need to be given in for central values
     and prior width. Otherwise, GLoBES will complain. */
     for (i=0; i<6; i++) glbSetOscParams(centers,0.1,i); glbSetDensityParams(centers,1.0,GLB_ALL); glbCopyParams(centers,input_errors);
@@ -91,9 +93,10 @@ int main(int argc, char *argv[])
     /*two loops for chi^2(x,eta)*/
     
     float th23,dCP,dth23,ddCP,lower_th23,upper_th23,lower_dCP,upper_dCP;
-    FILE* File=fopen("data/S4_th23_dCP(MOMENT).dat", "w");
[…]

### 2020-06-08 doc/FAS-GLoBES.tex
update manuscript

@@
 \usepackage[english]{babel}
-
+\usepackage{hyperref}
 \usepackage[nottoc]{tocbibind}
@@
 In the following, we give more details about using \textbf{FASE-GLoBES}.
-In Sec.~\ref{sec:download}, we will give the instruction to download and install \textbf{GLoBES} and \textbf{FASE}.
-Then, in Sec.~\ref{sec:compile}, we will introduce how to compile and run the code.
+In Sec.~\ref{sec:compile}, we will give the instruction to download and install \textbf{GLoBES} and \textbf{FASE}, and we will introduce how to compile and run the code.
 More complicated is setting the model, and the way to do this will be described in Sec.~\ref{sec:model_set}.
@@
 
-\subsection{Download and Installation}\label{sec:download}
-\textbf{download and install GLoBES and FASE-GLoBES}\\
-{\color{red}[will fill in after the code ready on Github]}
+\subsection{Download, compile and run}\label{sec:compile}
+{\color{blue}
 
-\subsection{Compile and Run}\label{sec:compile}
+The user can download \textbf{FaSE} simply from \url{https://github.com/tcwphy/FASE_GLoBES.git} directly. Or, the user can also download it with 
+\begin{verbatim}
+git clone https://github.com/tcwphy/FASE_GLoBES.git
+\end{verbatim}
+}
+
 As \textbf{FaSE} works based on \textbf{GLoBES}, the user should use the \textbf{GLoBES} \texttt{Makefile}, but include the binary file of \textbf{FaSE}.
@@
 \texttt{    MODEL\_init($N_{para}$); }\vspace{0.2cm}\\ 
+We note that $N_{para}$ should not be larger than the number of standard oscillation parameters, $6$.
 
@@
 We therefore in the \textbf{FaSE} distribution, show the warped flavor symmetry (WSF)~\cite{Chen:2015jta}, trimaximal mixing sum rule (TM1)~\cite{Albright:2008rp} as examples, which will not be further introduced in this manual.
+We summarise our examples for \textbf{FaSE-GLoBES} and references for those theoretical models in Tabl~\ref{tab:examples}.
+And in the rest of this section, we demonstrate the \textbf{example 1} and \textbf{example 4}.
 }
+
+\begin{table}[h!]
+\caption{\label{tab:examples}Summary of available AEDL files for some of most-discussed experiments.}
+\centering
+\begin{tabular}{c|c|c|c}
+example   & model & application & reference \\\hline\hline
+\textbf{example1}    &  TDLS  & parameter constraint & \cite{King:2013iva,King:2015dvf,King:2016yvg} \\
+\textbf{example2}    &  WSF  & parameter constraint & \cite{Chen:2015jta} \\
+\textbf{example3}    &  TM1 sum rule  & model testing & \cite{Albright:2008rp} \\
+\textbf{example4}    &  $S_4$ modular  & model testing &\cite{deMedeirosVarzielas:2019cyj}  \\
+\end{tabular}
+\end{table}
 

### 2020-06-08 doc/paper.tex
update docs and plots
update paper

@@
 
-\textbf{FaSE} is written in the \texttt{c} language, and consists of two source codes \textbf{FASE\_GLoBES.c} and \textbf{model-input.c}.
+\textbf{FaSE} is written in the \texttt{c} language, and consists of two source codes \textbf{FASE\_GLoBES.c} and \textbf{model-input.c}{\color{blue}, and is available on \url{https://github.com/tcwphy/FASE_GLoBES.git}}.
 About these two \texttt{c}-codes, the user defines the correlations between model inputs and standard neutrino mixing parameters in \textbf{model-input.c}, while \textbf{FASE\_GLoBES.c} is an engine to perform analysis with user-specified experiments in a simulaton.
@@
 \includegraphics[width=0.48\textwidth]{Figs/TM1_th23_dCP.pdf}
-\includegraphics[width=0.48\textwidth]{Figs/OP_th23_dCP.pdf}
+\includegraphics[width=0.48\textwidth]{Figs/MM_th23_dCP.pdf}
 \caption{\label{fig:th23_delta}Examples for using \textbf{FaSE-GLoBES} to obtain the 2-D exclusion contour at $99\%$ C.L.

### 2020-06-08 doc/paper.tex
Polish the texts and merge the latest conflicted updates.

@@
 
+\newcommand{\jt}[1]{\textcolor{red}{#1}}
+
 %\fontsize{3}{5}\selectfont
@@
 At the dawn of precision measurements of neutrino mixing parameters, neutrino mass models can be constrained and examined by on-going and up-coming neutrino experiments.
-We present a supplemental tool \textbf{F}l\textbf{a}vour \textbf{S}ymmetry \textbf{E}mbedded (\textbf{FaSE}) for \textbf{G}eneral \textbf{Lo}ng \textbf{B}aseline \textbf{E}xperiment \textbf{S}imulator (\textbf{GLoBES}).
+We present a supplemental tool \textbf{F}l\textbf{a}vour \textbf{S}ymmetry \textbf{E}mbedded (\textbf{FaSE}) for \textbf{G}eneral \textbf{Lo}ng \textbf{B}aseline \textbf{E}xperiment \textbf{S}imulator (\textbf{GLoBES}) \jt{(website?)}.
 It can translate the neutrino mass model {\color{blue}parameters} to standard neutrino oscillation parameters, and offers prior functions in a user-friendly way.
-We demonstrate the robustness of \textbf{FaSE-GLoBE} with two examples on how the model parameters can be constrained and even whether the model is excluded by an experiment or not.
+We demonstrate the robustness of \textbf{FaSE-GLoBE} with four examples on how the model parameters can be constrained and even whether the model is excluded by an experiment or not.
 We wish that this toolkit will facilitate the study of new neutrino mass models in an effecient and effective manner.\\
@@
 {\color{blue}
-The mass of neutrinos is still a mystery in particle physics.  
-Though the last cosmological result shows the smallness of neutrino mass $\sum m_\nu<0.12$~eV~\cite{Aghanim:2018eyx}, the mass of each neutrinos is not clear.
-In addition, the true theory that explains the origin of neutrino mass is waiting to be determined. 
+\jt{The generation mechanism of neutrino masses} is still a mystery in particle physics.  
+Though the latest cosmological result shows the smallness of neutrino mass $\sum m_\nu<0.12$~eV~\cite{Aghanim:2018eyx}, the mass of each neutrino is not clear.
+In addition, the true theory that explains the origin of neutrino mass is waiting to be determined. \jt{[Not clear to me.]}
 %It is clear that neutrinos carry the peculiar mass smaller than $\mathcal{O}(1)$ eV among elementary particles, although the absolute value of each neutrino mass is unknown. 
@@
 %The seesaw mechanism has been used to explain such a tiny mass in the neutrino sector with the help of neutrino flavor mixings. 
-One of these models, the seesaw mechanism has been used to explain such a tiny mass in the neutrino sector.}
+One of these models, the seesaw mechanism has been used to explain such a tiny mass in the neutrino sector.\jt{[Seesaw mechanism is not a model, isn't it?]}}
 %Anyhow new particles have to be introduced in such a mechanism. 
@@
 {\color{blue}
-Several neutrino mixing patterns have been proposed, such as tribimaximal (TB)~\cite{Harrison:2002er,Xing:2002sw}, bimaximal (BM)~\cite{Fukugita:1998vn,Barger:1998ta,Davidson:1998bi}, and golden ratio (GR)~\cite{Datta:2003qg,Everett:2008et,Feruglio:2011qq} mixings.
-After the measurement of non-zero $\theta_{13}$, which excludes TB, BM, GR mixings, the surviving extension of TB mixing is mainly discussed~\cite{Harrison:2002er,King:2007pr,Pakvasa:2007zj}.
+Several neutrino mixing patterns have been proposed, such as tribimaximal mixings(TB)~\cite{Harrison:2002er,Xing:2002sw}, \jt{democratic mixings}~\cite{Fritzsch:1995dj}, bimaximal mixings(BM)~\cite{Fukugita:1998vn,Barger:1998ta,Davidson:1998bi}, golden ratio mixings(GR)~\cite{Datta:2003qg,Kajiyama:2007gx,Everett:2008et,Feruglio:2011qq}, and \jt{hexogonal mixings}~\cite{Albright:2010ap}.
+After the measurement of non-zero $\theta_{13}$, which almost excluded TB, BM, GR mixings, the surviving extension of TB mixing is mainly discussed~\cite{Harrison:2002er,King:2007pr,Pakvasa:2007zj}.
 %\begin{equation*}
@@
 As some well-known models such as $A_4$ and $S_4$ can realise the TB mixing, $G_f$ contains at least one of these symmetries.
-There are several approaches for the breaking from the high energy: direct~(\textit{e.g.}~Ref.~\cite{King:2013eh}), indirect~(\textit{e.g.}~Ref.~\cite{King:2013eh}), semi-direct(\textit{e.g.}~Ref.~\cite{Holthausen:2012dk,Feruglio:2012cw,Feruglio:2013hia,Ding:2013hpa,Ding:2013bpa}), tri-direct~(\textit{e.g.}~Ref.~\cite{Ding:2018fyz,Ding:2018tuj}) models.
-All of they can explain the current data well, and predict the size of $\delta$, which will be measured with the high precision.
+There are several approaches for the \jt{symmetry} breaking from the high energy: direct~(\textit{e.g.}~Ref.~\cite{King:2013eh}), indirect~(\textit{e.g.}~Ref.~\cite{King:2013eh}), semi-direct(\textit{e.g.}~Ref.~\cite{Holthausen:2012dk,Feruglio:2012cw,Feruglio:2013hia,Ding:2013hpa,Ding:2013bpa}), tri-direct~(\textit{e.g.}~Ref.~\cite{Ding:2018fyz,Ding:2018tuj}) models.
+All of \jt{them} can explain the current data, and predict the size of $\delta$, which will be measured at the high precision in the upcoming neutrino experiments.
 Moreover, there are also different theories explaining the origin of the symmetry $G_f$ as well: continuous non-Abelian gauge theories \textit{such as} $SO(3)$ (\textit{e.g.}~Ref.~\cite{King:2005bj}) or $SU(3)$ (\textit{e.g.}~Ref.~\cite{King:2001uz,King:2003rf}), and the discrete symmetry from extra dimensions (\textit{e.g.}~Ref.~\cite{Feruglio:2017spp,Criado:2018thu,Penedo:2018nmg}).
@@
 NOvA   &     NOvA.glb on \cite{GLoBES}   &   \cite{Ambats:2004js}   \\
-T2HK   & sys-T2HK.glb on \cite{GLoBES}  &   \cite{Huber:2007xx}   \\
+T2HK   & sys-T2HK.glb on \cite{GLoBES}  &   \cite{Huber:2007em}   \\
 DUNE   &    \cite{Alion:2016uaj}    &  \cite{Alion:2016uaj}    \\
@@
 Some AEDL files to describe experiments are also available in \textbf{GLoBES} website~\cite{GLoBES}, while the working group in the DUNE experiment also releases their neutrino flux information and detector descriptions in a AEDL file, provided in~\cite{Alion:2016uaj}.
-{\color{blue}We summarise AEDL files for some of most-discussed experiments in Table.~\ref{tab:exp}, including their source and reference.} It is to be extended for the purpose of analysing flavour symmetry models in an universal way.
+{\color{blue}We summarise AEDL files for some of \jt{the most interesting} experiments in Table.~\ref{tab:exp}, including their source and reference.} It is to be extended for the purpose of analysing flavour symmetry models in an universal way.
 
 As we are entering the era of precision measurements in the neutrino oscillations, recent works pay more attentions to how the future neutrino experiments can be used to test these flavour-symmetry neutrino mass models, \textit{e.g.}~Ref.~\cite{Ballett:2016yod,Chatterjee:2017xkb, Ding:2019zhn, Tang:2019edw, Blennow:2020snb}.
-In this work, we will present our simulation toolkit \textbf{F}l\textbf{a}vour \textbf{S}ymmetry \textbf{E}mbedded - \textbf{GLoBES} (\textbf{FaSE-GloBES}) in a C-library to facilitate the study in the flavour symmetry neutrino models.
+In this work, we will present our simulation toolkit \textbf{F}l\textbf{a}vour \textbf{S}ymmetry \textbf{E}mbedded - \textbf{GLoBES} (\textbf{FaSE-GloBES}) in a C-library to facilitate the study in the flavour symmetry neutrino models \jt{(website???)}.
 \textbf{FaSE} is a supplemental tool for GLoBES, written in \texttt{c/c++} language, and allows users to assign any flavour symmetry model and analyze how a flavour symmetry model is constrained by the simulated neutrino oscillation experiments.
@@
 
-{\color{blue}Combining \textbf{GLoBES} with \textbf{Fase} (we call it `\textbf{FaSE-GLoBES}'),  the user can analyse flavour symmetry models with the simulated experimental configuration.} The concept of \textbf{FaSE-GLoBES} is shown in Fig.~\ref{fig:FASE}, in which three parts are shown: 1.~\textbf{the parameter translation}, 2.~\textbf{giving oscillation-parameter values}, and 3.~\textbf{the $\chi^2$-value calculation}.
+{\color{blue}Combining \textbf{GLoBES} with \textbf{Fase} (we call it `\textbf{FaSE-GLoBES}'),  the user can analyse flavour symmetry models with the simulated experimental configurations.} The concept of \textbf{FaSE-GLoBES} is shown in Fig.~\ref{fig:FASE}, in which three parts are shown: 1.~\textbf{the parameter translation}, 2.~\textbf{giving oscillation-parameter values}, and 3.~\textbf{the $\chi^2$-value calculation}.
 The idea behind this flow chart in Fig.~\ref{fig:FASE} is that given a set of model parameters, the corresponding values in standard oscillation parameters are obtained by a translation function, which is assigned by the user in \textbf{model-input.c}.
@@
 
-{\color{blue}There are three methods to translate from $\vec{\theta}_{Model}$ to $\vec{\theta}_{OSC}$ in \textbf{FaSE-GLoBES}:} 1.~the user can assign the correlation between the standard oscillation and model parameter sets{\color{blue}, 2.~give the mixing matrix in model parameter $U$}, or 3.~define the mass matrix in model parameters.
-%The relation between the oscillation and model parameter sets can be derived out by the user, 
+{\color{blue}There are three methods to translate from $\vec{\theta}_{Model}$ to $\vec{\theta}_{OSC}$ in \textbf{FaSE-GLoBES} as follows.} 
+\jt{
+\begin{enumerate}
+ \item {Assign the correlation between the standard oscillation and model parameter sets.
 In the way of directly giving the relation between oscillation and model parameter sets, the user needs to provide
-{\color{blue}
  \begin{equation}
@@
 \end{equation}
-in the function \texttt{MtoS}. }
-%
-
-{\color{blue}When the user give the mixing matrix $U$ in model parameters, the corresponding mixing angles can be obtained through relations,
+in the function \texttt{MtoS}.
+}
+ \item {Give the mixing matrix in model parameter $U$. When the user give the mixing matrix $U$ in model parameters, the corresponding mixing angles can be obtained through relations,
 \begin{eqnarray}\label{eq:U_angle}
@@
 }
-
-The oscillation parameters can also be obtained in the way based on
+ \item {Define the mass matrix in model parameters. The oscillation parameters can also be obtained in the way based on
 \begin{equation}\label{eq:MM}
@@
 This diagnolisation in Eq.~(\ref{eq:MM}) can be done by the function \texttt{STAN\_OSC}, which needs to be called in \texttt{MtoS} with outputs of the vector $\vec{\theta}_{OSC}$.
-{\color{blue}We note that with non-diagonal mass matrix for charged leptons, this translation method is not suggested.}
+{\color{blue}We note that with non-diagonal mass matrix for charged leptons, this translation method is not suggested.}}
+\end{enumerate}
+}
 
@@
 
-We compute the minimal $\chi^2$ value for the model, and allowed all model parameters varied, with the prior in Eq.~(\ref{eq:prior}) according to NuFit4.0 results.
+We compute the minimal $\chi^2$ value for the model, and allowed all model parameters varied \jt{within} the prior \jt{defined} in Eq.~(\ref{eq:prior}) according to NuFit4.0 results.
 %In the left panel, we include the prior in Eq.~(\ref{eq:prior}) according to NuFit4.0 results, while in the other one, we do not include priors.
 In addition, the studied statistics function is exactly given by Eq.~(\ref{eq:chi-squared}), but the true event rate $n_i$ is predicted by a set of oscillation parameters, which will be varied in the code.
+\jt{Explanations are note clear to me???}
 %
@@
 %And that is our output: \texttt{gsl\_cdf\_chisq\_Qinv(gsl\_cdf\_chisq\_Q(fabs(res),dof),1)}. \textcolor{red}{[I don't understand this sentence.]} 
-More details are presented in the user manual. 
+More details are presented in the user manual. \jt{(Website to download the manual???)}
 %The code for this example is provided as \textbf{th23\_delta.c} in the \textbf{FaSE} distribution.
@@
 While \textbf{FASE\_GLoBES.c} works as a bridge between models and standard neutrino mixings, all inputs from the user need to be given in \textbf{model-input.c}.
-With the help of two main functions provided by \textbf{FaSE}, it is convenient to assign a flavour symmetry model and include Gaussian priors associated with oscillation or model parameters.
-Users are able to study how a flavour model can be studied by the simulated experimental configuration in various perspectives, \textit{e.g.} model parameter constraints, hypothesis testing.
+With the help of two main functions provided by \textbf{FaSE-GLoBES}, it is convenient to assign a flavour symmetry model and include Gaussian priors associated with oscillation or model parameters.
+Users are able to study how a flavour model can be examined by the simulated experimental configurations in various perspectives, \textit{e.g.} model parameter constraints, hypothesis testing.
 \textbf{FaSE-GLoBES} will contribute to the selection and screening of underlying neutrino mass models by oscillation experiments.
-Further improvements and extensions can be envisioned as more requests are made by users.
+Further improvements and extensions can be envisioned \jt{as more requests come up in model buildings and phenomenology}.
 

### 2020-06-09 doc/paper.tex
update paper draft

@@
 At the dawn of precision measurements of neutrino mixing parameters, neutrino mass models can be constrained and examined by on-going and up-coming neutrino experiments.
-We present a supplemental tool \textbf{F}l\textbf{a}vour \textbf{S}ymmetry \textbf{E}mbedded (\textbf{FaSE}) for \textbf{G}eneral \textbf{Lo}ng \textbf{B}aseline \textbf{E}xperiment \textbf{S}imulator (\textbf{GLoBES}) \jt{(website?)}.
+We present a supplemental tool \textbf{F}l\textbf{a}vour \textbf{S}ymmetry \textbf{E}mbedded (\textbf{FaSE}) for \textbf{G}eneral \textbf{Lo}ng \textbf{B}aseline \textbf{E}xperiment \textbf{S}imulator (\textbf{GLoBES}) \jt{(website?)}{\color{blue}, and it is available on \url{https://github.com/tcwphy/FASE_GLoBES.git}}.
 It can translate the neutrino mass model {\color{blue}parameters} to standard neutrino oscillation parameters, and offers prior functions in a user-friendly way.
@@
 
-{\color{blue}
 \jt{The generation mechanism of neutrino masses} is still a mystery in particle physics.  
 Though the latest cosmological result shows the smallness of neutrino mass $\sum m_\nu<0.12$~eV~\cite{Aghanim:2018eyx}, the mass of each neutrino is not clear.
-In addition, the true theory that explains the origin of neutrino mass is waiting to be determined. \jt{[Not clear to me.]}
+In addition, the true theory that explains the origin of neutrino mass is waiting to be {\color{blue}found out}. \jt{[Not clear to me.]}
 %It is clear that neutrinos carry the peculiar mass smaller than $\mathcal{O}(1)$ eV among elementary particles, although the absolute value of each neutrino mass is unknown. 
@@
 %The seesaw mechanism has been used to explain such a tiny mass in the neutrino sector with the help of neutrino flavor mixings. 
-One of these models, the seesaw mechanism has been used to explain such a tiny mass in the neutrino sector.\jt{[Seesaw mechanism is not a model, isn't it?]}}
+One of these models, {\color{blue}models based on} the seesaw mechanism has been used to explain such a tiny mass in the neutrino sector.\jt{[Seesaw mechanism is not a model, isn't it?]}
 %Anyhow new particles have to be introduced in such a mechanism. 
@@
 As we are entering the era of precision measurements in the neutrino oscillations, recent works pay more attentions to how the future neutrino experiments can be used to test these flavour-symmetry neutrino mass models, \textit{e.g.}~Ref.~\cite{Ballett:2016yod,Chatterjee:2017xkb, Ding:2019zhn, Tang:2019edw, Blennow:2020snb}.
-In this work, we will present our simulation toolkit \textbf{F}l\textbf{a}vour \textbf{S}ymmetry \textbf{E}mbedded - \textbf{GLoBES} (\textbf{FaSE-GloBES}) in a C-library to facilitate the study in the flavour symmetry neutrino models \jt{(website???)}.
+In this work, we will present our simulation toolkit \textbf{F}l\textbf{a}vour \textbf{S}ymmetry \textbf{E}mbedded - \textbf{GLoBES} (\textbf{FaSE-GloBES}) in a C-library to facilitate the study in the flavour symmetry neutrino models~{\color{blue}\cite{GLoBES}} \jt{(website???)}.
 \textbf{FaSE} is a supplemental tool for GLoBES, written in \texttt{c/c++} language, and allows users to assign any flavour symmetry model and analyze how a flavour symmetry model is constrained by the simulated neutrino oscillation experiments.
@@
 }
- \item {Give the mixing matrix in model parameter $U$. When the user give the mixing matrix $U$ in model parameters, the corresponding mixing angles can be obtained through relations,
+ \item {Give the mixing matrix in model parameter $U$. When the user give{\color{blue}s} the mixing matrix $U$ in model parameters, the corresponding mixing angles can be obtained through relations,
 \begin{eqnarray}\label{eq:U_angle}
@@
 where $c_{ij}$ and $s_{ij}$ are $\cos \theta_{ij}$ and $\sin\theta_{ij}$, respectively.
-In \texttt{MtoS}, the user can pass the mixing matrix $U$ to the function  \texttt{STAN\_OSC\_U}, and can obtain the corresponding mixing matrix and the CP phase.
+In \texttt{MtoS}, the user can pass the mixing matrix $U$ to the function  \texttt{STAN\_OSC\_U} to obtain the corresponding mixing {\color{blue} angles} and the CP phase.
 }
@@
 To reproduce results shown in \cite{Chatterjee:2017xkb}, we do not include any priors.
-More details about these codes are presented in the user manual.
+More details about these codes are presented in the user manual\footnote{The manual is available on the \textbf{FaSE} repository  \url{https://github.com/tcwphy/FASE_GLoBES.git}.}.
 
@@
 We compute the minimal $\chi^2$ value for the model, and allowed all model parameters varied \jt{within} the prior \jt{defined} in Eq.~(\ref{eq:prior}) according to NuFit4.0 results.
-%In the left panel, we include the prior in Eq.~(\ref{eq:prior}) according to NuFit4.0 results, while in the other one, we do not include priors.
-In addition, the studied statistics function is exactly given by Eq.~(\ref{eq:chi-squared}), but the true event rate $n_i$ is predicted by a set of oscillation parameters, which will be varied in the code.
-\jt{Explanations are note clear to me???}
-%
-%
-%{\color{blue}And, true values of the other oscillation parameters are fixed at the best fit of NuFit4.0, and this setup is different from the left panel, in which we fix the other oscillation parameters at the model prediction for the true value.}
-%
-%As mentioned in Sec.~\ref{sec:chi-squared}, the user needs to consider Wilk's theorem with the different of degrees of freedom between the {\color{blue}assumed} true theory {\color{blue}($\vec{\theta}^{true}_{OSC}$)} and the hypothesis {\color{blue}($\vec{\theta}^{hyp}_{Model}$)}, \texttt{dof}.
-%{\color{blue}`The assumed true theory' here means that the oscillation parameters assumed for predicting the true event spectrum.} \textcolor{red}{[JT: what is the meaning of the true theory?]} 
-%Here the number \texttt{dof} is $2$. 
-%And that is our output: \texttt{gsl\_cdf\_chisq\_Qinv(gsl\_cdf\_chisq\_Q(fabs(res),dof),1)}. \textcolor{red}{[I don't understand this sentence.]} 
-More details are presented in the user manual. \jt{(Website to download the manual???)}
-%The code for this example is provided as \textbf{th23\_delta.c} in the \textbf{FaSE} distribution.
-
-%\begin{figure}[!h]
- %\flushleft
-%
-%\includegraphics[width=0.32\textwidth]{figs/SR_th13_th23.pdf}$~~~~~~$\\
-%\includegraphics[width=0.32\textwidth]{figs/SR_th13_dCP.pdf}
-%\includegraphics[width=0.32\textwidth]{figs/SR_th23_dCP.pdf}$~~~~~~$\\
-%\includegraphics[width=0.32\textwidth]{figs/SR_th13_ldm.pdf}
-%\includegraphics[width=0.32\textwidth]{figs/SR_th23_ldm.pdf}
-%\includegraphics[width=0.32\textwidth]{figs/SR_dCP_ldm.pdf}
- %\caption{\label{fig:SR_2D}The 2-D exclusion contour for tri-direct littlest seesaw model on the plane of any two true standard parameters, from $1\sigma$ to $5\sigma$.
-The range for each parameter is taken according to the $3\sigma$ uncertainty in NuFit4.0 results.
-The black dot denotes the best fit of NuFit4.0 results ($(\theta_{12},~\theta_{13},~\theta_{23},~\delta,~\Delta m_{21}^2,~\Delta m_{31}^2)=(33.82^\circ,~8.61^\circ,~49.6^\circ,~215^\circ,~7.39\times10^{-5}~\text{eV}^2,~2.525\times10^{-3}~\text{eV}^2)$), while the star is the prediction by the tri-direct littlest seesaw model with NuFit4.0 results ($(\theta_{12},~\theta_{13},~\theta_{23},~\delta,~\Delta m_{21}^2,~\Delta m_{31}^2)\sim(36.25^\circ,~8.63^\circ,~47^\circ,~279^\circ,~7.39\times10^{-5}~\text{eV}^2,~2.525\times10^{-3}~\text{eV}^2)$).}
-%\end{figure}
+In addition, the studied statistics function is exactly given by Eq.~(\ref{eq:chi-squared}), {\color{blue} the true event rate $n_i$ is predicted by a set of assumed oscillation parameters.
+Two parameters $\theta_{23}$ and $\delta$ in $\vec{\theta}^{true}_{OSC}$ keep varied in the range of $40^\circ<\theta_{23}<53^\circ$ and $125^\circ<\delta<390^\circ$, respectively.} \jt{Explanations are note clear to me???}
+More details are presented in the user manual\footnote{The manual is available on the \textbf{FaSE} repository  \url{https://github.com/tcwphy/FASE_GLoBES.git}.}.
+\jt{(Website to download the manual???)}
 

### 2020-06-09 doc/paper.tex
update paper manuscript and plot
Fix typos and delete the answered questions in the draft.

@@
 At the dawn of precision measurements of neutrino mixing parameters, neutrino mass models can be constrained and examined by on-going and up-coming neutrino experiments.
-We present a supplemental tool \textbf{F}l\textbf{a}vour \textbf{S}ymmetry \textbf{E}mbedded (\textbf{FaSE}) for \textbf{G}eneral \textbf{Lo}ng \textbf{B}aseline \textbf{E}xperiment \textbf{S}imulator (\textbf{GLoBES}) \jt{(website?)}{\color{blue}, and it is available on \url{https://github.com/tcwphy/FASE_GLoBES.git}}.
+We present a supplemental tool \textbf{F}l\textbf{a}vour \textbf{S}ymmetry \textbf{E}mbedded (\textbf{FaSE}) for \textbf{G}eneral \textbf{Lo}ng \textbf{B}aseline \textbf{E}xperiment \textbf{S}imulator (\textbf{GLoBES}) {\color{blue}, and it is available on \url{https://github.com/tcwphy/FASE_GLoBES.git}}.
 It can translate the neutrino mass model {\color{blue}parameters} to standard neutrino oscillation parameters, and offers prior functions in a user-friendly way.
@@
 Though the latest cosmological result shows the smallness of neutrino mass $\sum m_\nu<0.12$~eV~\cite{Aghanim:2018eyx}, the mass of each neutrino is not clear.
-In addition, the true theory that explains the origin of neutrino mass is waiting to be {\color{blue}found out}. \jt{[Not clear to me.]}
+In addition, the true theory that explains the origin of neutrino mass is waiting to be {\color{blue}found out}.
 %It is clear that neutrinos carry the peculiar mass smaller than $\mathcal{O}(1)$ eV among elementary particles, although the absolute value of each neutrino mass is unknown. 
@@
 %The seesaw mechanism has been used to explain such a tiny mass in the neutrino sector with the help of neutrino flavor mixings. 
-One of these models, {\color{blue}models based on} the seesaw mechanism has been used to explain such a tiny mass in the neutrino sector.\jt{[Seesaw mechanism is not a model, isn't it?]}
+One of these models, {\color{blue}models based on} the seesaw mechanism \jt{have} been used to explain such a tiny mass in the neutrino sector.\jt{[Seesaw mechanism is not a model, isn't it?]}
 %Anyhow new particles have to be introduced in such a mechanism. 
@@
 Some AEDL files to describe experiments are also available in \textbf{GLoBES} website~\cite{GLoBES}, while the working group in the DUNE experiment also releases their neutrino flux information and detector descriptions in a AEDL file, provided in~\cite{Alion:2016uaj}.
-{\color{blue}We summarise AEDL files for some of \jt{the most interesting} experiments in Table.~\ref{tab:exp}, including their source and reference.} It is to be extended for the purpose of analysing flavour symmetry models in an universal way.
+{\color{blue}We summarise AEDL files for some of \jt{the most interesting} experiments in Table.~\ref{tab:exp}, including their \jt{sources and references}.} It is to be extended for the purpose of analysing flavour symmetry models in an universal way.
 
 As we are entering the era of precision measurements in the neutrino oscillations, recent works pay more attentions to how the future neutrino experiments can be used to test these flavour-symmetry neutrino mass models, \textit{e.g.}~Ref.~\cite{Ballett:2016yod,Chatterjee:2017xkb, Ding:2019zhn, Tang:2019edw, Blennow:2020snb}.
-In this work, we will present our simulation toolkit \textbf{F}l\textbf{a}vour \textbf{S}ymmetry \textbf{E}mbedded - \textbf{GLoBES} (\textbf{FaSE-GloBES}) in a C-library to facilitate the study in the flavour symmetry neutrino models~{\color{blue}\cite{GLoBES}} \jt{(website???)}.
+In this work, we will present our simulation toolkit \textbf{F}l\textbf{a}vour \textbf{S}ymmetry \textbf{E}mbedded - \textbf{GLoBES} (\textbf{FaSE-GloBES}) in a C-library to facilitate the study in the flavour symmetry neutrino models~{\color{blue}\cite{GLoBES}}.
 \textbf{FaSE} is a supplemental tool for GLoBES, written in \texttt{c/c++} language, and allows users to assign any flavour symmetry model and analyze how a flavour symmetry model is constrained by the simulated neutrino oscillation experiments.
@@
 \centering
-\includegraphics[width=7.5in]{Figs/FASE-chart_1_2.pdf}
+\includegraphics[width=5.in]{Figs/FASE-chart_1_2.pdf}
 \caption{A scheme to correlate the model parameters with standard neutrino oscillation parameters. The error propagation is implemented in the simulation code up to the spectra analysis.}%
@@
 
-{\color{blue}Combining \textbf{GLoBES} with \textbf{Fase} (we call it `\textbf{FaSE-GLoBES}'),  the user can analyse flavour symmetry models with the simulated experimental configurations.} The concept of \textbf{FaSE-GLoBES} is shown in Fig.~\ref{fig:FASE}, in which three parts are shown: 1.~\textbf{the parameter translation}, 2.~\textbf{giving oscillation-parameter values}, and 3.~\textbf{the $\chi^2$-value calculation}.
+{\color{blue}Combining \textbf{GLoBES} with \textbf{FaSE} (we call it `\textbf{FaSE-GLoBES}'),  the user can analyse flavour symmetry models with the simulated experimental configurations.} The concept of \textbf{FaSE-GLoBES} is shown in Fig.~\ref{fig:FASE}, in which three parts are shown: 1.~\textbf{the parameter translation}, 2.~\textbf{giving oscillation-parameter values}, and 3.~\textbf{the $\chi^2$-value calculation}.
 The idea behind this flow chart in Fig.~\ref{fig:FASE} is that given a set of model parameters, the corresponding values in standard oscillation parameters are obtained by a translation function, which is assigned by the user in \textbf{model-input.c}.
@@
 
-We compute the minimal $\chi^2$ value for the model, and allowed all model parameters varied \jt{within} the prior \jt{defined} in Eq.~(\ref{eq:prior}) according to NuFit4.0 results.
+We compute the minimal $\chi^2$ value for the model, and allowed all model parameters varied \jt{within} the priors \jt{defined} in Eq.~(\ref{eq:prior}) according to NuFit4.0 results.
 In addition, the studied statistics function is exactly given by Eq.~(\ref{eq:chi-squared}), {\color{blue} the true event rate $n_i$ is predicted by a set of assumed oscillation parameters.
-Two parameters $\theta_{23}$ and $\delta$ in $\vec{\theta}^{true}_{OSC}$ keep varied in the range of $40^\circ<\theta_{23}<53^\circ$ and $125^\circ<\delta<390^\circ$, respectively.} \jt{Explanations are note clear to me???}
+Two parameters $\theta_{23}$ and $\delta$ in $\vec{\theta}^{true}_{OSC}$ keep varied in the range of $40^\circ<\theta_{23}<53^\circ$ and $125^\circ<\delta<390^\circ$, respectively.}
 More details are presented in the user manual\footnote{The manual is available on the \textbf{FaSE} repository  \url{https://github.com/tcwphy/FASE_GLoBES.git}.}.
-\jt{(Website to download the manual???)}
 

### 2020-06-11 doc/FAS-GLoBES.tex
update manual

@@
 \textbf{F}l\textbf{a}vor \textbf{S}ymmetry \textbf{E}mbedded (\textbf{FaSE}) is a supplemental tool for \textbf{G}eneral \textbf{Lo}ng \textbf{B}aseline \textbf{E}xperiment \textbf{S}imulator (\textbf{GLoBES})~\cite{Huber:2004ka,Huber:2007ji} in order to analyse how a leptonic flavor symmetry model can be tested in neutrino oscillation experiments.
-\textbf{FaSE} is written in the \texttt{c/c++} language, and consist with two codes \textbf{FASE\_GLoBES.c} and \textbf{model-input.c}.
+\textbf{FaSE} is written in \texttt{c/c++}, and consist with two codes \textbf{FASE\_GLoBES.c} and \textbf{model-input.c}.
 The user defines the model in to \textbf{model-input.c}, while \textbf{FASE\_GLoBES.c} does not need to be touched.
@@
 \centering
-\includegraphics[width=7in]{Figs/FASE-chart_1_2.pdf}
-\caption{A scheme to correlate the model parameters with standard neutrino oscillation parameters. The error propagation is implemented in the simulation code up to the spectra analysis.}%
+\includegraphics[width=5in]{Figs/FASE-chart_1_2.pdf}
+\caption{%A scheme to correlate the model parameters with standard neutrino oscillation parameters. The error propagation is implemented in the simulation code up to the spectra analysis.
+%{\color{blue}A sketch for the concept of \textbf{FaSE-GLoBES}.
+Upper of this sketch presents the translation from model $\vec{\theta}^{hyp}_{Model}$ to oscillation parameters $\vec{\theta}_{OSC}$ in \textbf{model-input.c}.
+In the middle, \textbf{FASE\_GLoBES.c} passes the oscillation parameters to simulate the spectra and compute the prior value.
+Then, the rest of work is be done in \textbf{GLoBES} to out put $\Delta\chi^2$ value for the hypothesis $\vec{\theta}^{hyp}_{Model}$.}
+{\color{blue}A sketch for the concept of \textbf{FaSE-GLoBES}.
+From top to down, this sketch shows three parts: 1.~\textbf{the parameter translation} (\textbf{model-input.c}), 2.~\textbf{giving oscillation-parameter values} (\textbf{FASE\_GLoBES.c}), and 3.~\textbf{the $\chi^2$-value calculation} (\textbf{GLoBES}).}
+}%
 \label{fig:FASE}
@@
 %
-The idea behind this flow chart in Fig.~\ref{fig:FASE} is that given a set of model parameters $\vec{\theta}_{Model}$, the corresponding values in standard oscillation parameters $\vec{\theta}_{OSC}$ are obtained by a translation function, which is assigned by the user in \textbf{model-input.c}.
-And then, through \textbf{FASE\_GLoBES.c} these oscillation-parameter values are passed into \textbf{GLoBES} library to simulate the event spectra so that we can perform physics analysis in the newly-defined $\chi^2$.
+The idea behind this flow chart in Fig.~\ref{fig:FASE} is that given a set of model parameters {\color{blue}$\vec{\theta}^{hyp}_{Model}$ as a hypothese}, the corresponding values in standard oscillation parameters $\vec{\theta}_{OSC}$ are obtained by a translation function, which is assigned by the user in \textbf{model-input.c}.
+And then, through \textbf{FASE\_GLoBES.c} these oscillation-parameter values are passed into \textbf{GLoBES} library to simulate the event spectra so that {\color{blue}the user} can perform physics analysis {\color{blue}with} the newly-defined $\chi^2$.
 
@@
 The first one is to initialise \textbf{FaSE} with the number of input parameters $N_{para}$.
-The next three functions need to be included to replace the default \textbf{GLoBES} probability engine by the one that can read the output from \textbf{model-input.c}, as follows.\vspace{0.2cm}\\
+The next three functions need to be included to replace the default \textbf{GLoBES} probability engine.
+{\color{blue}In the main code, the user needs to include the script as follows.}\vspace{0.2cm}\\
 \texttt{    glbRegisterProbabilityEngine(6,\\
@@
 {\color{blue}Many simulation packages are provided on internet.
-Some of them are also available in \textbf{GLoBES} website~\cite{GLoBES}, while the working group in the DUNE experiment also releases their neutrino flux information and detector descriptions in a AEDL file, provided in~\cite{Alion:2016uaj}.
-We summarise AEDL files for some of most-discussed experiments in Table.~\ref{tab:exp}, including their source and reference.}
+Some of them are also available on \textbf{GLoBES} website~\cite{GLoBES}, while the working group in the DUNE experiment also releases their neutrino flux information and detector descriptions in a AEDL file, provided in~\cite{Alion:2016uaj}.
+We summarise AEDL files for some experiments in Table.~\ref{tab:exp}, including their sources and references.}
 
@@
 
-The user can download \textbf{FaSE} simply from \url{https://github.com/tcwphy/FASE_GLoBES.git} directly. Or, the user can also download it with 
+The user can download \textbf{FaSE} simply from \url{https://github.com/tcwphy/FASE_GLoBES.git} directly. Or, the user can also download it: 
 \begin{verbatim}
@@
 
-As \textbf{FaSE} works based on \textbf{GLoBES}, the user should use the \textbf{GLoBES} \texttt{Makefile}, but include the binary file of \textbf{FaSE}.
+As \textbf{FaSE} works based on \textbf{GLoBES}, the user should use the \textbf{GLoBES} \texttt{Makefile}, but include two binary files of \textbf{FaSE}.
 To do so, we include the script in the \texttt{Makefile},\vspace{0.2cm}\\
@@
 The user can also compile the program without the \textbf{GLoBES} \texttt{Makefile} with the following script.\vspace{0.2cm}\\
-\texttt{gcc my\_program.o FASE\_GLoBES.o model-input.o -lglobes -LGLB\_DIR/lib/ -o my\_executable}\vspace{0.2cm}\\
+\texttt{gcc my\_program.o FASE\_GLoBES.o model-input.o -lglobes -LGLB\_DIR/lib/ -o my\_executable}\footnote{We note that only the \texttt{gcc} compiler has been tested.
+Users can also try other compilers.}\vspace{0.2cm}\\
 And, the execution is also in the same way: \texttt{./my\_executable}.\\
@@
 
-The function \texttt{MtoS} can do the translator from model parameters $\vec{\theta}_{Model}$ to oscillation parameters $\vec{\theta}_{OSC}$.
+The function \texttt{MtoS} can do the {\color{blue}translation} from model parameters $\vec{\theta}_{Model}$ to oscillation parameters $\vec{\theta}_{OSC}$.
 After the user gives the array $\vec{\theta}_{Model}$ to the function \texttt{MtoS}, the output is the corresponding oscillation parameter $\vec{\theta}_{OSC}$, of which components are $\theta_{12}$, $\theta_{13}$, $\theta_{23}$, $\delta$, $\Delta m_{21}^2$, and $\Delta m_{31}^2$.

### 2020-06-11 doc/FAS-GLoBES.tex
update paper and manual

@@
 ,epsfig}
+
+\newcommand{\jt}[1]{\textcolor{red}{#1}}
 
@@
 
-The function \texttt{MtoS} can do the {\color{blue}translation} from model parameters $\vec{\theta}_{Model}$ to oscillation parameters $\vec{\theta}_{OSC}$.
+The function \texttt{MtoS} can do the translation from model parameters $\vec{\theta}_{Model}$ to oscillation parameters $\vec{\theta}_{OSC}$.
 After the user gives the array $\vec{\theta}_{Model}$ to the function \texttt{MtoS}, the output is the corresponding oscillation parameter $\vec{\theta}_{OSC}$, of which components are $\theta_{12}$, $\theta_{13}$, $\theta_{23}$, $\delta$, $\Delta m_{21}^2$, and $\Delta m_{31}^2$.
 For the first four components, values are given in the unit of \textbf{rad}, while the other two are in \textbf{eV$^2$}.
-These values will be passed in to \textbf{FaSE\_GLoBES} to simulate
-the experimental spectra and compute the prior value.
+These values will be passed into \textbf{FaSE\_GLoBES.c} to simulate experimental spectra and compute prior values.
 
-To do the translation from $\vec{\theta}_{Model}$ to $\vec{\theta}_{OSC}$, the user can assign the relation between the oscillation and model parameter sets, or define the mass matrix in model parameters, which will be diagonalised by the function \texttt{STAN\_OSC} to obtain the corresponding oscillation-parameter values.
-%The relation between the oscillation and model parameter sets can be derived out by the user, 
+{\color{blue}There are three methods to translate from $\vec{\theta}_{Model}$ to $\vec{\theta}_{OSC}$ in \textbf{FaSE-GLoBES} as follows.} 
+\jt{
+\begin{enumerate}
+ \item {Assign the correlation between the standard oscillation and model parameter sets.
 In the way of directly giving the relation between oscillation and model parameter sets, the user needs to provide
-\begin{equation}\label{eq:modelofOSC}
-\vec{\theta}_{Model}=\vec{f}(\vec{\theta}_{OSC})
+ \begin{equation}
+\vec{\theta}_{Model}=\vec{f}(\vec{\theta}_{OSC}), 
 \end{equation}
 in the function \texttt{MtoS}.
-%
-
-The oscillation parameters can also be obtained in the way based on
+}
+ \item {Give the mixing matrix in model parameter $U$. When the user give{\color{blue}s} the mixing matrix $U$ in model parameters, the corresponding mixing angles can be obtained through relations,
+\begin{eqnarray}\label{eq:U_angle}
+\tan\theta_{12}=\left|\frac{U_{e2}}{U_{e1}}\right|,&  \sin\theta_{13}=|U_{e3}|,& \tan\theta_{23} = \left|\frac{U_{\mu 3}}{U_{\tau 3}}\right|.
+\end{eqnarray}
+After getting these mixing angles, we can easily get the Dirac CP phase $\delta$ with the Jarlskog invariant $J_{CP}$,\
+\begin{equation}\label{eq:U_phase}
+J_{CP}=c_{12}s_{12}c_{23}s_{23}c_{13}^2s_{13}\sin\delta,
+\end{equation}
+where $c_{ij}$ and $s_{ij}$ are $\cos \theta_{ij}$ and $\sin\theta_{ij}$, respectively.
+In \texttt{MtoS}, the user can pass the mixing matrix $U$ to the function  \texttt{STAN\_OSC\_U} to obtain the corresponding mixing {\color{blue} angles} and the CP phase.
+}
+ \item {Define the mass matrix in model parameters. The oscillation parameters can also be obtained in the way based on
 \begin{equation}\label{eq:MM}
@@
 \end{equation}
-where $\mathcal{M}$ ($\mathbf{M}$) is the neutrino mass matrix in the flavor (mass) state.
-The matrix $\mathcal{M}$ is given by user with model parameters $\vec{\theta}_{Model}$.
-The matrix $U$ is the neutrino mixing matrix, and can be used for getting mixing angles.
+where $\mathcal{M}$ ($\mathbf{M}$) is the neutrino mass matrix in the flavour (mass) state.
+The matrix $\mathcal{M}$ is given by the user with model parameters $\vec{\theta}_{Model}$.
+The mixing matrix $U$ can be used to get mixing angles and the CP phase, as Eqs.
+(\ref{eq:U_angle}) and (\ref{eq:U_phase}).
 The difference between any two diagonal elements of $\textbf{M}$ ($\textbf{M}_{ii}-\textbf{M}_{jj}=m_i^2-m_j^2$) is the mass-squared difference ($\Delta m_{ij}^2$).
-This diagnolisation Eq.~(\ref{eq:MM}) can be done with the function \texttt{STAN\_OSC}, which outputs directly the vector $\vec{\theta}_{OSC}$.
-The user needs to call it in \texttt{MtoS} with\vspace{0.2cm}\\
-\texttt{STAN\_OSC(\{}$M$\texttt{\},\{}$\vec{\theta}_{OSC}$\texttt{\});},\\
-where \texttt{\{}$M$\texttt{\}} and \texttt{\{}$\vec{\theta}_{OSC}$\texttt{\}} are the input neutrino mass matrix and the output array of oscillation parameter values, respectively.
+This diagnolisation in Eq.~(\ref{eq:MM}) can be done by the function \texttt{STAN\_OSC}, which needs to be called in \texttt{MtoS} with outputs of the vector $\vec{\theta}_{OSC}$.
+{\color{blue}We note that with non-diagonal mass matrix for charged leptons, this translation method is not suggested.}}
+\end{enumerate}
+}
 More details about how to assign a model will be introduced in Sec.~\ref{sec:ex_set_model}.

### 2020-06-11 doc/paper.tex
update paper and manual

@@
 
-\textbf{FaSE} is written in the \texttt{c} language, and consists of two source codes \textbf{FASE\_GLoBES.c} and \textbf{model-input.c}{\color{blue}, and is available on \url{https://github.com/tcwphy/FASE_GLoBES.git}}.
+\textbf{FaSE} is written in \texttt{c}, and consists of two source codes \textbf{FASE\_GLoBES.c} and \textbf{model-input.c}{\color{blue}, and is available on \url{https://github.com/tcwphy/FASE_GLoBES.git}}.
 About these two \texttt{c}-codes, the user defines the correlations between model inputs and standard neutrino mixing parameters in \textbf{model-input.c}, while \textbf{FASE\_GLoBES.c} is an engine to perform analysis with user-specified experiments in a simulaton.
@@
 \includegraphics[width=5.in]{Figs/FASE-chart_1_2.pdf}
-\caption{A scheme to correlate the model parameters with standard neutrino oscillation parameters. The error propagation is implemented in the simulation code up to the spectra analysis.}%
+\caption{%A scheme to correlate the model parameters with standard neutrino oscillation parameters. The error propagation is implemented in the simulation code up to the spectra analysis.
+%{\color{blue}A sketch for the concept of \textbf{FaSE-GLoBES}.
+Upper of this sketch presents the translation from model $\vec{\theta}^{hyp}_{Model}$ to oscillation parameters $\vec{\theta}_{OSC}$ in \textbf{model-input.c}.
+In the middle, \textbf{FASE\_GLoBES.c} passes the oscillation parameters to simulate the spectra and compute the prior value.
+Then, the rest of work is be done in \textbf{GLoBES} to out put $\Delta\chi^2$ value for the hypothesis $\vec{\theta}^{hyp}_{Model}$.}
+{\color{blue}A sketch for the concept of \textbf{FaSE-GLoBES}.
+From top to down, this sketch shows three parts: 1.~\textbf{the parameter translation} (\textbf{model-input.c}), 2.~\textbf{giving oscillation-parameter values} (\textbf{FASE\_GLoBES.c}), and 3.~\textbf{the $\chi^2$-value calculation} (\textbf{GLoBES}).}
+}%
 \label{fig:FASE}
@@
 {\color{blue}Combining \textbf{GLoBES} with \textbf{FaSE} (we call it `\textbf{FaSE-GLoBES}'),  the user can analyse flavour symmetry models with the simulated experimental configurations.} The concept of \textbf{FaSE-GLoBES} is shown in Fig.~\ref{fig:FASE}, in which three parts are shown: 1.~\textbf{the parameter translation}, 2.~\textbf{giving oscillation-parameter values}, and 3.~\textbf{the $\chi^2$-value calculation}.
-The idea behind this flow chart in Fig.~\ref{fig:FASE} is that given a set of model parameters, the corresponding values in standard oscillation parameters are obtained by a translation function, which is assigned by the user in \textbf{model-input.c}.
-And then, through \textbf{FASE\_GLoBES.c} these oscillation-parameter values are passed into \textbf{GLoBES} library to simulate the event spectra so that we can perform physics analysis in the newly-defined $\chi^2$.
+The idea behind this flow chart in Fig.~\ref{fig:FASE} is that given a set of model parameters {\color{blue}$\vec{\theta}^{hyp}_{Model}$ as a hypothese}, the corresponding values in standard oscillation parameters {\color{blue}$\vec{\theta}_{OSC}$} are obtained by a translation function, which is assigned by the user in \textbf{model-input.c}.
+And then, through \textbf{FASE\_GLoBES.c} these oscillation-parameter values are passed into \textbf{GLoBES} library to simulate the event spectra so that {\color{blue}the user} can perform physics analysis {\color{blue}with} the newly-defined $\chi^2$.
 
@@
 The first one is to initialise \textbf{FaSE} with the number of input parameters $N_{para}$.
-The next three functions need to be included to replace the default \textbf{GLoBES} probability engine by the one that can read the output from \textbf{model-input.c}, as follows.
+The next three functions need to be included to replace the default \textbf{GLoBES} probability engine.{\color{blue}In the main code, the user needs to include the script as follows.}\vspace{0.2cm}\\
 % \vspace{0.2cm}\\

### 2020-06-11 doc/FAS-GLoBES.tex
update the manual

@@
 In the way of directly giving the relation between oscillation and model parameter sets, the user needs to provide
- \begin{equation}
+ \begin{equation}\label{eq:modelofOSC}
 \vec{\theta}_{Model}=\vec{f}(\vec{\theta}_{OSC}), 
@@
 These two functions are for different purposes.
-If the user give the prior in oscillation (model) parameters, the user should register \texttt{FASE\_prior\_OSC} (\texttt{FASE\_prior\_model}) with the \textbf{GLoBES} function \texttt{glbRegisterPriorFunction}, as we introduced in the beginning of this section.
+If the user give{\color{blue}s} the prior in oscillation (model) parameters, the user should register \texttt{FASE\_prior\_OSC} (\texttt{FASE\_prior\_model}) with the \textbf{GLoBES} function \texttt{glbRegisterPriorFunction}, as we introduced in the beginning of this section.
 The user also needs to assign the parameter \texttt{PARA=STAN} (\texttt{PARA=Model}), when the user prefers to give the prior in oscillation (model) parameters.
@@
 \end{equation}
- where $\theta_i$ is one of parameters constrained by prior, $\theta^c_i$ ($\sigma_i$) is the central value (Gaussian width) of the prior for $\theta_i$.
-We note that $\theta_i$ can be either model ($\vec{\theta}_{Model}$) or oscillation parameters ($\vec{\theta}_{OSC}$).
+ where $\theta_i$ is {\color{blue}one parameter of the hypothesis $\vec{\theta}^{hyp}$}, $\theta^c_i$ ($\sigma_i$) is the central value (Gaussian width) of the prior for $\theta_i$.
+We note that {\color{blue}$\vec{\theta}^{hyp}$} can be either model ($\vec{\theta}_{Model}$) or oscillation parameters ($\vec{\theta}_{OSC}$).
 %
 The values of $\theta^c_i$ and $\sigma_i$ need to be given by the user through three arrays: \texttt{Central\_prior}, \texttt{UPPER\_prior}, and \texttt{LOWER\_prior}, in which there are six components.
-To treat asymmetry of width for upper ($\theta_i>\theta_i^c$) and lower ($\theta_i<\theta_i^c$) Gaussian widths, we give values in two arrays \texttt{UPPER\_prior}, and \texttt{LOWER\_prior}, respectively.
+To treat asymmetry of width for upper ($\theta_i>\theta_i^c$) and lower ($\theta_i<\theta_i^c$) Gaussian widths, we give values in two arrays \texttt{UPPER\_prior} and \texttt{LOWER\_prior}, respectively.
+{\color{blue}Once the user does not want to include any priors, two arrays \texttt{UPPER\_prior} and \texttt{LOWER\_prior} need to be $0$.}
+%
 If the user gives the prior in model parameters, the order of each component follows with the setup of input for the probability engine.
@@
 The user can use \textbf{FaSE-GLoBES} to constrain model parameters. 
-Suppose we have the measurement $\vec{x}$ and the likelihood function $L(\vec{\theta})=P(\vec{x}|\vec{\theta})$ for a set of parameters $\vec{\theta}=(\theta_1,...,\theta_N)$, where $P(\vec{x}|\vec{\theta})$ is the probability function for data $\vec{x}$ in favour of the hypothesis $\vec{\theta}$.
-The constraint of model parameters can be obtained with the statistis parameter $\chi^2\equiv \ln L(\vec{\theta})$.
+Suppose we have the measurement $\vec{x}$ and the likelihood function $L(\vec{\theta}^{hyp})=P(\vec{x}|\vec{\theta}^{hyp})$ for a set of parameters $\vec{\theta}^{hyp}=(\theta_1,...,\theta_N)$, where $P(\vec{x}|\vec{\theta}^{hyp})$ is the probability function for data $\vec{x}$ in favour of the hypothesis $\vec{\theta}^{hyp}$.
+The constraint of model parameters can be obtained with the statistis parameter $\chi^2\equiv \ln L(\vec{\theta}^{hyp})$.
 The expression $\chi^2$ is used as the default \textbf{GLoBES} setting. In more detail, the $\chi^2$ function, following the Poisson distribution, is constructed based on a log-likelihood ratio,
@@
 The parameters $\xi_s$ and $\xi_b$ are introduced to account for the systematic uncertainties in the normalisation for the signal (subscript $_s$) and background (subscript $_b$) components of the event rate, and are allowed to vary in the fit as nuisance parameters.
-For a given set of parameters $\vec{\theta}$, the event rate in the $i$th energy bin is calculated as\\
+For a given set of parameters $\vec{\theta}^{hyp}$, the event rate in the $i$th energy bin is calculated as\\
 \begin{equation}
@@
 {\color{blue}In the following, all examples are mainly presented for TDLS, except for Sec.~\ref{sec:ex_MT}.
-However, we remind the user that though we use TDLS as an example, \textbf{FaSE-GLoBES} should not be limited in any flavor model.
+However, we remind the user that though we use these two models as examples, \textbf{FaSE-GLoBES} should not be limited in any flavor model.
 We therefore in the \textbf{FaSE} distribution, show the warped flavor symmetry (WSF)~\cite{Chen:2015jta}, trimaximal mixing sum rule (TM1)~\cite{Albright:2008rp} as examples, which will not be further introduced in this manual.
-We summarise our examples for \textbf{FaSE-GLoBES} and references for those theoretical models in Tabl~\ref{tab:examples}.
-And in the rest of this section, we demonstrate the \textbf{example 1} and \textbf{example 4}.
+We summarise our examples for \textbf{FaSE-GLoBES} and references for models themselves in Tabl~\ref{tab:examples}.
+And, in the rest of this section, we demonstrate the \textbf{example 1} and \textbf{example 4}.
 }
@@
 \subsection{Initialise the code}
-In the beginning of main code, we need to initialise \textbf{GLoBES} and \textbf{FaSE}, and to include the AEDL file for MOMENTas follows.\vspace{0.2cm}\\ 
+In the beginning of main code, we need to initialise \textbf{GLoBES} and \textbf{FaSE}, and to include the AEDL file for MOMENT as follows.\vspace{0.2cm}\\ 
 \texttt{glbInit(argv[0]);}\\
@@
 %
-The \textbf{GLoBES} projector \texttt{free} allows all model parameters to vary, in order to find the value of \texttt{res0}, which is for $\chi^2_{min}$.
+The \textbf{GLoBES} projector \texttt{free} allows all model parameters to vary, in order to find the value of \texttt{res0}, which is $\chi^2_{min}$.
 Then, we set two loops varying different values of $x$ and $\eta$ in $\vec{\theta}^{hyp}_{Model}$ to get $\Delta \chi^2$ values for different hypotheses.
 We note here there is degenerate solutions where $x\sim-8$, $\eta\sim1.8\pi$, $r\sim 0.1$, and $m_a\sim3.8$~meV.
-To find this degenerate solutions we set the entry with $r=0$.\vspace{0.2cm}\\
+To find this degenerate solutions we set the other entry with $r=0$.\vspace{0.2cm}\\
 %
@@
 We use these data, and obtain the predicted $1\sigma$, $2\sigma$, and $3\sigma$ constraints of $x$ and $\eta$ by MOMENT shown in Fig.~\ref{fig:constraint}.
-The code for this example is provided as \textbf{x\_eta.c} in {\color{blue}\textbf{example1}} of the \textbf{FaSE} distribution.
+{\color{blue}To get the result for DUNE, the user adopt the same way, but use different simulation package.} The code for this example is provided as \textbf{x\_eta.c} in {\color{blue}\textbf{example1}} of the \textbf{FaSE} distribution.
 
@@
 }
-The output \texttt{data/S4Modular\_th23\_dCP\_test.dat} contains true values of $\theta_{23}$ (the first column) and $\delta$ (the second column) with $\chi^2_{min}$ for TDLS (the third column).
+The output \texttt{data/S4Modular\_th23\_dCP\_test.dat} contains true values of $\theta_{23}$ (the first column) and $\delta$ (the second column) with $\chi^2_{min}$ for this $S_4$ modular model (the third column).
 With these data, we then have the results shown in Fig.~\ref{fig:th23_delta}.
+{\color{blue}To get the result for DUNE, the user adopt the same way, but use different simulation package.}
 

### 2020-06-11 doc/paper.tex
update the manual

@@
 \end{equation}
- where $\theta_i$ is one of parameters constrained by prior, $\theta^c_i$ ($\sigma_i$) is the central value (Gaussian width) of the prior for $\theta_i$.
-We note that $\theta_i$ can be either model ($\vec{\theta}_{Model}$) or oscillation parameters ($\vec{\theta}_{OSC}$).
+ where $\theta_i$ is {\color{blue}one parameter of the hypothesis $\vec{\theta}^{hyp}$}, $\theta^c_i$ ($\sigma_i$) is the central value (Gaussian width) of the prior for $\theta_i$.
+We note that  {\color{blue}$\vec{\theta}^{hyp}$}  can be either model ($\vec{\theta}_{Model}$) or oscillation parameters ($\vec{\theta}_{OSC}$).
 %
@@
 To treat asymmetry of width for upper ($\theta_i>\theta_i^c$) and lower ($\theta_i<\theta_i^c$) Gaussian widths, we give values in two arrays \texttt{UPPER\_prior}, and \texttt{LOWER\_prior}, respectively.
-If the user gives the prior in model parameters, the order of each component follows with the setup of input of the probability engine.
+{\color{blue}Once the user does not want to include any priors, two arrays \texttt{UPPER\_prior} and \texttt{LOWER\_prior} need to be $0$.} If the user gives the prior in model parameters, the order of each component follows with the setup of input of the probability engine.
 While the user gives the prior in oscillation parameters, the six components of these three arrays in order are $\theta_{12}$, $\theta_{13}$, $\theta_{23}$, $\delta$, $\Delta m_{21}^2$, and  $\Delta m_{31}^2$.
@@
 The user can use \textbf{FaSE-GLoBES} to constrain model parameters. 
-Suppose we have the measurement $\vec{x}$ and the likelihood function $L(\vec{\theta})=P(\vec{x}|\vec{\theta})$ for a set of parameters $\vec{\theta}=(\theta_1,...,\theta_N)$, where $P(\vec{x}|\vec{\theta})$ is the probability function for data $\vec{x}$ in favour of the hypothesis $\vec{\theta}$.
-The constraint of model parameters can be obtained with the statistis parameter $\chi^2\equiv \ln L(\vec{\theta})$.
+Suppose we have the measurement $\vec{x}^{hyp}$ and the likelihood function $L(\vec{\theta}^{hyp})=P(\vec{x}|\vec{\theta}^{hyp})$ for a set of parameters $\vec{\theta}^{hyp}=(\theta_1,...,\theta_N)$, where $P(\vec{x}|\vec{\theta}^{hyp})$ is the probability function for data $\vec{x}$ in favour of the hypothesis $\vec{\theta}^{hyp}$.
+The constraint of model parameters can be obtained with the statistis parameter $\chi^2\equiv \ln L(\vec{\theta}^{hyp})$.
 The expression $\chi^2$ is used as the default \textbf{GLoBES} setting. In more detail, the $\chi^2$ function, following the Poisson distribution, is constructed based on a log-likelihood ratio,

### 2020-06-12 example4/FASE_GLoBES.c
update code and include plotting script

@@ -49,8 +49,6 @@ struct glb_projection_type {
     glb_density_proj_type *density;
 };
 
-//typedef struct OSC_PARAMS { double theta12; double theta13; double theta23; double delta; double alpha21; double alpha31; double Dm21; double Dm31; double m3; double m2; double m1; } OSC_PARAMS;
-
 /* Interface for non-standard implementations of the probability engine */
 int glb_oscp;
 glb_probability_matrix_function glb_hook_probability_matrix;
@@ -84,14 +82,15 @@ int STAN_OSC(double complex M[], double out[6])
     cblas_zgemm (CblasRowMajor, CblasConjTrans, CblasNoTrans, 3, 3, 3, &alpha, M, 3, M, 3, &beta, MMsquare, 3); //eq 4.5 page 107 Giunti
     
     
+    
+    
     gsl_matrix_complex *MM = gsl_matrix_complex_alloc(3, 3);
     int i,j;
     for(i=0;i<3;i++)
     {
         for(j=0;j<3;j++)
         {
-            //            gsl_matrix_complex_set(MM, i, j, gsl_complex_rect(creal(M[i*3+j]),cimag(M[i*3+j])));
-            gsl_matrix_complex_set(MM, i, j, gsl_complex_rect(creal(MMsquare[i*3+j]),cimag(MMsquare[i*3+j])));
+           gsl_matrix_complex_set(MM, i, j, gsl_complex_rect(creal(MMsquare[i*3+j]),cimag(MMsquare[i*3+j])));
         }
     }
     
@@ -133,33 +132,13 @@ int STAN_OSC(double complex M[], double out[6])
     double m2=   sqrt(gsl_vector_get(eval,1));
     double m3=   sqrt(gsl_vector_get(eval,2));
     
-    
     out[0]=the12; out[1]=the13; out[2]=the23;
     out[3]=dCP;   out[4]=gsl_vector_get(eval,1)-gsl_vector_get(eval,0);
-    out[5]=gsl_vector_get(eval,1)-gsl_vector_get(eval,0);
+    out[5]=gsl_vector_get(eval,2)-gsl_vector_get(eval,0);
     
     return 0;
 }
 
-
-int STAN_OSC_U(double complex U[], double out[4])
-{
-    
-    double s13 = cabs(U[2]);       double the13=asin(s13);
-    double t12 = cabs(U[1])/cabs(U[0]);           double the12=atan(t12);
[…]

### 2020-06-12 example4/FASE_GLoBES.h

@@ -13,7 +13,6 @@
 #include <gsl/gsl_vector.h>
 #include "model-input.h"
 
-/*#define GLB_NU_FLAVOURS 3*/
 #define GLB_SIGMA_E 6        /* Index of non-standard parameter sigma_E */
 #define GLB_ETA 0
 #define GLB_MA 1
@@ -50,10 +49,10 @@ int N_in;
 static double mq[3];
 int    PARA,PARA_in,ran,ran_in,n_ram,FIT,PRIOR;
 double x_in,eta_in,r_in,ma_in;
-
 double UPPER_prior[6],LOWER_prior[6],Central_prior[6];
+
 int STAN_OSC(double complex M[], double output[6]);
-int STAN_OSC_U(double complex U[], double out[6]);
+int ModelTO( double OSC_PARAMS[6],double M_para[]);
 inline double square(double x);
 int sinsq(double complex U[], double * a);
 int glb_free_probability_engine();

### 2020-06-12 example4/model-input.c

@@ -6,6 +6,7 @@
 #include <gsl/gsl_complex.h>
 #include <gsl/gsl_math.h>
 #include <globes/globes.h>   /* GLoBES library */
+
 #include <gsl/gsl_complex_math.h>
 #include <gsl/gsl_matrix.h>
 #include <gsl/gsl_blas.h>
@@ -28,23 +29,22 @@ double MODEL_init(int N) /*initialise the model-input*/
 double MtoS(double osc_para[6], double M_para[])
 /*revert model parameters to
  the standard oscillation parameters */
-{// set up according to arXiv:1906.02208*/
+{
     
     double mu1          = M_para[0]; //
     double mu2          = M_para[1];
     double theta_R      = M_para[2];
     double alpha1       = M_para[3];
     double alpha2       = M_para[4];
+
     double complex cR=cos(theta_R)*cos(alpha1)+I*cos(theta_R)*sin(alpha1);
     double complex sR=sin(theta_R)*cos(alpha2)+I*sin(theta_R)*sin(alpha2);
-    
     double complex sR_con=sin(theta_R)*cos(alpha2)-I*sin(theta_R)*sin(alpha2);
     double complex cR_con=cos(theta_R)*cos(alpha1)-I*cos(theta_R)*sin(alpha1);
     double complex cRs=cR*cR;
     double complex sRs=sR*sR;
     double complex cRs_con=cR_con*cR_con;
     double complex sRs_con=sR_con*sR_con;
-    
     
     double complex A=mu1*cRs+mu2*sRs_con;
     double complex B=mu1*sRs+mu2*cRs_con;
@@ -56,13 +56,21 @@ double MtoS(double osc_para[6], double M_para[])
     double complex M[]={A,A*(-2*omega_s)-C,-2*A*omega+C,-2*omega_s*A-C,4*omega*A+B+4*omega_s*C,\
         4*A-B+I*2*sqrt(3)*C,-2*omega*A+C,4*A-B+2*I*sqrt(3)*C,4*omega_s*A+B-4*omega*C};
     
-    STAN_OSC(M,osc_para);
+       STAN_OSC(M,osc_para);
  
+    
+    
     return 0;
 }
 
 double model_restriction(double M_para [])
 {
+    double mu1          = M_para[0]; //
+    double mu2          = M_para[1];
+    double theta_R      = M_para[2];
+    double alpha1       = M_para[3];
+    double alpha2       = M_para[4];
+    
     return 0;
 }
 

### 2020-06-12 example4/th23_dCP.c

@@ -17,8 +17,8 @@ int main(int argc, char *argv[])
 {
     /* Initialize libglobes */
     glbInit(argv[0]);
-//    glbInitExperiment("exp/DUNE_GLoBES.glb",&glb_experiment_list[0],&glb_num_of_exps);
-    glbInitExperiment("exp/MOMENT_FIX_FLUX_150KM_addATM_NC.glb",&glb_experiment_list[0],&glb_num_of_exps);
+    glbInitExperiment("exp/DUNE_GLoBES.glb",&glb_experiment_list[0],&glb_num_of_exps);
+//    glbInitExperiment("exp/MOMENT_FIX_FLUX_150KM_addATM_NC.glb",&glb_experiment_list[0],&glb_num_of_exps);
     /*Initialize FASE*/
     MODEL_init(5);
     
@@ -84,6 +84,7 @@ int main(int argc, char *argv[])
     for (i=0;i<6;i++) {UPPER_prior[i]=fabs(UPPER_prior[i]-Central_prior[i])/3;
         LOWER_prior[i]=fabs(LOWER_prior[i]-Central_prior[i])/3;}
     
+//    for (i=0;i<6;i++) {UPPER_prior[i]=0; LOWER_prior[i]=0;}
     /* centers and input_errors will not be used, but need to be given in for central values
     and prior width. Otherwise, GLoBES will complain. */
     for (i=0; i<6; i++) glbSetOscParams(centers,0.1,i); glbSetDensityParams(centers,1.0,GLB_ALL); glbCopyParams(centers,input_errors);
@@ -93,9 +94,12 @@ int main(int argc, char *argv[])
     /*two loops for chi^2(x,eta)*/
     
     float th23,dCP,dth23,ddCP,lower_th23,upper_th23,lower_dCP,upper_dCP;
-FILE* File=fopen("data/S4Modular_th23_dCP(MOMENT).dat", "w");
+FILE* File=fopen("data/MM_th23_dCP(DUNE)_v3.dat", "w");
+//    FILE* File=fopen("data/MM_th23_dCP(MOMENT)_no_prior_2.dat", "w");
     lower_th23=40; upper_th23=52.5; lower_dCP=125; upper_dCP=395;
-    dth23=(upper_th23-lower_th23)/50; ddCP=(upper_dCP-lower_dCP)/50;
+//    dth23=(upper_th23-lower_th23)/50; ddCP=(upper_dCP-lower_dCP)/50;
[…]

### 2020-06-12 FASE_GLoBES.c
update code

@@ -1,3 +1,10 @@
+/*Probability engine for a given flavour symmetry,
+which needs to be given in model-input.c. This code
+using output oscillation parameter values from
+model-input.c, compute the probability spectra and
+the prior value. This code is based on the default
+GLoBES probability engine.
+---------------------------------------------- */
 #include <stdio.h>
 #include <stdlib.h>
 #include <math.h>

### 2020-06-12 example4/FASE_GLoBES.c

@@ -1,3 +1,10 @@
+/*Probability engine for a given flavour symmetry,
+ which needs to be given in model-input.c. This code
+ using output oscillation parameter values from
+ model-input.c, compute the probability spectra and
+ the prior value. This code is based on the default
+ GLoBES probability engine.
+ ---------------------------------------------- */
 #include <stdio.h>
 #include <stdlib.h>
 #include <math.h>

### 2020-06-12 example3/th23_dCP.c
update code
make corrections

@@ -17,7 +17,7 @@ int main(int argc, char *argv[])
 {
     /* Initialize libglobes */
     glbInit(argv[0]);
-    glbInitExperiment("exp/DUNE_GLoBES.glb",&glb_experiment_list[0],&glb_num_of_exps);
+    glbInitExperiment("exp/MOMENT_FIX_FLUX_150KM_addATM_NC.glb",&glb_experiment_list[0],&glb_num_of_exps);
     /*Initialize FASE*/
     MODEL_init(4);
     

### 2020-06-12 example4/th23_dCP.c

@@ -17,8 +17,7 @@ int main(int argc, char *argv[])
 {
     /* Initialize libglobes */
     glbInit(argv[0]);
-    glbInitExperiment("exp/DUNE_GLoBES.glb",&glb_experiment_list[0],&glb_num_of_exps);
-//    glbInitExperiment("exp/MOMENT_FIX_FLUX_150KM_addATM_NC.glb",&glb_experiment_list[0],&glb_num_of_exps);
+    glbInitExperiment("exp/MOMENT_FIX_FLUX_150KM_addATM_NC.glb",&glb_experiment_list[0],&glb_num_of_exps);
     /*Initialize FASE*/
     MODEL_init(5);
     

### 2020-06-12 example1/model-input.c
update code
add references

@@ -1,3 +1,49 @@
+/*--------------------------------------------------------------------
+ This example is using littlest seesaw model for tri-direct approach
+ as an example. More details can be checked in arXiv:1304.6264[hep-ph],
+ arXiv:1512.07531[hep-ph] and arXiv:1607.05276[hep-ph].
+ The user using this model, should cite the references:
+ 
+ @article{King:2016yvg,
+ author = "King, Stephen F. and Luhn, Christoph",
+ title = "{Littlest Seesaw model from S$_{4} \times$ U(1)}",
+ eprint = "1607.05276",
+ archivePrefix = "arXiv",
+ primaryClass = "hep-ph",
+ reportNumber = "QFET-2016-12, SI-HEP-2016-20",
+ doi = "10.1007/JHEP09(2016)023",
+ journal = "JHEP",
+ volume = "09",
+ pages = "023",
+ year = "2016"
+ }
+ 
+ @article{King:2015dvf,
+ author = "King, Stephen F.",
+ title = "{Littlest Seesaw}",
+ eprint = "1512.07531",
+ archivePrefix = "arXiv",
+ primaryClass = "hep-ph",
+ doi = "10.1007/JHEP02(2016)085",
+ journal = "JHEP",
+ volume = "02",
+ pages = "085",
+ year = "2016"
+ }
+ 
+ @article{King:2013iva,
+ author = "King, Stephen F.",
+ title = "{Minimal predictive see-saw model with normal neutrino mass hierarchy}",
+ eprint = "1304.6264",
+ archivePrefix = "arXiv",
+ primaryClass = "hep-ph",
+ doi = "10.1007/JHEP07(2013)137",
+ journal = "JHEP",
+ volume = "07",
+ pages = "137",
+ year = "2013"
+ }
+ -----------------------------------------------------------------------*/
 #include <stdio.h>
 #include <stdlib.h>
 #include <math.h>

### 2020-06-12 example2/model-input.c

@@ -1,3 +1,22 @@
+/*--------------------------------------------------------------------
+ This example is using the warped flavor symmetry model
+ as an example. More details can be checked in arXiv:1906.02208[hep-ph]
+ The user using this model, should cite the reference:
+ 
+ @article{Chen:2015jta,
+ author = "Chen, Peng and Ding, Gui-Jun and Rojas, Alma. D. and Vaquera-Araujo, C.A. and Valle, J.W.F.",
+ title = "{Warped flavor symmetry predictions for neutrino physics}",
+ eprint = "1509.06683",
+ archivePrefix = "arXiv",
+ primaryClass = "hep-ph",
+ reportNumber = "IFIC-15-XX",
+ doi = "10.1007/JHEP01(2016)007",
+ journal = "JHEP",
+ volume = "01",
+ pages = "007",
+ year = "2016"
+ }
+ -----------------------------------------------------------------------*/
 #include <stdio.h>
 #include <stdlib.h>
 #include <math.h>

### 2020-06-12 example3/model-input.c

@@ -1,3 +1,23 @@
+/*--------------------------------------------------------------------
+ This example is using TM1 sum rule as an example.
+ More details can be checked in arXiv:0812.0436[hep-ph]
+ The user using this model, should cite the reference:
+ 
+ @article{Albright:2008rp,
+ author = "Albright, Carl H. and Rodejohann, Werner",
+ title = "{Comparing Trimaximal Mixing and Its Variants with Deviations from Tri-bimaximal Mixing}",
+ eprint = "0812.0436",
+ archivePrefix = "arXiv",
+ primaryClass = "hep-ph",
+ reportNumber = "FERMILAB-PUB-08-535-T",
+ doi = "10.1140/epjc/s10052-009-1074-3",
+ journal = "Eur. Phys. J. C",
+ volume = "62",
+ pages = "599--608",
+ year = "2009"
+ }
+ -----------------------------------------------------------------------*/
+
 #include <stdio.h>
 #include <stdlib.h>
 #include <math.h>

### 2020-06-12 example3/th23_dCP.c

@@ -17,9 +17,10 @@ int main(int argc, char *argv[])
 {
     /* Initialize libglobes */
     glbInit(argv[0]);
+//    glbInitExperiment("exp/DUNE_GLoBES.glb",&glb_experiment_list[0],&glb_num_of_exps);
     glbInitExperiment("exp/MOMENT_FIX_FLUX_150KM_addATM_NC.glb",&glb_experiment_list[0],&glb_num_of_exps);
     /*Initialize FASE*/
-    MODEL_init(4);
+    MODEL_init(5);
     
     /* Register non-standard probability engine. This has to be done
      * before any calls to glbAllocParams() or glbAllocProjections() */
@@ -42,6 +43,10 @@ int main(int argc, char *argv[])
     glb_params test_values = glbAllocParams();
     glb_params input_errors = glbAllocParams();
     glb_params centers = glbAllocParams();
+    double osc_para[6];
+    double M_para[5];
+    M_para[0]=0; M_para[1]=0; M_para[2]=dCP_true; M_para[3]=DM21_true; M_para[4]=DM31_true;
+    MtoS(osc_para, M_para);
     glbDefineParams(test_values,th13_true,th23_true,DM21_true,DM31_true,-1,0);
     glbSetDensityParams(true_values,1.0,GLB_ALL);
     int i;
@@ -70,9 +75,11 @@ int main(int argc, char *argv[])
     UPPER_prior[3]=392*degree;    LOWER_prior[3]=125*degree;     Central_prior[3]=215*degree;
     UPPER_prior[4]=8.01e-5;       LOWER_prior[4]=6.79e-5;        Central_prior[4]=7.39e-5;
     UPPER_prior[5]=2.625e-3;      LOWER_prior[5]=2.427e-3;       Central_prior[5]=2.525e-3;
+    
+    
     for (i=0;i<6;i++) {UPPER_prior[i]=fabs(UPPER_prior[i]-Central_prior[i])/3;
         LOWER_prior[i]=fabs(LOWER_prior[i]-Central_prior[i])/3;}
-    
+
     /* centers and input_errors will not be used, but need to be given in for central values
     and prior width. Otherwise, GLoBES will complain. */
     for (i=0; i<6; i++) glbSetOscParams(centers,0.1,i); glbSetDensityParams(centers,1.0,GLB_ALL); glbCopyParams(centers,input_errors);
@@ -109,8 +116,7 @@ int main(int argc, char *argv[])
[…]

### 2020-06-12 example4/model-input.c

@@ -1,3 +1,23 @@
+/*--------------------------------------------------------------------
+This example is using a S4 modular flavour symmetry model
+as an example. More details can be checked in arXiv:1906.02208[hep-ph]
+The user using this model, should cite the reference:
+
+ @article{deMedeirosVarzielas:2019cyj,
+ author = "de Medeiros Varzielas, Ivo and King, Stephen F. and Zhou, Ye-Ling",
+ title = "{Multiple modular symmetries as the origin of flavor}",
+ eprint = "1906.02208",
+ archivePrefix = "arXiv",
+ primaryClass = "hep-ph",
+ doi = "10.1103/PhysRevD.101.055033",
+ journal = "Phys. Rev. D",
+ volume = "101",
+ number = "5",
+ pages = "055033",
+ year
+ }
+-----------------------------------------------------------------------*/
+
 #include <stdio.h>
 #include <stdlib.h>
 #include <math.h>

### 2020-06-12 example4/FASE_GLoBES.c
update code
made some corrections

@@ -56,6 +56,8 @@ struct glb_projection_type {
     glb_density_proj_type *density;
 };
 
+//typedef struct OSC_PARAMS { double theta12; double theta13; double theta23; double delta; double alpha21; double alpha31; double Dm21; double Dm31; double m3; double m2; double m1; } OSC_PARAMS;
+
 /* Interface for non-standard implementations of the probability engine */
 int glb_oscp;
 glb_probability_matrix_function glb_hook_probability_matrix;
@@ -89,15 +91,14 @@ int STAN_OSC(double complex M[], double out[6])
     cblas_zgemm (CblasRowMajor, CblasConjTrans, CblasNoTrans, 3, 3, 3, &alpha, M, 3, M, 3, &beta, MMsquare, 3); //eq 4.5 page 107 Giunti
     
     
-    
-    
     gsl_matrix_complex *MM = gsl_matrix_complex_alloc(3, 3);
     int i,j;
     for(i=0;i<3;i++)
     {
         for(j=0;j<3;j++)
         {
-           gsl_matrix_complex_set(MM, i, j, gsl_complex_rect(creal(MMsquare[i*3+j]),cimag(MMsquare[i*3+j])));
+            //            gsl_matrix_complex_set(MM, i, j, gsl_complex_rect(creal(M[i*3+j]),cimag(M[i*3+j])));
+            gsl_matrix_complex_set(MM, i, j, gsl_complex_rect(creal(MMsquare[i*3+j]),cimag(MMsquare[i*3+j])));
         }
     }
     
@@ -139,13 +140,33 @@ int STAN_OSC(double complex M[], double out[6])
     double m2=   sqrt(gsl_vector_get(eval,1));
     double m3=   sqrt(gsl_vector_get(eval,2));
     
+    
     out[0]=the12; out[1]=the13; out[2]=the23;
     out[3]=dCP;   out[4]=gsl_vector_get(eval,1)-gsl_vector_get(eval,0);
-    out[5]=gsl_vector_get(eval,2)-gsl_vector_get(eval,0);
+    out[5]=gsl_vector_get(eval,1)-gsl_vector_get(eval,0);
     
     return 0;
 }
 
+
+int STAN_OSC_U(double complex U[], double out[4])
+{
+    
+    double s13 = cabs(U[2]);       double the13=asin(s13);
+    double t12 = cabs(U[1])/cabs(U[0]);           double the12=atan(t12);
[…]

### 2020-06-12 example4/FASE_GLoBES.h

@@ -49,10 +49,10 @@ int N_in;
 static double mq[3];
 int    PARA,PARA_in,ran,ran_in,n_ram,FIT,PRIOR;
 double x_in,eta_in,r_in,ma_in;
-double UPPER_prior[6],LOWER_prior[6],Central_prior[6];
 
+double UPPER_prior[6],LOWER_prior[6],Central_prior[6];
 int STAN_OSC(double complex M[], double output[6]);
-int ModelTO( double OSC_PARAMS[6],double M_para[]);
+int STAN_OSC_U(double complex U[], double out[6]);
 inline double square(double x);
 int sinsq(double complex U[], double * a);
 int glb_free_probability_engine();

### 2020-06-12 example4/th23_dCP.c

@@ -83,7 +83,6 @@ int main(int argc, char *argv[])
     for (i=0;i<6;i++) {UPPER_prior[i]=fabs(UPPER_prior[i]-Central_prior[i])/3;
         LOWER_prior[i]=fabs(LOWER_prior[i]-Central_prior[i])/3;}
     
-//    for (i=0;i<6;i++) {UPPER_prior[i]=0; LOWER_prior[i]=0;}
     /* centers and input_errors will not be used, but need to be given in for central values
     and prior width. Otherwise, GLoBES will complain. */
     for (i=0; i<6; i++) glbSetOscParams(centers,0.1,i); glbSetDensityParams(centers,1.0,GLB_ALL); glbCopyParams(centers,input_errors);
@@ -93,11 +92,8 @@ int main(int argc, char *argv[])
     /*two loops for chi^2(x,eta)*/
     
     float th23,dCP,dth23,ddCP,lower_th23,upper_th23,lower_dCP,upper_dCP;
-FILE* File=fopen("data/MM_th23_dCP(DUNE)_v3.dat", "w");
-//    FILE* File=fopen("data/MM_th23_dCP(MOMENT)_no_prior_2.dat", "w");
+    FILE* File=fopen("data/S4_th23_dCP(MOMENT).dat", "w");
     lower_th23=40; upper_th23=52.5; lower_dCP=125; upper_dCP=395;
-//    dth23=(upper_th23-lower_th23)/50; ddCP=(upper_dCP-lower_dCP)/50;
-//    lower_th23=40; upper_th23=53; lower_dCP=220; upper_dCP=340;
     dth23=.5; ddCP=5.;
 
     int dof=1;
@@ -129,10 +125,6 @@ FILE* File=fopen("data/MM_th23_dCP(DUNE)_v3.dat", "w");
         if(res>res2) res=res2; glbCopyParams(out2,out);
        }}
  
- 
-//                float res=glbChiNP(test_values,out,GLB_ALL);
-//        printf("%f %f %f %f\n",th23,dCP,gsl_cdf_chisq_Qinv(gsl_cdf_chisq_Q(fabs(res),dof),1),res);
[…]
